### 2019-11-04 paper/02mprelim.tex
Adding paper

\section{Mathematical preliminaries}
\subsection{Boundary value problems}
Consider a polygonal domain $\Omega \subset \mathbb{R}^2$ with boundary $\Gamma.$ 
Let $\gamma:[0,L] \to \Gamma$ be an arclength parametrization, and $\nu(t)$ denote the 
outward-pointing normal to $\Gamma$ at $\gamma(t).$  
Let $\omega \in \mathbb{C}$ in the first quadrant of the complex plane denote the 
Helmholtz wave number.
For ease of exposition our primary focus in the first portion of this paper will be on the 
following four boundary value problems.
\begin{enumerate}
\item The interior Dirichlet problem:
\begin{align}\label{eqn:BVPID}
(\Delta + \omega^2)u(x) &= 0, \hspace{1 cm} x \in \Omega,\\
u(\gamma(t)) &= f(t), \hspace{0.43 cm} t \in [0,L].
\end{align}

\item The exterior Dirichlet problem:
\begin{align}\label{eqn:BCPED}
(\Delta + \omega^2) u(x) &= 0, \hspace{1 cm} x \in \mathbb{R}^2\setminus\Omega,\\
u(\gamma(t)) &= f(t), \hspace{0.43 cm} t \in[0,L].
\end{align}

\item The interior Neumann problem:
\begin{align}\label{eqn:BVPIN}
(\Delta + \omega^2) u(x) &= 0, \hspace{1 cm} x \in \Omega,\\
\nabla u(\gamma(t))\cdot \nu(t)  &= f(t), \hspace{0.45 cm} t\in [0,L].
\end{align}

\item The exterior Neumann problem:
\begin{align}\label{eqn:BVPEN}
(\Delta + \omega^2) u(x) &= 0, \hspace{1 cm} x \in \mathbb{R}^2\setminus\Omega,\\
\nabla u(\gamma(t))\cdot \nu(t)  &= f(t), \hspace{0.45 cm} t\in [0,L].
\end{align}

\end{enumerate}

\begin{remark}
The existence and uniqueness of solutions to the above equations is a classical result. 
The exterior Dirichlet problem and interior Neumann problem require the additional assumption that
$$\int_0^L f(t)\,{\rm d}t = 0.$$
\end{remark}

### 2019-11-04 paper/03bvp.tex
Adding paper

 \section{Boundary integral equations}
A classical way of solving the interior and exterior Dirchlet and Neumann Laplace boundary value problems given above is to convert them to boundary integral equations. Before describing this reduction we first define the single and double layer potential operators and summarize their relevant properties.
 \subsection{Layer potentials}
\begin{definition}
Given a density $\sigma$ defined on $\Gamma$ the single-layer potential is defined by
\beqn
\cS[\sigma](\by) = -\frac{1}{2\pi} \int_{\Gamma} \log{|\bx - \by|} \sigma(\bx) dS_{\bx}.
\eeqn
Similarly, the double-layer potential is defined via the formula
\beqn
\cD[\sigma](\by) = \frac{1}{2\pi} \int_{\Gamma} \frac{\nu(\bx) \cdot( \by-\bx)}{|\bx-\by|^2}\sigma(\bx) dS_{\bx},
\eeqn
where with some abuse of notation we denote the normal to $\Gamma$ at $\bx$ by $\nu(\bx).$
\end{definition}
\begin{definition}
For $\bx \in \Gamma$ we define the kernel $K(x,y)$ by
\begin{equation}
K(\bx,\by) =\frac{1}{2\pi}  \frac{\nu(\bx) \cdot( \by-\bx)}{|\bx-\by|^2},
\end{equation}
where $\nu(\bx)$ is the normal to $\Gamma$ at $\bx.$ It is often convenient to work instead with the parametrization of $K$ which we will denote by $k:[0,L]\times k[0,L] \to \mathbb{R}$ and is defined by
\begin{align}
k(s,t) = \frac{1}{2 \pi} \frac{\nu(s) \cdot( \gamma(t)-\gamma(s))}{|\gamma(s)-\gamma(t)|^2}.
\end{align}
\end{definition}

The following theorems describe the behaviour of the single and double layer potentials in the vicinity of the boundary curve $\Gamma.$

\begin{theorem}\label{thm:potlim}
Suppose the point $\bx$ approaches a point $\bx_0 = \gamma(t_0)$ from the inside along a path such that 
\begin{align}
-1+\alpha<\frac{\bx-\bx_0}{\|\bx-\bx_0\|} \cdot \gamma'(t_0) <1-\alpha
\end{align}
for some $\alpha >0.$ Then 
\begin{align}
&\lim_{\bx \to \bx_0} \cS[\sigma](\bx) = \cS[\sigma](\bx_0)\\
&\lim_{\bx \to \bx_0} \cD[\rho](\bx) = \cD[\rho](\bx_0)- \rho(\bx_0)\\
&\lim_{\bx \to \bx_0} \left.\frac{{\rm d}}{{\rm d}\tau}\right|_{\tau= 0}\cS\rho(\bx+\tau \nu(t_0)) = \left.\frac{{\rm d}}{{\rm d}\tau}\right|_{\tau= 0}\cS[\rho](\bx_0+\tau \nu(t_0))+ \rho(\bx_0).
\end{align}
Similarly, if $\bx$ approaches a point $\bx_0 = \gamma(t_0)$ from the outside then
\begin{align}
&\lim_{\bx \to \bx_0} \cS[\sigma](\bx) = \cS[\sigma](\bx_0)\\
&\lim_{\bx \to \bx_0} \cD[\rho](\bx) = \cD[\rho](\bx_0)+ \rho(\bx_0)\\
&\lim_{\bx \to \bx_0} \left.\frac{{\rm d}}{{\rm d}\tau}\right|_{\tau= 0}\cS[\rho](\bx+\tau \nu(t_0)) = \left.\frac{{\rm d}}{{\rm d}\tau}\right|_{\tau= 0}\cS[\rho](\bx_0+\tau \nu(t_0))- \rho(\bx_0).
\end{align}
\end{theorem}

We define the following operator which arises in the study of Neumann boundary value problems.
\begin{definition}
Let $\cS$ be the single-layer potential operator. Let $\nu\cdot \nabla \cS$  denote its normal derivative restricted to $\Gamma.$ In particular, for $\by \in \Gamma,$
\begin{align}
\nu\cdot \nabla \cS[\rho] (\by) = \left.\frac{{\rm d}}{{\rm d}\tau}\right|_{\tau = 0} \cS[\rho](\by + \tau \nu(t_0)),
\end{align}
where $\gamma(t_0) = \by.$
\end{definition}

The following proposition relates the normal derivative of the single-layer operator to the double-layer operator. Its proof follows directly from the definitions.
\begin{proposition}
Let $\cS,\cD:L^2(\Gamma) \to L^2(\Gamma)$ be defined as above. Let $\nu \cdot \nabla \cS$ denote the normal derivative of $\cS$ in the sense of the previous definition. Then $\nu \cdot \nabla \cS = \cD^*$ where $*$ denotes the adjoint operator. In particular, for all $\rho,\sigma \in L^2(\Gamma)$
\begin{align}
\cD[\sigma](\gamma(t)] = \int_0^L k(s,t)\,\sigma(\gamma(s))\, {\rm d}s
\end{align}
and
\begin{align}
\nu\cdot \nabla\cS[\rho](\gamma(t)] = \int_0^L k(t,s)\,\rho(\gamma(s))\, {\rm d}s.
\end{align}
\end{proposition}

\subsection{Reduction of boundary value problems}
In this section we describe the conversion of the Laplace boundary value problems (interior Dirichlet, exterior  Dirichlet, interior Neumann, and exterior Neumann) to second-kind integral equations.

\begin{theorem}
Let $\sigma \in L^2([0,L])$ and $f: [0,L] \rightarrow \mathbb{R}$ be defined via the formula
\begin{align}
f(s)= - \sigma(s)+ \int_0^L k(t,s)\,\sigma(t)\,{\rm d}t,
\label{bie_intd}
\end{align}
for all $s \in [0,L].$ For $f \in L^2([0,L])$ the above integral equation has a unique solution for $\sigma \in L^2([0.L]).$ Moreover, the solution to the interior Dirichlet problem for Laplace's equation with boundary data $f$ is given by $u(\by) = \cD[\sigma](\by)$ for all $\by \in \Omega.$
\end{theorem}

\begin{theorem}
Let $\sigma \in L^2([0,L])$ and $f: [0,L] \rightarrow \mathbb{R}$ be defined via the formula
\begin{align}
f(s)=  \sigma(s)+ \int_0^L k(t,s)\,\sigma(t)\,{\rm d}t,
\end{align}
for all $s \in [0,L].$ For $f \in L^2([0,L])$ such that
\begin{align}
\int_0^L f(t)\,{\rm d}t = 0
\end{align}
 the above integral equation has a unique solution for $\sigma \in L^2([0.L]).$ Moreover, the solution to the exterior Dirichlet problem for Laplace's equation with boundary data $f$ is given by $u(\by) = \cD[\sigma](\by)$
for all $\by \in \mathbb{R}^2 \setminus \Omega.$
\end{theorem}

\begin{theorem}
Let $\rho \in L^2([0,L])$ and $f: [0,L] \rightarrow \mathbb{R}$ be defined via the formula
\begin{align}
f(s)= \rho(s)+ \int_0^L k(s,t)\,\rho(t)\,{\rm d}t,
\end{align}
for all $s \in [0,L].$ For $f \in L^2([0,L])$ the above integral equation has a unique solution for $\rho \in L^2([0,L])$  if and only if
\begin{align}
\int_0^L f(t)\,{\rm d}t.
\end{align}
 Moreover, the solution to the interior Neumann problem for Laplace's equation with boundary data $f$ is given by $u(\by) = \cS[\rho](\by)$ for all $\by \in \Omega.$
\end{theorem}

\begin{theorem}
Let $\rho \in L^2([0,L])$ and $f: [0,L] \rightarrow \mathbb{R}$ be defined via the formula
\begin{align}
f(s)= -\rho(s)+ \int_0^L k(s,t)\,\rho(t)\,{\rm d}t,
\end{align}
for all $s \in [0,L].$ For $f \in L^2([0,L])$ the above integral equation has a unique solution for $\rho \in L^2([0.L]).$ Moreover, the solution to the exterior Neumann problem for Laplace's equation with boundary data $f$ is given by $u(\by) = \cS[\rho](\by)$ for all $\by \in \Omega.$
\end{theorem}

\subsection{Corner expansions}

In the remainder of this section we assume $\Gamma$ is an open wedge with sides of length one and interior angle $\pi \alpha$ with $0 <\alpha<2.$ Let $\gamma:[-1,1] \rightarrow \Gamma$ be an arc length parametrization of $\Gamma$ and $\nu:[-1,1] \rightarrow \mathbb{R}^2$ be the inward-pointing normal to $\Gamma.$ 
The following theorem  gives an explicit representation of solutions near corners.

\begin{theorem}[\cite{serkhacha}]\label{thm_cord}
Suppose that $0<\alpha<2$ and that $N$ is a positive integer. Let 
$\lceil \cdot \rceil$ and $\lfloor \cdot \rfloor$ denote the ceiling and floor functions,
respectively, and define $\overline{L},$ $\underline{L},$ $\overline{M},$ and 
$\underline{M}$ by the following formulas
\begin{align}
&\overline{L} = \left\lceil\frac{\alpha N}{2} \right \rceil, \\
&\underline{L} = \left\lfloor\frac{\alpha N}{2} \right \rfloor,\\
&\overline{M} = \left\lceil\frac{(2-\alpha) N}{2} \right \rceil, \\
&\underline{M} = \left\lfloor\frac{(2-\alpha) N}{2} \right \rfloor.
\end{align}
Suppose further that $\rho$ is defined via the formula
\begin{align}
\rho(t) =& b_0+\sum_{i=1}^{\overline{L}} b_i |t|^{\frac{2i-1}{\alpha}}+\sum_{i=1}^{\underline{M}} b_{\overline{L}+i} |t|^\frac{2i}{2-\alpha}\left(\log|t|\right)^{\sigma_{N,\alpha}(i)}\nonumber\\
&+\sum_{i=1}^{\overline{M}}c_i \sgn(t) |t|^\frac{2i-1}{2-\alpha}+\sum_{i=1}^{\underline{L}}c_{\overline{M}+i} \sgn(t) |t|^\frac{2i}{\alpha}\left(\log|t|\right)^{\nu_{N,\alpha}(i)}\label{eqn_rhfm}
\end{align}
where $b_0,b_1,\dots,b_N$ and $c_1,c_2,\dots,c_N$ are arbitrary real numbers and the functions $\sigma_{\alpha,N}(i)$ and $\nu_{\alpha,N}(i)$ are defined as follows
\begin{align}
\sigma_{N,\alpha}(i) = \begin{cases}
1 \quad\quad & \,\text{if}\,\, \frac{2i}{2-\alpha} = \frac{2j-1}{\alpha}\,\,\text{for some}\,\, j \in \mathbb{Z},\, 1\le j \le \left\lceil \frac{\alpha N}{2} \right\rceil\\
0 \quad\quad & \,\text{otherwise},
\end{cases}
\end{align}
\begin{align}
\nu_{N,\alpha}(i) = \begin{cases}
1 \quad\quad & \,\text{if}\,\, \frac{2i}{\alpha} = \frac{2j-1}{2-\alpha}\,\,\text{for some}\,\, j \in \mathbb{Z},\, 1\le j \le \left\lceil \frac{(2-\alpha) N}{2} \right\rceil\\
0 \quad\quad & \,\text{otherwise}.
\end{cases}
\end{align}
\noindent If $g$ is defined by
\begin{align}
f(t) = \rho(s) +\int_{-1}^1 k(t,s)  \rho(t)\,{\rm d}t.
\label{eqn_grho}
\end{align}
then there exist sequences of real numbers $\beta_0$, $\beta_1,\,\dots$ and $\gamma_0,$ $\gamma_1,\,\dots$ such that
\begin{align}
f(t) = \sum_{n=0}^\infty\beta_n |t|^n + \sum_{n=0}^\infty \gamma_n \sgn(t) |t|^n,
\label{eqn_gfrm}
\end{align}
for all $-1 \le t \le 1.$ Conversely, suppose that $f$ has the form (\ref{eqn_gfrm}). Suppose further that $N$ is an arbitrary positive integer. Then, for all angles $\pi \alpha$ there exist unique real numbers $b_0,\,b_1,\,\dots,\,b_N$ and $c_0,\,c_1,\,\dots,\,c_N$ such that $\rho,$ defined by (\ref{eqn_rhfm}), solves equation  (\ref{eqn_grho}) to within an error ${\rm O}(t^{N+1}).$ 
\end{theorem}
\begin{remark1}
A similar result holds for the case where the identity term in (\ref{eqn_grho}) is replaced by its negative; the change in sign corresponds to replacing the boundary integral equation for the exterior Dirichlet problem with the boundary integral equation corresponding to interior Dirichlet problem. Similar expansions also hold for both the exterior and interior Neumann problems, in which case the singular powers are obtained by subtracting one from the singular powers arising in the Dirichlet problem.
\end{remark1}

The following Corollary characterizes of the solutions to the Dirichlet and Neumann boundary integral equations in the vicinity of a corner.

\begin{corollary}
Let $\Gamma$ be the boundary of a polygonal region and suppose one of its corners has interior angle $\pi \alpha$ where $\alpha \in (0,2).$ Let $\gamma:(-\delta,\delta) \rightarrow \mathbb{R}^2$ be an arclength parametrization of $\Gamma$ in the vicinity of the corner, with $\gamma(0)$ coinciding with the corner. If the boundary data, $f,$ is analytic on either side of the corner then there exist unique real numbers $b_0,\,b_1,\,\dots,\,b_N$ and $c_0,\,c_1,\,\dots,\,c_N$ such that the density, $\rho,$ defined by (\ref{eqn_rhfm}) satisfies the interior Dirichlet boundary integral equation to within an error ${\rm O}(t^{N+1})$ for $t$ within $\delta$ of the corner. For the Neumann problems the representation is the same with the powers in the expansion reduced by one.
\end{corollary}

### 2019-11-04 paper/04nprelim.tex
Adding paper

\section{Numerical preliminaries}
In this section we summarize the numerical tools which are necessary for the main result. In particular we summarize the method for discretizing the boundary integral equation for the Dirichlet problem described in \cite{}, which uses the expansion in Theorem \ref{thm_cord}.
\subsection{Discretization of the Dirichlet problem}
In this section we sketch an algorithm for solving the interior Dirichlet boundary integral equation using a Nystr\"{o}m method; the exterior Dirichlet boundary integral equation can be discretized in a similar way. See \cite{} for a thorough description of the method. We begin by constructing a discretization of the boundary $\Gamma$ with nodes $s_1,\dots,s_N,$ and weights $w_1,\dots,w_N,$ which enable interpolation of the left- and right-hand sides of the boundary integral equation
\begin{align}
f(t) = -\sigma(t) + \int_0^L k(t,s) \,\sigma(t)\, {\rm d} t
\end{align}
with precision $\epsilon.$ We proceed by enforcing equality at the discretization nodes, which yields the system of equations
\begin{align}
f(s_i) \sqrt{w_i} = -\pi \sigma(s_i)\sqrt{w_i} +  \sqrt{w_i}\int_0^L K(\gamma(s_i),\gamma(t))\, \sigma(t)\,{\rm d}t,\quad i=1,\dots,N. \label{eqn_1std}
\end{align}
Scaling by the square root of the weights is equivalent to solving the problem in the $L^2$ sense, and results in discretized operators with condition numbers which are close to those of the original physical systems \cite{bremer3}.

The boundary $\Gamma$ is separated into intervals which are at least some distance $\delta$  (measured in terms of arclength) away from a corner and intervals of length $2 \delta$ centered about each corner. The former are discretized using a standard smooth quadrature rule such as nested Gauss-Legendre quadrature while the latter are discretized using a custom set of interpolation nodes constructed in the following way.

First, all functions of the form $x^\mu,$ $\mu \in \{0\} \cup [1/2,40],$ $x \in [0,1/2]$ are discretized using nested Gauss-Legendre panels in $x$ and a single Gauss-Legendre panel in $\mu$. This creates a $N \times M$ matrix where $N$ denotes the number of spatial discretization points $r_i$ and $M$ denotes the number of $\mu_j$ chosen. $M$ and $N$ are increased until it is guaranteed that using Lagrange interpolation from the nested discretization the function $x^\mu$ can be interpolated to within an $L^2$ error less than $\epsilon$ on the interval $[0,1/2]$ for any $\mu$ in the specified range. A singular value decomposition is then performed on the $N\times M$ matrix. Let $K$ denote the number of singular values greater than $\epsilon.$ The right singular vectors correspond to discretizations of an orthonormal set of functions $\phi_1,\dots,\phi_K$ such that $x^\mu$ is in the span of $\phi_1,\dots,\phi_K$ to within an accuracy of $\epsilon.$

Finally, a set of interpolation points $x_j,$ $j=1,\dots,K$ and quadrature weights $w_j,$ $j=1,\dots,K$ are chosen for $\phi_1,\dots,\phi_K$ such that the matrix $U_{ij} = \phi_i(x_j) \sqrt{x_j}$ is well-conditioned. In practice suitable interpolation points can be obtained by using the roots of $\phi_{K+1}$ and calculating the corresponding weights by solving a linear system. The corresponding discretization nodes and weights for the corner-containing intervals of $\Gamma$ are obtained by suitable translations and scalings of $\{x_j\}$ and $\{w_j\}.$

Once the discretization has been constructed it is necessary to construct appropriate quadrature for the integrals appearing in equation (\ref{eqn_1std}). When $s_i$ and $t$ do not belong to the same corner panel (in particular when either is not itself contained in a corner panel) then the weights and nodes associated with the discretization can be used as the quadrature rule. When $s_i$ corresponds to a corner panel special care must be taken. Instead, using an algorithm for generating generalized Gaussian quadratures \cite{}, quadrature nodes are chosen which integrate
\begin{align}
\int_{0}^\delta k(t,s_j) \tilde{\phi}_j(t)\,{\rm d}t
\end{align} 
where for ease of exposition we assume that the corner panel corresponds to $(-\delta,\delta)$ in the parametrization with $t=0$ corresponding to the corner itself. Moreover, it is assumed that $s_j$ lies in the half of a corner panel parametrized by $(-\delta,0)$ and $\tilde{\phi}_j$ is a suitably scaled and translated copy of the singular function obtained in the discretization step.
\begin{remark1}
Due to scale invariance, it suffices to compute quadratures for 
\begin{align}
\int_{0}^\frac{1}{2} k(t,-x_j) {\phi}_j(t)\,{\rm d}t,
\end{align} 
where $x_j$ was one of the original discretization nodes generated on the interval $[0,1/2].$
\end{remark1}
\begin{remark1}
By interpolating from the discretization nodes to these quadrature nodes we obtain a set of weights $\tilde{w}_{i,j}$ such that if $s_1,\dots,s_{2K}$ correspond to the discretization of a corner parametrized by $(-\delta,\delta)$ with $0$ corresponding to the corner then
\begin{align}
\left| \int_{-\delta}^\delta k(t,s_i) \, \tilde{\phi}_m(t)\,{\rm d}t - \sum_{j=1}^{2K} \tilde{w}_{ij} \tilde{\phi}_{m}(t_j) \right| < \epsilon
\end{align}
for all $i=1,\dots,2K$ and $m=1,\dots,K.$
\end{remark1}

After all the quadratures have been constructed the result is an $N \times N$ linear system the solution of which gives an approximation to $\sigma$ sampled at the discretization nodes.

\begin{definition}\label{def:seps}
Let $S_\epsilon \subset L^2([0,L])$ denote the set of functions which can be interpolated from their values at the $N$ discretization nodes to any point in $[0,L]$ with an $L^2$ accuracy of $\epsilon.$ That is to say that for $f \in S_\epsilon$ if $\tilde{f}:[0,L] \to \mathbb{R}$ denotes the function obtained by interpolating using the values $f(s_1),\dots,f(s_N)$ then $\|f -\tilde{f}\|_{L^2} < \epsilon.$ 
\end{definition}

The results of this algorithm are summarized in the following theorem (see \cite{}).
\begin{theorem}
Let $A$ be the $N\times N$ matrix obtained by discretizing the interior Dirichlet problem in the preceding manner. In particular if $f \in S_\epsilon $ is piecewise analytic and ${\bf f} = (\sqrt{w_1}f(s_1),\dots,\sqrt{w_N}f(s_N))^T$ then
\begin{align}
\underline{\bf \sigma} = A^{-1} {\bf f}
\end{align}
can be interpolated to a function $\tilde{\sigma}$ which is within $\epsilon$ of the true density $\sigma$ in an $L^2$-sense. 
\end{theorem}

\subsection{Discretization of the Neumann problem}
In principle a similar method could be employed to discretize the Neumann boundary integral equations. Unfortunately, the singular nature of the powers (the smallest in the expansion given in Theorem \ref{thm_cord} lies in the range $(-1/2,0)$) makes it difficult to produce universal discretizations and quadratures which work for large ranges of angles. When the above method is run on these problems, discretization nodes tend to accumulate close to the corner (within $10^{-14}$). Apart from posing certain numerical challenges, it also makes the task of finding suitable quadrature formulae difficult. Instead a different set of discretization nodes and a different set of quadrature nodes must be constructed for each angle, drastically increasing the precomputation cost.

Finally, in many applications one already has a discretization of the Dirichlet problem. For example, when considering Laplace transmission problems or triple junction problems one has to solve two decoupled boundary integral equations: one of them a Dirichlet-type boundary integral equation with the diagonal term scaled and the other a Neumann-type boundary integral equation with the identity term scaled (see \cite{} and \cite{} for example). In such cases it is convenient to reuse the Dirichlet discretization for the Neumann problem.

### 2019-11-04 paper/05apparatus.tex
Adding paper

\section{Numerical apparatus}
\subsection{Adjoint method}

The following lemma relates the discretization of the inverse of an operator to the adjoint of the discretization of its inverse. Its proof follows directly from the definition of the adjoint and is omitted.
\begin{lemma}\label{lem_adjm}
Suppose $A: L^2([0,L]) \to L^2([0,L])$ is a bounded invertible operator and that $A_\epsilon$ is an operator such that
\begin{align}
\left| \langle f,A^{-1} g \rangle - \langle f,A^{-1}_\epsilon g \rangle \right| \le \epsilon \|f\| \|g\|,
\end{align}
for all $f$ and $g$ in some subspace $S \subset L^2([0,L]).$ Here $\langle \cdot, \cdot \rangle$ denotes the inner product on $L^2([0,L])$ and $\| \cdot\|$ denotes the norm for $L^2([0,L]).$ Then, for all functions $f$ and $g$ in $S$
\begin{align}
\left| \langle f,(A^{-1})^* g \rangle - \langle f,\left(A^{-1}_\epsilon\right)^* g \rangle \right| \le \epsilon \|f\| \|g\|
\end{align}
where $\,{{}^*}\,$ denotes the adjoint.
\end{lemma}

The following corollary follows immediately from the previous result.
\begin{corollary}
Let $A$ be the $N\times N$ matrix obtained by discretizing the interior Dirichlet problem and $S_\epsilon$ be the collection of functions defined in Definition \ref{def:seps}. Then for all functions $f,g \in S_\epsilon$
\begin{align}
\left| \langle {\bf g}, (A^T)^{-1}{\bf f} \rangle - \int_0^L g(t)\,\sigma(t)\,{\rm d}t \right| < \epsilon \|f\|\, \|g\|,
\end{align}
where ${\bf f},{\bf g}$ are the discretizations of $f$ and $g$ scaled by the square roots of the discretization weights, and $\sigma$ is the solution to the exterior Neumann problem with boundary data $f$.
\end{corollary}

Hence a discretization of the Neumann problem can be obtained simply by taking the adjoint of the Dirichlet problem. The resulting density $\sigma$ obtained is accurate in a weak sense, ie. its inner products against functions in $S_\epsilon$ are accurate to within an error of $\epsilon.$

We conclude this section with a few remarks.

\begin{remark1}
We observe that if the solution to the boundary value problem is being calculated at a point $\by \in \mathbb{R}^2\setminus \Omega$ more than a panel length away from the boundary curve $\Gamma$ then the Neumann density $\sigma$ obtained using the above result will give an accuracy of $\epsilon,$ ie. the function $K(\by,\gamma(t)) \in S_\epsilon.$ Thus accurate values of the solution in the far-field can be obtained almost immediately.
\end{remark1}
\begin{remark1}
Similarly, if the point $\by \in \mathbb{R}^2 \setminus \Omega$ at which the solution to the Neumann boundary value problem is to be calculated lies close to a smooth panel then the density $\sigma$ near that point can be interpolated to a finer set of quadrature points and the value of $u(\by)$ can once again be obtained to precision $\epsilon.$ We note, however, that in general the density in the vicinity of a corner cannot be interpolated accurately. This follows from the fact that the interpolation scheme constructed is only guaranteed to interpolate the powers arising in the Dirichlet problem accurately near the corner. The Neumann problem expansions contain negative powers which are not contained in this set and hence are not interpolated accurately.
\end{remark1}

\subsection{Weak corner re-solving}
In this section we address the problem highlighted in the previous one; namely, the accurate evaluation of the solution to the exterior Neumann problem in the vicinity of a corner. Our approach is based on the observation that the contribution from the density on the boundary outside of a sufficiently small neighborhood of the corner is smooth when evaluated in the vicinity of the corner. This allows us to convert the problem of evaluating the potential near the corner (given the approximation to the density obtained using the adjoint approach described in the previous section) into a purely local one. In particular, we rediscretize only a small neighborhood of the corner which in turn allows us to evaluate the potential arbitrarily close to the corner to within a small factor of machine precision.

In the following we assume that we are given a discretization of the interior Dirichlet boundary integral equation (\ref{}) with nodes $x_1,\dots,x_N$ and corresponding weights $w_1,\dots,w_N.$ In particular, we assume that the discretization nodes are obtained by subdividing the boundary into panels. Those panels which contain a vertex are discretized using a custom discretization scheme (see Section \ref{}) while the remaining panels are discretized using a standard smooth quadrature rule (such as Gauss-Legendre or Chebyshev nodes). In the following we assume that an $M$-point Gauss-Legendre quadrature rule is used. Additionally, we denote the discretization of the interior Dirichlet operator (using the custom quadratures described in Section \ref{}) by $A.$ Let $\underline{f} = (f_1,\dots,f_N)^T$ where $f_i = f(x_i) \sqrt{w_i}$ and $f: \partial \Omega \to \mathbb{R}$ is the right-hand side of the exterior Neumann problem. Finally, let $\underline{\sigma}$ be the approximation to the density (scaled by the square roots of the weights) obtained by solving the linear system
\begin{align}\label{eqn:adj_linalg}
A^T \underline{\sigma} = \underline{f}.
\end{align}
For notational convenience we let $\gamma:[-\delta,L-\delta] \to \partial \Omega$ be a counterclockwise arclength parametrization of $\partial \Omega$ such that  $\gamma(0)$ corresponds to a vertex and $\gamma[-\delta,\delta]$ corresponds to a corner panel.

For a panel $\gamma([s_1,s_2])$ with discretization nodes $x_i,\dots,x_{i+M}$ corresponding to a Gauss-Legendre panel the density is smooth and thus it is expected to be well-represented in the basis of Legendre polynomials (shifted and scaled to the interval $[s_1,s_2]$). Hence standard interpolation techniques can be used to obtain an accurate approximation to the density $\sigma$ on the interval $s_1 \le s\le s_2$ (see \cite{} for a detailed description of this process and quantitative estimates on the accuracy of the result).\\

{\color{red}add remark about ratio of size of panel to distance from the corner}\\

For corner panels the nodes were constructed to enable stable interpolation of densities $s^\mu,$ $\mu \in 0 \cup [1/2,40],$ on the interval $s \in (-\delta,\delta)$ - assuming for simplicity that the corner is at $0$ and the panel is of length $2 \delta.$ As mentioned above, the density is expected to contain terms of the form $s^\mu$ for some finite collection of $\mu$ in the interval $(-1/2,1/2),$ and hence will not in general be stably interpolable on the interval $(-\delta,\delta).$ However, it is possible to use the density obtained using (\ref{eqn:adj_linalg}) to construct a sequence of nested problems in the neighborhood of the corner, the solutions of which enable accurate interpolation of the density arbitrarily close to the vertex. The number of these problems depends only on the distance of the closest evaluation point to the corner. In particular, if $r$ is the smallest distance of an evaluation point from the corner then only $\log_2 r/\delta$ levels are required. Each problem involves the solution of a small linear system (typically less than $100 \times 100$) and as such can be performed quickly. Furthermore, we note that the algorithm can be easily parallelized to treat multiple corners concomitantly.

We begin with the following proposition, the proof of which follows immediately from the definition of the kernel $k$ and is omitted.
\begin{proposition}
Suppose that $f$ be a piecewise-analytic function in $S_\epsilon$ and  $\underline{\sigma} = (A^T)^{-1} {\bf f}$ is the approximation to the Neumann density obtained using the adjoint of the discretization for the interior Dirichlet boundary integral equation. Then for all $t \in (-\delta,\delta)$
\begin{align}
h(t) = \sum_{i=M+1}^N k(t,s_i) \sqrt{w_i} \,\underline{\sigma}_i
\end{align}
is an analytic function of $t$ for all $t \in (-\delta,\delta).$
\end{proposition}

In light of this we consider the following integral equation
\begin{align}\label{eqn:resolve_neum0}
-\sigma(s) + \int_{-\delta}^\delta k(s,t) \sigma(t)\,{\rm d}t = f(s)-h(s), \quad -\delta \le s \le \delta.
\end{align}
We note that the solution to (\ref{eqn:resolve_neum0}) is equal to the solution of (\ref{}) restricted to the interval $[-\delta,\delta].$ Taking the adjoint of (\ref{eqn:resolve_neum0}) we obtain
\begin{align}\label{eqn:resolve_diri0}
-\sigma(s) + \int_{-\delta}^\delta k(t,s) \sigma(t)\,{\rm d}t = f(s)-h(s), \quad -\delta \le s \le \delta.
\end{align}
which is a Dirichlet boundary integral equation for a wedge with a piecewise analytic right-hand side. In particular, we can discretize the operator using the method summarized in the previous section. Specifically, we subdivide the interval $[-\delta,\delta]$ into three subintervals $I_0 = [-\delta,\delta/2],$ $L_0 = [-\delta/2,\delta/2],$ and $J_0 = [\delta/2,\delta].$ On $I_0$ and $J_0$ we place standard Gauss-Legendre discretization nodes, while on $L_0$ we use the custom discretization scheme for corners, outlined in Section \ref{} (see \cite{} for a detailed description of the method). Let $\underline{f}_0$ denote the right-hand side of (\ref{eqn:resolve_neum0}) evaluated at these discretization nodes and scaled by the square roots of the corresponding weights. Let $A_0$ be the discretization of the interior Dirichlet problem operator (ie. the operator acting on $\sigma$ on the left-hand side of (\ref{eqn:resolve_diri0})). We note that due to the scale invariance of Laplace's equation for polygonal domains the portion of $A_0$ corresponding to the self-interaction of $L_0$ is a submatrix of the original matrix $A.$ All other blocks can be generated using the discretization nodes as quadrature nodes.

The analysis of the previous section then shows that if $\underline{\sigma}_0$ is the solution of the equation
\begin{align}
A_0^T \underline{\sigma}_0 = \underline{f}_0
\end{align}
then $\underline{\sigma}_0$ gives a {\color{red}weak solution} to the integral equation (\ref{eqn:resolve_neum0}), i.e. for any function $g$ which is analytic on $[-\delta,0]$ and $[0,\delta]$ the inner product $\langle g,\sigma \rangle$ can be calculated to precision $\epsilon$ using the solution $\underline{\sigma}_0.$ Moreover, since the true density $\sigma$ is smooth on $I_0$ and $J_0$ the Gauss-Legendre discretization allows accurate interpolation of the density on those regions.

This can be represated to obtain an interpolable approximation to the density on $L_0 = [-\delta/2,\delta/2].$ In particular, we consider the restriction of the exterior Neumann integral equation, as well as its, adjoint to the interval $L_0.$ For the right-hand side we use the original right-hand side $f$ minus the contribution from the remainder of the domain. In particular, if we define
\begin{align}
h_1(s) = \sum_{x_i \in I_0,J_0} k(s,x_i) \sigma_0^{(i)} \sqrt{w_i}
\end{align}
then $\sigma$ restricted to the interval $L_0$ satisfies
\begin{align}\label{eqn:resolve_neum1}
-\sigma(s) + \int_{-\delta/2}^{\delta/2} k(s,t) \sigma(t)\,{\rm d} t = f(s)-h(s)-h_1(s), \quad -\delta/2 \le s \le \delta/2.
\end{align}
The corresponding adjoint equation is given by 
\begin{align}\label{eqn:resolve_diri1}
-\sigma(s) + \int_{-\delta/2}^{\delta/2} k(t,s) \sigma(t)\,{\rm d} t = f(s)-h(s)-h_1(s), \quad -\delta/2 \le s \le \delta/2.
\end{align}

Once again, we divide $L_0$ into three intervals $I_1,$ $L_1,$ and $J_1$ and discretize each interval as before. After solving the corresponding discretization of (\ref{eqn:resolve_neum1}) using the adjoint of the discretization of the integral operator appearing in (\ref{eqn:resolve_diri1}) we obtain a weak solution of $\sigma$ on the interval $L_0$ which can be interpolated on $I_1,$ and $J_1$ to within precision $\epsilon.$

This process can be repeated an arbitrary number of times to yield a sequence of solutions $\underline{\sigma}_j,$ $j=0,1,2,\dots$ together with corresponding intervals $I_0,I_1,\dots$ and $J_0,J_1,\dots$ on which it can be interpolated.

Note that if $\bx$ is a point a distance $r$ away from the corner then after $J=1+\log_2 r/d$ such subdivisions $\bx$ will be at least twice the corner panel length away from the corner. Thus $K(\bx,\cdot)$ will be smooth when restricted to the corner panel $[-\delta/2^{J},\delta/2^J]$ and hence will be integrated accurately using the corner panel discretization nodes and weights.

### 2019-11-05 paper/04nprelim.tex
updates

@@
 
-First, all functions of the form $x^\mu,$ $\mu \in \{0\} \cup [1/2,40],$ $x \in [0,1/2]$ are discretized using nested Gauss-Legendre panels in $x$ and a single Gauss-Legendre panel in $\mu$.
+First, all functions of the form $x^\mu,$ $\mu \in \{0\} \cup [1/2,40],$ $x \in [0,1]$ are discretized using nested Gauss-Legendre panels in $x$ and a single Gauss-Legendre panel in $\mu$.
 This creates a $N \times M$ matrix where $N$ denotes the number of spatial discretization points $r_i$ and $M$ denotes the number of $\mu_j$ chosen.

### 2019-11-05 paper/02mprelim.tex

@@
 outward-pointing normal to $\Gamma$ at $\gamma(t).$  
-Let $\omega \in \mathbb{C}$ in the first quadrant of the complex plane denote the 
+Let $\omega \in \mathbb{C} \setminus \{ 0 \}$ in the first quadrant of the complex plane denote the 
 Helmholtz wave number.
-For ease of exposition our primary focus in the first portion of this paper will be on the 
-following four boundary value problems.
 \begin{enumerate}
-\item The interior Dirichlet problem:
-\begin{align}\label{eqn:BVPID}
-(\Delta + \omega^2)u(x) &= 0, \hspace{1 cm} x \in \Omega,\\
+\item The interior Dirichlet problem for Laplace's equation:
+\begin{align}\label{eqn:BVPIDL}
+\Delta u(\bx) &= 0, \hspace{1 cm} \bx \in \Omega,\\
 u(\gamma(t)) &= f(t), \hspace{0.43 cm} t \in [0,L].
@@
 
-\item The exterior Dirichlet problem:
-\begin{align}\label{eqn:BCPED}
-(\Delta + \omega^2) u(x) &= 0, \hspace{1 cm} x \in \mathbb{R}^2\setminus\Omega,\\
-u(\gamma(t)) &= f(t), \hspace{0.43 cm} t \in[0,L].
+\item The interior Dirichlet problem for Helmholtz's equation:
+\begin{align}\label{eqn:BVPIDH}
+(\Delta + \omega^2) u(\bx) &= 0, \hspace{1 cm} \bx \in \Omega,\\
+u(\gamma(t)) &= f(t), \hspace{0.43 cm} t \in [0,L].
 \end{align}
 
-\item The interior Neumann problem:
-\begin{align}\label{eqn:BVPIN}
-(\Delta + \omega^2) u(x) &= 0, \hspace{1 cm} x \in \Omega,\\
-\nabla u(\gamma(t))\cdot \nu(t)  &= f(t), \hspace{0.45 cm} t\in [0,L].
+\item The exterior Dirichlet problem for Laplace's equation:
+\begin{align}\label{eqn:BVPEDL}
+\Delta u(\bx) &= 0, \hspace{1 cm} \bx \in \mathbb{R}^2\setminus\Omega,\\
+u(\gamma(t)) &= f(t), \hspace{0.43 cm} t \in[0,L], \\
+u(\bx) &= O(1) , \hspace{0.4cm} |\bx| \to \infty.
 \end{align}
 
-\item The exterior Neumann problem:
-\begin{align}\label{eqn:BVPEN}
-(\Delta + \omega^2) u(x) &= 0, \hspace{1 cm} x \in \mathbb{R}^2\setminus\Omega,\\
-\nabla u(\gamma(t))\cdot \nu(t)  &= f(t), \hspace{0.45 cm} t\in [0,L].
+\item The exterior Dirichlet problem for Helmholtz's equation:
+\begin{align}\label{eqn:BVPEDH}
+\Delta u(\bx) &= 0, \hspace{1 cm} x \in \mathbb{R}^2\setminus\Omega,\\
+u(\gamma(t)) &= f(t), \hspace{0.43 cm} t \in[0,L], \\
+\sqrt{|\bx|} \left|\partial_{|\bx|} u - i\omega u(\bx)\right| &\to 0 , \hspace{0.86cm} |\bx| \to \infty.
+\end{align}
+
+\item The interior Neumann problem for Laplace's equation:
+\begin{align}\label{eqn:BVPINL}
+\Delta u(\bx) &= 0, \hspace{1 cm} \bx \in \Omega,\\
+\nabla u(\gamma(t))\cdot \bnu(t)  &= f(t), \hspace{0.45 cm} t\in [0,L],\\
+\int_{0}^{L} f(t) dt &= 0.
+\end{align}
+
+\item The interior Neumann problem for Helmholtz's equation:
+\begin{align}\label{eqn:BVPINH}
+(\Delta + \omega^2) u(\bx) &= 0, \hspace{1 cm} \bx \in \Omega,\\
+\nabla u(\gamma(t))\cdot \bnu(t)  &= f(t), \hspace{0.45 cm} t\in [0,L].
+\end{align}
+
+\item The exterior Neumann problem for Laplace's equation:
+\begin{align}\label{eqn:BVPEDL}
+\Delta u(\bx) &= 0, \hspace{1 cm} \bx \in \mathbb{R}^2\setminus\Omega,\\
+\nabla u(\gamma(t))\cdot \bnu(t)  &= f(t), \hspace{0.43 cm} t \in[0,L], \\
+\left|u(\bx) + \left(\frac{1}{2\pi} \int_{0}^{L} f(t) dt\right) \log{|\bx|}\right| &\to 0 , \hspace{0.4cm} |\bx| \to \infty.
+\end{align}
+
+\item The exterior Neumann problem for Helmholtz's equation:
+\begin{align}\label{eqn:BVPEDH}
+\Delta u(\bx) &= 0, \hspace{1 cm} x \in \mathbb{R}^2\setminus\Omega,\\
+\nabla u(\gamma(t))\cdot \bnu(t)  &= f(t), \hspace{0.43 cm} t \in[0,L], \\
+\sqrt{|\bx|} \left|\partial_{|\bx|} u - i\omega u(\bx)\right| &\to 0 , \hspace{0.86cm} |\bx| \to \infty.
 \end{align}
@@
 The existence and uniqueness of solutions to the above equations is a classical result. 
-The exterior Dirichlet problem and interior Neumann problem require the additional assumption that
-$$\int_0^L f(t)\,{\rm d}t = 0.$$
+The interior Dirichlet and Neumann problems for Helmholtz equation have a countable set of
+real $\omega$'s (which only accumulate at $\infty$)  for which the PDE has a non-unique solution. 
 \end{remark}

### 2019-11-05 paper/03bvp.tex

@@
  \section{Boundary integral equations}
-A classical way of solving the interior and exterior Dirchlet and Neumann Laplace boundary value problems given above is to convert them to boundary integral equations.
+A classical way of solving the interior and exterior Dirchlet and Neumann Laplace and Helmholtz boundary value problems given above is to convert them to boundary integral equations.
 Before describing this reduction we first define the single and double layer potential operators and summarize their relevant properties.
@@
 \beqn
-\cS[\sigma](\by) = -\frac{1}{2\pi} \int_{\Gamma} \log{|\bx - \by|} \sigma(\bx) dS_{\bx}.
+\cS_{\omega}[\sigma](\by) =  \int_{\Gamma} G_{\omega} (\bx,\by)\sigma(\bx) dS_{\bx} \, ,
 \eeqn
+where
+\beqn
+G_{\omega}(\bx,\by) = \begin{cases} 
+\frac{i}{4} H_{0}(\omega |\bx-\by|) &\quad \omega \neq 0 \,, \\
+-\frac{1}{2\pi} \log{|\bx-\by|} &\quad \omega = 0.
+\end{cases}
+\eeqn
+Here $H_{0}$ is the Hankel 
+function of the first kind of order $0$. 
 Similarly, the double-layer potential is defined via the formula
 \beqn
-\cD[\sigma](\by) = \frac{1}{2\pi} \int_{\Gamma} \frac{\nu(\bx) \cdot( \by-\bx)}{|\bx-\by|^2}\sigma(\bx) dS_{\bx},
+\cD_{\omega}[\sigma](\by) =\int_{\Gamma} \bnu(\bx) \cdot \nabla_{\bx} G_{\omega}(\bx,\by) \sigma(\bx) dS_{\bx},
 \eeqn
-where with some abuse of notation we denote the normal to $\Gamma$ at $\bx$ by $\nu(\bx).$
+where with some abuse of notation we denote the normal to $\Gamma$ at $\bx$ by $\bnu(\bx).$
 \end{definition}
+\begin{remark}
+The layer potentials $\cS_{0}[\sigma]$ and $\cD_{0}[\omega]$ are the layer potentials for Laplace's equation.
+\end{remark}
 \begin{definition}
-For $\bx \in \Gamma$ we define the kernel $K(x,y)$ by
+For $\bx \in \Gamma$ we define the kernel $K_{\omega}(\bx,\by)$ by
 \begin{equation}
-K(\bx,\by) =\frac{1}{2\pi}  \frac{\nu(\bx) \cdot( \by-\bx)}{|\bx-\by|^2},
+K_{\omega}(\bx,\by) =\bnu(\bx) \cdot \nabla_{\bx} G_{\omega}(\bx,\by),
 \end{equation}
-where $\nu(\bx)$ is the normal to $\Gamma$ at $\bx.$ It is often convenient to work instead with the parametrization of $K$ which we will denote by $k:[0,L]\times k[0,L] \to \mathbb{R}$ and is defined by
+where $\nu(\bx)$ is the normal to $\Gamma$ at $\bx.$ It is often convenient to work instead with the parametrization of $K_{\omega}$ which we will denote by $k_{\omega}:[0,L]\times k[0,L] \to \mathbb{R}$ and is defined by
 \begin{align}
-k(s,t) = \frac{1}{2 \pi} \frac{\nu(s) \cdot( \gamma(t)-\gamma(s))}{|\gamma(s)-\gamma(t)|^2}.
+k_{\omega}(s,t) = K_{\omega}(\gamma(s),\gamma(t)).
 \end{align}
@@
 \begin{align}
-&\lim_{\bx \to \bx_0} \cS[\sigma](\bx) = \cS[\sigma](\bx_0)\\
-&\lim_{\bx \to \bx_0} \cD[\rho](\bx) = \cD[\rho](\bx_0)- \rho(\bx_0)\\
-&\lim_{\bx \to \bx_0} \left.\frac{{\rm d}}{{\rm d}\tau}\right|_{\tau= 0}\cS\rho(\bx+\tau \nu(t_0)) = \left.\frac{{\rm d}}{{\rm d}\tau}\right|_{\tau= 0}\cS[\rho](\bx_0+\tau \nu(t_0))+ \rho(\bx_0).
+&\lim_{\bx \to \bx_0} \cS_{\omega}[\sigma](\bx) = \cS_{\omega}[\sigma](\bx_0)\\
+&\lim_{\bx \to \bx_0} \cD_{\omega}[\rho](\bx) = \cD_{\omega}[\rho](\bx_0)- \rho(\bx_0)\\
+&\lim_{\bx \to \bx_0} \left.\frac{{\rm d}}{{\rm d}\tau}\right|_{\tau= 0}\cS_{\omega}[\rho](\bx+\tau \bnu(t_0)) = \left.\frac{{\rm d}}{{\rm d}\tau}\right|_{\tau= 0}\cS_{\omega}[\rho](\bx_0+\tau \bnu(t_0))+ \rho(\bx_0).
 \end{align}
@@
 \begin{align}
-&\lim_{\bx \to \bx_0} \cS[\sigma](\bx) = \cS[\sigma](\bx_0)\\
-&\lim_{\bx \to \bx_0} \cD[\rho](\bx) = \cD[\rho](\bx_0)+ \rho(\bx_0)\\
-&\lim_{\bx \to \bx_0} \left.\frac{{\rm d}}{{\rm d}\tau}\right|_{\tau= 0}\cS[\rho](\bx+\tau \nu(t_0)) = \left.\frac{{\rm d}}{{\rm d}\tau}\right|_{\tau= 0}\cS[\rho](\bx_0+\tau \nu(t_0))- \rho(\bx_0).
+&\lim_{\bx \to \bx_0} \cS_{\omega}[\sigma](\bx) = \cS_{\omega}[\sigma](\bx_0)\\
+&\lim_{\bx \to \bx_0} \cD_{\omega}[\rho](\bx) = \cD_{\omega}[\rho](\bx_0)+ \rho(\bx_0)\\
+&\lim_{\bx \to \bx_0} \left.\frac{{\rm d}}{{\rm d}\tau}\right|_{\tau= 0}\cS_{\omega}[\rho](\bx+\tau \bnu(t_0)) = \left.\frac{{\rm d}}{{\rm d}\tau}\right|_{\tau= 0}\cS_{\omega}[\rho](\bx_0+\tau \bnu(t_0))- \rho(\bx_0).
 \end{align}
@@
 \begin{definition}
-Let $\cS$ be the single-layer potential operator. Let $\nu\cdot \nabla \cS$  denote its normal derivative restricted to $\Gamma.$ In particular, for $\by \in \Gamma,$
+Let $\cS_{\omega}$ be the single-layer potential operator. Let $\bnu\cdot \nabla \cS_{\omega}$  denote its normal derivative restricted to $\Gamma.$ In particular, for $\by \in \Gamma,$
 \begin{align}
-\nu\cdot \nabla \cS[\rho] (\by) = \left.\frac{{\rm d}}{{\rm d}\tau}\right|_{\tau = 0} \cS[\rho](\by + \tau \nu(t_0)),
+\bnu(\by)\cdot \nabla \cS_{\omega}[\rho] (\by) = \left.\frac{{\rm d}}{{\rm d}\tau}\right|_{\tau = 0} \cS_{\omega}[\rho](\by + \tau \bnu(t_0)),
 \end{align}
@@
 \begin{proposition}
-Let $\cS,\cD:L^2(\Gamma) \to L^2(\Gamma)$ be defined as above.
-Let $\nu \cdot \nabla \cS$ denote the normal derivative of $\cS$ in the sense of the previous definition.
-Then $\nu \cdot \nabla \cS = \cD^*$ where $*$ denotes the adjoint operator.
+Let $\cS_{\omega},\cD_{\omega}:L^2(\Gamma) \to L^2(\Gamma)$ be defined as above.
+Let $\bnu \cdot \nabla \cS_{\omega}$ denote the normal derivative of $\cS_{\omega}$ in the sense of the previous definition.
+Then $\bnu \cdot \nabla \cS _{\omega}= \cD_{\omega}^{T}$ where $T$ denotes the adjoint operator with respect to the inner product
+\beqn
+< f,g > = \int_{0}^{L} f(\gamma(t)) g(\gamma(t)) dt\,.
+\eeqn
 In particular, for all $\rho,\sigma \in L^2(\Gamma)$
 \begin{align}
-\cD[\sigma](\gamma(t)] = \int_0^L k(s,t)\,\sigma(\gamma(s))\, {\rm d}s
+\cD_{\omega}[\sigma](\gamma(t)] = \int_0^L k_{\omega}(s,t)\,\sigma(\gamma(s))\, {\rm d}s
 \end{align}
@@
 \begin{align}
-\nu\cdot \nabla\cS[\rho](\gamma(t)] = \int_0^L k(t,s)\,\rho(\gamma(s))\, {\rm d}s.
+\bnu(\gamma(t))\cdot \nabla\cS_{\omega}[\rho](\gamma(t)] = \int_0^L k_{\omega}(t,s)\,\rho(\gamma(s))\, {\rm d}s.
 \end{align}
@@
 
-\begin{theorem}
-Let $\sigma \in L^2([0,L])$ and $f: [0,L] \rightarrow \mathbb{R}$ be defined via the formula
+\begin{theorem} [Interior Dirichlet problem for the Laplace and Helmholtz equations]
+Let $f:[0,L] \rightarrow \mathbb{C}$ be in $L^{2}[0,L]$. If $\omega$ is not an Dirichlet resonance of $\Omega$, then 
+there exists a unique $\sigma \in L^{2}[0,L]$ which satisfies
 \begin{align}
-f(s)= - \sigma(s)+ \int_0^L k(t,s)\,\sigma(t)\,{\rm d}t,
+f(s)= - \sigma(s)+ \int_0^L k_{\omega}(t,s)\,\sigma(t)\,{\rm d}t,
 \label{bie_intd}
 \end{align}
-for all $s \in [0,L].$ For $f \in L^2([0,L])$ the above integral equation has a unique solution for $\sigma \in L^2([0.L]).$ Moreover, the solution to the interior Dirichlet problem for Laplace's equation with boundary data $f$ is given by $u(\by) = \cD[\sigma](\by)$ for all $\by \in \Omega.$
+Moreover, the solution to the interior Dirichlet problem for Laplace/Helmeholtz equation with boundary data $f$ is given by $u(\by) = \cD_{\omega}[\sigma](\by)$ for all $\by \in \Omega.$
 \end{theorem}
 
-\begin{theorem}
-Let $\sigma \in L^2([0,L])$ and $f: [0,L] \rightarrow \mathbb{R}$ be defined via the formula
+\begin{theorem} [Exterior Dirichlet problem for the Laplace equation]
+Let $f:[0,L] \rightarrow \mathbb{C}$ be in $L^{2}[0,L]$. Then there exists a unique $\sigma \in L^{2}[0,L]$ which
+satisfies
 \begin{align}
-f(s)=  \sigma(s)+ \int_0^L k(t,s)\,\sigma(t)\,{\rm d}t,
+f(s)=  \sigma(s)+ \int_0^L (k_{0}(t,s) + 1)\,\sigma(t)\,{\rm d}t,
 \end{align}
-for all $s \in [0,L].$ For $f \in L^2([0,L])$ such that
-\begin{align}
-\int_0^L f(t)\,{\rm d}t = 0
-\end{align}
- the above integral equation has a unique solution for $\sigma \in L^2([0.L]).$ Moreover, the solution to the exterior Dirichlet problem for Laplace's equation with boundary data $f$ is given by $u(\by) = \cD[\sigma](\by)$
+for all $s \in [0,L].$ 
+Moreover, the solution to the exterior Dirichlet problem for Laplace's equation with boundary data $f$ is given by $u(\by) = \cD_{0}[\sigma](\by) + \int_{0}^{L} \sigma(t) dt$
 for all $\by \in \mathbb{R}^2 \setminus \Omega.$
@@
 
-\begin{theorem}
-Let $\rho \in L^2([0,L])$ and $f: [0,L] \rightarrow \mathbb{R}$ be defined via the formula
+\begin{theorem} [Exterior Dirichlet problem for the Helmholtz equation]
+Let $f:[0,L] \rightarrow \mathbb{C}$ be in $L^{2}[0,L]$. Suppose $\omega$ is not an interior Neumann resonance of $\Omega$. Then there exists a unique $\sigma \in L^{2}[0,L]$ which
+satisfies
 \begin{align}
-f(s)= \rho(s)+ \int_0^L k(s,t)\,\rho(t)\,{\rm d}t,
+f(s)=  \sigma(s)+ \int_0^L k_{\omega}(t,s) \,\sigma(t)\,{\rm d}t,
 \end{align}
-for all $s \in [0,L].$ For $f \in L^2([0,L])$ the above integral equation has a unique solution for $\rho \in L^2([0,L])$  if and only if
-\begin{align}
-\int_0^L f(t)\,{\rm d}t.
-\end{align}
- Moreover, the solution to the interior Neumann problem for Laplace's equation with boundary data $f$ is given by $u(\by) = \cS[\rho](\by)$ for all $\by \in \Omega.$
+for all $s \in [0,L].$ 
+Moreover, the solution to the exterior Dirichlet problem for Helmholtz's equation with boundary data $f$ is given by $u(\by) = \cD_{\omega}[\sigma](\by)$
+for all $\by \in \mathbb{R}^2 \setminus \Omega.$
 \end{theorem}
 
-\begin{theorem}
-Let $\rho \in L^2([0,L])$ and $f: [0,L] \rightarrow \mathbb{R}$ be defined via the formula
+\begin{theorem}[Interior Neumann problem for the Laplace equation]
+Let $f:[0,L] \rightarrow \mathbb{C}$ be in $L^{2}[0,L]$ and satisfy $\int_{0}^{L} f(t) = 0$ \, .
+Then there exists a unique $\rho \in L^{2}[0,L]$ which satisfies
 \begin{align}
-f(s)= -\rho(s)+ \int_0^L k(s,t)\,\rho(t)\,{\rm d}t,
+f(s)=  \rho(s)+ \int_0^L (k_{0}(s,t) + 1)\,\sigma(t)\,{\rm d}t,
+\label{bie_intd}
 \end{align}
-for all $s \in [0,L].$ For $f \in L^2([0,L])$ the above integral equation has a unique solution for $\rho \in L^2([0.L]).$ Moreover, the solution to the exterior Neumann problem for Laplace's equation with boundary data $f$ is given by $u(\by) = \cS[\rho](\by)$ for all $\by \in \Omega.$
+Moreover, the solution to the interior Neumann problem for Laplace equation with boundary data $f$ is given by $u(\by) = \cS_{0}[\rho](\by)$ for all $\by \in \Omega.$
 \end{theorem}
+
+\begin{theorem}[Interior Neumann problem for the Helmholtz equation]
+Let $f:[0,L] \rightarrow \mathbb{C}$ be in $L^{2}[0,L]$. Suppose that $\omega$ is not an interior Neumann resonance for 
+$\Omega$. 
+Then there exists a unique $\rho \in L^{2}[0,L]$ which satisfies
+\begin{align}
+f(s)=  \rho(s)+ \int_0^L k_{\omega}(s,t) \,\sigma(t)\,{\rm d}t,
+\label{bie_intd}
+\end{align}
+Moreover, the solution to the interior Neumann problem for the Helmholtz equation with boundary data $f$ is given by $u(\by) = \cS_{\omega}[\rho](\by)$ for all $\by \in \Omega.$
+\end{theorem}
+
+\begin{theorem}[Exterior Neumann problem for the Laplace and Helmholtz equations]
+Let $f:[0,L] \rightarrow \mathbb{C}$ be in $L^{2}[0,L]$. Suppose that $\omega$ is not an interior Dirichlet resonance for 
+$\Omega$. 
+Then there exists a unique $\rho \in L^{2}[0,L]$ which satisfies
+\begin{align}
+f(s)=  \rho(s)+ \int_0^L k_{\omega}(s,t) \,\sigma(t)\,{\rm d}t,
+\label{bie_intd}
+\end{align}
+Moreover, the solution to the interior Neumann problem for the Laplace ($\omega =0$) and Helmholtz equation with boundary data $f$ is given by $u(\by) = \cS_{\omega}[\rho](\by)$ for all $\by \in \Omega.$
+\end{theorem}
+
+\begin{remark}
+Even though the exterior Dirichlet and Neumann problems for Helmholtz equations are well-posed partial differential equations, the corresponding integral equations obtained by setting $u = \cD_{\omega}[\sigma](\by)$ for the Dirichlet problem and
+$u = \cS_{\omega}[\rho](\by)$ are known to have a countable set of spurious resonances at the interior Neumann and Dirichlet resonances respectively.
+These spurious resonances can be eliminated by using a combined field integral representation
+for $u$ instead. We defer the extension of our method to the combined field representation to section (ENTER section number here).
+\end{remark}
 

### 2019-11-05 paper_lap/02mprelim.tex
updates

--- 2019-11-05 paper/02mprelim.tex
@@
 \subsection{Boundary value problems}
-Consider a polygonal domain $\Omega \subset \mathbb{R}^2$ with boundary $\Gamma.$ 
-Let $\gamma:[0,L] \to \Gamma$ be an arclength parametrization, and $\nu(t)$ denote the 
-outward-pointing normal to $\Gamma$ at $\gamma(t).$  
-Let $\omega \in \mathbb{C} \setminus \{ 0 \}$ in the first quadrant of the complex plane denote the 
-Helmholtz wave number.
+Given a polygonal domain  $\Omega \subset \mathbb{R}^2$ with boundary $\Gamma$ and a function
+$f: \Gamma \to \mathbb{R},$ we consider 
+the following four boundary value problems.
+
 \begin{enumerate}
@@
 \Delta u(\bx) &= 0, \hspace{1 cm} \bx \in \Omega,\\
-u(\gamma(t)) &= f(t), \hspace{0.43 cm} t \in [0,L].
-\end{align}
-
-\item The interior Dirichlet problem for Helmholtz's equation:
-\begin{align}\label{eqn:BVPIDH}
-(\Delta + \omega^2) u(\bx) &= 0, \hspace{1 cm} \bx \in \Omega,\\
-u(\gamma(t)) &= f(t), \hspace{0.43 cm} t \in [0,L].
+u(\bx) &= f(\bx), \hspace{0.43 cm} \bx \in \Gamma.
 \end{align}
@@
 \Delta u(\bx) &= 0, \hspace{1 cm} \bx \in \mathbb{R}^2\setminus\Omega,\\
-u(\gamma(t)) &= f(t), \hspace{0.43 cm} t \in[0,L], \\
+u(\bx) &= f(\bx), \hspace{0.43 cm}\bx \in \Gamma, \\
 u(\bx) &= O(1) , \hspace{0.4cm} |\bx| \to \infty.
-\end{align}
-
-\item The exterior Dirichlet problem for Helmholtz's equation:
-\begin{align}\label{eqn:BVPEDH}
-\Delta u(\bx) &= 0, \hspace{1 cm} x \in \mathbb{R}^2\setminus\Omega,\\
-u(\gamma(t)) &= f(t), \hspace{0.43 cm} t \in[0,L], \\
-\sqrt{|\bx|} \left|\partial_{|\bx|} u - i\omega u(\bx)\right| &\to 0 , \hspace{0.86cm} |\bx| \to \infty.
 \end{align}
@@
 \Delta u(\bx) &= 0, \hspace{1 cm} \bx \in \Omega,\\
-\nabla u(\gamma(t))\cdot \bnu(t)  &= f(t), \hspace{0.45 cm} t\in [0,L],\\
-\int_{0}^{L} f(t) dt &= 0.
-\end{align}
-
-\item The interior Neumann problem for Helmholtz's equation:
-\begin{align}\label{eqn:BVPINH}
-(\Delta + \omega^2) u(\bx) &= 0, \hspace{1 cm} \bx \in \Omega,\\
-\nabla u(\gamma(t))\cdot \bnu(t)  &= f(t), \hspace{0.45 cm} t\in [0,L].
+\nabla u(\bx)\cdot \bnu(\bx)  &= f(\bx), \hspace{0.45 cm} \bx \in \Gamma,\\
+\int_\Gamma f(\bx) {\rm d}s &= 0.
 \end{align}
@@
 \Delta u(\bx) &= 0, \hspace{1 cm} x \in \mathbb{R}^2\setminus\Omega,\\
-\nabla u(\gamma(t))\cdot \bnu(t)  &= f(t), \hspace{0.43 cm} t \in[0,L], \\
+\nabla u(\bx)\cdot \bnu(\bx)  &= f(\bx), \hspace{0.43 cm} t \in[0,L], \\
 \sqrt{|\bx|} \left|\partial_{|\bx|} u - i\omega u(\bx)\right| &\to 0 , \hspace{0.86cm} |\bx| \to \infty.

### 2019-11-06 paper_lap/03bvp.tex
updates

--- 2019-11-04 paper/03bvp.tex
@@
  \section{Boundary integral equations}
-A classical way of solving the interior and exterior Dirchlet and Neumann Laplace boundary value problems given above is to convert them to boundary integral equations.
-Before describing this reduction we first define the single and double layer potential operators and summarize their relevant properties.
+A classical technique for solving the four Laplace boundary value problems given above is to reduce them to boundary integral equations.
+Before describing this procedure we first define the single and double layer potential operators and summarize their relevant properties.
  \subsection{Layer potentials}
-\begin{definition}
-Given a density $\sigma$ defined on $\Gamma$ the single-layer potential is defined by
+\begin{definition}\label{def_layerpots}
+Given a density $\sigma:\Gamma \to \mathbb{R}$ the single-layer potential is defined by
 \beqn
-\cS[\sigma](\by) = -\frac{1}{2\pi} \int_{\Gamma} \log{|\bx - \by|} \sigma(\bx) dS_{\bx}.
+\cS[\sigma](\by) =  \int_{\Gamma} G (\bx,\by)\sigma(\bx) {\rm d}S_{\bx} \, ,
+\eeqn
+where
+\beqn
+G(\bx,\by) = -\frac{1}{2\pi} \log{|\bx-\by|}.
 \eeqn
@@
 \beqn
-\cD[\sigma](\by) = \frac{1}{2\pi} \int_{\Gamma} \frac{\nu(\bx) \cdot( \by-\bx)}{|\bx-\by|^2}\sigma(\bx) dS_{\bx},
+\cD[\sigma](\by) =\int_{\Gamma} \bnu(\bx) \cdot \nabla_{\bx} G(\bx,\by) \sigma(\bx) {\rm d}S_{\bx}.
 \eeqn
-where with some abuse of notation we denote the normal to $\Gamma$ at $\bx$ by $\nu(\bx).$
 \end{definition}
+
 \begin{definition}
-For $\bx \in \Gamma$ we define the kernel $K(x,y)$ by
+For $\bx \in \Gamma$ we define the kernel $K(\bx,\by)$ by
 \begin{equation}
-K(\bx,\by) =\frac{1}{2\pi}  \frac{\nu(\bx) \cdot( \by-\bx)}{|\bx-\by|^2},
+K(\bx,\by) =\bnu(\bx) \cdot \nabla_{\bx} G(\bx,\by),
 \end{equation}
-where $\nu(\bx)$ is the normal to $\Gamma$ at $\bx.$ It is often convenient to work instead with the parametrization of $K$ which we will denote by $k:[0,L]\times k[0,L] \to \mathbb{R}$ and is defined by
+where $\nu(\bx)$ is the inward-pointing normal to $\Gamma$ at $\bx.$ It will often be convenient to 
+work instead with a parametrization of $K.$ In particular, if $\gamma :[0,L] \to \Gamma$ is a counterclockwise 
+arclength parametrization of $\Gamma,$ 
+we denote by $k:[0,L]\times [0,L] \to \mathbb{R}$ the function defined by
 \begin{align}
-k(s,t) = \frac{1}{2 \pi} \frac{\nu(s) \cdot( \gamma(t)-\gamma(s))}{|\gamma(s)-\gamma(t)|^2}.
+k(s,t) = K(\gamma(s),\gamma(t)).
 \end{align}
@@
 
-The following theorems describe the behaviour of the single and double layer potentials in the vicinity of the boundary curve $\Gamma.$
+The following theorems describe the behavior of the single and double layer potentials in the vicinity of the boundary curve $\Gamma.$
 
@@
 &\lim_{\bx \to \bx_0} \cD[\rho](\bx) = \cD[\rho](\bx_0)- \rho(\bx_0)\\
-&\lim_{\bx \to \bx_0} \left.\frac{{\rm d}}{{\rm d}\tau}\right|_{\tau= 0}\cS\rho(\bx+\tau \nu(t_0)) = \left.\frac{{\rm d}}{{\rm d}\tau}\right|_{\tau= 0}\cS[\rho](\bx_0+\tau \nu(t_0))+ \rho(\bx_0).
+&\lim_{\bx \to \bx_0} \left.\frac{{\rm d}}{{\rm d}\tau}\right|_{\tau= 0}\cS[\rho](\bx+\tau \bnu(\bx_0)) = \left.\frac{{\rm d}}{{\rm d}\tau}\right|_{\tau= 0}\cS[\rho](\bx_0+\tau \bnu(\bx_0))+ \rho(\bx_0).
 \end{align}
@@
 &\lim_{\bx \to \bx_0} \cD[\rho](\bx) = \cD[\rho](\bx_0)+ \rho(\bx_0)\\
-&\lim_{\bx \to \bx_0} \left.\frac{{\rm d}}{{\rm d}\tau}\right|_{\tau= 0}\cS[\rho](\bx+\tau \nu(t_0)) = \left.\frac{{\rm d}}{{\rm d}\tau}\right|_{\tau= 0}\cS[\rho](\bx_0+\tau \nu(t_0))- \rho(\bx_0).
+&\lim_{\bx \to \bx_0} \left.\frac{{\rm d}}{{\rm d}\tau}\right|_{\tau= 0}\cS[\rho](\bx+\tau \bnu(\bx_0)) = \left.\frac{{\rm d}}{{\rm d}\tau}\right|_{\tau= 0}\cS[\rho](\bx_0+\tau \bnu(\bx_0))- \rho(\bx_0).
 \end{align}
@@
 We define the following operator which arises in the study of Neumann boundary value problems.
-\begin{definition}
-Let $\cS$ be the single-layer potential operator. Let $\nu\cdot \nabla \cS$  denote its normal derivative restricted to $\Gamma.$ In particular, for $\by \in \Gamma,$
+\begin{definition}\label{def_singder}
+Let $\cS$ be the single-layer potential operator and $\bnu\cdot \nabla \cS$  denote its normal derivative restricted to $\Gamma.$ In particular, for $\bx_0 \in \Gamma,$
 \begin{align}
-\nu\cdot \nabla \cS[\rho] (\by) = \left.\frac{{\rm d}}{{\rm d}\tau}\right|_{\tau = 0} \cS[\rho](\by + \tau \nu(t_0)),
+\bnu(\by)\cdot \nabla \cS[\rho] (\bx_0) = \left.\frac{{\rm d}}{{\rm d}\tau}\right|_{\tau = 0} \cS[\rho](\bx_0 + \tau \bnu(\bx_0)),
 \end{align}
-where $\gamma(t_0) = \by.$
+where $\gamma(t_0) = \bx_0.$
 \end{definition}
 
-The following proposition relates the normal derivative of the single-layer operator to the double-layer operator. Its proof follows directly from the definitions.
+The following proposition relates the normal derivative of the single-layer operator to the double-layer operator.
+Its proof follows directly from Definitions \ref{def_layerpots} and \ref{def_singder}.
 \begin{proposition}
 Let $\cS,\cD:L^2(\Gamma) \to L^2(\Gamma)$ be defined as above.
-Let $\nu \cdot \nabla \cS$ denote the normal derivative of $\cS$ in the sense of the previous definition.
-Then $\nu \cdot \nabla \cS = \cD^*$ where $*$ denotes the adjoint operator.
-In particular, for all $\rho,\sigma \in L^2(\Gamma)$
+Let $\bnu \cdot \nabla \cS$ denote the normal derivative of $\cS$ in the sense of the previous definition.
+Then $\bnu \cdot \nabla \cS= \cD^{T}$ where $T$ denotes the adjoint operator with respect to the inner product
+\beqn
+\langle f,g \rangle = \int_{0}^{L} f(\gamma(t)) g(\gamma(t)) {\rm d}t\,,
+\eeqn
+where $\gamma:[0,L] \to \Gamma$ is a counterclockwise arclength parametrization of $\Gamma.$ 
+In particular, for all $\rho,\sigma \in L^2(\Gamma),$
 \begin{align}
-\cD[\sigma](\gamma(t)] = \int_0^L k(s,t)\,\sigma(\gamma(s))\, {\rm d}s
+\cD[\sigma](\gamma(t)) = \int_0^L k(s,t)\,\sigma(\gamma(s))\, {\rm d}s
 \end{align}
@@
 \begin{align}
-\nu\cdot \nabla\cS[\rho](\gamma(t)] = \int_0^L k(t,s)\,\rho(\gamma(s))\, {\rm d}s.
+\bnu(\gamma(t))\cdot \nabla\cS[\rho](\gamma(t)) = \int_0^L k(t,s)\,\rho(\gamma(s))\, {\rm d}s.
 \end{align}
@@
 
-\begin{theorem}
-Let $\sigma \in L^2([0,L])$ and $f: [0,L] \rightarrow \mathbb{R}$ be defined via the formula
+\begin{theorem} [Interior Dirichlet problem for Laplace's equation]
+For every $f:[0,L] \rightarrow \mathbb{R}$ in $L^{2}[0,L],$ there exists a unique $\sigma \in L^{2}[0,L]$ which satisfies
 \begin{align}
@@
 \end{align}
-for all $s \in [0,L].$ For $f \in L^2([0,L])$ the above integral equation has a unique solution for $\sigma \in L^2([0.L]).$ Moreover, the solution to the interior Dirichlet problem for Laplace's equation with boundary data $f$ is given by $u(\by) = \cD[\sigma](\by)$ for all $\by \in \Omega.$
+Moreover, the solution to the interior Dirichlet problem for Laplace's equation with boundary data $f$ is given by $u(\by) = \cD_{\omega}[\sigma](\by)$ for all $\by \in \Omega.$
 \end{theorem}
 
-\begin{theorem}
-Let $\sigma \in L^2([0,L])$ and $f: [0,L] \rightarrow \mathbb{R}$ be defined via the formula
+\begin{theorem} [Exterior Dirichlet problem for Laplace's equation]
+For every $f:[0,L] \rightarrow \mathbb{R}$ in $L^{2}[0,L]$ there exists a unique $\sigma \in L^{2}[0,L]$ which
+satisfies
 \begin{align}
-f(s)=  \sigma(s)+ \int_0^L k(t,s)\,\sigma(t)\,{\rm d}t,
+f(s)=  \sigma(s)+ \int_0^L (k(t,s) + 1)\,\sigma(t)\,{\rm d}t,
 \end{align}
-for all $s \in [0,L].$ For $f \in L^2([0,L])$ such that
-\begin{align}
-\int_0^L f(t)\,{\rm d}t = 0
-\end{align}
- the above integral equation has a unique solution for $\sigma \in L^2([0.L]).$ Moreover, the solution to the exterior Dirichlet problem for Laplace's equation with boundary data $f$ is given by $u(\by) = \cD[\sigma](\by)$
+for all $s \in [0,L].$ 
+Moreover, the solution to the exterior Dirichlet problem for Laplace's equation with boundary data $f$ is given by $u(\by) = \cD_{0}[\sigma](\by) + \int_{0}^{L} \sigma(t) dt$
 for all $\by \in \mathbb{R}^2 \setminus \Omega.$
@@
 
-\begin{theorem}
-Let $\rho \in L^2([0,L])$ and $f: [0,L] \rightarrow \mathbb{R}$ be defined via the formula
+\begin{theorem}[Interior Neumann problem for Laplace's equation]
+For every  $f:[0,L] \rightarrow \mathbb{C}$ in $L^{2}[0,L]$ such that $\int_{0}^{L} f(t) = 0,$ \, there exists a unique $\rho \in L^{2}[0,L]$ which satisfies
 \begin{align}
-f(s)= \rho(s)+ \int_0^L k(s,t)\,\rho(t)\,{\rm d}t,
+f(s)=  \rho(s)+ \int_0^L (k(s,t) + 1)\,\sigma(t)\,{\rm d}t,
+\label{bie_intn}
 \end{align}
-for all $s \in [0,L].$ For $f \in L^2([0,L])$ the above integral equation has a unique solution for $\rho \in L^2([0,L])$  if and only if
-\begin{align}
-\int_0^L f(t)\,{\rm d}t.
-\end{align}
- Moreover, the solution to the interior Neumann problem for Laplace's equation with boundary data $f$ is given by $u(\by) = \cS[\rho](\by)$ for all $\by \in \Omega.$
+Moreover, the solution to the interior Neumann problem for Laplace's equation with boundary data $f$ is given by $u(\by) = \cS_{0}[\rho](\by)$ for all $\by \in \Omega.$
 \end{theorem}
 
-\begin{theorem}
-Let $\rho \in L^2([0,L])$ and $f: [0,L] \rightarrow \mathbb{R}$ be defined via the formula
+\begin{theorem}[Exterior Neumann problem for Laplace's equation]
+For every $f:[0,L] \rightarrow \mathbb{C}$ in $L^{2}[0,L]$ there exists a unique $\rho \in L^{2}[0,L]$ which satisfies
 \begin{align}
-f(s)= -\rho(s)+ \int_0^L k(s,t)\,\rho(t)\,{\rm d}t,
+f(s)=  \rho(s)+ \int_0^L k_{\omega}(s,t) \,\sigma(t)\,{\rm d}t,
+\label{bie_extn}
 \end{align}
-for all $s \in [0,L].$ For $f \in L^2([0,L])$ the above integral equation has a unique solution for $\rho \in L^2([0.L]).$ Moreover, the solution to the exterior Neumann problem for Laplace's equation with boundary data $f$ is given by $u(\by) = \cS[\rho](\by)$ for all $\by \in \Omega.$
+Moreover, the solution to the interior Neumann problem for Laplace'sequation with boundary data $f$ is given by $u(\by) = \cS_{\omega}[\rho](\by)$ for all $\by \in \Omega.$
 \end{theorem}
@@
 
-The following Corollary characterizes of the solutions to the Dirichlet and Neumann boundary integral equations in the vicinity of a corner.
+The following Corollary, proved in \cite{serkhacha} gives a characterization of the solutions to the Dirichlet and Neumann boundary integral equations in the vicinity of a corner.
 

### 2019-11-06 paper_lap/04nprelim.tex
updates

--- 2019-11-05 paper/04nprelim.tex
@@
 In particular we summarize the method for discretizing the boundary integral equation for the Dirichlet problem described in \cite{}, which uses the expansion in Theorem \ref{thm_cord}.
-\subsection{Discretization of the Dirichlet problem}
+\subsection{Discretization of the Dirichlet problem}\label{sec:disc_dir}
 In this section we sketch an algorithm for solving the interior Dirichlet boundary integral equation using a Nystr\"{o}m method; the exterior Dirichlet boundary integral equation can be discretized in a similar way.
 See \cite{} for a thorough description of the method.
+
+The Nystr\"{o}m method proceeds as follows.
 We begin by constructing a discretization of the boundary $\Gamma$ with nodes $s_1,\dots,s_N,$ and weights $w_1,\dots,w_N,$ which enable interpolation of the left- and right-hand sides of the boundary integral equation
-\begin{align}
+\begin{align}\label{eqn:numpreint}
 f(t) = -\sigma(t) + \int_0^L k(t,s) \,\sigma(t)\, {\rm d} t
 \end{align}
-with precision $\epsilon.$ We proceed by enforcing equality at the discretization nodes, which yields the system of equations
+with precision $\epsilon.$ Once these nodes and weights have been generated we proceed by enforcing equality of (\ref{eqn:numpreint}) at the discretization nodes, which yields the system of equations
 \begin{align}
@@
 \end{align}
-Scaling by the square root of the weights is equivalent to solving the problem in the $L^2$ sense, and results in discretized operators with condition numbers which are close to those of the original physical systems \cite{bremer3}.
+We note that scaling by the square root of the weights in the above equation is equivalent to solving the problem in the $L^2$ sense, and results in discretized operators with condition numbers which are close to those of the original physical systems \cite{bremer3}.
+The new unknowns are $\sigma_i = \sigma(s_i) \sqrt{w_i},$ $i=1,\dots,N.$ Next, for each interpolation node $s_i$ we find a collection of weights $W_{ij}$ such that
+\begin{align}
+\left|\int_0^L K(\gamma(s_i),\gamma(t))\, \sigma(t)\,{\rm d}t- \sum_{j=1}^N W_{ij} \sigma_j\, \sqrt{w_j} \right| < \epsilon,
+\end{align}
+resulting in the linear system
+\begin{align}
+  -\pi \sigma_i +  \sum_{j=1}^N W_{ij} \sigma_j \sqrt{w_i w_j}=f(s_i) \sqrt{w_i},\quad i,j=1,\dots,N. 
+\end{align}
 
-The boundary $\Gamma$ is separated into intervals which are at least some distance $\delta$  (measured in terms of arclength) away from a corner and intervals of length $2 \delta$ centered about each corner.
+%{\color{red} then find quadratures}
+
+\subsubsection{Obtaining interpolation nodes}
+
+The boundary $\Gamma$ is separated into a collection of intervals which are at least a fixed distance $\delta$  (measured in terms of arclength) away from a corner and the collection of intervals of length $2 \delta$ centered about each corner.
 The former are discretized using a standard smooth quadrature rule such as nested Gauss-Legendre quadrature while the latter are discretized using a custom set of interpolation nodes constructed in the following way.
@@
 This creates a $N \times M$ matrix where $N$ denotes the number of spatial discretization points $r_i$ and $M$ denotes the number of $\mu_j$ chosen.
-$M$ and $N$ are increased until it is guaranteed that using Lagrange interpolation from the nested discretization the function $x^\mu$ can be interpolated to within an $L^2$ error less than $\epsilon$ on the interval $[0,1/2]$ for any $\mu$ in the specified range.
+$M$ and $N$ are increased until it is guaranteed that using Lagrange interpolation from the nested discretization the function $x^\mu$ can be interpolated to within an $L^2$ error less than $\epsilon$ on the interval $[0,1]$ for any $\mu$ in the specified range.
 A singular value decomposition is then performed on the $N\times M$ matrix.
@@
 
-Finally, a set of interpolation points $x_j,$ $j=1,\dots,K$ and quadrature weights $w_j,$ $j=1,\dots,K$ are chosen for $\phi_1,\dots,\phi_K$ such that the matrix $U_{ij} = \phi_i(x_j) \sqrt{x_j}$ is well-conditioned.
+Finally, a set of interpolation points $x_j,$ $j=1,\dots,K$ and quadrature weights $w_j,$ $j=1,\dots,K$ are chosen for $\phi_1,\dots,\phi_K$ such that the matrix $U_{ij} = \phi_i(x_j) \sqrt{w_j}$ is well-conditioned.
 In practice suitable interpolation points can be obtained by using the roots of $\phi_{K+1}$ and calculating the corresponding weights by solving a linear system.
 The corresponding discretization nodes and weights for the corner-containing intervals of $\Gamma$ are obtained by suitable translations and scalings of $\{x_j\}$ and $\{w_j\}.$
+
+\subsubsection{Construction of quadrature rules}
 
@@
 \end{align} 
-where for ease of exposition we assume that the corner panel corresponds to $(-\delta,\delta)$ in the parametrization with $t=0$ corresponding to the corner itself.
-Moreover, it is assumed that $s_j$ lies in the half of a corner panel parametrized by $(-\delta,0)$ and $\tilde{\phi}_j$ is a suitably scaled and translated copy of the singular function obtained in the discretization step.
+where $\tilde{\phi}_j$ is a suitably scaled and translated copy of the singular function obtained in the discretization step, and for ease of exposition we assume that the corner panel corresponds to $(-\delta,\delta)$ in the parametrization with $t=0$ corresponding to the corner itself.
+Moreover, in light of symmetry between the two legs of the wedge it suffices to design quadratures assuming  $s_j$ lies in the half of a corner panel parametrized by $(-\delta,0).$
 \begin{remark1}
@@
 \begin{align}
-\int_{0}^\frac{1}{2} k(t,-x_j) {\phi}_j(t)\,{\rm d}t,
+\int_{0}^1 k(t,-x_j) {\phi}_j(t)\,{\rm d}t,
 \end{align} 
-where $x_j$ was one of the original discretization nodes generated on the interval $[0,1/2].$
+where $x_j$ was one of the original discretization nodes generated on the interval $[0,1].$
 \end{remark1}
 \begin{remark1}
-By interpolating from the discretization nodes to these quadrature nodes we obtain a set of weights $\tilde{w}_{i,j}$ such that if $s_1,\dots,s_{2K}$ correspond to the discretization of a corner parametrized by $(-\delta,\delta)$ with $0$ corresponding to the corner then
+By interpolating from the discretization nodes to these quadrature nodes we obtain a set of weights $\tilde{W}_{i,j}$ such that if $s_1,\dots,s_{2K}$ correspond to the discretization of a corner parametrized by $(-\delta,\delta)$ with $0$ corresponding to the corner then
 \begin{align}
-\left| \int_{-\delta}^\delta k(t,s_i) \, \tilde{\phi}_m(t)\,{\rm d}t - \sum_{j=1}^{2K} \tilde{w}_{ij} \tilde{\phi}_{m}(t_j) \right| < \epsilon
+\left| \int_{-\delta}^\delta k(t,s_i) \, \tilde{\phi}_m(t)\,{\rm d}t - \sum_{j=1}^{2K} \tilde{W}_{ij} \tilde{\phi}_{m}(t_j) \right| < \epsilon
 \end{align}
@@
 Apart from posing certain numerical challenges, it also makes the task of finding suitable quadrature formulae difficult.
-Instead a different set of discretization nodes and a different set of quadrature nodes must be constructed for each angle, drastically increasing the precomputation cost.
+Instead a different set of discretization nodes and a different set of quadrature nodes can be constructed for each angle, though this would significantly increase the precomputation cost.
 

### 2019-11-06 paper_lap/05apparatus.tex
updates

--- 2019-11-04 paper/05apparatus.tex
@@
 \begin{corollary}
-Let $A$ be the $N\times N$ matrix obtained by discretizing the interior Dirichlet problem and $S_\epsilon$ be the collection of functions defined in Definition \ref{def:seps}.
+Let $A$ be the $N\times N$ matrix obtained by discretizing the interior Dirichlet problem and $S_\epsilon$ be the collection of functions given by Definition \ref{def:seps}.
 Then for all functions $f,g \in S_\epsilon$
@@
 This follows from the fact that the interpolation scheme constructed is only guaranteed to interpolate the powers arising in the Dirichlet problem accurately near the corner.
-The Neumann problem expansions contain negative powers which are not contained in this set and hence are not interpolated accurately.
+The collection of singular powers arising in Neumann problems contain negative powers which are not contained in this set and hence are not interpolated accurately.
 \end{remark1}
@@
 In this section we address the problem highlighted in the previous one; namely, the accurate evaluation of the solution to the exterior Neumann problem in the vicinity of a corner.
-Our approach is based on the observation that the contribution from the density on the boundary outside of a sufficiently small neighborhood of the corner is smooth when evaluated in the vicinity of the corner.
+Our approach is based on the observation that the potential generated by the density on the boundary outside of a sufficiently small neighborhood of the corner is smooth when evaluated in the vicinity of the corner.
 This allows us to convert the problem of evaluating the potential near the corner (given the approximation to the density obtained using the adjoint approach described in the previous section) into a purely local one.
-In particular, we rediscretize only a small neighborhood of the corner which in turn allows us to evaluate the potential arbitrarily close to the corner to within a small factor of machine precision.
+In particular, we re-discretize only a small neighborhood of the corner which in turn allows us to evaluate the potential arbitrarily close to the corner to within a small factor of machine precision.
 
-In the following we assume that we are given a discretization of the interior Dirichlet boundary integral equation (\ref{}) with nodes $x_1,\dots,x_N$ and corresponding weights $w_1,\dots,w_N.$ In particular, we assume that the discretization nodes are obtained by subdividing the boundary into panels.
-Those panels which contain a vertex are discretized using a custom discretization scheme (see Section \ref{}) while the remaining panels are discretized using a standard smooth quadrature rule (such as Gauss-Legendre or Chebyshev nodes).
+In the following we assume that we are given a discretization of the interior Dirichlet boundary integral equation (\ref{bie_intd}) with nodes $x_1,\dots,x_N$ and corresponding weights $w_1,\dots,w_N.$ In particular, we assume that the discretization nodes are obtained by subdividing the boundary into panels.
+Those panels which contain a vertex are discretized using a custom discretization scheme (see Section \ref{sec:disc_dir}) while the remaining panels are discretized using a standard smooth quadrature rule (such as Gauss-Legendre or Chebyshev nodes).
 In the following we assume that an $M$-point Gauss-Legendre quadrature rule is used.
-Additionally, we denote the discretization of the interior Dirichlet operator (using the custom quadratures described in Section \ref{}) by $A.$ Let $\underline{f} = (f_1,\dots,f_N)^T$ where $f_i = f(x_i) \sqrt{w_i}$ and $f: \partial \Omega \to \mathbb{R}$ is the right-hand side of the exterior Neumann problem.
+Additionally, we denote the discretization of the interior Dirichlet operator (using the custom quadratures described in Section \ref{sec:disc_dir}) by $A.$ Let $\underline{f} = (f_1,\dots,f_N)^T$ where $f_i = f(x_i) \sqrt{w_i}$ and $f: \partial \Omega \to \mathbb{R}$ is the right-hand side of the exterior Neumann problem.
 Finally, let $\underline{\sigma}$ be the approximation to the density (scaled by the square roots of the weights) obtained by solving the linear system
@@
 For a panel $\gamma([s_1,s_2])$ with discretization nodes $x_i,\dots,x_{i+M}$ corresponding to a Gauss-Legendre panel the density is smooth and thus it is expected to be well-represented in the basis of Legendre polynomials (shifted and scaled to the interval $[s_1,s_2]$).
-Hence standard interpolation techniques can be used to obtain an accurate approximation to the density $\sigma$ on the interval $s_1 \le s\le s_2$ (see \cite{} for a detailed description of this process and quantitative estimates on the accuracy of the result).\\
-
-{\color{red}add remark about ratio of size of panel to distance from the corner}\\
+Hence standard interpolation techniques can be used to obtain an accurate approximation to the density $\sigma$ on the interval $s_1 \le s\le s_2$ (see \cite{} for a detailed description of this process and quantitative estimates on the accuracy of the result).
+Typically we use 16th order Gauss-Legendre panels and choose their sizes so that their length is no more than their distance to the nearest corner.
 
@@
 \end{align}
-We note that the solution to (\ref{eqn:resolve_neum0}) is equal to the solution of (\ref{}) restricted to the interval $[-\delta,\delta].$ Taking the adjoint of (\ref{eqn:resolve_neum0}) we obtain
+We note that the solution to (\ref{eqn:resolve_neum0}) is equal to the solution of the original boundary integral equation (\ref{bie_extn}) restricted to the interval $[-\delta,\delta].$ Taking the adjoint of (\ref{eqn:resolve_neum0}) we obtain
 \begin{align}\label{eqn:resolve_diri0}
@@
 In particular, we can discretize the operator using the method summarized in the previous section.
-Specifically, we subdivide the interval $[-\delta,\delta]$ into three subintervals $I_0 = [-\delta,\delta/2],$ $L_0 = [-\delta/2,\delta/2],$ and $J_0 = [\delta/2,\delta].$ On $I_0$ and $J_0$ we place standard Gauss-Legendre discretization nodes, while on $L_0$ we use the custom discretization scheme for corners, outlined in Section \ref{} (see \cite{} for a detailed description of the method).
+Specifically, we subdivide the interval $[-\delta,\delta]$ into three subintervals $I_0 = [-\delta,\delta/2],$ $L_0 = [-\delta/2,\delta/2],$ and $J_0 = [\delta/2,\delta].$ On $I_0$ and $J_0$ we place standard Gauss-Legendre discretization nodes, while on $L_0$ we use the custom discretization scheme for corners, outlined in Section \ref{sec:disc_dir} (see \cite{} for a detailed description of the method).
 Let $\underline{f}_0$ denote the right-hand side of (\ref{eqn:resolve_neum0}) evaluated at these discretization nodes and scaled by the square roots of the corresponding weights.
@@
 \end{align}
-then $\underline{\sigma}_0$ gives a {\color{red}weak solution} to the integral equation (\ref{eqn:resolve_neum0}), i.e.
+then $\underline{\sigma}_0$ gives a {weak solution} to the integral equation (\ref{eqn:resolve_neum0}), i.e.
 for any function $g$ which is analytic on $[-\delta,0]$ and $[0,\delta]$ the inner product $\langle g,\sigma \rangle$ can be calculated to precision $\epsilon$ using the solution $\underline{\sigma}_0.$ Moreover, since the true density $\sigma$ is smooth on $I_0$ and $J_0$ the Gauss-Legendre discretization allows accurate interpolation of the density on those regions.
 
-This can be represated to obtain an interpolable approximation to the density on $L_0 = [-\delta/2,\delta/2].$ In particular, we consider the restriction of the exterior Neumann integral equation, as well as its, adjoint to the interval $L_0.$ For the right-hand side we use the original right-hand side $f$ minus the contribution from the remainder of the domain.
+\begin{remark}
+Though the above method produces a viable method for reducing the problem, as written the reduction is non-local --- in order to compute the right-hand side for the sub-problem one must evaluate contributions from the rest of the domain.
+\end{remark}
+
+The following theorem shows that the right-hand side $\underline{f}_0$ can be computed only using local data (i.e. values of the weak solution in the vicinity of the corner).
+\begin{theorem}
+Let $\underline{f}_0$ be the discretization of the right-hand side of (\ref{eqn:resolve_diri0}). 
+\end{theorem}
+
+This can be represented to obtain an interpolable approximation to the density on $L_0 = [-\delta/2,\delta/2].$ In particular, we consider the restriction of the exterior Neumann integral equation, as well as its, adjoint to the interval $L_0.$ For the right-hand side we use the original right-hand side $f$ minus the contribution from the remainder of the domain.
 In particular, if we define

### 2019-11-06 paper_lap/05apparatus.tex
updates

@@
 Those panels which contain a vertex are discretized using a custom discretization scheme (see Section \ref{sec:disc_dir}) while the remaining panels are discretized using a standard smooth quadrature rule (such as Gauss-Legendre or Chebyshev nodes).
-In the following we assume that an $M$-point Gauss-Legendre quadrature rule is used.
+In the following we assume that an $M$-point Gauss-Legendre quadrature rule is used and the corner panels are discretized using $P$ nodes (together with a collection of orthonormal functions on that interval $\phi_1,\dots,\phi_P$).
+
+.
 Additionally, we denote the discretization of the interior Dirichlet operator (using the custom quadratures described in Section \ref{sec:disc_dir}) by $A.$ Let $\underline{f} = (f_1,\dots,f_N)^T$ where $f_i = f(x_i) \sqrt{w_i}$ and $f: \partial \Omega \to \mathbb{R}$ is the right-hand side of the exterior Neumann problem.
@@
 Suppose that $f$ be a piecewise-analytic function in $S_\epsilon$ and  $\underline{\sigma} = (A^T)^{-1} {\bf f}$ is the approximation to the Neumann density obtained using the adjoint of the discretization for the interior Dirichlet boundary integral equation.
-Then for all $t \in (-\delta,\delta)$
+Then
 \begin{align}
-h(t) = \sum_{i=M+1}^N k(t,s_i) \sqrt{w_i} \,\underline{\sigma}_i
+h(t) = \sum_{i=P+1}^N k(t,s_i) \sqrt{w_i} \,\underline{\sigma}_i
 \end{align}
-is an analytic function of $t$ for all $t \in (-\delta,\delta).$
+is an analytic function of $t$ for all $t \in (-\delta,\delta),$ assuming that $s_1,\dots,s_P$ correspond to the discretization of $(-\delta,\delta)$ with the corner point corresponding to $t=0.$
 \end{proposition}
@@
 
-The following theorem shows that the right-hand side $\underline{f}_0$ can be computed only using local data (i.e. values of the weak solution in the vicinity of the corner).
+The following theorem shows that the right-hand side $\underline{f}_0$ can be computed only using local data (i.e. values of the weak solution in the vicinity of the corner).\\
+{\color{red} Manas: there is something a little bad with this proof - Taylor series vs $\epsilon$}
 \begin{theorem}
-Let $\underline{f}_0$ be the discretization of the right-hand side of (\ref{eqn:resolve_diri0}). 
+Suppose that $\underline{f}_0$ is the discretization of the right-hand side of (\ref{eqn:resolve_diri0}) corresponding to nodes $s^0_1,\dots,s^0_{N_0}.$ Further suppose that $U$ is the $P\times P$ matrix with entries $U_{ij} = \phi_i(s_j) \sqrt{w_j},$ where $\phi_1,\dots,\phi_P$ are the orthonormal functions on $(-\delta,\delta)$ spanning $,{\rm sgn}(s)|s|^\mu, |s|^\mu,$ $\mu=0,1/2-40$ on that interval.
+Let $w:(-\delta,\delta) \to \mathbb{R}^P$ be the vector-valued function defined by
+\begin{align}
+w(t) = (\phi_1(t),\phi_2(t),\dots,\phi_P(t)),
+\end{align}
+and $\tilde{\sigma} = (\sigma_1,\dots,\sigma_P)^T$ be the approximation to the solution in the vicinity of the corner obtained by solving the original system (\ref{eqn:adj_linalg}).
+Then $|(f(t)-h(t)) - w(t) U^{-1} A_0^T \tilde{\sigma}| = O(\epsilon)$ for all $t \in(-\delta,\delta).$ In particular, if $\tilde{f}_0$ is the vector of length $N_0$ with entries defined by
+\begin{align}
+(\tilde{f}_0)_i = w(s^0_i) U^{-1} A_0^T \tilde{\sigma}, \quad i=1,\dots,N_0,
+\end{align}
+then $\| \underline{f}_0 - \tilde{f}_0\| = O(\epsilon).$
 \end{theorem}
+\begin{proof}
+We begin by observing that both $f$ and $h$ are analytic on the interval $(-\delta,\delta).$ In particular, they can be accurately interpolated using $\phi_1,\dots,\phi_P$ on the interval $(-\delta,\delta).$ In particular,
+\begin{align}\label{eqn:approx_thm}
+f(t)-h(t) \approx w(t) U^{-1} (f(s_1)-h(s_1),\dots,f(s_P)-h(s_P))^T
+\end{align}
+On the other hand, by construction,
+\begin{align}\label{eqn:linalg_thm}
+\underline{f} = A^T \begin{pmatrix}\tilde{\sigma}\\ \sigma_{P+1}\\ \vdots\\ \sigma_N\end{pmatrix}.
+\end{align}
+Let $A_0$ be the $P\times P$ submatrix of $A$ corresponding to the first $P$ rows and columns of $A,$ and $A_{\rm red}$ be the $P \times (N-P)$  submatrix of $A$ corresponding to selecting the first $P$ rows of $A$ and all but the first $P$ columns of $A.$ Using this notation, the first $P$ rows of (\ref{eqn:linalg_thm}) can be re-written as
+\begin{align}
+\begin{pmatrix}f_1\\\vdots \\ f_P\end{pmatrix}  = A_{\rm red}^T \begin{pmatrix} \sigma_{P+1}\\ \vdots\\ \sigma_N\end{pmatrix} + A_0^T \tilde{\sigma}.
+\end{align}
+The first term on the right-hand side is $(h(s_1),\dots,h(s_P))^T.$ Substituting this into the previous equation, we obtain
+\begin{align}
+(f(s_1)-h(s_1),\dots,f(s_P)-h(s_P))^T = A_0^T \tilde{\sigma}.
+\end{align}
+The result follows by substituting the above equality into (\ref{eqn:approx_thm}).
+\end{proof}
 
-This can be represented to obtain an interpolable approximation to the density on $L_0 = [-\delta/2,\delta/2].$ In particular, we consider the restriction of the exterior Neumann integral equation, as well as its, adjoint to the interval $L_0.$ For the right-hand side we use the original right-hand side $f$ minus the contribution from the remainder of the domain.
+This can be iterated to obtain an interpolable approximation to the density on $L_0 = [-\delta/2,\delta/2].$ In particular, we consider the restriction of the exterior Neumann integral equation, as well as its, adjoint to the interval $L_0.$ For the right-hand side we use the original right-hand side $f$ minus the contribution from the remainder of the domain.
 In particular, if we define

### 2019-11-22 paper_lap/04nprelim.tex
updates

@@
 \begin{align}\label{eqn:numpreint}
-f(t) = -\sigma(t) + \int_0^L k(t,s) \,\sigma(t)\, {\rm d} t
+f(s) = -\sigma(s) + \int_0^L k(t,s) \,\sigma(t)\, {\rm d} t
 \end{align}
-with precision $\epsilon.$ Once these nodes and weights have been generated we proceed by enforcing equality of (\ref{eqn:numpreint}) at the discretization nodes, which yields the system of equations
+with precision $\epsilon.$ In other words, given $f(s_i),-\sigma(s_i) + \int_0^L k(t,s_i) \,\sigma(t)\, {\rm d} t,$ for $i=1,\dots,N,$ the values $f(s)$ and $-\sigma(s) + \int_0^L k(t,s) \,\sigma(t)\, {\rm d} t$ can be obtained for all $0 \le s \le L$ to within $\epsilon.$
+
+Once these nodes and weights have been generated we proceed by enforcing equality of (\ref{eqn:numpreint}) at the discretization nodes, which yields the system of equations
 \begin{align}
-f(s_i) \sqrt{w_i} = -\pi \sigma(s_i)\sqrt{w_i} +  \sqrt{w_i}\int_0^L K(\gamma(s_i),\gamma(t))\, \sigma(t)\,{\rm d}t,\quad i=1,\dots,N. \label{eqn_1std}
+f(s_i) \sqrt{w_i} = -\sigma(s_i)\sqrt{w_i} +  \sqrt{w_i}\int_0^L k(t,s_i)\, \sigma(t)\,{\rm d}t,\quad i=1,\dots,N. \label{eqn_1std}
 \end{align}
@@
 \begin{align}
-\left|\int_0^L K(\gamma(s_i),\gamma(t))\, \sigma(t)\,{\rm d}t- \sum_{j=1}^N W_{ij} \sigma_j\, \sqrt{w_j} \right| < \epsilon,
+\left|\int_0^L k(t,s_i)\, \sigma(t)\,{\rm d}t- \sum_{j=1}^N W_{ij} \sigma_j\, \sqrt{w_j} \right| < \epsilon,
 \end{align}
@@
 \begin{align}
-  -\pi \sigma_i +  \sum_{j=1}^N W_{ij} \sigma_j \sqrt{w_i w_j}=f(s_i) \sqrt{w_i},\quad i,j=1,\dots,N. 
+  -\sigma_i +  \sum_{j=1}^N W_{ij} \sigma_j \sqrt{w_i w_j}=f(s_i) \sqrt{w_i},\quad i,j=1,\dots,N. 
 \end{align}
@@
 \begin{definition}\label{def:seps}
-Let $S_\epsilon \subset L^2([0,L])$ denote the set of functions which can be interpolated from their values at the $N$ discretization nodes to any point in $[0,L]$ with an $L^2$ accuracy of $\epsilon.$ That is to say that for $f \in S_\epsilon$ if $\tilde{f}:[0,L] \to \mathbb{R}$ denotes the function obtained by interpolating using the values $f(s_1),\dots,f(s_N)$ then $\|f -\tilde{f}\|_{L^2} < \epsilon.$
+Let $S_\epsilon \subset L^2([0,L])$ denote the set of functions which can be interpolated from their values at the $N$ discretization nodes to any point in $[0,L]$ with a relative $L^2$ accuracy of $\epsilon.$ That is to say that for $f \in S_\epsilon$ if $\tilde{f}:[0,L] \to \mathbb{R}$ denotes the function obtained by interpolating using the values $f(s_1),\dots,f(s_N)$ then $\|f -\tilde{f}\|_{L^2} < \epsilon.$
 \end{definition}
@@
 Apart from posing certain numerical challenges, it also makes the task of finding suitable quadrature formulae difficult.
-Instead a different set of discretization nodes and a different set of quadrature nodes can be constructed for each angle, though this would significantly increase the precomputation cost.
+Instead, a different set of discretization nodes and a different set of quadrature nodes can be constructed for each angle, though this would significantly increase the precomputation cost.
 

### 2019-11-27 paper_lap/02mprelim.tex
updates

@@
 \subsection{Boundary value problems}
-Given a polygonal domain  $\Omega \subset \mathbb{R}^2$ with boundary $\Gamma$ and a function
+Given a polygonal domain  $\Omega \subset \mathbb{R}^2$ with boundary $\Gamma$ and outward-pointing 
+unit normal $\bnu: \Gamma \to S^1,$ as well as a function 
 $f: \Gamma \to \mathbb{R},$ we consider 
@@
 \nabla u(\bx)\cdot \bnu(\bx)  &= f(\bx), \hspace{0.45 cm} \bx \in \Gamma,\\
-\int_\Gamma f(\bx) {\rm d}s &= 0.
+\int_\Gamma f(\bx) {\rm d}S_{\bx} &= 0.
 \end{align}
@@
 \Delta u(\bx) &= 0, \hspace{1 cm} \bx \in \mathbb{R}^2\setminus\Omega,\\
-\nabla u(\gamma(t))\cdot \bnu(t)  &= f(t), \hspace{0.43 cm} t \in[0,L], \\
-\left|u(\bx) + \left(\frac{1}{2\pi} \int_{0}^{L} f(t) dt\right) \log{|\bx|}\right| &\to 0 , \hspace{0.4cm} |\bx| \to \infty.
-\end{align}
-
-\item The exterior Neumann problem for Helmholtz's equation:
-\begin{align}\label{eqn:BVPEDH}
-\Delta u(\bx) &= 0, \hspace{1 cm} x \in \mathbb{R}^2\setminus\Omega,\\
-\nabla u(\bx)\cdot \bnu(\bx)  &= f(\bx), \hspace{0.43 cm} t \in[0,L], \\
-\sqrt{|\bx|} \left|\partial_{|\bx|} u - i\omega u(\bx)\right| &\to 0 , \hspace{0.86cm} |\bx| \to \infty.
+\nabla u(\bx)\cdot \bnu(\bx)  &= f(\bx), \hspace{0.43 cm} \bx \in \Gamma, \\
+&\hspace{-2 cm}\left|u(\bx) + \left(\frac{1}{2\pi} \int_\Gamma f(\bx) {\rm d}S_{\bx}\right) \log{|\bx|}\right| \to 0 , \hspace{0.4cm} |\bx| \to \infty.
 \end{align}
@@
 \begin{remark}
-The existence and uniqueness of solutions to the above equations is a classical result. 
-The interior Dirichlet and Neumann problems for Helmholtz equation have a countable set of
-real $\omega$'s (which only accumulate at $\infty$)  for which the PDE has a non-unique solution. 
+The existence and uniqueness of the solutions to the above equations is a well-known result (see \cite{} for example). 
 \end{remark}

### 2019-11-27 paper_lap/03bvp.tex

@@
 \begin{definition}\label{def_layerpots}
-Given a density $\sigma:\Gamma \to \mathbb{R}$ the single-layer potential is defined by
+Given a function $\sigma:\Gamma \to \mathbb{R}$, the single-layer potential is defined by
 \beqn
@@
 \end{definition}
-
+In the following we will often refer to the function $\sigma$ as the {\it density} which generates the corresponding potential.
 \begin{definition}
@@
 \end{align}
-for some $\alpha >0.$ Then 
+for some $\alpha >0.$ Then {\color{red}for any continuous function $\sigma:\Gamma \to \mathbb{R},$}
 \begin{align}
 &\lim_{\bx \to \bx_0} \cS[\sigma](\bx) = \cS[\sigma](\bx_0)\\
-&\lim_{\bx \to \bx_0} \cD[\rho](\bx) = \cD[\rho](\bx_0)- \rho(\bx_0)\\
-&\lim_{\bx \to \bx_0} \left.\frac{{\rm d}}{{\rm d}\tau}\right|_{\tau= 0}\cS[\rho](\bx+\tau \bnu(\bx_0)) = \left.\frac{{\rm d}}{{\rm d}\tau}\right|_{\tau= 0}\cS[\rho](\bx_0+\tau \bnu(\bx_0))+ \rho(\bx_0).
+&\lim_{\bx \to \bx_0} \cD[\sigma](\bx) = \cD[\sigma](\bx_0)- \sigma(\bx_0)\\
+&\lim_{\bx \to \bx_0} \left.\frac{{\rm d}}{{\rm d}\tau}\right|_{\tau= 0}\cS[\sigma](\bx+\tau \bnu(\bx_0)) = \left.\frac{{\rm d}}{{\rm d}\tau}\right|_{\tau= 0}\cS[\sigma](\bx_0+\tau \bnu(\bx_0))+ \sigma(\bx_0).
 \end{align}
-Similarly, if $\bx$ approaches a point $\bx_0 = \gamma(t_0)$ from the outside then
+Similarly, if $\bx$ approaches a point $\bx_0 = \gamma(t_0)$ from the outside then for any continuous function $\sigma:\Gamma \to \mathbb{R},$
 \begin{align}
 &\lim_{\bx \to \bx_0} \cS[\sigma](\bx) = \cS[\sigma](\bx_0)\\
-&\lim_{\bx \to \bx_0} \cD[\rho](\bx) = \cD[\rho](\bx_0)+ \rho(\bx_0)\\
-&\lim_{\bx \to \bx_0} \left.\frac{{\rm d}}{{\rm d}\tau}\right|_{\tau= 0}\cS[\rho](\bx+\tau \bnu(\bx_0)) = \left.\frac{{\rm d}}{{\rm d}\tau}\right|_{\tau= 0}\cS[\rho](\bx_0+\tau \bnu(\bx_0))- \rho(\bx_0).
+&\lim_{\bx \to \bx_0} \cD[\sigma](\bx) = \cD[\sigma](\bx_0)+ \sigma(\bx_0)\\
+&\lim_{\bx \to \bx_0} \left.\frac{{\rm d}}{{\rm d}\tau}\right|_{\tau= 0}\cS[\sigma](\bx+\tau \bnu(\bx_0)) = \left.\frac{{\rm d}}{{\rm d}\tau}\right|_{\tau= 0}\cS[\sigma](\bx_0+\tau \bnu(\bx_0))- \sigma(\bx_0).
 \end{align}
@@
 
-We define the following operator which arises in the study of Neumann boundary value problems.
+Next we define the following operator which arises in the study of Neumann boundary value problems.
 \begin{definition}\label{def_singder}
@@
 \end{align}
-Moreover, the solution to the interior Dirichlet problem for Laplace's equation with boundary data $f$ is given by $u(\by) = \cD_{\omega}[\sigma](\by)$ for all $\by \in \Omega.$
+Moreover, the solution to the interior Dirichlet problem for Laplace's equation with boundary data $f$ is given by $u(\by) = \cD[\sigma](\by)$ for all $\by \in \Omega.$
 \end{theorem}
@@
 f(s)=  \sigma(s)+ \int_0^L (k(t,s) + 1)\,\sigma(t)\,{\rm d}t,
-\end{align}
+\end{align}\label{bie_extd}
 for all $s \in [0,L].$ 
-Moreover, the solution to the exterior Dirichlet problem for Laplace's equation with boundary data $f$ is given by $u(\by) = \cD_{0}[\sigma](\by) + \int_{0}^{L} \sigma(t) dt$
+Moreover, the solution to the exterior Dirichlet problem for Laplace's equation with boundary data $f$ is given by $u(\by) = \cD[\sigma](\by) + \int_{0}^{L} \sigma(t) dt$
 for all $\by \in \mathbb{R}^2 \setminus \Omega.$
@@
 \begin{theorem}[Interior Neumann problem for Laplace's equation]
-For every  $f:[0,L] \rightarrow \mathbb{C}$ in $L^{2}[0,L]$ such that $\int_{0}^{L} f(t) = 0,$ \, there exists a unique $\rho \in L^{2}[0,L]$ which satisfies
+For every  $f:[0,L] \rightarrow \mathbb{C}$ in $L^{2}[0,L]$ such that $\int_{0}^{L} f(t) = 0,$ there exists a unique $\sigma \in L^{2}[0,L]$ which satisfies
 \begin{align}
-f(s)=  \rho(s)+ \int_0^L (k(s,t) + 1)\,\sigma(t)\,{\rm d}t,
+f(s)=  \sigma(s)+ \int_0^L (k(s,t) + 1)\,\sigma(t)\,{\rm d}t,
 \label{bie_intn}
 \end{align}
-Moreover, the solution to the interior Neumann problem for Laplace's equation with boundary data $f$ is given by $u(\by) = \cS_{0}[\rho](\by)$ for all $\by \in \Omega.$
+Moreover, the solution to the interior Neumann problem for Laplace's equation with boundary data $f$ is given by $u(\by) = \cS[\sigma](\by)$ for all $\by \in \Omega.$
 \end{theorem}
@@
 \begin{theorem}[Exterior Neumann problem for Laplace's equation]
-For every $f:[0,L] \rightarrow \mathbb{C}$ in $L^{2}[0,L]$ there exists a unique $\rho \in L^{2}[0,L]$ which satisfies
+For every $f:[0,L] \rightarrow \mathbb{C}$ in $L^{2}[0,L]$ there exists a unique $\sigma \in L^{2}[0,L]$ which satisfies
 \begin{align}
-f(s)=  \rho(s)+ \int_0^L k_{\omega}(s,t) \,\sigma(t)\,{\rm d}t,
+f(s)=  \sigma(s)+ \int_0^L k(s,t) \,\sigma(t)\,{\rm d}t,
 \label{bie_extn}
 \end{align}
-Moreover, the solution to the interior Neumann problem for Laplace'sequation with boundary data $f$ is given by $u(\by) = \cS_{\omega}[\rho](\by)$ for all $\by \in \Omega.$
+Moreover, the solution to the interior Neumann problem for Laplace's equation with boundary data $f$ is given by $u(\by) = \cS[\sigma](\by)$ for all $\by \in \Omega.$
 \end{theorem}
@@
 In the remainder of this section we assume $\Gamma$ is an open wedge with sides of length one and interior angle $\pi \alpha$ with $0 <\alpha<2.$ Let $\gamma:[-1,1] \rightarrow \Gamma$ be an arc length parametrization of $\Gamma$ and $\nu:[-1,1] \rightarrow \mathbb{R}^2$ be the inward-pointing normal to $\Gamma.$
-The following theorem  gives an explicit representation of solutions near corners.
+The following theorem  gives an explicit representation of the solutions of the boundary integral equation (\ref{bie_intd}) in this geometry.
 
@@
 \end{align}
-Suppose further that $\rho$ is defined via the formula
+Suppose further that $\sigma$ is defined via the formula
 \begin{align}
-\rho(t) =& b_0+\sum_{i=1}^{\overline{L}} b_i |t|^{\frac{2i-1}{\alpha}}+\sum_{i=1}^{\underline{M}} b_{\overline{L}+i} |t|^\frac{2i}{2-\alpha}\left(\log|t|\right)^{\sigma_{N,\alpha}(i)}\nonumber\\
+\sigma(t) =& b_0+\sum_{i=1}^{\overline{L}} b_i |t|^{\frac{2i-1}{\alpha}}+\sum_{i=1}^{\underline{M}} b_{\overline{L}+i} |t|^\frac{2i}{2-\alpha}\left(\log|t|\right)^{\sigma_{N,\alpha}(i)}\nonumber\\
 &+\sum_{i=1}^{\overline{M}}c_i \sgn(t) |t|^\frac{2i-1}{2-\alpha}+\sum_{i=1}^{\underline{L}}c_{\overline{M}+i} \sgn(t) |t|^\frac{2i}{\alpha}\left(\log|t|\right)^{\nu_{N,\alpha}(i)}\label{eqn_rhfm}
@@
 \end{align}
-\noindent If $g$ is defined by
+\noindent If $f$ is defined by
 \begin{align}
-f(t) = \rho(s) +\int_{-1}^1 k(t,s)  \rho(t)\,{\rm d}t.
+f(t) = -\sigma(s) +\int_{-1}^1 k(t,s)  \sigma(t)\,{\rm d}t.
 \label{eqn_grho}
 \end{align}
-then there exist sequences of real numbers $\beta_0$, $\beta_1,\,\dots$ and $\gamma_0,$ $\gamma_1,\,\dots$ such that
+and $\sigma$ is defined by (\ref{eqn_rhfm}) then there exist two sequences of real numbers $\beta_0$, $\beta_1,\,\dots$ and $\gamma_0,$ $\gamma_1,\,\dots$ such that
 \begin{align}
@@
 \end{theorem}
+{\color{red}CHECK THE POWERS}
+
 \begin{remark1}
-A similar result holds for the case where the identity term in (\ref{eqn_grho}) is replaced by its negative; the change in sign corresponds to replacing the boundary integral equation for the exterior Dirichlet problem with the boundary integral equation corresponding to interior Dirichlet problem.
+A similar result holds for the case where the identity term in (\ref{eqn_grho}) is replaced by its negative; the change in sign corresponds to replacing the boundary integral equation for the interior Dirichlet problem with the boundary integral equation corresponding to exterior Dirichlet problem.
 Similar expansions also hold for both the exterior and interior Neumann problems, in which case the singular powers are obtained by subtracting one from the singular powers arising in the Dirichlet problem.

### 2019-11-27 paper_lap/05apparatus.tex

@@
 \begin{remark1}
-We observe that if the solution to the boundary value problem is being calculated at a point $\by \in \mathbb{R}^2\setminus \Omega$ more than a panel length away from the boundary curve $\Gamma$ then the Neumann density $\sigma$ obtained using the above result will give an accuracy of $\epsilon,$ ie.
+We observe that if the solution to the boundary value problem is being calculated at a point $\by \in \mathbb{R}^2\setminus \Omega$ more than {\color{red}two panel lengths} away from the boundary curve $\Gamma$ then the Neumann density $\sigma$ obtained using the above result will give an accuracy of $\epsilon,$ ie.
 the function $K(\by,\gamma(t)) \in S_\epsilon.$ Thus accurate values of the solution in the far-field can be obtained almost immediately.
@@
 Typically we use 16th order Gauss-Legendre panels and choose their sizes so that their length is no more than their distance to the nearest corner.
+{\color{red}This latter choice guarantees that for any $\epsilon>0$ there exists an $M$ such that if the Gauss-Legendre panels are discretized using an $M$-point Gauss-Legendre rule then the density on that panel can be interpolated to relative precision $\epsilon$ in an $L^2$-sense.}
 
@@
 Suppose that $f$ be a piecewise-analytic function in $S_\epsilon$ and  $\underline{\sigma} = (A^T)^{-1} {\bf f}$ is the approximation to the Neumann density obtained using the adjoint of the discretization for the interior Dirichlet boundary integral equation.
+Further suppose that the discretization nodes are ordered so that $s_1,\dots,s_P$ correspond to the corner panel associated with the interval $(-\delta,\delta),$ $s_{P+1},\dots,s_{P+M}$ correspond to the Gauss-Legendre panel immediately to the left associated with the interval $(-2\delta,-\delta),$ and $s_{P+M+1},\dots,s_{P+2M}$ to the Gauss-Legendre panel immediately to the right associated with the interval $(\delta,2\delta).$
 Then
 \begin{align}
-h(t) = \sum_{i=P+1}^N k(t,s_i) \sqrt{w_i} \,\underline{\sigma}_i
+h(t) = \sum_{i=P+2M+1}^N k(s_i,t) \sqrt{w_i} \,\underline{\sigma}_i
 \end{align}
-is an analytic function of $t$ for all $t \in (-\delta,\delta),$ assuming that $s_1,\dots,s_P$ correspond to the discretization of $(-\delta,\delta)$ with the corner point corresponding to $t=0.$
+is an analytic function of $t$ for all $t \in (-2\delta,2\delta).$
 \end{proposition}
@@
 \begin{align}\label{eqn:resolve_neum0}
--\sigma(s) + \int_{-\delta}^\delta k(s,t) \sigma(t)\,{\rm d}t = f(s)-h(s), \quad -\delta \le s \le \delta.
+-\sigma(s) + \int_{-2\delta}^{2\delta} k(s,t) \sigma(t)\,{\rm d}t = f(s)-h(s), \quad -2\delta \le s \le 2\delta.
 \end{align}
-We note that the solution to (\ref{eqn:resolve_neum0}) is equal to the solution of the original boundary integral equation (\ref{bie_extn}) restricted to the interval $[-\delta,\delta].$ Taking the adjoint of (\ref{eqn:resolve_neum0}) we obtain
+We note that the solution to (\ref{eqn:resolve_neum0}) is equal to the solution of the original boundary integral equation (\ref{bie_extn}) restricted to the interval $[-2\delta,2\delta].$ Taking the adjoint of (\ref{eqn:resolve_neum0}) we obtain
 \begin{align}\label{eqn:resolve_diri0}
--\sigma(s) + \int_{-\delta}^\delta k(t,s) \sigma(t)\,{\rm d}t = f(s)-h(s), \quad -\delta \le s \le \delta.
+-\sigma(s) + \int_{-2\delta}^{2\delta} k(t,s) \sigma(t)\,{\rm d}t = f(s)-h(s), \quad -2\delta \le s \le 2\delta.
 \end{align}
@@
 Specifically, we subdivide the interval $[-\delta,\delta]$ into three subintervals $I_0 = [-\delta,\delta/2],$ $L_0 = [-\delta/2,\delta/2],$ and $J_0 = [\delta/2,\delta].$ On $I_0$ and $J_0$ we place standard Gauss-Legendre discretization nodes, while on $L_0$ we use the custom discretization scheme for corners, outlined in Section \ref{sec:disc_dir} (see \cite{} for a detailed description of the method).
+On the intervals $[-2\delta,-\delta]$ and $[\delta,2\delta]$ we use the same discretization nodes and weights as in the original system for those intervals (we call these panels $K_0$ and $Q_0$ respectively).
 Let $\underline{f}_0$ denote the right-hand side of (\ref{eqn:resolve_neum0}) evaluated at these discretization nodes and scaled by the square roots of the corresponding weights.
@@
 then $\underline{\sigma}_0$ gives a {weak solution} to the integral equation (\ref{eqn:resolve_neum0}), i.e.
-for any function $g$ which is analytic on $[-\delta,0]$ and $[0,\delta]$ the inner product $\langle g,\sigma \rangle$ can be calculated to precision $\epsilon$ using the solution $\underline{\sigma}_0.$ Moreover, since the true density $\sigma$ is smooth on $I_0$ and $J_0$ the Gauss-Legendre discretization allows accurate interpolation of the density on those regions.
+for any function $g$ which is analytic on $[-2\delta,0]$ and $[0,2\delta]$ the inner product $\langle g,\sigma \rangle$ can be calculated to precision $\epsilon$ using the solution $\underline{\sigma}_0.$ Moreover, since the true density $\sigma$ is smooth on $[\delta,2\delta]$ and $[-2\delta,-\delta]$ the Gauss-Legendre discretization allows accurate interpolation of the density on those regions.
 
@@
 \begin{proof}
-We begin by observing that both $f$ and $h$ are analytic on the interval $(-\delta,\delta).$ In particular, they can be accurately interpolated using $\phi_1,\dots,\phi_P$ on the interval $(-\delta,\delta).$ In particular,
+We begin by observing that both $f$ and $h$ are analytic on the interval $(-\delta,\delta).$ In particular, they can be accurately interpolated using $\phi_1,\dots,\phi_P$ on the interval $(-\delta,\delta).$ Hence,
 \begin{align}\label{eqn:approx_thm}
-f(t)-h(t) \approx w(t) U^{-1} (f(s_1)-h(s_1),\dots,f(s_P)-h(s_P))^T
+f(t)-h(t) \approx w(t) U^{-1} (f(s_1)-h(s_1),\dots,f(s_P)-h(s_P))^T.
 \end{align}
+{\color{red}A similar argument shows that $f(t)-h(t)$ is interpolable on $[-2\delta,-\delta]$ and $[\delta,2\delta].$}
 On the other hand, by construction,
 \begin{align}\label{eqn:linalg_thm}
-\underline{f} = A^T \begin{pmatrix}\tilde{\sigma}\\ \sigma_{P+1}\\ \vdots\\ \sigma_N\end{pmatrix}.
+\underline{f} = A^T \begin{pmatrix}\tilde{\sigma}\\ \sigma_{P+{2M+1}}\\ \vdots\\ \sigma_N\end{pmatrix}.
 \end{align}
-Let $A_0$ be the $P\times P$ submatrix of $A$ corresponding to the first $P$ rows and columns of $A,$ and $A_{\rm red}$ be the $P \times (N-P)$  submatrix of $A$ corresponding to selecting the first $P$ rows of $A$ and all but the first $P$ columns of $A.$ Using this notation, the first $P$ rows of (\ref{eqn:linalg_thm}) can be re-written as
+Let $A_0$ be the $(P+2M)\times (P+2M)$ submatrix of $A$ corresponding to the first $P+2M$ rows and columns of $A,$ and $A_{\rm red}$ be the $P+2M \times (N-P-2M)$  submatrix of $A$ corresponding to selecting the first $P+2M$ rows of $A$ and all but the first $P+2M$ columns of $A.$ Using this notation, the first $P+2M$ rows of (\ref{eqn:linalg_thm}) can be re-written as
 \begin{align}
-\begin{pmatrix}f_1\\\vdots \\ f_P\end{pmatrix}  = A_{\rm red}^T \begin{pmatrix} \sigma_{P+1}\\ \vdots\\ \sigma_N\end{pmatrix} + A_0^T \tilde{\sigma}.
+\begin{pmatrix}f_1\\\vdots \\ f_{P+2M}\end{pmatrix}  = A_{\rm red}^T \begin{pmatrix} \sigma_{P+2M+1}\\ \vdots\\ \sigma_N\end{pmatrix} + A_0^T \tilde{\sigma}.
 \end{align}
-The first term on the right-hand side is $(h(s_1),\dots,h(s_P))^T.$ Substituting this into the previous equation, we obtain
+The first term on the right-hand side is $(h(s_1),\dots,h(s_{P+2M}))^T.$ Substituting this into the previous equation, we obtain
 \begin{align}
-(f(s_1)-h(s_1),\dots,f(s_P)-h(s_P))^T = A_0^T \tilde{\sigma}.
+(f(s_1)-h(s_1),\dots,f(s_{P+2M})-h(s_{P+2M}))^T = A_0^T \tilde{\sigma}.
 \end{align}
@@
 
-This can be iterated to obtain an interpolable approximation to the density on $L_0 = [-\delta/2,\delta/2].$ In particular, we consider the restriction of the exterior Neumann integral equation, as well as its, adjoint to the interval $L_0.$ For the right-hand side we use the original right-hand side $f$ minus the contribution from the remainder of the domain.
+This can be iterated to obtain an interpolable approximation to the density on $L_0 = [-\delta,\delta].$ In particular, we consider the restriction of the exterior Neumann integral equation, as well as its, adjoint to the interval $I_0$ and $J_0.$ For the right-hand side we use the original right-hand side $f$ minus the contribution from the remainder of the domain.
 In particular, if we define
 \begin{align}
-h_1(s) = \sum_{x_i \in I_0,J_0} k(s,x_i) \sigma_0^{(i)} \sqrt{w_i}
+h_1(s) = \sum_{x_i \in K_0,Q_0} k(s,x_i) \sigma_0^{(i)} \sqrt{w_i}
 \end{align}
-then $\sigma$ restricted to the interval $L_0$ satisfies
+then $\sigma$ restricted to the interval $I_0\cup L_0 \cup J_0$ satisfies
 \begin{align}\label{eqn:resolve_neum1}
--\sigma(s) + \int_{-\delta/2}^{\delta/2} k(s,t) \sigma(t)\,{\rm d} t = f(s)-h(s)-h_1(s), \quad -\delta/2 \le s \le \delta/2.
+-\sigma(s) + \int_{-\delta}^{\delta} k(s,t) \sigma(t)\,{\rm d} t = f(s)-h(s)-h_1(s), \quad -\delta \le s \le \delta.
 \end{align}
@@
 \begin{align}\label{eqn:resolve_diri1}
--\sigma(s) + \int_{-\delta/2}^{\delta/2} k(t,s) \sigma(t)\,{\rm d} t = f(s)-h(s)-h_1(s), \quad -\delta/2 \le s \le \delta/2.
+-\sigma(s) + \int_{-\delta}^{\delta} k(t,s) \sigma(t)\,{\rm d} t = f(s)-h(s)-h_1(s), \quad -\delta \le s \le \delta.
 \end{align}
@@
 Once again, we divide $L_0$ into three intervals $I_1,$ $L_1,$ and $J_1$ and discretize each interval as before.
-After solving the corresponding discretization of (\ref{eqn:resolve_neum1}) using the adjoint of the discretization of the integral operator appearing in (\ref{eqn:resolve_diri1}) we obtain a weak solution of $\sigma$ on the interval $L_0$ which can be interpolated on $I_1,$ and $J_1$ to within precision $\epsilon.$
+After solving the corresponding discretization of (\ref{eqn:resolve_neum1}) using the adjoint of the discretization of the integral operator appearing in (\ref{eqn:resolve_diri1}) we obtain a weak solution of $\sigma$ on the interval $I_0\cup L_0 \cup J_0$ which can be interpolated on $I_0,$ and $J_0$ to within precision $\epsilon.$
 

### 2019-11-27 examples/helm_poly_solver.f
small changes to helm_poly_solver

@@ -349,7 +349,8 @@ c
        allocate(ts(ncorner),wts(ncorner),umatt(ncorner,ncorner))
        allocate(vmatt(ncorner,ncorner))
 
-       itype = 1
+
+       itype = 2
        call lapdisc(ts,wts,umatt,vmatt,ncorner,itype)
 
        ipan = 0
@@ -680,7 +681,6 @@ c
  1500 format(i8)
         
         read(isvd,1500) keep
-        call prinf('keep = *',keep,1)
         call laparrread(isvd,coefs,keep)
 
         ifirst = 0
@@ -11894,7 +11894,7 @@ c
         implicit real *8 (a-h,o-z)
         real *8, allocatable :: rquads(:),wquads(:),work(:)
         real *8 x0s(nr0),w0s(nr0),u(nr0,nr0),v(nr0,nr0)
-        real *8 akern(nr0,nr0),coefs(ncoefs)
+        real *8 akern(nr0,nr0),coefs(lcoefs)
 
         allocate(work(20000),rquads(1000),wquads(1000))
 

### 2019-11-28 examples/helm_poly_solver.f
poly solver with fmm

@@ -1,11 +1,14 @@
       implicit real *8 (a-h,o-z)
       real *8, allocatable :: verts(:,:)
       real *8 xyin(2),xyout(2),dpars(2)
-      complex *16 zpars,zk
+      real *8 xysrc(2),xytarg(2)
+      complex *16 zpars,zk,pot,potex
 
       character *100 fname
 
-      external helm_slp
+      procedure (), pointer :: fker
+
+      external helm_slp,helm_dlp
 
       call prini(6,13)
 
@@ -64,21 +67,99 @@ c          iffast = 1 => iterative solver using blas for matvec
 c          iffast = 2 => iterative solver using fmm for matvec
 c          
  
-      ifdn = 1 
+      ifdn = 0 
       ifinout = 0
-      iffast = 0
+      iffast = 2
 
-      zk = 2.1d0
+      zk = 1.1d0
 
       ifwrite = 1
       fname = 'equi_interior_test.dat'
 
-      call helm_solver(zk,nverts,verts,ifdn,ifinout,iffast,fker,
-     1   dpars,zpars,ipars,ntarg,xyin,pot,ifwrite,fname)
+      if(ifinout.eq.0) then
+        xysrc(1) = xyout(1)
+        xysrc(2) = xyout(2)
 
+        xytarg(1) = xyin(1)
+        xytarg(2) = xyin(2)
+      endif
+
+      if(ifinout.eq.1) then
+        xysrc(1) = xyin(1)
+        xysrc(2) = xyin(2)
+        
+        xytarg(1) = xyout(1)
+        xytarg(2) = xyout(2)
+      endif
+
+
+
+      if(ifdn.eq.0) fker => helm_slp
+      if(ifdn.eq.1) fker => helm_dlp
+
+      
+
+      ntarg = 1
+
+      call helm_solver(zk,nverts,verts,ifdn,ifinout,iffast,fker,
+     1   xysrc,zk,ipars,ntarg,xytarg,pot,ifwrite,fname)
+
+      call helm_slp(xysrc,xytarg,zk,ipars,potex)
+      
+      erra = abs(pot-potex)/abs(potex)
+      call prin2('error in potential=*',erra,1)
       
       stop
       end
+
+c
+c
+c 
+c
+      subroutine helm_slp(y,x,zk,ipars,f)
+      implicit real *8 (a-h,o-z)
+      real *8 y(*),x(*)
[…]

### 2019-11-28 src/cgmres_blas.f

@@ -1,0 +1,276 @@
+ccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccc
+c
+c       This is the end of the debugging routines and the beginning 
+c       of the complex GMRES routines
+c
+ccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccc
+c
+c
+c
+c
+c
+        subroutine cgmres_blas(ier,n,a,multa,ift,y,eps,numit,
+     1     x,niter,errs,ngmrec,w)
+        implicit real *8 (a-h,o-z)
+        dimension errs(1)
+        complex *16 a(n,n),x(1),y(1),w(1)
+c
+        external multa
+c
+c     This subroutine solves a complex linear system Ax=y by means
+c     of GMRES algorithm. This is a memory management routine for 
+c     cgmres1 which performs the actual work.
+c
+c     Input parameters:
+c
+c     n - the dimensionality of the linear system
+c     y - the right hand side
+c     a - the matrix of the system (or whatever other parameter)
+c     eps - the required accuracy
+c     multa - the user-defined matrix-vector multiplication subroutine
+c
+c     the calling sequence for multa must be
+c
+c     multa(a,x,y,n,ift)               (1)
+c
+c       in (1), a is a matrix the system or whatever other parameter,
+c       par1, par2 are whatever other parameters, x is an input vector,
+c       y is a product Ax, and n is the dimensionality of a, x, and y.
+c
+c     numit - the maximum number of iteration permitted
+c     ngmrec - the maximum number of iteration 
+c            which GMRES algorithm needs to be restarted
+c
+c     w - must be at least (ngmrec*2+4)*n complex *16 elements long
+c
+c     Output parameters:
+c
+c     ier - error return code
+c        ier=0 normal execution of the subroutine
+c        ier=4 means that the maximum number iterations numit
+c           has been reached without achieving the required accuracy eps
+c        ier=8 means that the errors failed to decrease before the maximum
[…]

### 2019-11-28 src/cgmres_fmm.f

@@ -1,0 +1,313 @@
+ccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccc
+c
+c       This is the end of the debugging routines and the beginning 
+c       of the complex GMRES routines
+c
+ccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccc
+c
+c
+c
+c
+c
+        subroutine cgmres_fmm(ier,n,multa,zk,ifdn,ifinout,
+     1     xys,dxys,qwts,nedges,ncint,lns,rns,icl,icr,icsgnl,icsgnr,
+     2     xsgnl,xsgnr,ncorner,xmatc,xmatcsub,y,eps,numit,
+     1     x,niter,errs,ngmrec,w)
+        implicit real *8 (a-h,o-z)
+        dimension errs(1)
+        complex *16 x(1),y(1),w(1)
+
+        real *8 xys(2,n),dxys(2,n),qwts(n)
+        integer ncint,nedges
+        integer lns(nedges),rns(nedges),icl(ncint),icr(ncint)
+        integer icsgnl(ncint),icsgnr(ncint)
+        integer ncorner
+        real *8 xsgnl(ncint),xsgnr(ncint)
+        complex *16 xmatc(ncorner,ncorner,ncint)
+        complex *16 xmatcsub(ncorner,ncorner,ncint)
+        complex *16 zk
+        
+        
+c
+        external multa
+c
+c     This subroutine solves a complex linear system Ax=y by means
+c     of GMRES algorithm. This is a memory management routine for 
+c     cgmres1 which performs the actual work.
+c
+c     Input parameters:
+c
+c     n - the dimensionality of the linear system
+c     y - the right hand side
+c     a - the matrix of the system (or whatever other parameter)
+c     eps - the required accuracy
+c     multa - the user-defined matrix-vector multiplication subroutine
+c
+c     the calling sequence for multa must be
+c
+c     multa(x,y,n,ifdn,ifinout,xys,dxys,qwts,nedges,ncint,
+c         lns,rns,icl,icr,icsgnl,icsgnr,xsgnl,xsgnr,ncorner,
+c         xmatc)
+c
+c       in (1), a is a matrix the system or whatever other parameter,
[…]

### 2019-11-28 src/h2dterms.f

@@ -1,0 +1,562 @@
+cc Copyright (C) 2009: Leslie Greengard and Zydrunas Gimbutas
+cc Contact: greengard@cims.nyu.edu
+cc 
+cc This program is free software; you can redistribute it and/or modify 
+cc it under the terms of the GNU General Public License as published by 
+cc the Free Software Foundation; either version 2 of the License, or 
+cc (at your option) any later version.  This program is distributed in 
+cc the hope that it will be useful, but WITHOUT ANY WARRANTY; without 
+cc even the implied warranty of MERCHANTABILITY or FITNESS FOR A 
+cc PARTICULAR PURPOSE.  See the GNU General Public License for more 
+cc details. You should have received a copy of the GNU General Public 
+cc License along with this program; 
+cc if not, see <http://www.gnu.org/licenses/>.
+ccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccc
+c
+c    $Date: 2011-02-22 17:34:23 -0500 (Tue, 22 Feb 2011) $
+c    $Revision: 1670 $
+c
+c
+c-----------------------------------------------------------------------------
+c
+c      h2dterms - determine number of terms in mpole expansions for box
+c           of size "bsize" with Helmholtz parameter zk.
+c
+c      h2dterms_list2 - build the number of terms table for all boxes 
+c           in list 2
+c
+c      h2dterms_list2e - build the number of terms table for all boxes 
+c           in extended list 2
+c
+c-----------------------------------------------------------------------------
+c
+c
+c
+      subroutine h2dterms(bsize, zk, eps, nterms, ier)
+      implicit real *8 (a-h,o-z)
+c
+c     Determine number of terms in mpole expansions for box of size
+c     "bsize" with Helmholtz parameter zk.
+c
+c     The method is based on examining the decay of H_n * J_n.
+c
+c     Maximum number of terms is 10000, which 
+c     works for boxes up to 1000 wavelengths in size     
+c
[…]

### 2019-11-28 src/hfmm2dpart.f

@@ -1,0 +1,1543 @@
+cc Copyright (C) 2010-2011: Leslie Greengard, Zydrunas Gimbustas 
+cc and Manas Rachh
+cc Contact: greengard@cims.nyu.edu
+cc 
+cc This program is free software; you can redistribute it and/or modify 
+cc it under the terms of the GNU General Public License as published by 
+cc the Free Software Foundation; either version 2 of the License, or 
+cc (at your option) any later version.  This program is distributed in 
+cc the hope that it will be useful, but WITHOUT ANY WARRANTY; without 
+cc even the implied warranty of MERCHANTABILITY or FITNESS FOR A 
+cc PARTICULAR PURPOSE.  See the GNU General Public License for more 
+cc details. You should have received a copy of the GNU General Public 
+cc License along with this program; 
+cc if not, see <http://www.gnu.org/licenses/>.
+
+
+
+c       
+c   Helmholtz FMM in R^2: evaluate all pairwise particle
+c   interactions (ignoring self-interaction) 
+c   and interactions with targets.
+c
+c   We use H_0(kr)*(i/4) for the Green's function.
+c   Self-interactions are not included
+c
+c   h2d: charge and dipstr are complex valued, x in \R^2
+c
+c   \phi(x_i) = (i/4)\sum_{j\ne i} charge_j H^{(1)}_0(k |x_i - x_j|)
+c   + dipstr_j (dipvec_j \dot (x_i - x_j)) H^{(1)}_1(k |x_i - x_j|*
+c                                          k/|x_i-x_j|
+c
+c
+
+      subroutine hfmm2dpartstostcp(eps,zk,ns,sources,
+     1            charge,pot,nt,targ,pottarg)
+c----------------------------------------------
+c   INPUT PARAMETERS:
+c   eps           : FMM precision requested
+c   zk            : Helmholtz parameter
+c   ns            : number of sources
+c   sources(2,ns) : source locations
+c   charge(ns)    : charge strengths
+c   nt            : number of targets
+c   targ(2,nt)    : target locations
+c
+c   OUTPUT PARAMETERS
+c   pot(ns)       : potential at the source locations
+c   pottarg(nt)   : potential at the target locations
+c
+
+
+      implicit none
+c
+cc      calling sequence variables
+c  
+      real *8 eps
+      complex *16 zk
[…]

### 2019-11-28 src/levrtree2d.f

@@ -1,0 +1,3275 @@
+c
+c     d2hplratree.f - hung pruned level restricted adaptive
+c                     tree
+c     radsrc parameter (preventing sources with large radius 
+c                         from being pushed to the finest level)
+c     radexp parameter (preventing exp centers with large radius 
+c                         from being pushed to the finest level)
+c     ndiv parameter (usual refinement parameter extending tree
+c                         depth until all leaf nodes hanve fewer than
+c                         ndiv particles)
+c     idivflag       (allows use of ndiv parameter for sources OR
+c                         targets OR sources+targets OR sources+targets
+c                         + expansion centers)
+c
+c     We first create a fully adaptive tree and then 
+c     use the fix tree algorithm to make it a level restricted
+c     tree. This algorithm is discussed in depth in Frank Ethridge's
+c     thesis
+c
+c     This tree code MUST be used along with its memory code
+c     maketreemem located at the end of this file. The memory
+c     code precomputes the number of levels, the number of
+c     boxes, the max number of hung sources and the length
+c     of the tree.
+c
+      subroutine maketree2d(src,ns,radsrc,trg,nt,expc,nexpc,
+     $                   radexp,idivflag,ndiv,
+     $                   mhung,nlevels,nboxes,
+     $                   centers,boxsize,itree,ltree,
+     $                   ipointer,mnlist1,mnlist2,mnlist3,mnlist4)
+      implicit none
+      integer ns,nt,nexpc,idivflag,ndiv,isep,mhung
+      integer nlevels,lcenters,ltree
+      integer nlmax,nbmax,nboxes, nlevtmp,nbtmp, mhungtmp
+      integer itree(ltree)
+      integer i,j
+      integer, allocatable :: laddr(:,:)
+      integer, allocatable :: ilevel(:)
+      integer, allocatable :: iparenttemp(:)
+      integer, allocatable :: nchild(:)
+      integer, allocatable :: ichildtemp(:,:)
+      integer, allocatable :: nnbors(:)
+      integer, allocatable :: nbors(:,:)
+      integer, allocatable :: isourcetemp(:)
+      integer, allocatable :: itargettemp(:)
+      integer, allocatable :: iexpctemp(:)
+      integer, allocatable :: ihsfirsttemp(:)
+      integer, allocatable :: ihslasttemp(:)
+      integer, allocatable :: isfirsttemp(:)
+      integer, allocatable :: islasttemp(:)
+      integer, allocatable :: itfirsttemp(:)
[…]

### 2019-11-28 examples/helm_dir2.f
updating helm solver

@@ -171,7 +171,7 @@ c
 
        k = 16
        zk = 33.1d0
-cc        zk = 1.1d0
+        zk = 1.1d0
 c
 c        read svd coefs
 c
@@ -213,11 +213,11 @@ c
        verts(1,1) = 0
        verts(2,1) = 0
 
-       verts(1,2) = sqrt(done*3)/2 + 0.1d0
-       verts(2,2) = -done/2
+       verts(1,2) = 0.5d0
+       verts(2,2) = -sqrt(3.0d0)/2-0.1d0
 
-       verts(1,3) = sqrt(done*3)/2
-       verts(2,3) = done/2-0.19d0
+       verts(1,3) = 0.57d0
+       verts(2,3) = sqrt(3.0d0)/2.0d0 
 
 c
 ccc     declare edges
@@ -291,6 +291,20 @@ c             panels
          n = n + imid(i)*kmid + 2*ncorner
          n2 = n2 + imid(i)*kmid + 2*ncorner2
        enddo
+
+       call prinf('imid=*',imid,1)
+
+cc       imid(1) = 3
+cc       imid(2) = 5
+cc       imid(3) = 3
+
+       pl(1) = 0.155516076339393d0
+       pl(3) = pl(1)
+       pl(2) = 0.163162846006773d0
+
+       pr(1) = pl(2)
+       pr(2) = pl(1)
+       pr(3) = pl(1)
 
        allocate(xs_ref(nref),ys_ref(nref),rnx_ref(nref))
        allocate(rny_ref(nref),rkappa_ref(nref),qwts_ref(nref))
@@ -454,19 +468,19 @@ c
       allocate(alpha(ncint),xsgnl(ncint),xsgnr(ncint))
       allocate(ixmatc(ncint))
       icl(1) = 1
-      icr(1) = 3
-      icsgnl(1) = 0
-      icsgnr(1) = 1
+      icr(1) = 2
+      icsgnl(1) = 1
+      icsgnr(1) = 0
 
 
-      icl(2) = 1
-      icr(2) = 2
+      icl(2) = 2
+      icr(2) = 3
       icsgnl(2) = 1
       icsgnr(2) = 0
 
 
-      icl(3) = 2
-      icr(3) = 3
+      icl(3) = 3
+      icr(3) = 1
       icsgnl(3) = 1
       icsgnr(3) = 0
 
@@ -539,22 +553,30 @@ c
         drp = drp/(dr1*dr2)
[…]

### 2019-11-28 examples/helm_poly_solver.f

@@ -67,7 +67,7 @@ c          iffast = 1 => iterative solver using blas for matvec
 c          iffast = 2 => iterative solver using fmm for matvec
 c          
  
-      ifdn = 0 
+      ifdn = 1 
       ifinout = 0
       iffast = 2
 
@@ -513,14 +513,10 @@ c
         allocate(errs(numit+10),work((ngmrec*10+4)*npts))
         allocate(xmatcsub(ncorner,ncorner,ncint))
 
-        call prin2('tsc=*',tsc,ncorner)
-        call prin2('wtsc=*',wtsc,ncorner)
 
         do i=1,ncint
           call helmcornmatsub(angs(i),zk,pl(i),tsc,wtsc,ncorner,
      1      xmatcsub(1,1,i))
-          call prin2('xmatcsub=*',xmatcsub(1,1,i),24)
-          call prin2('xmatc=*',xmatc(1,1,i),24)
         enddo
 
 
@@ -536,8 +532,6 @@ c
      1   ncint,lns,rns,icl,icr,icsgnl,icsgnr,xsgnl,xsgnr,ncorner,
      2   xmatc,xmatcsub)
 
-        call prin2('soln=*',soln,24)
-        call prin2('solntmp=*',solntmp,24)
 
         ra = 0
         erra = 0
@@ -549,6 +543,7 @@ c
 
         erra = sqrt(erra/ra)
         call prin2('error in two matvec routines=*',erra,1)
+
        
 
         
@@ -686,13 +681,6 @@ c
         grad(2,i) = 0
       enddo
 
-      call prin2('charges=*',charges,24)
-      call prin2('dipstr=*',dipstr,24)
-      call prin2('dipvec=*',dipvec,24)
-
-
-
-
       nd = 1
       eps = 1.0d-15
       nt = 0
@@ -710,8 +698,6 @@ c
         do i=1,n
           pot(i) = pot(i)*sqrt(qwts(i))
         enddo
-
-        call prin2('pot=*',pot,2*n)
 
         do icint=1,ncint
           
@@ -747,7 +733,6 @@ c
             pot(ipts2+i-1) = pot(ipts2+i-1) + pottmp*xsgnr(icint)
           enddo
         enddo
-cc        call prin2('pot=*',pot,2*n)
 
         do i=1,n
           y(i) = pot(i) -0.5d0*(-1)**(ifdn+ifinout)*x(i) 
[…]

### 2019-11-28 examples/helm_poly_solver.f
adding volume plotting capabilities

@@ -2,6 +2,10 @@
       real *8, allocatable :: verts(:,:)
       real *8 xyin(2),xyout(2),dpars(2)
       real *8 xysrc(2),xytarg(2)
+      real *8, allocatable :: targ(:,:)
+      complex *16, allocatable :: pottargex(:)
+      integer, allocatable :: isin(:)
+      
       complex *16 zpars,zk,pot,potex
 
       character *100 fname
@@ -46,11 +50,12 @@ c      line 2: n - number of discretization points
 c      line 3: nch - number of panels
 c      line 4: ntarg - targets for plotting in interior/exterior
 c          (auto generated and potential computed to 13 digits)
-c      line 4-3+nverts- xy locations of vertices
-c      line 4+nverts-3+n+nverts: 
+c      line 5-4+nverts- xy locations of vertices
+c      line 5+nverts-4+n+nverts: 
 c        y1,y2, dy1/dt,dy2/dt,real(rhs),imag(rhs),real(soln),imag(soln)
-c      line 4+n+nverts-3+n+nverts+nch: ixyzs,ks,iscorn
-c      line 4+n+nverts+nch -3+n+nverts+nch+ntarg:
+c      line 5+n+nverts-5+n+nverts+nch: ixyzs,ks,iscorn
+c      line 5+n+nverts+nch - xylim info
+c      line 5+n+nverts+nch -4+n+nverts+nch+ntarg:
 c         targ1,targ2,real(pot),imag(pot)
 c
 c       ifdn = dirichlet/Neumann flag
@@ -67,11 +72,11 @@ c          iffast = 1 => iterative solver using blas for matvec
 c          iffast = 2 => iterative solver using fmm for matvec
 c          
  
-      ifdn = 1 
-      ifinout = 0
+      ifdn = 0 
+      ifinout = 1
       iffast = 2
 
-      zk = 1.1d0
+      zk = 1.2d0
 
       ifwrite = 1
       fname = 'equi_interior_test.dat'
@@ -108,6 +113,24 @@ c
       
       erra = abs(pot-potex)/abs(potex)
       call prin2('error in potential=*',erra,1)
+
+      nlat = 300
+      ntargv = nlat*nlat
+      
+      rfud = 1.2d0
+
+
[…]

### 2019-11-29 data/plot_all.py
helm poly solver almost finalized

@@ -1,0 +1,19 @@
+from numpy import *
+from pylab import *
+
+x = loadtxt('fort.47')
+y = loadtxt('fort.48')
+
+nlat = 300
+
+xx = x[:,0].reshape(nlat,nlat)
+yy = y[:,0].reshape(nlat,nlat)
+
+z = abs(xx-yy)
+z[z<10**-16] = 10**-16
+z[z>10**10] = NaN
+
+z = log10(z)
+imshow(z)
+colorbar()
+clim((-16,2))

### 2019-11-29 examples/helm_poly_solver.f

@@ -1,9 +1,10 @@
       implicit real *8 (a-h,o-z)
       real *8, allocatable :: verts(:,:)
       real *8 xyin(2),xyout(2),dpars(2)
-      real *8 xysrc(2),xytarg(2)
+      real *8 xysrc(2),xytarg(2),xylim(2,2)
       real *8, allocatable :: targ(:,:)
       complex *16, allocatable :: pottargex(:)
+      complex *16 pp
       integer, allocatable :: isin(:)
       
       complex *16 zpars,zk,pot,potex
@@ -72,7 +73,7 @@ c          iffast = 1 => iterative solver using blas for matvec
 c          iffast = 2 => iterative solver using fmm for matvec
 c          
  
-      ifdn = 0 
+      ifdn = 1 
       ifinout = 1
       iffast = 2
 
@@ -109,13 +110,16 @@ c
       call helm_solver(zk,nverts,verts,ifdn,ifinout,iffast,fker,
      1   xysrc,zk,ipars,ntarg,xytarg,pot,ifwrite,fname)
 
+
       call helm_slp(xysrc,xytarg,zk,ipars,potex)
       
       erra = abs(pot-potex)/abs(potex)
       call prin2('error in potential=*',erra,1)
 
+
       nlat = 300
       ntargv = nlat*nlat
+
       
       rfud = 1.2d0
 
@@ -123,14 +127,16 @@ c
       allocate(targ(2,ntargv),isin(ntargv),pottargex(ntargv))
       call gentarg(nverts,verts,rfud,nlat,ntargv,targ,isin,xylim)
 
+cc      ntargv = 1
+cc      targ(1,1) = 0.05d0
+cc      targ(2,1) = -0.09d0
 
       do i=1,ntargv
         pottargex(i) = 0
         call helm_slp(xysrc,targ(1,i),zk,ipars,pottargex(i))
-        write(48,*) targ(1,i),targ(2,i),
-     1     real(pottargex(i)),imag(pottargex(i))
+        write(48,*) real(pottargex(i)),imag(pottargex(i))
       enddo
-      
+
       
       stop
       end
@@ -142,16 +148,19 @@ c
       subroutine helm_slp(y,x,zk,ipars,f)
       implicit real *8 (a-h,o-z)
[…]

### 2019-11-29 src/vol_plot_routs.f

@@ -1,0 +1,534 @@
+c
+c
+c
+c
+
+
+      subroutine findnearslow(xyzs,ns,rads,targets,nt,row_ptr,col_ind)
+c
+cc      identify targets which are contained in 
+c       |xyzs(:,i)-targets(:,j)|<=rads(i)
+c       This is a dense O(ns \times nt) algorithm
+c
+c       Calling sequence variables
+c       xyzs    in: real *8 (2,ns)
+c               location of the sources
+c
+c       ns      in: integer
+c               number of sources
+c
+c       rads    in: real *8(ns)
+c               radii associated with the sources
+c
+c       targets in: real *8(2,nt)
+c               location of the targets
+c
+c       nt      in: integer
+c               number of targets
+c
+c
+c       OUTPUT
+c       row_ptr    out: integer(nt+1)
+c                itptr(i) is the starting point in the iflg
+c                array for the list of sources
+c                relevant for target i
+c
+c       col_ind  out: integer(nnz) (nnz is computed using mem routine)
+c                iflg(row_ptr(i):row_ptr(i+1)) is the list
+c                of sources which satisfy
+c                d(s_{j},t_{i}) <= rs_{j}
+c               
+c-------------------------------
+
+      implicit real *8 (a-h,o-z)
+      real *8 xyzs(2,ns),targets(2,nt),rads(ns)
+      integer row_ptr(*),col_ind(*)
+      integer, allocatable :: nlst(:)
+
+      allocate(nlst(nt))
+
+      do i=1,nt
+        nlst(i) = 0
+        do j=1,ns
+          rr = (xyzs(1,j)-targets(1,i))**2 + 
+     1          (xyzs(2,j)-targets(2,i))**2 
+          if(rr.le.rads(j)**2) then
+            nlst(i) = nlst(i) + 1
+          endif
+        enddo
+      enddo
+
+      row_ptr(1) = 1
+      do i=1,nt
+        row_ptr(i+1) = row_ptr(i)+nlst(i)
+      enddo
+
+      do i=1,nt
+        nlst(i) = 0
+      enddo
+
+      do i=1,nt
+        do j=1,ns
+          rr = (xyzs(1,j)-targets(1,i))**2 + 
+     1         (xyzs(2,j)-targets(2,i))**2 
+
+          if(rr.le.rads(j)**2) then
+            col_ind(row_ptr(i)+nlst(i)) = j
+            nlst(i) = nlst(i) + 1
+          endif
+        enddo
+      enddo
+
+
+
+      return
[…]

### 2019-11-29 data/plot_helm_solver.py
and it's done

@@ -1,0 +1,113 @@
+from numpy import *
+from pylab import *
+
+fname = 'equi_interior_neu.dat'
+
+f = open(fname)
+nverts = int(f.readline())
+n = int(f.readline())
+nch = int(f.readline())
+a=f.readline().split()
+nlat = int(a[0])
+nt = int(a[1])
+
+xys = zeros((2,n))
+dxys = zeros((2,n))
+rhs = zeros((2,n))
+soln = zeros((2,n))
+qwts = zeros(n)
+
+verts = zeros((2,nverts))
+vtmp = zeros((2,nverts+1))
+
+for i in range(nverts):
+    a= f.readline().split()
+    verts[0,i] = float(a[0])
+    verts[1,i] = float(a[1])
+
+vtmp[:,0:nverts] = verts
+vtmp[:,nverts] = verts[:,0]
+
+for i in range(n):
+    a = f.readline().split()
+    xys[0,i] = float(a[0])
+    xys[1,i] = float(a[1])
+    dxys[0,i] = float(a[2])
+    dxys[1,i] = float(a[3])
+    qwts[i] = float(a[4])
+    rhs[0,i] = float(a[5])
+    rhs[1,i] = float(a[6])
+    soln[0,i] = float(a[7])
+    soln[1,i] = float(a[8])
+
+figure(1)
+clf()
+plot(vtmp[0,:],vtmp[1,:],'k-',linewidth=0.5)
+plot(xys[0,:],xys[1,:],'g.',markersize=2)
+axis('equal')
+show()
+
+arclength = zeros(n)
+for i in range(n-1):
+    arclength[i+1] = arclength[i] + qwts[i]
+
+figure(2)
+clf()
+plot(arclength,rhs[0,:],'k.',label='rhs real part',markersize=5)
+plot(arclength,rhs[1,:],'kx',label='rhs imag part',markersize=5)
+legend()
+
+figure(3)
+semilogy(arclength,abs(soln[0,:]),'b.',label='soln real part',markersize=5)
+semilogy(arclength,abs(soln[1,:]),'bx',label='soln imag part',markersize=5)
+legend()
+show()
+
+ixys = zeros(nch)
+ks = zeros(nch)
+iscorn = zeros(nch)
+
+
+for i in range(nch):
+    a = f.readline().split()
+    ixys[i] = int(a[0])
[…]

### 2019-11-29 examples/helm_poly_solver.f

@@ -20,7 +20,12 @@
       nvmax = 100000
       allocate(verts(2,nvmax))
 
+c
+c       igeom =1, skew triangle
+c       igeom =2, jeremy's magnetron
+
       igeom = 1
+      igeom = 2
 
       call loadverts_demos(igeom,nverts,verts,xyin,xyout)
 
@@ -53,7 +58,7 @@ c      line 4: ntarg - targets for plotting in interior/exterior
 c          (auto generated and potential computed to 13 digits)
 c      line 5-4+nverts- xy locations of vertices
 c      line 5+nverts-4+n+nverts: 
-c        y1,y2, dy1/dt,dy2/dt,real(rhs),imag(rhs),real(soln),imag(soln)
+c        y1,y2, dy1/dt,dy2/dt,qwts,real(rhs),imag(rhs),real(soln),imag(soln)
 c      line 5+n+nverts-5+n+nverts+nch: ixyzs,ks,iscorn
 c      line 5+n+nverts+nch - xylim info
 c      line 5+n+nverts+nch -4+n+nverts+nch+ntarg:
@@ -71,16 +76,19 @@ c       iffast = flag for solving linear system
 c          iffast = 0 => direct inversion using blas
 c          iffast = 1 => iterative solver using blas for matvec
 c          iffast = 2 => iterative solver using fmm for matvec
+c
+c
+c       if exact solution is known, store it in 'fort.48'
 c          
  
       ifdn = 1 
-      ifinout = 1
+      ifinout = 0
       iffast = 2
 
       zk = 1.2d0
 
       ifwrite = 1
-      fname = 'equi_interior_test.dat'
+      fname = 'equi_interior_neu.dat'
 
       if(ifinout.eq.0) then
         xysrc(1) = xyout(1)
@@ -388,6 +396,8 @@ c
       subroutine loadverts_demos(igeom,nverts,verts,xyin,xyout)
       implicit real *8 (a-h,o-z)
       real *8 verts(2,*),xyin(2),xyout(2)
+      real *8, allocatable :: xverts(:),yverts(:)
+
 
       if(igeom.eq.1) then
 
@@ -407,6 +417,25 @@ c
         xyin(1) = 0.3d0
         xyin(2) = 0.2d0
       endif
+
+      if(igeom.eq.2) then
+        allocate(xverts(108),yverts(108))
+        call getmagnetroncorner(xverts,yverts,nverts)
+
+        do i=1,nverts
+          verts(1,i) = xverts(i)/100.0d0
[…]

### 2019-12-20 data/plot_helm_eig.py
updaing helm eig solvers and adding laplace poly solver

@@ -1,7 +1,7 @@
 from numpy import *
 from pylab import *
 
-fname = 'equi_eig_neu.dat'
+fname = 'star_eig_neu.dat'
 
 f = open(fname)
 nverts = int(f.readline())
@@ -71,6 +71,8 @@ rrt = zeros(nt)
 isin = zeros(nt)
 errs = zeros(nt)
 
+
+itmp = 0
 for irr in range(nroots):
     zk = float(f.readline())
     print(zk)
@@ -100,14 +102,23 @@ for irr in range(nroots):
         pot[0,i] = pot[0,i]/rr1 
         
 
-    figure(4+irr)
-    clf()
-    xx = pot[0,:]
-    xx[isin<0] = NaN
-    xx = xx.reshape(nlat,nlat)
-    imshow(xx,extent=[xmin,xmax,ymin,ymax])
-    plot(vtmp[0,:],vtmp[1,:],'w-',linewidth=0.5)
-    colorbar()
-    show()
+    a = f.readline().split()
+    print(a)
+    epsdisc = float(a[0])
+    epsrt = float(a[1])
+    err = float(a[2])
+
+    errcomp = 10*max(epsdisc,epsrt)
+    if(err<=errcomp):
+        itmp = itmp+1
+        figure(4+itmp)
+        clf()
+        xx = pot[0,:]
+        xx[isin<0] = NaN
+        xx = xx.reshape(nlat,nlat)
+        imshow(xx,extent=[xmin,xmax,ymin,ymax])
+        plot(vtmp[0,:],vtmp[1,:],'w-',linewidth=0.5)
+        colorbar()
+        savefig('star_eig_'+str(itmp)+'.pdf',bbox_inches='tight')
  
  

### 2019-12-20 examples/helm_eig_solver2.f

@@ -25,10 +25,10 @@ c       igeom =1, rectangle
 c       igeom =2, jeremy's magnetron
 c       igeom =3, kirill's star
 
-      igeom = 3
+      igeom = 1
 cc      igeom = 2
 
-      call loadverts_demos(igeom,nverts,verts)
+      call loadverts_demos(igeom,nverts,verts,nsrc,xyin,ntarg,xyout)
 
 
 c
@@ -61,7 +61,8 @@ c
       b = 4.0d0
 
 
-      call helm_eig_solver(a,b,nverts,verts,ifdn,ifwrite,fname)
+      call helm_eig_solver(a,b,nverts,verts,ifdn,nsrc,xyin,ntarg,
+     1   xyout,ifwrite,fname)
 
       
       stop
@@ -311,9 +312,9 @@ c
 c
 c
 c 
-      subroutine loadverts_demos(igeom,nverts,verts)
+      subroutine loadverts_demos(igeom,nverts,verts,ns,xyin,nt,xyout)
       implicit real *8 (a-h,o-z)
-      real *8 verts(2,*),xyin(2),xyout(2)
+      real *8 verts(2,*),xyin(2,*),xyout(2,*)
       real *8, allocatable :: xverts(:),yverts(:)
 
 
@@ -334,6 +335,14 @@ c
         verts(1,4) = 0
         verts(2,4) = 1.05d0*pi
 
+        ns = 1
+        nt = 1
+        xyin(1,1) = 1.4d0
+        xyin(2,1) = 1.7d0
+
+        xyout(1,1) = 6.2d0
+        xyout(2,1) = 5.7d0
+
       endif
 
       if(igeom.eq.2) then
@@ -345,11 +354,13 @@ c
           verts(2,i) = yverts(i)/100.0d0
         enddo
 
-        xyin(1) = 1.2d0
-        xyin(2) = 0.75d0
+        ns = 1
+        nt = 1
+        xyin(1,1) = 1.2d0
+        xyin(2,1) = 0.75d0
 
-        xyout(1) = 3.0d0
-        xyout(2) = 1.0d0
+        xyout(1,1) = 3.0d0
+        xyout(2,1) = 1.0d0
 
       endif
 
@@ -396,7 +407,7 @@ c*******************************
 
 
         subroutine helm_eig_solver(a0,b0,nverts,verts,ifdn,
-     1   ifwrite,fname)
[…]

### 2019-12-20 examples/lap_poly_solver.f

@@ -3,8 +3,9 @@
       real *8 xyin(2),xyout(2),dpars(2)
       real *8 xysrc(2),xytarg(2),xylim(2,2)
       real *8, allocatable :: targ(:,:)
-      complex *16, allocatable :: pottargex(:)
-      complex *16 pp
+      real *8, allocatable :: pottargex(:)
+      real *8 pp
+      complex *16 zpars
       integer, allocatable :: isin(:)
       
       complex *16 zpars,zk,pot,potex
@@ -13,7 +14,7 @@
 
       procedure (), pointer :: fker
 
-      external helm_slp,helm_dlp
+      external lap_slp,lap_dlp
 
       call prini(6,13)
 
@@ -21,47 +22,131 @@
       allocate(verts(2,nvmax))
 
 c
-c       igeom =1, rectangle
+c       igeom =1, skew triangle
 c       igeom =2, jeremy's magnetron
-c       igeom =3, kirill's star
 
-      igeom = 3
-cc      igeom = 2
+      igeom = 1
+      igeom = 2
 
-      call loadverts_demos(igeom,nverts,verts)
-
+      call loadverts_demos(igeom,nverts,verts,xyin,xyout)
 
 c
 c
-c     This subroutine computes the interior Dirichlet/neumann 
-c     eigenvalues using a double layer as the representation
-c     for the dirichlet problem, and single layer as the
-c     representation for the neumann problem.
+c     This subroutine solves the interior/exterior
+c        Dirichlet/Neumann Laplace boundary value
+c        problem using a double layer as the representation
+c        for the dirichlet problem, and single layer as the
+c        representation for the neumann problem.
+c
+c     Note: special care is taken with 1s matrices for the
+c     exterior dirichlet problem and the interior neumann problem
+c
+c     The right hand side is a user supplied subroutine 
+c       fker whose calling sequence is of the form
+c
+c      fker(y,dpars,zpars,ipars,f)
+c       
+c       y contains the source info 
[…]

### 2019-12-20 examples/helm_poly_solver.f
updating lap poly solver

@@ -25,7 +25,7 @@ c       igeom =1, skew triangle
 c       igeom =2, jeremy's magnetron
 
       igeom = 1
-      igeom = 2
+cc      igeom = 2
 
       call loadverts_demos(igeom,nverts,verts,xyin,xyout)
 
@@ -81,7 +81,7 @@ c
 c       if exact solution is known, store it in 'fort.48'
 c          
  
-      ifdn = 1 
+      ifdn = 0 
       ifinout = 0
       iffast = 2
 

### 2019-12-20 src/dgmres_fmm.f

@@ -1,0 +1,311 @@
+ccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccc
+c
+c       This is the end of the debugging routines and the beginning 
+c       of the complex GMRES routines
+c
+ccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccc
+c
+c
+c
+c
+c
+        subroutine dgmres_fmm(ier,n,multa,ifdn,ifinout,
+     1     xys,dxys,qwts,nedges,ncint,lns,rns,icl,icr,icsgnl,icsgnr,
+     2     xsgnl,xsgnr,ncorner,xmatc,xmatcsub,y,eps,numit,
+     1     x,niter,errs,ngmrec,w)
+        implicit real *8 (a-h,o-z)
+        dimension errs(1)
+        real *8 x(1),y(1),w(1)
+
+        real *8 xys(2,n),dxys(2,n),qwts(n)
+        integer ncint,nedges
+        integer lns(nedges),rns(nedges),icl(ncint),icr(ncint)
+        integer icsgnl(ncint),icsgnr(ncint)
+        integer ncorner
+        real *8 xsgnl(ncint),xsgnr(ncint)
+        real *8 xmatc(ncorner,ncorner,ncint)
+        real *8 xmatcsub(ncorner,ncorner,ncint)
+        
+        
+c
+        external multa
+c
+c     This subroutine solves a complex linear system Ax=y by means
+c     of GMRES algorithm. This is a memory management routine for 
+c     cgmres1 which performs the actual work.
+c
+c     Input parameters:
+c
+c     n - the dimensionality of the linear system
+c     y - the right hand side
+c     a - the matrix of the system (or whatever other parameter)
+c     eps - the required accuracy
+c     multa - the user-defined matrix-vector multiplication subroutine
+c
+c     the calling sequence for multa must be
+c
+c     multa(x,y,n,ifdn,ifinout,xys,dxys,qwts,nedges,ncint,
+c         lns,rns,icl,icr,icsgnl,icsgnr,xsgnl,xsgnr,ncorner,
+c         xmatc)
+c
+c       in (1), a is a matrix the system or whatever other parameter,
+c       par1, par2 are whatever other parameters, x is an input vector,
[…]

### 2019-12-20 src/laprouts2d.f

@@ -1,0 +1,3674 @@
+cc Copyright (C) 2010-2011: Leslie Greengard and Zydrunas Gimbutas
+cc Contact: greengard@cims.nyu.edu
+cc 
+cc This program is free software; you can redistribute it and/or modify 
+cc it under the terms of the GNU General Public License as published by 
+cc the Free Software Foundation; either version 2 of the License, or 
+cc (at your option) any later version.  This program is distributed in 
+cc the hope that it will be useful, but WITHOUT ANY WARRANTY; without 
+cc even the implied warranty of MERCHANTABILITY or FITNESS FOR A 
+cc PARTICULAR PURPOSE.  See the GNU General Public License for more 
+cc details. You should have received a copy of the GNU General Public 
+cc License along with this program; 
+cc if not, see <http://www.gnu.org/licenses/>.
+ccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccc
+c
+c    $Date$
+c    $Revision$
+c
+c
+c      This file contains the basic subroutines for 
+c      forming and evaluating multipole (partial wave) expansions
+c      in two dimensions.
+c
+c      Since log(z) is a multivalued complex function, we use
+c      the real part Re(log(z)) = log(abs(z)) in all computations.
+c
+c      All multipole and local expansions are properly scaled 
+c
+c-----------------------------------------------------------------------
+c
+c      L2DFORMMP: creates multipole expansion (outgoing) due to 
+c                 a collection of charge sources.
+c
+c      L2DFORMTA: creates local expansion due to 
+c                 a collection of charge sources.
+c
+c      L2DFORMMP_DP: creates multipole expansion (outgoing) due to 
+c                 a collection of dipole sources.
+c
+c      L2DFORMTA_DP: creates local expansion due to 
+c                 a collection of dipole sources.
+c
+c-----------------------------------------------------------------------
+c
+c      Multipole and local translation operators
+c
+c      L2DMPMP:     converts multipole expansion to a multipole expansion.
+c      L2DMPLOC:     converts multipole expansion to a local expansion.
+c      L2DLOCLOC:     converts local expansion to a local expansion.
+c
[…]

### 2019-12-22 paper_lap/01intro.tex
Introduction - rough

\section{Introduction}
Laplace's equation arises in a vast array of contexts (classical electrostatics, harmonic functions, low-frequency acoustics, percolation theory, homogenization theory, and the study field enhancements in vacuum insulators for example) and serves as a useful model problem for the study of general elliptic partial differential equations (PDEs). As such, effective numerical methods for quickly and robustly solving Laplace's equation with high accuracy are desirable. Approaches based on potential theory proceed by reducing PDEs to second-kind boundary integral equations (BIEs), representing the solution to the boundary value problem as the potential produced by charges (single-layer potentials) or dipoles (double-layer potentials) on the boundary of the domain. Once these boundary integral equations are discretized the resulting linear systems are better-conditioned than those obtained by directly discretizing the PDE. When the boundary of the domain is smooth there are numerous methods for solving BIEs quickly and accurately (see \cite{hao}, for example).

Near corners, however, the solutions to both the partial differential equations and corresponding boundary integral equations may have singularities, preventing the application of many traditional methods. Fortunately, a number of approaches have been developed to obviate this difficulty. One class of methods proceeds by introducing many additional degrees of freedom in the vicinity of the corners. In order to prevent the resulting linear systems from becoming intractably large one can use a variety of methods for {\it compressing} the linear system, effectively eliminating the extra degrees of freedom added in the vicinity of the corners. Moreover, the corner refinement and compression can be done in tandem resulting in fast and accurate solvers for elliptic PDEs (see \cite{helsing}, \cite{helsing2},  \cite{ojala}, \cite{helsjcp} and \cite{helsinv}  for  one approach called recursive compressed preconditioning, and  \cite{gillman}, \cite{bremer},\cite{bremer2}, and \cite{bremer3}  for other compression-based methods for solving Laplace's equation). Unfortunately, this approach becomes considerably more expensive in three dimensions limiting its application in that context.

 Another class of methods is based on approximating the solution to the two-dimensional problem by rational functions \cite{} with poles exponentially clustered near the corners. While this approach allows for fast evaluation of the solution near the boundary of the domain, current implementations are specialized to two-dimensions, are significantly slower than other approaches, and have difficulties handling complicated domains and boundary data.

 Finally, a recent approach is based on leveraging explicit representations of the solutions to the BIEs in the vicinity of the corner as sums of fractional powers depending on the angle \cite{}. Using these representations one can construct high-order discretizations which introduce relatively few extra degrees of freedom near the corners (i.e. an amount which is comparable to the number required for smooth portions of the boundary). This approach has been used to generate efficient discretizations for Dirichlet problems for Laplace's equation on polygonal domains\cite{}. In this paper we describe a method for solving Laplace's equation on polygonal domains with Neumann boundary conditions given only a discretization of a corresponding Dirichlet problem. Our approach is based on the adjoint method \cite{}. In particular, we show that if the transpose of the discretization of a suitable Dirichlet BIE is used, then the resulting solution will be accurate in a ``weak sense''; namely, it can be used to compute inner products with smooth functions accurately, though it cannot be interpolated. We then show how this solution can be used to obtain accurate solutions to the Neumann problem arbitrarily close to a corner by solving a set of local subproblems in the vicinity of that corner.

 The paper is organized as follows. In Section \ref{} we review relevant mathematical results associated with Laplace's equation. Section \ref{} describes the reduction of boundary value problems to boundary integral equations via potential theory, and reviews the analytic behavior of solutions near a corner. In Section \ref{} we present our numerical algorithm and the associated analysis. Finally, in Section \ref{} we illustrate its application with several numerical experiments.

### 2020-01-02 examples/lap_poly_solver.f
updating lap_poly_solver

@@ -84,9 +84,9 @@ c
 c       if exact solution is known, store it in 'fort.48'
 c          
  
-      ifdn = 1 
-      ifinout = 1
-      iffast = 0
+      ifdn = 0 
+      ifinout = 0
+      iffast = 2
 
       zk = 1.2d0
 
@@ -967,6 +967,10 @@ c
       complex *16 ima
       data ima/(0.0d0,1.0d0)/
 
+      done = 1
+      pi = atan(done)*4
+
+
       ifhess = 0
 
       if(ifdn.eq.0) then
@@ -1003,14 +1007,25 @@ c
         grad(2,i) = 0
       enddo
 
+cc      call prin2('dipstr=*',dipstr,24)
+
+
       nd = 1
       eps = 1.0d-15
       nt = 0
 
       iprec = 5
 
+cc      call prinf('n=*',n,1)
+cc      call prinf('ifcharge=*',ifcharge,1)
+cc      call prinf('ifdipole=*',ifdipole,1)
+cc      call prinf('ifpot=*',ifpot,1)
+cc      call prinf('igrad=*',ifgrad,1)
+cc      call prinf('ifhess=*',ifhess,1)
 
-      call cfmm2dpart(ier,ipredc,in,xys,ifcharge,charges,ifdipole,
+      ier = 0
+
+      call cfmm2dpart(ier,iprec,n,xys,ifcharge,charges,ifdipole,
      1   dipstr,ifpot,pot,ifgrad,grad,ifhess,hess) 
 
 
@@ -1019,8 +1034,9 @@ c
 c       take care of all corrections now
 c
       if(ifdn.eq.0) then
+
         do i=1,n
-          pot(i) = pot(i)*sqrt(qwts(i))
+          pot(i) = pot(i)*sqrt(qwts(i))/2/pi
         enddo
 
         do icint=1,ncint
@@ -1059,7 +1075,7 @@ c
         enddo
 
         do i=1,n
-          y(i) = pot(i) -0.5d0*(-1)**(ifdn+ifinout)*x(i) 
+          y(i) = real(pot(i)) -0.5d0*(-1)**(ifdn+ifinout)*x(i) 
         enddo
       endif
 
@@ -2267,7 +2283,7 @@ c
             bottom = sqrt( (cos(alpha)*x0s(i) - x0s(j))**2 +
      1          (x0s(i)*sin(alpha))**2)
             akern(i,j) =
[…]

### 2020-01-02 paper_lap/manuscript.tex

\documentclass[12pt]{article}
\usepackage{amsmath,amsthm,amssymb,amscd,fancybox,epsfig,float,subfigure}
\usepackage[margin=1in]{geometry}
\usepackage{graphics}
\usepackage{epstopdf}
\usepackage{multirow}
\usepackage{hhline}
\usepackage{cleveref}
\usepackage{xcolor}
\usepackage{tikz}
\usetikzlibrary{arrows,automata}
\usepackage[nocompress]{cite}
\newtheorem{definition}{Definition}[section]
\newtheorem{remark}{Remark}[section]
\newtheorem{conjecture}{Conjecture}[section]
\newtheorem{proposition}{Proposition}[section]
\newtheorem{corollary}{Corollary}[section]
\newtheorem{remark1}{Remark}[section]
\newcommand{\beqn}{\begin{equation}}
\newcommand{\eeqn}{\end{equation}}
\newcommand{\psub}{\mbox{$\ddot{-}$}}
\newcommand{\cS}{\mathcal{S}}
\newcommand{\sgn}{{\rm sgn}}
\newcommand{\cN}{\mathcal{N}}
\newcommand{\cD}{\mathcal{D}}
\newcommand{\cA}{\mathcal{A}}
\newcommand{\cB}{\mathcal{B}}
\newcommand{\bS}{\mathbb{S}}
\newcommand{\bR}{\mathbb{R}}
\newcommand{\cR}{\mathcal{R}}
\newcommand{\cI}{\mathcal{I}}
\newcommand{\cG}{\mathcal{G}}
\newcommand{\cH}{\mathcal{H}}
\newcommand{\cF}{\overline{\bf F}}
\newcommand{\cU}{\overline{\bf U}}
\newcommand{\cT}{\mathcal{T}}
\newcommand{\bP}{{\bf P}}
\newcommand{\bT}{\mathbb{T}}
\newcommand{\bq}{{\bf q}}
\newcommand{\bv}{{\bf v}}
\newcommand{\bu}{{\bf u}}
\newcommand{\boldf}{{\bf f}}
\newcommand{\bphi}{{\boldsymbol \phi}}
\newcommand{\bmu}{{\boldsymbol \mu}}
\newcommand{\brho}{{\boldsymbol \rho}}
\newcommand{\bC}{{\bf C}}
\newcommand{\bV}{{\bf V}}
\newcommand{\bU}{{\bf U}}
\newcommand{\bF}{{\bf F}}
\newcommand{\bRes}{{\bf R}}
\newcommand{\bM}{{\bf M}}
\newcommand{\bI}{\mathbb{I}}
\newcommand{\bN}{\mathbb{N}}
\newcommand{\bL}{\mathbb{L}}
\newcommand{\bX}{\mathbb{X}}
\newcommand{\bx}{\boldsymbol{x}}
\newcommand{\bnu}{\boldsymbol{\nu}}
\newcommand{\bn}{\boldsymbol{n}}
\newcommand{\by}{\boldsymbol{y}}
\newcommand{\cL}{\mathcal{L}}
\newcommand{\bub}{\underbar{b}}
\newcommand{\xmyo}{\sqrt{x^2 + y^2 - 2xy\cos{\pi \alpha}}}
\newcommand{\sina}{\sin{(\pi \alpha)}}
\newcommand{\sqsina}{\sin^{2}{(\pi \alpha)}}
\newcommand{\cosa}{\cos{(\pi \alpha)}}
\newcommand{\sinna}{\sin{(\pi \nu (1-\alpha))}}
\newcommand{\cosna}{\cos{(\pi \nu (1-\alpha))}}
\newcommand{\sinn}{\sin{(\pi \nu)}}
\newcommand{\cosn}{\cos{(\pi \nu)}}
\newcommand{\bbmat}{\begin{bmatrix}}
\newcommand{\ebmat}{\end{bmatrix}}
\newcommand{\dudn}[1]{\frac{\partial u_{#1}}{\partial n}}

\usepackage{boxit}
%\newcommand{\boxit}[1]{#1}
%\newcommand{\dashboxit}[1]{#1}

\newtheorem{theorem}{Theorem}
\newtheorem{thm}{Theorem}
\newtheorem{lemma}{Lemma}
\newtheorem{lem}{Lemma}
\newtheorem{rem}{Remark}
\newtheorem{comment}{Remark}

\begin{document}
 \title{Dirichlet discretization of Neumann problems}
 \author{Jeremy Hoskins and Manas Rachh}
 \maketitle

\input{01intro}
\input{02mprelim}
\input{03bvp}
\input{04nprelim}
\input{05apparatus}
\input{06num}
\input{07conc}
\section*{Appendix A}
Here we give explicit bounds for the rate of convergence of the contribution of the rest of the boundary to a corner panel. In particular, given a polygonal domain with boundary $\Gamma,$ let $\bx$ denote a vertex of $\Gamma$ and $C = \Gamma \cap B_r(\bx),$ where $B_r(\bx)$ is the ball of radius of $r$ centered at $\bx.$ We choose $r$ so that $\Gamma \cap B_{2r}(\bx)$ corresponds to a wedge with internal angle $\pi \alpha$ and side lengths $2r.$

Let $\Gamma_*$ be any other straight line segment contained entirely within $\Gamma \setminus B_{2r}(\bx).$ Then

\begin{theorem}
Let $\Gamma$ be the boundary of a polygon and $\bx$ be a vertex. Let $r>0$ be a real number such that $\Gamma \cap B_{2r}(\bx)$ corresponds to a wedge with internal angle $\pi \alpha$ and side lengths $2r,$ where $B_R(\bx)$ denotes a ball of radius $R$ centered at $\bx.$ Let $L$ denote the length of $\Gamma$ and $\gamma: [-L/2,L/2]\to \Gamma$ be an arclength counterclockwise parameterization of $\Gamma$ such that $\gamma(0) = \bx.$ Finally, for any $f \in L^2(\Gamma),$ let $H:[0,r] \to \mathbb{R}$ be the function defined by
\begin{align}
H(t) = \int_{\Gamma\backslash B_{2r}(\bx)} K(\gamma(t),\gamma(s)) f(s)\,{\rm d}s.
\end{align}
Then $H$ is analytic in a neighborhood of $0$ with Taylor series coefficients $\{ a_n\}$ satisfying
\begin{align}
|a_n| \le \frac{\sqrt{L}}{2^nr^{n+1}} \|f\|_{L_2(\Gamma \backslash B_{2r}(\bx))}.
\end{align}
\end{theorem}
\begin{proof}
Without loss of generality we can assume that $\Gamma$ is shifted, oriented and parameterized so that $\bx = \gamma(0)= 0$ and the leg of the wedge corresponding to positive $t$ is oriented along the positive $x$ axis. Then
\begin{align}
H(t) = \int_{\Gamma\backslash B_{2r}(\bx)} K(\gamma(t),\gamma(s)) f(s)\,{\rm d}s = \int_{\Gamma\backslash B_{2r}(\bx)} \frac{y(s)}{(t-x(s))^2+y(s)^2}f(s)\,{\rm d}s.
\end{align}
Since $\|\gamma(s)-\gamma(t)\| >2r$ it follows that
\begin{align}
H(t) =\int _{\Gamma\backslash B_{2r}(\bx)}\sum {t^n i}\left(\frac{1}{(x(s)+i y(s))^{n+1}}-\frac{1}{(x(s)-i y(s))^{n+1}} \right)\,{\rm d}s.
\end{align}
In particular, $H$ has a Taylor series about $t=0,$
\begin{align}
\sum_{n=0}^\infty c_n \left(\frac{t}{2r}\right)^n
\end{align}
where
\begin{align}
|c_n| \le  \frac{\sqrt{L}}{r} \|f\|_{L_2(\Gamma \backslash B_{2r}(\bx))}.
\end{align}
\end{proof}

\end{document}

### 2020-01-02 examples/lap_poly_solver.f
fixed dirichlet fmm - neumann fmm pending

@@ -84,8 +84,8 @@ c
 c       if exact solution is known, store it in 'fort.48'
 c          
  
-      ifdn = 0 
-      ifinout = 0
+      ifdn = 1 
+      ifinout = 1
       iffast = 2
 
       zk = 1.2d0
@@ -763,6 +763,12 @@ cc        call prin2('xmat=*',xmat,npts*npts)
 
           call prin2('soln=*',soln,24)
 
+          rint = 0
+          do i=1,npts
+            rint = rint + soln(i)*sqrt(qwts(i))
+          enddo
+          call prin2('integral of density=*',rint,1)
+
         endif
       endif
 
@@ -785,7 +791,13 @@ cc        call prin2('xmat=*',xmat,npts*npts)
      2    xsgnl,xsgnr,ncorner,xmatc,xmatcsub,rhs,eps,numit,
      3    soln,niter,errs,
      3    ngmrec,work)
-        
+         
+         call prin2('soln=*',soln,24)
+          rint = 0
+          do i=1,npts
+            rint = rint + soln(i)*sqrt(qwts(i))
+          enddo
+          call prin2('integral of density=*',rint,1)
       endif
 
       call cpu_time(t2)
@@ -932,7 +944,10 @@ c
       alpha = 1.0d0
       beta = 0.0d0
 
-      call dgemv(transa,n,n,alpha,xmat,n,x,1,beta,y,1) 
+      call dgemv(transa,n,n,alpha,xmat,n,x,1,beta,y,1)
+      call prin2('x=*',x,24)
+      call prin2('y=*',y,24)
+      stop
       
 
       return
@@ -959,7 +974,7 @@ c
 
       complex *16, allocatable :: charges(:),dipstr(:)
       real *8, allocatable :: dipvec(:,:)
-      complex *16, allocatable :: pot(:),grad(:,:)
+      complex *16, allocatable :: pot(:),grad(:)
       complex *16 pottarg,gradtarg(2),hess(3),hesstarg(3),pottmp
 
       real *8 targ(2)
@@ -989,7 +1004,7 @@ c
 
 
       allocate(charges(n),dipstr(n),dipvec(2,n))
-      allocate(pot(n),grad(2,n))
+      allocate(pot(n),grad(n))
 
 
       do i=1,n
[…]

### 2020-01-03 data/plot_lap_solver.py
finished interior dirichlet laplace

@@ -1,0 +1,108 @@
+from numpy import *
+from pylab import *
+
+fname = 'equi_interior_neu.dat'
+
+f = open(fname)
+nverts = int(f.readline())
+n = int(f.readline())
+nch = int(f.readline())
+a=f.readline().split()
+nlat = int(a[0])
+nt = int(a[1])
+
+xys = zeros((2,n))
+dxys = zeros((2,n))
+rhs = zeros((n))
+soln = zeros((n))
+qwts = zeros(n)
+
+verts = zeros((2,nverts))
+vtmp = zeros((2,nverts+1))
+
+for i in range(nverts):
+    a= f.readline().split()
+    verts[0,i] = float(a[0])
+    verts[1,i] = float(a[1])
+
+vtmp[:,0:nverts] = verts
+vtmp[:,nverts] = verts[:,0]
+
+for i in range(n):
+    a = f.readline().split()
+    xys[0,i] = float(a[0])
+    xys[1,i] = float(a[1])
+    dxys[0,i] = float(a[2])
+    dxys[1,i] = float(a[3])
+    qwts[i] = float(a[4])
+    rhs[i] = float(a[5])
+    soln[i] = float(a[6])
+
+figure(1)
+clf()
+plot(vtmp[0,:],vtmp[1,:],'k-',linewidth=0.5)
+plot(xys[0,:],xys[1,:],'g.',markersize=2)
+axis('equal')
+show()
+
+arclength = zeros(n)
+for i in range(n-1):
+    arclength[i+1] = arclength[i] + qwts[i]
+
+figure(2)
+clf()
+plot(arclength,rhs,'k.',label='rhs real part',markersize=5)
+legend()
+
+figure(3)
+semilogy(arclength,abs(soln),'b.',label='soln real part',markersize=5)
+legend()
+show()
+
+ixys = zeros(nch)
+ks = zeros(nch)
+iscorn = zeros(nch)
+
+
+for i in range(nch):
+    a = f.readline().split()
+    ixys[i] = int(a[0])
+    ks[i] = int(a[1])
+    iscorn[i] = int(a[2])
+
+a = f.readline().split()
+xmin = float(a[0])
+ymin = float(a[1])
+xmax = float(a[2])
+ymax = float(a[3])
+
+pot = zeros((nt))
+targ = zeros((2,nt))
+
+for i in range(nt):
[…]

### 2020-01-03 examples/lap_poly_solver.f

@@ -84,8 +84,8 @@ c
 c       if exact solution is known, store it in 'fort.48'
 c          
  
-      ifdn = 1 
-      ifinout = 1
+      ifdn = 0 
+      ifinout = 0
       iffast = 2
 
       zk = 1.2d0
@@ -145,11 +145,13 @@ cc      ntargv = 1
 cc      targ(1,1) = 0.05d0
 cc      targ(2,1) = -0.09d0
 
+
       do i=1,ntargv
         pottargex(i) = 0
         call lap_slp(xysrc,targ(1,i),zpars,ipars,pottargex(i))
         write(48,*) pottargex(i)
       enddo
+      call prin2('pottargex=*',pottargex,1)
 
       
       stop
@@ -251,6 +253,9 @@ c
       real *8 pols(100)
       real *8 f,val,dd,pi
 
+      done = 1
+      pi = atan(done)*4
+
       dd = 0
       xx = 0
       yy = 0
@@ -326,6 +331,9 @@ c
       real *8 par1(*),par2(*)
       real *8 pols(100)
       real *8 val,dd,pi,f
+
+      done = 1
+      pi = atan(done)*4
 
       dd = 0
       xx = 0
@@ -479,6 +487,8 @@ c
 
       done = 1
       pi = atan(done)*4
+
+
 
       read(32,*) lcoefs
 
@@ -845,7 +855,6 @@ cc        call prin2('xmat=*',xmat,npts*npts)
         enddo
       endif
 
-      return
 
 
 
@@ -881,7 +890,13 @@ cc      targ(2,1) = -0.09d0
       call prin2('quadrature correction for volume targets time=*',
      1       t2-t1,1)
 
+      call prin2('pottarg=*',pottarg,1)
+
       call cpu_time(t1)
+      call prinf('npts=*',npts,1)
+      call prinf('ifdn=*',ifdn,1)
+      call prinf('ntarg=*',ntarg,1)
+      call prin2('xytarg=*',xytarg,2*ntarg)
       call comppottarg_fmm(npts,xys,dxys,qwts,ifdn,soln,ntarg,
      1    xytarg,pot)
 
@@ -899,7 +914,7 @@ cc      targ(2,1) = -0.09d0
      1       t2-t1,1)
 
 
-      
+ 
       open(unit=47,file=trim(fname))
       write(47,*) nverts
       write(47,*) npts
[…]

### 2020-01-03 examples/lap_poly_solver.f
adding lap poly solver

@@ -84,8 +84,8 @@ c
 c       if exact solution is known, store it in 'fort.48'
 c          
  
-      ifdn = 0 
-      ifinout = 0
+      ifdn = 1 
+      ifinout = 1
       iffast = 2
 
       zk = 1.2d0
@@ -143,7 +143,7 @@ c
 
 cc      ntargv = 1
 cc      targ(1,1) = 0.05d0
-cc      targ(2,1) = -0.09d0
+cc      targ(2,1) = -0.12d0
 
 
       do i=1,ntargv
@@ -871,7 +871,7 @@ c
 
 cc      ntargv = 1
 cc      targ(1,1) = 0.05d0
-cc      targ(2,1) = -0.09d0
+cc      targ(2,1) = -0.12d0
 
       call cpu_time(t1)
       call comppottarg_fmm(npts,xys,dxys,qwts,ifdn,soln,ntargv,
@@ -1331,7 +1331,7 @@ c
      3  hesstarg)
       
       do i=1,ntarg
-        pottarg(i) = real(pottargtmp(i))/2/pi
+        pottarg(i) = -real(pottargtmp(i))/2/pi
       enddo
 
 
@@ -1673,6 +1673,7 @@ c
       if(ifdn.eq.1) then
         allocate(vtmp(2,nverts+2))
 
+
         do i=1,nverts+2
           ii = i
           if(ii.gt.nverts) ii = ii-nverts
@@ -1796,11 +1797,15 @@ c
            enddo
 
 
+
 c
            call resolve_dens(kmid,nc,tsc,wtsc,vmatc,rpan,angs(icint),
      1       soln(ixys(ichl(icint))),soln(ixys(ichr(icint))),
      2       xsgnl(icint),xsgnr(icint),nlev,nresolve,coefs,lcoefs,
      3       ifinout,soln_resolve)
+          
+
+          
 
 
            
@@ -2433,12 +2438,15 @@ c
 
       allocate(xmatcnew(nc2,nc2))
 
+
       call getlapcornermat(thet,nc2,rtmp,tsloc,wtsloc,xmatcnew)
 
       allocate(xmatnew(nn,nn))
       allocate(xmatnewcopy(nn,nn))
       nnn = 2*ncorner
       allocate(xmatsub(nnn,nnn),xmatsub0(nnn,nnn))
+
+
 
 
       do i=1,nn
@@ -2458,7 +2466,7 @@ c
[…]

### 2020-01-06 paper_lap/01intro.tex
adding numerical and small changes to intro and section 2

@@
 \section{Introduction}
-Laplace's equation arises in a vast array of contexts (classical electrostatics, harmonic functions, low-frequency acoustics, percolation theory, homogenization theory, and the study field enhancements in vacuum insulators for example) and serves as a useful model problem for the study of general elliptic partial differential equations (PDEs).
+Laplace's equation arises in a vast array of contexts (electrostatics, harmonic functions, low-frequency acoustics, percolation theory, homogenization theory, and the study field enhancements in vacuum insulators for example) and serves as a useful model problem for the study of general elliptic partial differential equations (PDEs).
 As such, effective numerical methods for quickly and robustly solving Laplace's equation with high accuracy are desirable.
-Approaches based on potential theory proceed by reducing PDEs to second-kind boundary integral equations (BIEs), representing the solution to the boundary value problem as the potential produced by charges (single-layer potentials) or dipoles (double-layer potentials) on the boundary of the domain.
+Approaches based on potential theory proceed by reducing PDEs to second-kind boundary integral equations (BIEs), where the solution to the boundary value problem is represented by layer potentials on the boundary of the domain.
 Once these boundary integral equations are discretized the resulting linear systems are better-conditioned than those obtained by directly discretizing the PDE.
@@
  Another class of methods is based on approximating the solution to the two-dimensional problem by rational functions \cite{} with poles exponentially clustered near the corners.
-While this approach allows for fast evaluation of the solution near the boundary of the domain, current implementations are specialized to two-dimensions, are significantly slower than other approaches, and have difficulties handling complicated domains and boundary data.
+While this approach allows for fast evaluation of the solution near the boundary of the domain, current implementations are specialized to two-dimensions, are significantly slower than other approaches for large problems, and have difficulties handling complicated domains and boundary data.
 
@@
 This approach has been used to generate efficient discretizations for Dirichlet problems for Laplace's equation on polygonal domains\cite{}.
+
  In this paper we describe a method for solving Laplace's equation on polygonal domains with Neumann boundary conditions given only a discretization of a corresponding Dirichlet problem.

### 2020-01-06 paper_lap/02mprelim.tex
adding numerical and small changes to intro and section 2

@@
 Given a polygonal domain  $\Omega \subset \mathbb{R}^2$ with boundary $\Gamma$ and outward-pointing 
-unit normal $\bnu: \Gamma \to S^1,$ as well as a function 
+unit normal $\bnu$, as well as a function 
 $f: \Gamma \to \mathbb{R},$ we consider 

### 2020-01-06 paper_lap/06num.tex
adding numerical and small changes to intro and section 2

\section{Numerical results}
\subsection{Accuracy}
In this section, we demonstrate accuracy of the proposed numerical method (both in the "weak" sense, and 
"strong sense" after sufficiently many re-solves) on the triangular domain shown below. 
The reference solution for each of the examples is computed using a discretization with
a graded mesh in the vicinity of the corners, where the smallest panel at the corner is $2^{-150}$ times
the length of the first macroscopic panel away from the corner (see~\cref{fig:dom}). 
\begin{rem}
$2^{-150}$ is significantly smaller than machine precision, however the matrix entries corresponding to the
corner interactions can be computed accurately by recentering the corner at the origin. 
\end{rem} 
\begin{rem}
It is well-known that a smallest panel size of $2^{-100}$ is sufficient to resolve the density corresponding
to solutions of the Neumann problem in order to obtain full machine precision in the solution anywhere in the volume.
However, it is not true the value of the density is accurate to machine precision at all the nodes. In fact the quality
of the density deteriorates as one approaches the corner. Thus, in order to obtain accurate point values
of the density to machine precision at all points which are $2^{-100}$ away from the corner, we use a smallest
panel size of $2^{-150}$. 
\end{rem}
In these examples, the solutions are computed dense linear solves.

The potential at target locations which are more than 1 panel length away is the inner product of the 
density with a smooth function. For a target location $\boldsymbol{y}$, we compute the solution via the formula,
\begin{equation}
u(\by) = \int_{\Gamma} G(\bx,\by) \sigma(\bx) dS_{\bx} \approx \sum_{i=1}^{N}  G(\gamma(s_{i}),\by) \sigma_{i} \sqrt{w_{i}}
\end{equation}
In figure~\cref{fig:far-field}, we compute the error in the solution at target
locations in the volume for the right hand side given by
\begin{equation}
f(\bx) = 
\end{equation}

Another example of weak quantity is the polarization tensor associated with a domain. This requires the solution of the
exterior problems with boundary data $f_{1} = \bnu_{1}$ or $f_{2} = \bnu_{2}$. Let $\sigma_{1}$ and $\sigma_{2}$ denote
the corresponding solutions. The polarization tensor can be expressed in terms of the solutions $\sigma_{1}$ and $\sigma_{2}$
as
\begin{equation}
P = \begin{bmatrix}
\int_{\Gamma} x_{1} \sigma_{1}(\bx) dS_{\bx} & \int_{\Gamma} x_{2} \sigma_{1}(\bx) dS_{\bx} \\
\int_{\Gamma} x_{1} \sigma_{2}(\bx) dS_{\bx} & \int_{\Gamma} x_{2} \sigma_{2}(\bx) dS_{\bx} 
\end{bmatrix}
\end{equation}
The polarization tensor as computed by the reference solution, and the error in computation using the adjoint method
are given by
\begin{equation}
P = \begin{bmatrix}
\end{bmatrix} \, , \quad \text{Error} = 
\begin{bmatrix} 
\end{bmatrix}
\end{equation}

In order to demonstrate the capability to obtain the true density at the corner panels, we  apply the procedure
discussed in~\cref{sec:resolve} iteratively, and compare the obtained density with the reference density after 20,40,60, and
80 iterations of resolves in the vicinity of one of the corners. The reference density and the errors are shown in ~\cref{fig:dens-error}.

After re-solving the density, we also compute the solution at target locations on a tensor product polar grid, where the grid
is exponentially spaced in the radial direction and equispaced in the angular direction. For target locations
close to panels which are not at the corner, we use adaptive integration in order to resolve the near-singular behavior of
the kernel for accurate computation of the integrals. For target locations close to the corner panel, since we do not have
the capability to interpolate the density, we use the underlying smooth quadrature rules for computing their contribution. 
The reference solution and the errors are demonstrated in~\cref{fig:vol-plot}.
\subsection{Performance}
In this section, we demonstrate the performance of the solver of two large domains. We solve scattering problems in the
exterior of a magnetron like region, and the maple leaf. The right hand side is the potential due to a collection of charges in the exterior of the region, and we impose that

### 2020-01-06 paper_lap/06num.tex
changes

@@
 \subsection{Accuracy}
-In this section, we demonstrate accuracy of the proposed numerical method (both in the "weak" sense, and 
-"strong sense" after sufficiently many re-solves) on the triangular domain shown below. 
+In this section, we demonstrate the accuracy of the proposed numerical method (both in the {\it weak} sense 
+described above, 
+as well as in the classical sense after sufficiently many re-solves) on the triangular domain shown below. 
 The reference solution for each of the examples is computed using a discretization with
@@
 \begin{rem}
-$2^{-150}$ is significantly smaller than machine precision, however the matrix entries corresponding to the
-corner interactions can be computed accurately by recentering the corner at the origin. 
+Though $2^{-150}$ is significantly smaller than machine precision, the matrix entries corresponding to the
+corner interactions can be computed accurately by {\color{red}translating the corners to the origin when 
+computing interactions of nearby points.} 
 \end{rem} 
 \begin{rem}
+Simple arguments from complex analysis show that when using graded meshes, in order to obtain full 
+machine precision 
+($\sim 1.11 \times 10^{-16}$) for solutions of the Neumann problem at any point in the interior 
+at least $10^{-16}$ away from a corner, it suffices to choose the smallest panel size (i.e. the size of the 
+panel closest to the corner) to be of size $2^{-100}.$ However, it is not true that the value of the density is 
+accurate to machine precision at all nodes. In fact the quality
+of the density deteriorates as one approaches the corner. Thus, in order to obtain accurate point values
+of the density to machine precision at all points which are $2^{-100}$ away from the corner, we use a smallest
+panel size of $2^{-150}$.
+
 It is well-known that a smallest panel size of $2^{-100}$ is sufficient to resolve the density corresponding
-to solutions of the Neumann problem in order to obtain full machine precision in the solution anywhere in the volume.
-However, it is not true the value of the density is accurate to machine precision at all the nodes. In fact the quality
+to solutions of the Neumann problem in order to obtain full machine precision {\color{red}($\sim 1.11 \times 10^{-16}$)} for the solution anywhere in the volume {\color{red} sufficiently far from the corner.}
+However, it is not true that the value of the density is accurate to machine precision at all nodes. In fact the quality
 of the density deteriorates as one approaches the corner. Thus, in order to obtain accurate point values

### 2020-01-07 paper_lap/05apparatus.tex
updating manuscript

@@
 \end{align}
-for all $f$ and $g$ in some subspace $S \subset L^2([0,L]).$ Here $\langle \cdot, \cdot \rangle$ denotes the inner product on $L^2([0,L])$ and $\| \cdot\|$ denotes the norm for $L^2([0,L]).$ Then, for all functions $f$ and $g$ in $S$
+for all $f$ and $g$ in some subspace $S_{\epsilon} \subset L^2([0,L]).$ Here $\langle \cdot, \cdot \rangle$ denotes the inner product on $L^2([0,L])$ and $\| \cdot\|$ denotes the norm for $L^2([0,L]).$ Then, for all functions $f$ and $g$ in $S_{\epsilon}$
 \begin{align}
@@
 \begin{remark1}
-We observe that if the solution to the boundary value problem is being calculated at a point $\by \in \mathbb{R}^2\setminus \Omega$ more than {\color{red}two panel lengths} away from the boundary curve $\Gamma$ then the Neumann density $\sigma$ obtained using the above result will give an accuracy of $\epsilon,$ ie.
+We observe that if the solution to the boundary value problem is being calculated at a point $\by \in \mathbb{R}^2\setminus \Omega$ more than one panel length away from the boundary curve $\Gamma$ then the Neumann density $\sigma$ obtained using the above result will give an accuracy of $\epsilon,$ ie.
 the function $K(\by,\gamma(t)) \in S_\epsilon.$ Thus accurate values of the solution in the far-field can be obtained almost immediately.
@@
 
-.
 Additionally, we denote the discretization of the interior Dirichlet operator (using the custom quadratures described in Section \ref{sec:disc_dir}) by $A.$ Let $\underline{f} = (f_1,\dots,f_N)^T$ where $f_i = f(x_i) \sqrt{w_i}$ and $f: \partial \Omega \to \mathbb{R}$ is the right-hand side of the exterior Neumann problem.
@@
 For a panel $\gamma([s_1,s_2])$ with discretization nodes $x_i,\dots,x_{i+M}$ corresponding to a Gauss-Legendre panel the density is smooth and thus it is expected to be well-represented in the basis of Legendre polynomials (shifted and scaled to the interval $[s_1,s_2]$).
-Hence standard interpolation techniques can be used to obtain an accurate approximation to the density $\sigma$ on the interval $s_1 \le s\le s_2$ (see \cite{} for a detailed description of this process and quantitative estimates on the accuracy of the result).
+Hence standard interpolation techniques can be used to obtain an accurate approximation to the density $\sigma$ on the interval $s_1 \le s\le s_2$ .
 Typically we use 16th order Gauss-Legendre panels and choose their sizes so that their length is no more than their distance to the nearest corner.
-{\color{red}This latter choice guarantees that for any $\epsilon>0$ there exists an $M$ such that if the Gauss-Legendre panels are discretized using an $M$-point Gauss-Legendre rule then the density on that panel can be interpolated to relative precision $\epsilon$ in an $L^2$-sense.}
+This latter choice guarantees that for any $\epsilon>0$ there exists an $M$ such that if the Gauss-Legendre panels are discretized using an $M$-point Gauss-Legendre rule then the density on that panel can be interpolated to relative precision $\epsilon$ in an $L^2$-sense.
+(We discuss a sketch of a proof in~\cref{sec:appb})
 

### 2020-01-07 paper_lap/manuscript.tex
updating manuscript

@@
 \input{07conc}
+
 \section*{Appendix A}
@@
 \begin{align}
-H(t) =\int _{\Gamma\backslash B_{2r}(\bx)}\sum {t^n i}\left(\frac{1}{(x(s)+i y(s))^{n+1}}-\frac{1}{(x(s)-i y(s))^{n+1}} \right)\,{\rm d}s.
+H(t) =\int _{\Gamma\backslash B_{2r}(\bx)}\sum {t^n i}\left(\frac{1}{(x(s)+i y(s))^{n+1}}-\frac{1}{(x(s)-i y(s))^{n+1}} \right) f(s)\,{\rm d}s.
 \end{align}
@@
 
+\section{Appendix B}
+\label{sec:appb}
+In this section, we demonstrate that for a panel which is away from the corner, which is discretized using $M$ Gauss-Legendre nodes, where the solution is computed using the adjoint of a Dirichlet discretization, the density can be interpolated
+accurately at any point on the panel. As before let $\Omega$ denote a polygonal domain with boundary $\Gamma$. Let
+$L$ denote the length of the boundary, and let $\gamma: [-L/2,L/2]$ denote an arc-length parameterization of the boundary.
+Let $\gamma([s_{1},s_{2}])$ be a panel discretized using $M$ Gauss-Legendre nodes be such that if $r_{0}$ denotes
+the distance to the closest corner on the particular edge, the length of the panel $L_{0}<r_{0}/2$, i.e. the panel
+is separated from the nearest corner by at least two times its own length.
+Further assume that no point on the boundary $\Gamma$ which is not on the same edge as as $\gamma([s_{1},s_{2}])$ is contained in some $\rho-$Bernstein ellipse
+corresponding to the line segment $\gamma([s_{1},s_{2}])$ with $\rho>1$.
+Furthermore suppose that all of the panels away from the corner and not on the edge containing the segment $\gamma([s_{1},s_{2}])$ are such that any point on $\gamma([s_{1},s_{2}])$ is not contained in their $\rho-$ Bernstein ellipse.
+Both of these assumptions can always be met by choosing sufficiently small panels away from the corners. Finally 
+assume that all panels at any corner $r_{c}$ are such that any point on $\gamma([s_{1},s_{2}])$ is at least $2r_{c}$ 
+away from the corner vertex. Under all of these assumptions, it can be shown that the accuracy in computing the
+Legendre coefficients of the density corresponding to the Neumann problem, is the same as the accuracy
+of a related Dirichlet problem where the boundary data is resolved with controlled error on the given discretization.
+
+Let $A$ denote the operator corresponding to interior Dirichlet problem using a double layer potential. Let $g$ denote the
+right hand side for the Neumann problem, let $\sigma$ denote the corresponding solution. Let $f$ be a Legendre polynomial of
+degree $n$ scaled to the panel $\gamma_{[s_{1},s_{2}]}$ and $0$ everywhere else. Then
+\begin{equation}
+\left<\sigma, f \right> = \left< (A^{T})^{-1} g, f\right> = \left< g, A^{-1} f \right> = <g, \sigma_{f}> \, ,
+\end{equation}
+where $\sigma_{f}$ is the solution of the interior Dirichlet problem with boundary data $f$ using a double layer potential.
+
+Using~\cref{lem_adjm}, the above statement implies that the error in computing the $n$ Legendre coefficient of
+the density for the Neumann problem, is the same as error in computing the solution of a Dirichlet problem with 
+data given by a Legendre polynomial on the same edge.  This seems problematic since the right hand side
+is not smooth, however, in the special case of polygonal domains, this problem is alleviated since the kernel corresponding
+to the double layer potential is identically zero on line segments.
+
+Let $V$ denote the collection of corner points in parameter space $[0,L]$, i.e. $a \in V$ if $\gamma(a)$ is a corner vertex.
+Recall that $\sigma_{f}$ denote the solution to the Dirichlet problem with boundary data $f$, i.e., 
+$\sigma_{f}$ satisfies
+\begin{equation}
+\sigma_{f}(s)   + \int_{0}^{L} k(s,t) \sigma_{f}(t) dt  = f(s) \,  \quad s\in[0,L]\setminus{V}.
+\end{equation}
+ Then $\sigma_{f} = f + \tilde{\sigma}$ where $\tilde{\sigma}$ satisfies the integral equation
+ \begin{equation}
+-\tilde{\sigma}+ \int_{0}^{L} k(s,t) \tilde{\sigma}(t) dt = \int_{s_{1}}^{s_{2}} k(s,t) f(t) dt \, , \quad s\in[0,L] \setminus V \, ,
+ \end{equation}
+i.e, $\tilde{\sigma}$ is the solution of Dirichle with data at $\tilde{f}$ given by
+\begin{equation}
+\tilde{f}(s) = \int_{s_{1}}^{s_{2}} k(s,t) f(t) dt \, , s \in [0,L] \setminus V \, .
+\end{equation}
+Now there are two concerns that need to be addressed. First, the accuracy of computing $\tilde{f}(s)$ 
+for any point $s \in [0,L]$ using an $M$ point Gauss-Legendre quadrature on $[s_{1},s_{2}]$, and secondly, 
+the resolution of the function $\tilde{f}(s)$ on the given discretization of the boundary.
+
+For any $s$ which is contained on the same segment as $\gamma_{[s_{1},s_{2}]}$, the kernel $k(s,t)$ is identically $0$.
+Thus the boundary data $\tilde{f}(s)=0$  on the same edge as the panel $\gamma([s_{1},s_{2}])$. 
+We further observe that $f(t)$ is an entire function when extended to the complex plane (since it is a Legendre polynomial)
+and the nearest singularity of the function $k(s,t)$ in the complex plane as a function of $t$ is corresponding to $\gamma(s)$.
+Since we have assumed that no other point on the boundary $\Gamma$ is contained in the $\rho-$ bernstein ellipse
+of the panel $\gamma[(s_{1},s_{2})]$, 
+the error in computing $\tilde{f}(s)$ using an $M$ point Gauss-Legendre rule is bounded by $C \rho^{-M}$, where
+the constant $C$ is related to the boundedness of the function $k(s,t)$ when $t$ is complexified.
+(Note the error is not $\rho^{-2M}$ since $P_{M}$ would grow like $\rho^{M}$ on the $\rho-$ Bernstein ellipse.) 
+Thus the function $\tilde{f}(s)$ can be computed to any desired precision by increasing the order of quadrature nodes
+used to compute the integrals.
+
+With regards to the resolution of the of the function $\tilde{f}(s)$ on the given discretization of the boundary, 
+we note that the closest singularity of the function $\tilde{f}(s)$ when restricted to a panel away from the corner
+and not on the same edge as $\gamma([s_{1},s_{2}])$ is the closest point on the panel $\gamma([s_{1},s_{2}])$. 
+However, since we have assumed that all panels away from corners are such that no point on $\gamma([s_{1},s_{2}])$ 
+is contained in their $\rho-$ Bernstein ellipse, the error in resolving the function $\tilde{f}(s)$ using an $M$ point Gauss-Legendre
+or Chebyshev panel is bounded by $C \rho^{-M}$. Note that the behavior of $\tilde{f}(s)$ in the complex plane is related
+to the behavior of $k(s,t)$ in the complex $s$ plane and hence can be made $O(1)$.
+For the panels, at the corner, based on the proof in Appendix A, the error in resolving the function $\tilde{f}(s)$ when
+truncated to a taylor series of order $N$ is less than $C 2^{-N}$, since all points on $\gamma([s_{1},s_{2}])$ are 
+well-separated from corners by twice the panel length $r_{c}$.
+Thus, by making the panels small enough, $\rho$ can be increased arbitrarily to obtain desired tolerances on the boundary data $\tilde{f}(s)$ on the corresponding discretization of the boundary.
+
+ Thus, the boundary data $\tilde{f}(s)$ is piecewise analytic , which can be approximated to any desired tolerance by appropriately reducing the panel sizes.
+This is the precise setup for which the discretization of the Dirichlet problem is designed to obtain accurate solutions to the density $\tilde{\sigma}$.
 \end{document}

### 2020-01-07 paper_lap/03bvp.tex
updating paper to clean out comments

@@
 \begin{theorem}\label{thm:potlim}
-Suppose the point $\bx$ approaches a point $\bx_0 = \gamma(t_0)$ from the inside along a path such that 
+Suppose the point $\bx$ approaches a point $\bx_0 = \gamma(t_0)$ (where $\bx_{0}$ is not a corner vertex) from the inside along a path such that 
 \begin{align}
@@
 \end{align}
-for some $\alpha >0.$ Then {\color{red}for any continuous function $\sigma:\Gamma \to \mathbb{R},$}
+for some $\alpha >0.$ Then for any continuous function $\sigma:\Gamma \to \mathbb{R},$
 \begin{align}
@@
 \end{theorem}
-{\color{red}CHECK THE POWERS}
 

### 2020-01-07 paper_lap/05apparatus.tex
updating paper to clean out comments

@@
 The following theorem shows that the right-hand side $\underline{f}_0$ can be computed only using local data (i.e. values of the weak solution in the vicinity of the corner).\\
-{\color{red} Manas: there is something a little bad with this proof - Taylor series vs $\epsilon$}
 \begin{theorem}
@@
 \end{align}
-{\color{red}A similar argument shows that $f(t)-h(t)$ is interpolable on $[-2\delta,-\delta]$ and $[\delta,2\delta].$}
+A similar argument shows that $f(t)-h(t)$ is interpolable on $[-2\delta,-\delta]$ and $[\delta,2\delta].$
 On the other hand, by construction,

### 2020-01-07 paper_lap/06num.tex
updating manuscript
updating paper to clean out comments

@@
 Though $2^{-150}$ is significantly smaller than machine precision, the matrix entries corresponding to the
-corner interactions can be computed accurately by {\color{red}translating the corners to the origin when 
-computing interactions of nearby points.} 
+corner interactions can be computed accurately by translating the corners to the origin when 
+computing interactions of nearby points.
 \end{rem} 
@@
 It is well-known that a smallest panel size of $2^{-100}$ is sufficient to resolve the density corresponding
-to solutions of the Neumann problem in order to obtain full machine precision {\color{red}($\sim 1.11 \times 10^{-16}$)} for the solution anywhere in the volume {\color{red} sufficiently far from the corner.}
+to solutions of the Neumann problem in order to obtain full machine precision ($\sim 1.11 \times 10^{-16}$) for the solution anywhere in the volume sufficiently far from the corner.
 However, it is not true that the value of the density is accurate to machine precision at all nodes. In fact the quality
@@
 \end{rem}
-In these examples, the solutions are computed dense linear solves.
+In these examples, the solutions are computed via dense linear solves.
 

### 2020-01-07 paper_lap/manuscript.tex
updating paper to clean out comments

@@
 
-\section*{Appendix A}
+\appendix
+\section{Approximation of data on corner panels for re-solve}
 Here we give explicit bounds for the rate of convergence of the contribution of the rest of the boundary to a corner panel.
@@
 
-\section{Appendix B}
+\section{Strong approximation of density away from corner panels}
 \label{sec:appb}
@@
 This is the precise setup for which the discretization of the Dirichlet problem is designed to obtain accurate solutions to the density $\tilde{\sigma}$.
+
+ \bibliographystyle{plain}
+ \bibliography{bib_file2}
 \end{document}

### 2020-01-07 paper_lap/06num.tex
small changes to lap_neumann2 to plot scattering proboelm in the volume and vertices and small cahnges to numerical results too

@@
 In figure~\cref{fig:far-field}, we compute the error in the solution at target
-locations in the volume for the right hand side given by
+locations for a scattering problem whose right hand side is given by a collection of three interior charges
 \begin{equation}
-f(\bx) = 
+u(\bx) = \sum_{j=1}^{3} \log |\bx - \bx_{j}| \, ,  
 \end{equation}
+where the locations $\bx_{j}$ are denoted by square dots in~\cref{fig:analytictest}. Note that the density $\sigma$ plotted
+as a function of arclength goes to infinity at the corner vertices, indicating that the native Dirichlet discretization 
+presented in~\cref{sec:disc_dir} wouldn't have sufficed. However, the potential in the volume is accurate to 14 digits at
+target locations away from the boundary.
 
@@
 P = \begin{bmatrix}
+-0.823641009939200 & -0.139714174784448 \\
+ -0.139714174784448 &  -1.1421444446470226
 \end{bmatrix} \, , \quad \text{Error} = 
 \begin{bmatrix} 
+2.3 \times 10^{-15} & 7.9 \times 10^{-16} \\
+1.3 \times. 10^{-14} & 2.7 \times 10^{-15}
 \end{bmatrix}
@@
 discussed in~\cref{sec:resolve} iteratively, and compare the obtained density with the reference density after 20,40,60, and
-80 iterations of resolves in the vicinity of one of the corners. The reference density and the errors are shown in ~\cref{fig:dens-error}.
+80 iterations of resolves in the vicinity of one of the corners.
+The reference density and the errors are shown in ~\cref{fig:dens-error}.
+Furthermore, to highlight the need for special purpose discretizations in the vicinity of corners in the adjoint method, we also compare the solution computed using a graded mesh in the vicinity of corners, where the smallest panel is identical
+to the one after resolves. So for 20 iterations, the smallest panel is $2^{-20}$ times the original panel, for $40$ iterations,
+the smallest panel is $2^{-40}$ times the original panel and so on.
 

### 2020-01-07 paper_lap/06num.tex
conclusion and minor edits

--- 2020-01-07 paper_lap/06num.tex
@@
 ($\sim 1.11 \times 10^{-16}$) for solutions of the Neumann problem at any point in the interior 
-at least $10^{-16}$ away from a corner, it suffices to choose the smallest panel size (i.e. the size of the 
-panel closest to the corner) to be of size $2^{-100}.$ However, it is not true that the value of the density is 
+at least $10^{-16}$ away from a corner, it suffices to choose the smallest panel (i.e. the size of the 
+panel closest to the corner) to be of size $2^{-100}.$ However, resulting values of the density will not be 
 accurate to machine precision at all nodes. In fact the quality
 of the density deteriorates as one approaches the corner. Thus, in order to obtain accurate point values
-of the density to machine precision at all points which are $2^{-100}$ away from the corner, we use a smallest
-panel size of $2^{-150}$.
-
-It is well-known that a smallest panel size of $2^{-100}$ is sufficient to resolve the density corresponding
-to solutions of the Neumann problem in order to obtain full machine precision ($\sim 1.11 \times 10^{-16}$) for the solution anywhere in the volume sufficiently far from the corner.
-However, it is not true that the value of the density is accurate to machine precision at all nodes. In fact the quality
-of the density deteriorates as one approaches the corner. Thus, in order to obtain accurate point values
-of the density to machine precision at all points which are $2^{-100}$ away from the corner, we use a smallest
+of the density to machine precision at all points which are at least $2^{-100}$ away from the corner, we use a smallest
 panel size of $2^{-150}$. 
@@
 
-The potential at target locations which are more than 1 panel length away is the inner product of the 
-density with a smooth function. For a target location $\boldsymbol{y}$, we compute the solution via the formula,
+The potential at target locations which are sufficiently far from the boundary (i.e. at least one panel length away from 
+every panel) is the inner product of the 
+density with a smooth function and hence can be computed accurately without re-solving. For a target 
+location $\boldsymbol{y}$, we compute the solution via the formula,
 \begin{equation}
@@
 
-Another example of weak quantity is the polarization tensor associated with a domain. This requires the solution of the
+Another example of a ``weak quantity'' is the polarization tensor associated with a domain. This requires the solution of the
 exterior problems with boundary data $f_{1} = \bnu_{1}$ or $f_{2} = \bnu_{2}$. Let $\sigma_{1}$ and $\sigma_{2}$ denote
@@
 
-In order to demonstrate the capability to obtain the true density at the corner panels, we  apply the procedure
+In order to demonstrate the accuracy of the corner re-solving approach in obtaining the true density at the corner panels, we  apply the procedure
 discussed in~\cref{sec:resolve} iteratively, and compare the obtained density with the reference density after 20,40,60, and
@@
 \subsection{Performance}
-In this section, we demonstrate the performance of the solver of two large domains. We solve scattering problems in the
-exterior of a magnetron like region, and the maple leaf. The right hand side is the potential due to a collection of charges in the exterior of the region, and we impose that
+In this section, we demonstrate the performance of the solver on two large domains. We solve scattering problems in the
+exterior of a ``broken wheel'' region, and the maple leaf. The right hand side is the potential due to a collection of charges in the exterior of the region, and we impose that

### 2020-01-07 paper_lap/07conc.tex
conclusion and minor edits

\section{Conclusion and future work}

In this paper we described a method for obtaining solutions to Laplace's equation with Neumann boundary conditions 
on polygonal domains given an accurate discretization of a corresponding Dirichlet problem, based on applying the 
adjoint method to an appropriately-chosen boundary integral equation. The resulting solutions are accurate in a 
``weak sense'', allowing evaluation of the solution at points which are located sufficiently far from the boundary of the 
domain. We then presented a method for using these ``weak solutions'' to obtain accurate solutions to the Neumann problem 
in an $L^\infty$-sense arbitrarily close to the corner in a computationally efficient manner.

Though the present paper treats only Laplace's equation for polygonal domains, the method shown here extends 
much more broadly. In particular, the approach easily extends to accommodate curved boundaries. Moreover, in addition 
to Laplace's equation, this approach can be easily adapted to solve the Helmholtz equation and the biharmonic equation with analogous boundary conditions. A manuscript detailing this extension is currently in preparation.

### 2020-01-07 paper_lap/manuscript.tex
conclusion and minor edits

@@
 \label{sec:appb}
-In this section, we demonstrate that for a panel which is away from the corner, which is discretized using $M$ Gauss-Legendre nodes, where the solution is computed using the adjoint of a Dirichlet discretization, the density can be interpolated
+In this section, we demonstrate that for a panel which is sufficiently far from the corner and  discretized using $M$ Gauss-Legendre nodes, the density computed using the adjoint of a Dirichlet discretization can be interpolated
 accurately at any point on the panel. As before let $\Omega$ denote a polygonal domain with boundary $\Gamma$. Let
@@
 \begin{equation}
-\left<\sigma, f \right> = \left< (A^{T})^{-1} g, f\right> = \left< g, A^{-1} f \right> = <g, \sigma_{f}> \, ,
+\left<\sigma, f \right> = \left< (A^{T})^{-1} g, f\right> = \left< g, A^{-1} f \right> = \langle g, \sigma_{f}\rangle \, ,
 \end{equation}
@@
 Using~\cref{lem_adjm}, the above statement implies that the error in computing the $n$ Legendre coefficient of
-the density for the Neumann problem, is the same as error in computing the solution of a Dirichlet problem with 
-data given by a Legendre polynomial on the same edge.  This seems problematic since the right hand side
-is not smooth, however, in the special case of polygonal domains, this problem is alleviated since the kernel corresponding
-to the double layer potential is identically zero on line segments.
+the density for the Neumann problem is the same as the error in computing the solution of a Dirichlet problem with 
+data given by a Legendre polynomial on the same panel.  %This seems problematic since the right hand side
+%is not smooth, however, in the special case of polygonal domains, this problem is alleviated since the kernel corresponding
+%to the double layer potential is identically zero on line segments.
 

### 2020-01-08 paper_lap/01intro.tex
updating paper

@@
 
- Another class of methods is based on approximating the solution to the two-dimensional problem by rational functions \cite{} with poles exponentially clustered near the corners.
-While this approach allows for fast evaluation of the solution near the boundary of the domain, current implementations are specialized to two-dimensions, are significantly slower than other approaches for large problems, and have difficulties handling complicated domains and boundary data.
+ Another class of methods is based on approximating the solution to the two-dimensional problem by rational functions \cite{gopal2019solving} with poles exponentially clustered near the corners.
+While this approach allows for fast evaluation of the solution near the boundary of the domain, current implementations are specialized to two-dimensions, and do not scale well  for large problems.
 
- Finally, a recent approach is based on leveraging explicit representations of the solutions to the BIEs in the vicinity of the corner as sums of fractional powers depending on the angle \cite{}.
+ Finally, a recent approach is based on leveraging explicit representations of the solutions to the BIEs in the vicinity of the corner as sums of fractional powers depending on the angle \cite{serkhacha}.
 Using these representations one can construct high-order discretizations which introduce relatively few extra degrees of freedom near the corners (i.e.
 an amount which is comparable to the number required for smooth portions of the boundary).
-This approach has been used to generate efficient discretizations for Dirichlet problems for Laplace's equation on polygonal domains\cite{}.
+This approach has been used to generate efficient discretizations for Dirichlet problems for Laplace's equation on polygonal domains\cite{hoskins2019numerical}.
 
@@
  The paper is organized as follows.
-In Section \ref{} we review relevant mathematical results associated with Laplace's equation.
-Section \ref{} describes the reduction of boundary value problems to boundary integral equations via potential theory, and reviews the analytic behavior of solutions near a corner.
-In Section \ref{} we present our numerical algorithm and the associated analysis.
-Finally, in Section \ref{} we illustrate its application with several numerical experiments.
+In~\cref{sec:mprelim} we review relevant mathematical results associated with Laplace's equation.
+~\cref{sec:bvp} describes the reduction of boundary value problems to boundary integral equations via potential theory, and reviews the analytic behavior of solutions near a corner.
+In~\cref{sec:nprelim,sec:napp} we present our numerical algorithm and the associated analysis.
+Finally, in ~\cref{sec:num} we illustrate its application with several numerical experiments.

### 2020-01-08 paper_lap/03bvp.tex
updating paper

@@
- \section{Boundary integral equations}
+ \section{Boundary integral equations \label{sec:bvp}}
 A classical technique for solving the four Laplace boundary value problems given above is to reduce them to boundary integral equations.

### 2020-01-08 paper_lap/04nprelim.tex
updating paper to clean out comments
updating paper

@@
-\section{Numerical preliminaries}
+\section{Numerical preliminaries \label{sec:nprelim}}
 In this section we summarize the numerical tools which are necessary for the main result.
@@
 When $s_i$ corresponds to a corner panel special care must be taken.
-Instead, using an algorithm for generating generalized Gaussian quadratures \cite{}, quadrature nodes are chosen which integrate
+Instead, using an algorithm for generating generalized Gaussian quadratures \cite{bremer2010}, quadrature nodes are chosen which integrate
 \begin{align}

### 2020-01-08 paper_lap/05apparatus.tex
updating paper

@@
-\section{Numerical apparatus}
+\section{Numerical apparatus \label{sec:napp}}
 \subsection{Adjoint method}
@@
 
-\subsection{Weak corner re-solving}
+\subsection{Weak corner re-solving \label{sec:resolve}}
 In this section we address the problem highlighted in the previous one; namely, the accurate evaluation of the solution to the exterior Neumann problem in the vicinity of a corner.

### 2020-01-08 paper_lap/06num.tex
updating paper

@@
-\section{Numerical results}
+\section{Numerical results \label{sec:num}}
 \subsection{Accuracy}
@@
 the length of the first macroscopic panel away from the corner (see~\cref{fig:dom}).
+
+\begin{figure}
+\begin{center}
+\includegraphics[width=0.7\linewidth]{media/discretization}
+\caption{Problem domain and panel discretization of the boundary. The discretization on the left is based on using the Dirichlet
+discretization at corner panels (indicated by blue panels) discussed in~\cref{sec:disc_dir}, while the discretization on the right is a sample discretization with 2 levels of refinement in the vicinity of the corner.
+All the panels in black are discretized using scaled Gauss-Legendre nodes.
+The square ticks indicate location of the charges $\bx_{j}$ for defining the boundary data for the scattering problem.}
+\end{center}
+\label{fig:dom}
+\end{figure}
+
 \begin{rem}
@@
 \begin{equation}
+\label{eq:farfieldpot}
 u(\by) = \int_{\Gamma} G(\bx,\by) \sigma(\bx) dS_{\bx} \approx \sum_{i=1}^{N}  G(\gamma(s_{i}),\by) \sigma_{i} \sqrt{w_{i}}
@@
 \begin{equation}
-u(\bx) = \sum_{j=1}^{3} \log |\bx - \bx_{j}| \, ,  
+\label{eq:scatboundarydata}
+f(\bx) = -\nabla  \left(\sum_{j=1}^{3} \log |\bx - \bx_{j}|  \right)  \cdot \bnu(\bx)\, ,  
 \end{equation}
-where the locations $\bx_{j}$ are denoted by square dots in~\cref{fig:analytictest}. Note that the density $\sigma$ plotted
+where the locations $\bx_{j}$ are denoted by square dots in~\cref{fig:scatteringtest}. Note that the density $\sigma$ plotted
 as a function of arclength goes to infinity at the corner vertices, indicating that the native Dirichlet discretization 
@@
 target locations away from the boundary. 
+\begin{figure}
+\begin{center}
+\includegraphics[width=\linewidth]{media/weaktest}
+\caption{Left panel: Solution to Neumann problem with data given by~\cref{eq:scatboundarydata}, center panel: error in computing the potential in the formula using the underlying smooth quadrature~\cref{eq:farfieldpot}, and on the right the density $\sigma$ as a function of arc-length}.
+\end{center}
+\label{fig:scatteringtest}
+\end{figure}
 
@@
 
+\begin{figure}
+\begin{center}
+\includegraphics[width=\linewidth]{media/density}
+\caption{Top row: (left) Illustrative mesh used for iteratively computing the solution in the vicinity of a corner, (right) the density in the vicinity of one of the corner panels.
+Bottom row: error in computing the density, where $\tilde{\sigma}$ denotes the density computed using special purpose discretizations at corner panels, and $\tilde{\sigma_{g}}$ denotes the density using a graded mesh with the smallest panel equal to the length of the smallest panel after the iterative resolve procedure.
+The errors are scaled by square roots of the quadrature weights.
+}.
+\end{center}
+\label{fig:dens-error}
+\end{figure}
+
 After re-solving the density, we also compute the solution at target locations on a tensor product polar grid, where the grid
@@
 The reference solution and the errors are demonstrated in~\cref{fig:vol-plot}.
+\begin{figure}
+\begin{center}
+\includegraphics[width=\linewidth]{media/volume}
+\caption{Top row: Solution on the volume after 10, 20, and 40 iterations of resolve.
+The target locations are a tensor product polar grid, where the nodes are exponentially spaced in the radial direction.
+The closest node is approximately $10^{-13}$ away from the corner.
+Near quadrature is handled via adaptive integration except for the corner panel where the smooth quadrature weights are used.
+Bottom row: analogous results where the solution is computed using a graded mesh.
+}.
+\end{center}
+\label{fig:vol-plot}
+\end{figure}
+
 \subsection{Performance}
 In this section, we demonstrate the performance of the solver on two large domains. We solve scattering problems in the
-exterior of a ``broken wheel'' region, and the maple leaf. The right hand side is the potential due to a collection of charges in the exterior of the region, and we impose that
+exterior of a ``broken wheel'' region. The boundary data is given by
+\begin{equation}
+f(x) = \nabla  \sum_{j=1}^{57} c_{j} \log| \bx - \bx_{j}| \cdot \bnu(\bx) \, , 
+\end{equation}
+where there is one $\bx_{j}$ located in each of the spokes, one of the $\bx_{j}$ is in the central disc, and the remaining $50$ $\bx_{j}$ are chosen randomly in the exrterior of the bounding disc containing the domain.
+The strengths $c_{j}$ are chosen such that they average to $0$.
+The domain contains $108$ corners, was discretized using $22240$ nodes and required $105$ iterations to converge to a residue of $10^{-15}$.
+The matrix at each iteration was applied using an FMM whose tolerance was also set to $10^{-15}$.
+The solution was computed in $15$ secs, and plotted at a $500\times 500$ grid of targets in $6.5$ secs.
+All of the results have been computed on a single core on a Macintosh machine with Intel core i5 2.3GHz processors.
+In~\cref{fig:magnetron}, we plot the scattered field, the right hand side, and the computed density.
+
+\begin{figure}
+\begin{center}
+\includegraphics[width=\linewidth]{media/magnetron}
+\caption{(left): Boundary data as a function of arclength, (center): absolute value of density as a function of arclength, and 
+(right): solution in the volume computed using an FMM.}
+\label{fig:magnetron}
+\end{center}
+\end{figure}

### 2020-01-08 paper_lap/01intro.tex
updating apper

@@
  In this paper we describe a method for solving Laplace's equation on polygonal domains with Neumann boundary conditions given only a discretization of a corresponding Dirichlet problem.
-Our approach is based on the adjoint method \cite{}.
+Our approach is based on using the discretization of a suitable adjoint problem.
 In particular, we show that if the transpose of the discretization of a suitable Dirichlet BIE is used, then the resulting solution will be accurate in a ``weak sense''; namely, it can be used to compute inner products with smooth functions accurately, though it cannot be interpolated.
@@
 In~\cref{sec:nprelim,sec:napp} we present our numerical algorithm and the associated analysis.
-Finally, in ~\cref{sec:num} we illustrate its application with several numerical experiments.
+Finally, in~\cref{sec:num} we illustrate its application with several numerical experiments.

### 2020-01-08 paper_lap/03bvp.tex
updating apper

@@
 &\lim_{\bx \to \bx_0} \cS[\sigma](\bx) = \cS[\sigma](\bx_0)\\
-&\lim_{\bx \to \bx_0} \cD[\sigma](\bx) = \cD[\sigma](\bx_0)- \sigma(\bx_0)\\
-&\lim_{\bx \to \bx_0} \left.\frac{{\rm d}}{{\rm d}\tau}\right|_{\tau= 0}\cS[\sigma](\bx+\tau \bnu(\bx_0)) = \left.\frac{{\rm d}}{{\rm d}\tau}\right|_{\tau= 0}\cS[\sigma](\bx_0+\tau \bnu(\bx_0))+ \sigma(\bx_0).
+&\lim_{\bx \to \bx_0} \cD[\sigma](\bx) = \cD[\sigma](\bx_0)- \frac{\sigma(\bx_0)}{2})\\
+&\lim_{\bx \to \bx_0} \left.\frac{{\rm d}}{{\rm d}\tau}\right|_{\tau= 0}\cS[\sigma](\bx+\tau \bnu(\bx_0)) = \left.\frac{{\rm d}}{{\rm d}\tau}\right|_{\tau= 0}\cS[\sigma](\bx_0+\tau \bnu(\bx_0))+ \frac{\sigma(\bx_0)}{2}.
 \end{align}
@@
 &\lim_{\bx \to \bx_0} \cS[\sigma](\bx) = \cS[\sigma](\bx_0)\\
-&\lim_{\bx \to \bx_0} \cD[\sigma](\bx) = \cD[\sigma](\bx_0)+ \sigma(\bx_0)\\
-&\lim_{\bx \to \bx_0} \left.\frac{{\rm d}}{{\rm d}\tau}\right|_{\tau= 0}\cS[\sigma](\bx+\tau \bnu(\bx_0)) = \left.\frac{{\rm d}}{{\rm d}\tau}\right|_{\tau= 0}\cS[\sigma](\bx_0+\tau \bnu(\bx_0))- \sigma(\bx_0).
+&\lim_{\bx \to \bx_0} \cD[\sigma](\bx) = \cD[\sigma](\bx_0)+ \frac{\sigma(\bx_0)}{2}\\
+&\lim_{\bx \to \bx_0} \left.\frac{{\rm d}}{{\rm d}\tau}\right|_{\tau= 0}\cS[\sigma](\bx+\tau \bnu(\bx_0)) = \left.\frac{{\rm d}}{{\rm d}\tau}\right|_{\tau= 0}\cS[\sigma](\bx_0+\tau \bnu(\bx_0))- \frac{\sigma(\bx_0)}{2}.
 \end{align}
@@
 \begin{align}
-f(s)= - \sigma(s)+ \int_0^L k(t,s)\,\sigma(t)\,{\rm d}t,
+f(s)= - \frac{\sigma(s)}{2}+ \int_0^L k(t,s)\,\sigma(t)\,{\rm d}t,
 \label{bie_intd}
@@
 \begin{align}
-f(s)=  \sigma(s)+ \int_0^L (k(t,s) + 1)\,\sigma(t)\,{\rm d}t,
+f(s)=  \frac{\sigma(s)}{2}+ \int_0^L (k(t,s) + 1)\,\sigma(t)\,{\rm d}t,
 \end{align}\label{bie_extd}
@@
 \begin{align}
-f(s)=  \sigma(s)+ \int_0^L (k(s,t) + 1)\,\sigma(t)\,{\rm d}t,
+f(s)=  \frac{\sigma(s)}{2}+ \int_0^L (k(s,t) + 1)\,\sigma(t)\,{\rm d}t,
 \label{bie_intn}
@@
 \begin{align}
-f(s)=  \sigma(s)+ \int_0^L k(s,t) \,\sigma(t)\,{\rm d}t,
+f(s)=  \frac{\sigma(s)}{2}+ \int_0^L k(s,t) \,\sigma(t)\,{\rm d}t,
 \label{bie_extn}
@@
 
-In the remainder of this section we assume $\Gamma$ is an open wedge with sides of length one and interior angle $\pi \alpha$ with $0 <\alpha<2.$ Let $\gamma:[-1,1] \rightarrow \Gamma$ be an arc length parametrization of $\Gamma$ and $\nu:[-1,1] \rightarrow \mathbb{R}^2$ be the inward-pointing normal to $\Gamma.$
+In the remainder of this section, we assume $\Gamma$ is an open wedge with sides of length one and interior angle $\pi \alpha$ with $0 <\alpha<2.$ Let $\gamma:[-1,1] \rightarrow \Gamma$ be an arc length parametrization of $\Gamma$ and $\nu:[-1,1] \rightarrow \mathbb{R}^2$ be the inward-pointing normal to $\Gamma.$
 The following theorem  gives an explicit representation of the solutions of the boundary integral equation (\ref{bie_intd}) in this geometry.
@@
 \begin{align}
-f(t) = -\sigma(s) +\int_{-1}^1 k(t,s)  \sigma(t)\,{\rm d}t.
+f(t) = -\frac{\sigma(s)}{2} +\int_{-1}^1 k(t,s)  \sigma(t)\,{\rm d}t.
 \label{eqn_grho}
@@
 
-The following Corollary, proved in \cite{serkhacha} gives a characterization of the solutions to the Dirichlet and Neumann boundary integral equations in the vicinity of a corner.
+The following corollary, proved in \cite{serkhacha} gives a characterization of the solutions to the Dirichlet and Neumann boundary integral equations in the vicinity of a corner.
 

### 2020-01-08 paper_lap/05apparatus.tex
updating apper

@@
 \section{Numerical apparatus \label{sec:napp}}
-\subsection{Adjoint method}
+\subsection{Adjoint discretization}
 
@@
 \begin{remark1}
+\label{rem:far-field-accuracy}
 We observe that if the solution to the boundary value problem is being calculated at a point $\by \in \mathbb{R}^2\setminus \Omega$ more than one panel length away from the boundary curve $\Gamma$ then the Neumann density $\sigma$ obtained using the above result will give an accuracy of $\epsilon,$ ie.
@@
 \begin{remark1}
+\label{rem:strong-sol-smooth}
 Similarly, if the point $\by \in \mathbb{R}^2 \setminus \Omega$ at which the solution to the Neumann boundary value problem is to be calculated lies close to a smooth panel then the density $\sigma$ near that point can be interpolated to a finer set of quadrature points and the value of $u(\by)$ can once again be obtained to precision $\epsilon.$ We note, however, that in general the density in the vicinity of a corner cannot be interpolated accurately.
@@
 
-For corner panels the nodes were constructed to enable stable interpolation of densities $s^\mu,$ $\mu \in 0 \cup [1/2,40],$ on the interval $s \in (-\delta,\delta)$ - assuming for simplicity that the corner is at $0$ and the panel is of length $2 \delta.$ As mentioned above, the density is expected to contain terms of the form $s^\mu$ for some finite collection of $\mu$ in the interval $(-1/2,1/2),$ and hence will not in general be stably interpolable on the interval $(-\delta,\delta).$ However, it is possible to use the density obtained using (\ref{eqn:adj_linalg}) to construct a sequence of nested problems in the neighborhood of the corner, the solutions of which enable accurate interpolation of the density arbitrarily close to the vertex.
+For corner panels the nodes were constructed to enable stable interpolation of densities $s^\mu,$ $\mu \in 0 \cup [1/2,50],$ on the interval $s \in (-\delta,\delta)$ - assuming for simplicity that the corner is at $0$ and the panel is of length $2 \delta.$ As mentioned above, the density is expected to contain terms of the form $s^\mu$ for some finite collection of $\mu$ in the interval $(-1/2,1/2),$ and hence will not in general be stably interpolable on the interval $(-\delta,\delta).$ However, it is possible to use the density obtained using (\ref{eqn:adj_linalg}) to construct a sequence of nested problems in the neighborhood of the corner, the solutions of which enable accurate interpolation of the density arbitrarily close to the vertex.
 The number of these problems depends only on the distance of the closest evaluation point to the corner.

### 2020-01-08 paper_lap/06num.tex
updating apper

@@
 a graded mesh in the vicinity of the corners, where the smallest panel at the corner is $2^{-150}$ times
-the length of the first macroscopic panel away from the corner (see~\cref{fig:dom}).
+the length of the first macroscopic panel away from the corner (see~\cref{fig:dom}). In these examples, the solutions are computed via dense linear solves.
 
@@
 The square ticks indicate location of the charges $\bx_{j}$ for defining the boundary data for the scattering problem.}
+\label{fig:dom}
 \end{center}
-\label{fig:dom}
 \end{figure}
@@
 \end{rem}
-In these examples, the solutions are computed via dense linear solves.
 
@@
 every panel) is the inner product of the 
-density with a smooth function and hence can be computed accurately without re-solving. For a target 
-location $\boldsymbol{y}$, we compute the solution via the formula,
+density with a smooth function and hence can be computed accurately without re-solving (see~\cref{rem:far-field-accuracy}). For a target 
+location $\boldsymbol{y}$, we compute the potential via the formula,
 \begin{equation}
@@
 \end{equation}
-In figure~\cref{fig:far-field}, we compute the error in the solution at target
+In~\cref{fig:scatteringtest}, we compute the error in the solution at target
 locations for a scattering problem whose right hand side is given by a collection of three interior charges
@@
 \caption{Left panel: Solution to Neumann problem with data given by~\cref{eq:scatboundarydata}, center panel: error in computing the potential in the formula using the underlying smooth quadrature~\cref{eq:farfieldpot}, and on the right the density $\sigma$ as a function of arc-length}.
+\label{fig:scatteringtest}
 \end{center}
-\label{fig:scatteringtest}
 \end{figure}
@@
 \end{equation}
-The polarization tensor as computed by the reference solution, and the error in computation using the adjoint method
+The polarization tensor as computed by the reference solution, and the error in computation using the adjoint discretization
 are given by
@@
 The reference density and the errors are shown in ~\cref{fig:dens-error}.
-Furthermore, to highlight the need for special purpose discretizations in the vicinity of corners in the adjoint method, we also compare the solution computed using a graded mesh in the vicinity of corners, where the smallest panel is identical
-to the one after resolves. So for 20 iterations, the smallest panel is $2^{-20}$ times the original panel, for $40$ iterations,
-the smallest panel is $2^{-40}$ times the original panel and so on.
+Furthermore, to highlight the need for special purpose discretizations in the vicinity of corners in the adjoint discretization, we also compare the solution computed using a graded mesh in the vicinity of corners, where the size of the smallest panels for both discretizations are equal.
 
@@
 }.
+\label{fig:dens-error}
 \end{center}
-\label{fig:dens-error}
 \end{figure}
@@
 The target locations are a tensor product polar grid, where the nodes are exponentially spaced in the radial direction.
-The closest node is approximately $10^{-13}$ away from the corner.
+The closest target location is approximately $10^{-13}$ away from the corner.
 Near quadrature is handled via adaptive integration except for the corner panel where the smooth quadrature weights are used.
@@
 }.
+\label{fig:vol-plot}
 \end{center}
-\label{fig:vol-plot}
 \end{figure}
@@
 \subsection{Performance}
-In this section, we demonstrate the performance of the solver on two large domains. We solve scattering problems in the
+In this section, we demonstrate the performance of the solver by solving a scattering problem in the
 exterior of a ``broken wheel'' region. The boundary data is given by
@@
 \caption{(left): Boundary data as a function of arclength, (center): absolute value of density as a function of arclength, and 
-(right): solution in the volume computed using an FMM.}
+(right): $\log_{10}$ of the absolute value of the solution in the volume computed using an FMM.}
 \label{fig:magnetron}

### 2020-01-08 paper_lap/07conc.tex
updating apper

@@
 In this paper we described a method for obtaining solutions to Laplace's equation with Neumann boundary conditions 
-on polygonal domains given an accurate discretization of a corresponding Dirichlet problem, based on applying the 
-adjoint method to an appropriately-chosen boundary integral equation. The resulting solutions are accurate in a 
+on polygonal domains given an accurate discretization of a corresponding Dirichlet problem. 
+The resulting solutions are accurate in a 
 ``weak sense'', allowing evaluation of the solution at points which are located sufficiently far from the boundary of the 

### 2020-01-08 paper_lap/manuscript.tex
updating apper

@@
 \usepackage{amsmath,amsthm,amssymb,amscd,fancybox,epsfig,float,subfigure}
+\usepackage{authblk}
 \usepackage[margin=1in]{geometry}
@@
 \begin{document}
- \title{Dirichlet discretization of Neumann problems}
- \author{Jeremy Hoskins and Manas Rachh}
+ \title{On the discretization of Laplace's equation with Neumann boundary conditions on polygonal domains}
+\author{Jeremy Hoskins\thanks{Applied Mathematics Program, Yale University, USA. \\ email: jeremy.hoskins@yale.edu}, \,
+Manas Rachh\thanks{Center for Computational Mathematics, Flatiron Institute, USA. \\ email: mrachh@flatironinstitute.org}}
  \maketitle
@@
 \input{07conc}
+
+\section{Acknowledgements}
+The authors would like to thank Leslie Greengard, and Vladimir Rokhlin for many useful discussions.
 
@@
 \begin{equation}
-\sigma_{f}(s)   + \int_{0}^{L} k(s,t) \sigma_{f}(t) dt  = f(s) \,  \quad s\in[0,L]\setminus{V}.
+-\frac{\sigma_{f}(s)}{2}   + \int_{0}^{L} k(s,t) \sigma_{f}(t) dt  = f(s) \,  \quad s\in[0,L]\setminus{V}.
 \end{equation}
- Then $\sigma_{f} = f + \tilde{\sigma}$ where $\tilde{\sigma}$ satisfies the integral equation
+ Then $\sigma_{f} = -2f + \tilde{\sigma}$ where $\tilde{\sigma}$ satisfies the integral equation
  \begin{equation}
--\tilde{\sigma}+ \int_{0}^{L} k(s,t) \tilde{\sigma}(t) dt = \int_{s_{1}}^{s_{2}} k(s,t) f(t) dt \, , \quad s\in[0,L] \setminus V \, ,
+-\frac{\tilde{\sigma}}{2}+ \int_{0}^{L} k(s,t) \tilde{\sigma}(t) dt = -2\int_{s_{1}}^{s_{2}} k(s,t) f(t) dt \, , \quad s\in[0,L] \setminus V \, ,
  \end{equation}
@@
 \begin{equation}
-\tilde{f}(s) = \int_{s_{1}}^{s_{2}} k(s,t) f(t) dt \, , s \in [0,L] \setminus V \, .
+\tilde{f}(s) = -2\int_{s_{1}}^{s_{2}} k(s,t) f(t) dt \, , s \in [0,L] \setminus V \, .
 \end{equation}

### 2020-01-14 paper_lap/01intro.tex
updating manuscript

@@
  The paper is organized as follows.
-In~\cref{sec:mprelim} we review relevant mathematical results associated with Laplace's equation.
-~\cref{sec:bvp} describes the reduction of boundary value problems to boundary integral equations via potential theory, and reviews the analytic behavior of solutions near a corner.
+In~\cref{sec:mprelim} we review relevant mathematical results associated with Laplace's equation.~\cref{sec:bvp} describes the reduction of boundary value problems to boundary integral equations via potential theory, and reviews the analytic behavior of solutions near a corner.
 In~\cref{sec:nprelim,sec:napp} we present our numerical algorithm and the associated analysis.

### 2020-01-14 paper_lap/06num.tex
updating manuscript

@@
 
-After re-solving the density, we also compute the solution at target locations on a tensor product polar grid, where the grid
-is exponentially spaced in the radial direction and equispaced in the angular direction. For target locations
+After re-solving the density, the solution is evaluated on a tensor product polar grid, where the grid
+is exponentially spaced in the radial direction and equispaced in the angular direction. For evaluation points (targets)
 close to panels which are not at the corner, we use adaptive integration in order to resolve the near-singular behavior of
@@
 \includegraphics[width=\linewidth]{media/volume}
-\caption{Top row: Solution on the volume after 10, 20, and 40 iterations of resolve.
-The target locations are a tensor product polar grid, where the nodes are exponentially spaced in the radial direction.
+\caption{Top row: Solution on the volume after 10, 20, and 40 iterations of re-solve.
+The solution is computed on a tensor product polar grid, where the evaluation points (targets) are exponentially spaced in the radial direction.
 The closest target location is approximately $10^{-13}$ away from the corner.
@@
 All of the results have been computed on a single core on a Macintosh machine with Intel core i5 2.3GHz processors.
-In~\cref{fig:magnetron}, we plot the scattered field, the right hand side, and the computed density.
+In~\cref{fig:magnetron}, we plot the scattered field, the boundary data, and the computed density.
 

### 2020-01-14 paper_lap/manuscript.tex
updating manuscript

@@
 $L$ denote the length of the boundary, and let $\gamma: [-L/2,L/2]$ denote an arc-length parameterization of the boundary.
-Let $\gamma([s_{1},s_{2}])$ be a panel discretized using $M$ Gauss-Legendre nodes be such that if $r_{0}$ denotes
-the distance to the closest corner on the particular edge, the length of the panel $L_{0}<r_{0}/2$, i.e. the panel
-is separated from the nearest corner by at least two times its own length.
-Further assume that no point on the boundary $\Gamma$ which is not on the same edge as as $\gamma([s_{1},s_{2}])$ is contained in some $\rho-$Bernstein ellipse
-corresponding to the line segment $\gamma([s_{1},s_{2}])$ with $\rho>1$.
-Furthermore suppose that all of the panels away from the corner and not on the edge containing the segment $\gamma([s_{1},s_{2}])$ are such that any point on $\gamma([s_{1},s_{2}])$ is not contained in their $\rho-$ Bernstein ellipse.
-Both of these assumptions can always be met by choosing sufficiently small panels away from the corners. Finally 
-assume that all panels at any corner $r_{c}$ are such that any point on $\gamma([s_{1},s_{2}])$ is at least $2r_{c}$ 
-away from the corner vertex. Under all of these assumptions, it can be shown that the accuracy in computing the
-Legendre coefficients of the density corresponding to the Neumann problem, is the same as the accuracy
-of a related Dirichlet problem where the boundary data is resolved with controlled error on the given discretization.
+Assume that the discretization satisfies the following assumptions:
+\begin{enumerate}
+\item All panels which are not at a corner, are separated from the closest corner by their panel length.
+\item Let $E_{\rho}(\Gamma_{i})$ denote the Bernstein $\rho-$ellipse corresponding to panel $\Gamma_{i}$, and let $\rho_{i}$ 
+be such that $E_{\rho_{i}}(\Gamma_{i})$ does not intersect $\Gamma \setminus S_{\Gamma_{i}}$, where 
+$S_{\Gamma_{i}}$ is the edge containing $\Gamma_{i}$ (see~\cref{fig:illus-cons}). Let $\rho_{0} = \min_{i} \rho_{i} >1$.
+\item All panels which are not adjacent to a panel at the corner, are separated from the corner by $2r_{c}$ where $r_{c}$ 
+denotes the length of the panel at the corner.
+\end{enumerate}
+Under these assumptions, it can be shown that the accuracy in computing the
+Legendre coefficients of the density (at panels which are not adjacent to a corner panel) for the Neumann problem, is related to the accuracy 
+of a Dirichlet problem where the boundary data is resolved with controlled error on the given discretization.
+\begin{figure}
+\begin{center}
+\includegraphics[width=0.3\linewidth]{media/geom-restriction-illus}
+\caption{Illustrative figure for demonstrating constraints required on the geometry discretization.
+The panel $\Gamma_{i}$ satisfies restriction 1 if $L_{i}/L_{0}>1$.
+Panel $\Gamma_{j}$ illustrates the largest Bernstein ellipse which intersects the other edges, and Panel $\Gamma_{k}$ illustrates restriction 3 if $r_{k}>2r_{c}$.
+}
+\label{fig:illus-cons}
+\end{center}
+\end{figure}
 
@@
 right hand side for the Neumann problem, let $\sigma$ denote the corresponding solution. Let $f$ be a Legendre polynomial of
-degree $n$ scaled to the panel $\gamma_{[s_{1},s_{2}]}$ and $0$ everywhere else. Then
+degree $n$ scaled to the panel $\gamma([s_{1},s_{2}])$ and $0$ everywhere else. Then
 \begin{equation}
@@
 and the nearest singularity of the function $k(s,t)$ in the complex plane as a function of $t$ is corresponding to $\gamma(s)$.
-Since we have assumed that no other point on the boundary $\Gamma$ is contained in the $\rho-$ bernstein ellipse
-of the panel $\gamma[(s_{1},s_{2})]$, 
-the error in computing $\tilde{f}(s)$ using an $M$ point Gauss-Legendre rule is bounded by $C \rho^{-M}$, where
+From assumption 2, it follows that
+the error in computing $\tilde{f}(s)$ using an $M$ point Gauss-Legendre rule is bounded by $C \rho_{0}^{-M}$, where
 the constant $C$ is related to the boundedness of the function $k(s,t)$ when $t$ is complexified.
-(Note the error is not $\rho^{-2M}$ since $P_{M}$ would grow like $\rho^{M}$ on the $\rho-$ Bernstein ellipse.) 
+(Note the error is not $\rho_{0}^{-2M}$ since $P_{M}$ would grow like $\rho_{0}^{M}$ on the $\rho_{0}-$ Bernstein ellipse.) 
 Thus the function $\tilde{f}(s)$ can be computed to any desired precision by increasing the order of quadrature nodes
@@
 and not on the same edge as $\gamma([s_{1},s_{2}])$ is the closest point on the panel $\gamma([s_{1},s_{2}])$. 
-However, since we have assumed that all panels away from corners are such that no point on $\gamma([s_{1},s_{2}])$ 
-is contained in their $\rho-$ Bernstein ellipse, the error in resolving the function $\tilde{f}(s)$ using an $M$ point Gauss-Legendre
-or Chebyshev panel is bounded by $C \rho^{-M}$. Note that the behavior of $\tilde{f}(s)$ in the complex plane is related
-to the behavior of $k(s,t)$ in the complex $s$ plane and hence can be made $O(1)$.
+However, by assumption 2, the error in resolving the function $\tilde{f}(s)$ using an $M$ point Gauss-Legendre
+or Chebyshev panel is bounded by $C \rho_{0}^{-M}$. Note that the behavior of $\tilde{f}(s)$ in the complex plane is related
+to the behavior of $k(s,t)$ in the complex $s$ plane and hence the constant $C$ is $O(1)$.
 For the panels, at the corner, based on the proof in Appendix A, the error in resolving the function $\tilde{f}(s)$ when

### 2020-01-14 paper_lap/manuscript.tex
some edits

@@
 
-Let $\Gamma_*$ be any other straight line segment contained entirely within $\Gamma \setminus B_{2r}(\bx).$ Then
+%Let $\Gamma_*$ be any other straight line segment contained entirely within $\Gamma \setminus B_{2r}(\bx).$ Then
 
@@
 accurately at any point on the panel. As before let $\Omega$ denote a polygonal domain with boundary $\Gamma$. Let
-$L$ denote the length of the boundary, and let $\gamma: [-L/2,L/2]$ denote an arc-length parameterization of the boundary.
+$L$ denote the length of the boundary, and let $\gamma: [-L/2,L/2]\to \mathbb{R}^2$ denote an arc-length parameterization of the boundary.
 Assume that the discretization satisfies the following assumptions:
 \begin{enumerate}
-\item All panels which are not at a corner, are separated from the closest corner by their panel length.
-\item Let $E_{\rho}(\Gamma_{i})$ denote the Bernstein $\rho-$ellipse corresponding to panel $\Gamma_{i}$, and let $\rho_{i}$ 
+\item All panels which are not at a corner, are separated from the closest corner by at least their panel length.
+\item Let $E_{\rho}(\Gamma_{i})$ denote the Bernstein $\rho-$ellipse (see \cite{tref_approx}) corresponding to the panel $\Gamma_{i}$, and let $\rho_{i}$ 
 be such that $E_{\rho_{i}}(\Gamma_{i})$ does not intersect $\Gamma \setminus S_{\Gamma_{i}}$, where 
@@
 \end{enumerate}
-Under these assumptions, it can be shown that the accuracy in computing the
-Legendre coefficients of the density (at panels which are not adjacent to a corner panel) for the Neumann problem, is related to the accuracy 
-of a Dirichlet problem where the boundary data is resolved with controlled error on the given discretization.
+Under these assumptions, it can be shown that the accuracy of computing the
+Legendre coefficients of the density (at panels which are not adjacent to a corner panel) for the Neumann problem using the adjoint discretization is related to the accuracy 
+in the computation of the solution to an associated Dirichlet problem.
 \begin{figure}
@@
 
-Using~\cref{lem_adjm}, the above statement implies that the error in computing the $n$ Legendre coefficient of
+Using~\cref{lem_adjm}, the above statement implies that the error in computing the $M$ Legendre coefficients of
 the density for the Neumann problem is the same as the error in computing the solution of a Dirichlet problem with 
-data given by a Legendre polynomial on the same panel.  %This seems problematic since the right hand side
-%is not smooth, however, in the special case of polygonal domains, this problem is alleviated since the kernel corresponding
-%to the double layer potential is identically zero on line segments.
+data given by a Legendre polynomial on the same panel.
 
 Let $V$ denote the collection of corner points in parameter space $[0,L]$, i.e. $a \in V$ if $\gamma(a)$ is a corner vertex.
-Recall that $\sigma_{f}$ denote the solution to the Dirichlet problem with boundary data $f$, i.e., 
+Recall that $\sigma_{f}$ denotes the solution of the Dirichlet problem with boundary data $f$, i.e., 
 $\sigma_{f}$ satisfies
@@
  \end{equation}
-i.e, $\tilde{\sigma}$ is the solution of Dirichle with data at $\tilde{f}$ given by
+i.e, $\tilde{\sigma}$ is the solution of the Dirichlet with data $\tilde{f}$ given by
 \begin{equation}
@@
 \end{equation}
-Now there are two concerns that need to be addressed. First, the accuracy of computing $\tilde{f}(s)$ 
+There are two concerns which must be addressed. First, the accuracy of computing $\tilde{f}(s)$ 
 for any point $s \in [0,L]$ using an $M$ point Gauss-Legendre quadrature on $[s_{1},s_{2}]$, and secondly, 
@@
 Thus the boundary data $\tilde{f}(s)=0$  on the same edge as the panel $\gamma([s_{1},s_{2}])$. 
-We further observe that $f(t)$ is an entire function when extended to the complex plane (since it is a Legendre polynomial)
-and the nearest singularity of the function $k(s,t)$ in the complex plane as a function of $t$ is corresponding to $\gamma(s)$.
+We further observe that $f(t)$ is an entire function when extended to the complex plane, since it is a Legendre polynomial.
+Moreover, the nearest singularity of the function $k(s,t)$ in the complex plane as a function of $t$ is at $\gamma(s)$.
 From assumption 2, it follows that
 the error in computing $\tilde{f}(s)$ using an $M$ point Gauss-Legendre rule is bounded by $C \rho_{0}^{-M}$, where
-the constant $C$ is related to the boundedness of the function $k(s,t)$ when $t$ is complexified.
-(Note the error is not $\rho_{0}^{-2M}$ since $P_{M}$ would grow like $\rho_{0}^{M}$ on the $\rho_{0}-$ Bernstein ellipse.) 
+the constant $C$ is related to the smoothness of $k(s,t)$ as a function of $t \in \mathbb{C}.$
 Thus the function $\tilde{f}(s)$ can be computed to any desired precision by increasing the order of quadrature nodes

### 2020-01-14 data/lapfinalres/plot_dens.py
adding .py files

@@ -1,0 +1,77 @@
+from numpy import *
+from pylab import *
+
+y = loadtxt('sqwts.dat')
+
+ffs = ['ref','px','rand','scat']
+for i in range(4):
+    fname = 'dir_sigma_'+ffs[i]+'_100.dat'
+    x = loadtxt(fname)
+    figure(1)
+    clf()
+    loglog(x[:,0],abs(x[:,1]),'k.')
+    xticks([10**-5,10**-15,10**-30])
+    savefig('dens_lap_dir_'+ffs[i]+'.pdf',bbox_inches='tight')
+    figure(2)
+    clf()
+    e = abs(x[:,1]-x[:,2])
+    e[e<10**-16] = 10**-16
+    e = e*y
+    loglog(x[:,0],e,'k.')
+    xticks([10**-5,10**-15,10**-30])
+    savefig('dens_err_lap_dir_'+ffs[i]+'.pdf',bbox_inches='tight')
+
+
+nlevs = ['10','20','40','80']
+for i in range(4):
+    figure(2)
+    clf()
+    figure(3)
+    clf()
+    for j in range(4):
+        fname = 'sigma_'+ffs[i]+'_300_'+nlevs[j]+'.dat'
+        x = loadtxt(fname)
+
+        if(j == 1):
+            figure(1)
+            clf()
+            loglog(x[:,0],abs(x[:,1]),'k.')
+            xticks([10**-5,10**-15,10**-30])
+            savefig('dens_lap_neu_'+ffs[i]+'.pdf',bbox_inches='tight')
+
+        e = abs(x[:,1]-x[:,3])
+        e[e<10**-16] = 10**-16
+        e = e*y
+        figure(2)
+        loglog(x[:,0],e,'.',label=nlevs[j])
+        
+        figure(4)
+        clf()
+        loglog(x[:,0],e,'k.',label=nlevs[j])
+        xticks([10**-5,10**-15,10**-30])
+        savefig('dens_err_lap_neu_'+ffs[i]+'_'+nlevs[j]+'.pdf',bbox_inches='tight')
+        
+
+        e = abs(x[:,1]-x[:,2])
+        e[e<10**-16] = 10**-16
+        e = e*y
+        figure(3)
+        loglog(x[:,0],e,'.',label=nlevs[j])
+
+        figure(5)
+        clf()
+        loglog(x[:,0],e,'k.',label=nlevs[j])
[…]

### 2020-01-14 data/lapfinalres/plot_dens2.py

@@ -1,0 +1,28 @@
+from numpy import *
+from pylab import *
+
+y = loadtxt('sqwts.dat')
+nlev = 80
+nlat = 300
+fname = 'sigma_scat_'+str(nlat)+'_'+str(nlev)+'.dat'
+x = loadtxt(fname)
+
+figure(1)
+clf()
+loglog(x[:,0],abs(x[:,1]),'k.')
+savefig('dens_scat.pdf',bbox_inches='tight')
+
+
+figure(2)
+clf()
+e1 = abs(x[:,2]-x[:,1])*y
+e2 = abs(x[:,3]-x[:,1])*y
+
+loglog(x[:,0],e1,'k.',label='Corner panel - Gauss Legendre nodes')
+loglog(x[:,0],e2,'r.',label='Corner panel - custom dirichlet discretization')
+xticks([10**-5,10**-15,10**-30])
+ylim((10**(-17),10**(3)))
+#legend()
+fname = 'dens_scat_err_'+str(nlev)+'.pdf'
+savefig(fname,bbox_inches='tight')
+

### 2020-01-14 data/lapfinalres/plot_grid.py

@@ -1,0 +1,68 @@
+from numpy import *
+from pylab import *
+
+ttmin = -0.477616226
+ttmax = 0.34374594
+
+
+x = [0,0.6*cos(ttmin)]
+y = [0,0.6*sin(ttmin)]
+
+plot(x,y,'k-')
+
+
+x = [0,0.6*cos(ttmax)]
+y = [0,0.6*sin(ttmax)]
+
+plot(x,y,'k-')
+
+x = [0.6*cos(ttmin),0.9*cos(ttmin)]
+y = [0.6*sin(ttmin),0.9*sin(ttmin)]
+
+plot(x,y,'k--')
+
+
+x = [0.6*cos(ttmax),0.9*cos(ttmax)]
+y = [0.6*sin(ttmax),0.9*sin(ttmax)]
+
+plot(x,y,'k--')
+
+
+x = [0.9*cos(ttmin),cos(ttmin)]
+y = [0.9*sin(ttmin),sin(ttmin)]
+
+plot(x,y,'k-')
+
+
+x = [0.9*cos(ttmax),cos(ttmax)]
+y = [0.9*sin(ttmax),sin(ttmax)]
+
+
+plot(x,y,'k-')
+
+
+
+nlev = 4
+rticks = 2.0**(-arange(nlev))
+print(rticks)
+xx = rticks
+rn1 = [-sin(ttmin),cos(ttmin)]
+rn2 = [-sin(ttmax),cos(ttmax)]
+h = 0.005
+for i in range(nlev):
+    x0 = [xx*cos(ttmin),xx*sin(ttmin)]
+
+    x = [x0[0]-rn1[0]*h,x0[0]+rn1[0]*h]
+    y = [x0[1]-rn1[1]*h,x0[1]+rn1[1]*h]
+    plot(x,y,'k-')
+
+    x0 = [xx*cos(ttmax),xx*sin(ttmax)]
+
+    x = [x0[0]-rn2[0]*h,x0[0]+rn2[0]*h]
+    y = [x0[1]-rn2[1]*h,x0[1]+rn2[1]*h]
+    plot(x,y,'k-')
+
+
+axis('equal')
+axis('off')
+savefig('grid.pdf',bbox_inches='tight')

### 2020-01-14 data/lapfinalres/sector_numpy.py

@@ -1,0 +1,42 @@
+#!/usr/bin/env python
+
+import ccm_widgets as cw
+import numpy as np
+from matplotlib import cm
+cw.init_electron()
+
+nlev = 40
+nlat = 300
+#fname = 'targ_'+str(nlat)+'.dat'
+#rtdat = np.loadtxt(fname)
+
+#rr = np.log10(rtdat[:,1].reshape(nlat,nlat))+14 
+#tt= rtdat[:,2].reshape(nlat,nlat)
+fname1 = 'scat_'+str(nlat)+'_'+str(nlev)+'.dat'
+pref = np.loadtxt(fname1)
+ttmin = -0.4776162260822098
+ttmax = 0.34374594733735681
+
+zz1 = np.abs(pref[:,0].reshape(nlat,nlat)-pref[:,2].reshape(nlat,nlat))
+zz1[zz1<10**-16] = 10**-16
+zz1 = np.log10(zz1)
+zz1 = np.flipud(zz1)
+
+print(np.min(zz1[:]))
+print(np.max(zz1[:]))
+
+r0 = 0.068659
+
+y = cm.viridis(range(256))
+X = cw.SectorPlot(
+    data_samples=np.array(zz1),
+    theta_range=[ttmin, ttmax],
+    data_range=[-16,0],
+    colorbarticks=[-16,-12,-8,-4,0],
+    colorbarticklabels=["10^-16","10^-12","10^-8","10^-4","10^0"],
+    colormap=y.T,
+    rticks=[r0,0.25+r0,0.5+r0,0.75+r0],
+    rticklabels=["10^-12","10^-9","10^-6","10^-3"],
+    fontSize=18
+)
+X.show()

### 2020-01-15 paper_lap/01intro.tex
updting paper

@@
 
- Finally, a recent approach is based on leveraging explicit representations of the solutions to the BIEs in the vicinity of the corner as sums of fractional powers depending on the angle \cite{serkhacha}.
+ Finally, a recent approach is based on leveraging explicit representations of the solutions to the BIEs in the vicinity of the corner as sums of fractional powers depending on the angle \cite{serkhacha,serkh2016solution}.
 Using these representations one can construct high-order discretizations which introduce relatively few extra degrees of freedom near the corners (i.e.

### 2020-01-15 paper_lap/06num.tex
updting paper

@@
 The reference solution for each of the examples is computed using a discretization with
-a graded mesh in the vicinity of the corners, where the smallest panel at the corner is $2^{-150}$ times
+a graded mesh in the vicinity of the corners, where the smallest panel at the corner is $2^{-200}$ times
 the length of the first macroscopic panel away from the corner (see~\cref{fig:dom}). In these examples, the solutions are computed via dense linear solves.
@@
 \begin{center}
-\includegraphics[width=0.7\linewidth]{media/discretization}
+\includegraphics[width=0.7\linewidth]{paper-figs/discretization}
 \caption{Problem domain and panel discretization of the boundary. The discretization on the left is based on using the Dirichlet
@@
 \begin{rem}
-Though $2^{-150}$ is significantly smaller than machine precision, the matrix entries corresponding to the
+Though $2^{-200}$ is significantly smaller than machine precision, the matrix entries corresponding to the
 corner interactions can be computed accurately by translating the corners to the origin when 
@@
 of the density to machine precision at all points which are at least $2^{-100}$ away from the corner, we use a smallest
-panel size of $2^{-150}$. 
+panel size of $2^{-200}$. 
 \end{rem}
@@
 \begin{center}
-\includegraphics[width=\linewidth]{media/weaktest}
+\includegraphics[width=\linewidth]{paper-figs/weaktest}
 \caption{Left panel: Solution to Neumann problem with data given by~\cref{eq:scatboundarydata}, center panel: error in computing the potential in the formula using the underlying smooth quadrature~\cref{eq:farfieldpot}, and on the right the density $\sigma$ as a function of arc-length}.
@@
 \begin{center}
-\includegraphics[width=\linewidth]{media/density}
+\includegraphics[width=\linewidth]{paper-figs/density}
 \caption{Top row: (left) Illustrative mesh used for iteratively computing the solution in the vicinity of a corner, (right) the density in the vicinity of one of the corner panels.
@@
 \begin{center}
-\includegraphics[width=\linewidth]{media/volume}
+\includegraphics[width=\linewidth]{paper-figs/volume}
 \caption{Top row: Solution on the volume after 10, 20, and 40 iterations of re-solve.
@@
 \begin{center}
-\includegraphics[width=\linewidth]{media/magnetron}
+\includegraphics[width=\linewidth]{paper-figs/magnetron}
 \caption{(left): Boundary data as a function of arclength, (center): absolute value of density as a function of arclength, and 

### 2020-01-15 paper_lap/07conc.tex
updting paper

@@
 much more broadly. In particular, the approach easily extends to accommodate curved boundaries. Moreover, in addition 
-to Laplace's equation, this approach can be easily adapted to solve the Helmholtz equation and the biharmonic equation with analogous boundary conditions.
+to Laplace's equation, this approach can be easily adapted to solve the Helmholtz equation and the biharmonic equation with analogous boundary conditions for which the nature of singularities of corresponding integral equations have been analyzed~\cite{serkhrachh,serkhpnas}.
 A manuscript detailing this extension is currently in preparation.

### 2020-01-15 paper_lap/manuscript.tex
updting paper

@@
 
-\usepackage{boxit}
+%\usepackage{boxit}
 %\newcommand{\boxit}[1]{#1}
@@
 accurately at any point on the panel. As before let $\Omega$ denote a polygonal domain with boundary $\Gamma$. Let
-$L$ denote the length of the boundary, and let $\gamma: [-L/2,L/2]\to \mathbb{R}^2$ denote an arc-length parameterization of the boundary.
+$L$ denote the length of the boundary, and let $\gamma: [0,L]\to \mathbb{R}^2$ denote an arc-length parameterization of the boundary.
 Assume that the discretization satisfies the following assumptions:
@@
 \begin{center}
-\includegraphics[width=0.3\linewidth]{media/geom-restriction-illus}
+\includegraphics[width=0.3\linewidth]{paper-figs/geom-restriction-illus}
 \caption{Illustrative figure for demonstrating constraints required on the geometry discretization.
@@
 
-For any $s$ which is contained on the same segment as $\gamma_{[s_{1},s_{2}]}$, the kernel $k(s,t)$ is identically $0$.
+For any $s$ which is contained on the same segment as $\gamma([s_{1},s_{2}])$, the kernel $k(s,t)$ is identically $0$.
 Thus the boundary data $\tilde{f}(s)=0$  on the same edge as the panel $\gamma([s_{1},s_{2}])$. 

### 2020-01-21 paper_lap/JCP_submission/06num.tex
Adding jcp submission

--- 2020-01-15 paper_lap/06num.tex
@@
 \end{equation}
-where there is one $\bx_{j}$ located in each of the spokes, one of the $\bx_{j}$ is in the central disc, and the remaining $50$ $\bx_{j}$ are chosen randomly in the exrterior of the bounding disc containing the domain.
+where there is one $\bx_{j}$ located in each of the spokes, one of the $\bx_{j}$ is in the central disc, and the remaining $50$ $\bx_{j}$ are chosen randomly in the exterior of the bounding disc containing the domain.
 The strengths $c_{j}$ are chosen such that they average to $0$.

### 2020-01-21 paper_lap/JCP_submission/Significance.tex
Adding jcp submission

\documentclass[10pt]{article}
\usepackage{amsmath,amsthm,amssymb,amscd,fancybox,epsfig,float,subfigure}
\usepackage[margin=1.2in]{geometry}
\usepackage{graphics}
\usepackage{epstopdf}
\usepackage{multirow}
\usepackage{hhline}
\usepackage[nocompress]{cite}
\newcommand{\bx}{\boldsymbol {x}}

\begin{document}
 \title{Significance and novelty of this paper}
 \maketitle
The solution to boundary integral equations corresponding to Laplace's equations
with polygonal domains
develop singularities near corners; this poses a challenge for designing
efficient numerical methods for their solution. 
If the boundary data on each edge of the polygon is smooth, then the solution
to the corresponding boundary equation has an expansion terms of certain analytically
available singular powers. 
Using the known behavior of he solution to the integral equation, efficient
discretizations have been constructed for the Dirichlet problem.
However, these methods do not directly extend to the solution of the Neumann problem
since the leading order behavior of solutions to the Neumann problem is $O(t^{\mu})$ 
for $\mu \in (-1/2,1/2)$ depending on the angle at the corner, while that of solutions
to the Dirichlet problem is $O(C + t^{\mu})$ for $\mu>1/2$.

In this paper, we present a universal discretization for the solution of the Neumann problem
on polygonal domains based on an adjoint Dirichlet discretization.
We show that the solution obtained in this manner is accurate in a ``weak-sense'', i.e. 
inner-products of the solution with smooth functions can be computed accurately. 
Further, we show that the solution is also accurate point wise away from the corners. 
We also present an algorithm to obtain accurate solutions in the vicinity of the corner
by solving a series of local sub-problems in the vicinity of the corner. 
This enables accurate evaluation of the corresponding potential at target locations arbitrarily
close to the corner. We present the effectiveness of our method, both in terms of accuracy
and speed through several numerical examples.
\end{document}

### 2020-01-21 paper_lap/JCP_submission/manuscript.tex
Adding jcp submission

--- 2020-01-15 paper_lap/manuscript.tex
@@
-\documentclass[12pt]{article}
+\documentclass[12pt]{elsarticle}
 \usepackage{amsmath,amsthm,amssymb,amscd,fancybox,epsfig,float,subfigure}
-\usepackage{authblk}
 \usepackage[margin=1in]{geometry}
@@
 \usetikzlibrary{arrows,automata}
-\usepackage[nocompress]{cite}
 \newtheorem{definition}{Definition}[section]
@@
 
+\journal{Computational Physics}
+
 \begin{document}
+
+\begin{frontmatter}
+
  \title{On the discretization of Laplace's equation with Neumann boundary conditions on polygonal domains}
-\author{Jeremy Hoskins\thanks{Applied Mathematics Program, Yale University, USA. \\ email: jeremy.hoskins@yale.edu}, \,
-Manas Rachh\thanks{Center for Computational Mathematics, Flatiron Institute, USA. \\ email: mrachh@flatironinstitute.org}}
- \maketitle
+\author[jh]{Jeremy Hoskins}
+\author[mr]{Manas Rachh}
+\address[jh]{Applied Mathematics Program, Yale University, USA. \\ email: jeremy.hoskins@yale.edu}
+\address[mr]{Center for Computational Mathematics, Flatiron Institute, USA. \\ email: mrachh@flatironinstitute.org}
+
+\begin{abstract}
+In the present paper we describe a class of algorithms for the solution of Laplace's equation on polygonal domains with Neumann boundary conditions.
+It is well known that in such cases the solutions have singularities near the corners which poses a challenge for many existing methods.
+If the boundary data is smooth on each edge of the polygon, then in the vicinity of each corner the solution to the corresponding boundary integral equation has an expansion in terms of certain (analytically available) singular powers.
+Using the known behavior of the solution, universal discretizations have been constructed for the solution of the Dirichlet problem.
+However, the leading order behavior of solutions to the Neumann problem is $O(t^{\mu})$ for $\mu \in (-1/2,0)$ depending on the angle at the corner (compared to $O(C+t^{\mu})$ with $\mu>1/2$ for the Dirichlet problem); this presents a significant challenge in the design of universal discretizations.
+Our approach is based on using the discretization for the Dirichlet problem in order to compute a solution in the ``weak sense'' by solving an adjoint linear system; namely, it can be used to compute inner products with smooth functions accurately, but it cannot be interpolated.
+Furthermore we present a procedure to obtain accurate solutions arbitrarily close to the corner, by solving a sequence of small local subproblems in the vicinity of that corner.
+The results are illustrated with several numerical examples.
+\end{abstract}
+
+\begin{highlights}
+\item Efficient discretization to boundary integral equations corresponding to Laplace's equation with Neumann boundary conditions based on an adjoint Dirichlet discretization resulting
+in weak solutions to the integral equation. 
+\item A local re-solve algorithm for obtaining pointwise accurate solutions of the integral equation arbitrarily close to the corner.
+\item Rapid evaluation of solution at target locations in the volume arbitrarily close to the corner.
+\end{highlights}
+
+\begin{keyword}
+Boundary value problems, Potential theory, Singular solutions, Integral equations, Corners
+\end{keyword}
+
+\end{frontmatter}
 
@@
 
-\section{Acknowledgements}
-The authors would like to thank Leslie Greengard, and Vladimir Rokhlin for many useful discussions.
+\section{Acknowledgments}
+J. Hoskins was supported in part by AFOSR FA9550-16-1-0175 and by the ONR (award no. N00014-14-1-0797).
+The authors would like to thank Alex Barnett, Leslie Greengard, Michael O'Neil, and Vladimir Rokhlin for many useful discussions, and Jeremy Magland for providing sector plotting tools.
 
@@
 For the panels, at the corner, based on the proof in Appendix A, the error in resolving the function $\tilde{f}(s)$ when
-truncated to a taylor series of order $N$ is less than $C 2^{-N}$, since all points on $\gamma([s_{1},s_{2}])$ are 
+truncated to a Taylor series of order $N$ is less than $C 2^{-N}$, since all points on $\gamma([s_{1},s_{2}])$ are 
 well-separated from corners by twice the panel length $r_{c}$.
@@
 
- \bibliographystyle{plain}
+ \bibliographystyle{elsarticle-num}
  \bibliography{bib_file2}

### 2020-04-09 paper_lap/JCP_response1/response.tex
adding response

\documentclass[11pt]{letter}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{color}
\usepackage{parskip}
\usepackage{comment}
\usepackage{mathpazo}
\usepackage[utf8]{inputenc}

\usepackage[margin=1in]{geometry}
\usepackage{setspace}

\onehalfspacing

\newcommand\qa{\begin{center}\line(1,0){250}\end{center}\begin{quote}\begin{em}}
\newcommand\qb{\end{em}\begin{center}\line(1,0){250}\end{center}\end{quote}}
\newcommand{\bx}{\boldsymbol {x}}
\newcommand{\bs}{\boldsymbol {s}}
\newcommand{\bt}{\boldsymbol {t}}
\newcommand{\bc}{\boldsymbol {c}}
\newcommand{\eps}{\varepsilon}
\newcommand{\todo}[1]{ {\color{red} #1 }}

\begin{document}

\signature{Jeremy Hoskins\\
Manas Rachh}

\address{Jeremy Hoskins (Yale University)\\
jeremy.hoskins@yale.edu\\
\vspace{.02in}\\
Manas Rachh (Flatiron Institute)\\
mrachh@flatironinstitute.org}

\begin{letter}{Editorial Office\\
Journal of Computational Physics - X}

\opening{Dear Editor:}

The following document contains a response to the comments made by the
reviewers after reading our manuscript \emph{On the discretization of Laplace's equation with Neumann boundary conditions on polygonal domains}.
In short, we have made revisions to the paper, namely:

Below are the reviews reports indented and in italics, interlaced with
our responses.

\qa
Reviewer \#1:
This manuscript extends a recent line of work on handling the singularities in the density of the standard boundary integral equation formulation of Laplace?s equation that arise at the corners of polygonal domains, through the use of specialized, high-order quadratures, which are computed using analytic expansions of the density. Previous work in this direction has difficulties directly applying this strategy to Neumann problems, since the singularities are significantly worse here than in the Dirichlet case. The current work makes the incredibly interesting observation that one can instead use the adjoint of a discretization to the Dirichlet problem to obtain a solution that is accurate in a weak sense. Furthermore, pointwise accuracy in a region arbitrarily close to a corner can be obtained through a novel local refinement process. The relevant theory for justifying both that this approach yields a density that can be accurately interpolated away from the corners and that the refinement process can be done in a completely local manner is developed. Furthermore, the approach is illustrated through exceptionally thorough and impressive numerical results.

In my opinion, this paper certainly should be published, due to the very high quality of the work and good presentation. However, the manuscript in its current state is missing a few details that I believe are of crucial interest to potential readers and is confusing in a few places. I suspect that a couple of these missing details are present elsewhere in the literature, but I still believe that it would be valuable to include them here for the purpose of producing a relatively self-contained work. Furthermore, there are several suspected typos and notational inconsistencies that should be fixed to maximize readability. When these are resolved, I think this will be a very strong paper.

Remarks on content and readability

1) p. 2. The last sentence of the first paragraph mentions that the disadvantage of compression-based approaches to quadrature is cost in 3D. Given that these approaches have already been used in 3D problems, unlike the work in the current paper, I think that as a minimum there should be a couple of brief remarks somewhere about how the method here would extend and scale to 3D.

\qb

\todo{JH}

\qa
2) p. 6. On a first reading, Theorem 6 is not easy to digest. Could you add a few comments to provide some intuition for this result, and also a comment on the connection of the result on an open wedge to the case of polygons? Do we expect the expansions to be exactly the same?

\qb

\todo{JH}

\qa
3) p. 8. I think it is extremely important to explicitly discuss how large we expect K to be in section 4.1.1, especially how it relates to the accuracy a user might desire. I realize the relevant information is likely in [14], but it is of sufficient importance to the current work to make this clear by either stating a result or computational experience.

\qb
\todo{JH}

\qa
4) p. 11. The theory as developed considers only the exterior Neumann problem. I?m guessing a similar duality relationship holds with the interior Neumann problem and the exterior Dirichlet problem, and the procedure carries over straightforwardly (indeed, you consider an interior Neumann problem in the numerical results). For the sake of completeness, could you add a brief remark on whether or not the procedure is exactly the same for the interior Neumann problem, and state if there are any special considerations that are different from the exterior Neumann case?

\qb
\todo{JH}

\qa
5) p. 13. I find the choice of notation in Theorem 8 to be very poor. In particular $A_{0}$ and $f_{0}$ are
used right above in (56) to denote the local problem after the corner has been refined ($A_{0}$ is of size
$P + 2M \times P + 2M$). Then in the statement of the theorem, these variables are used to denote the
analogous variables on just the corner panel of the unrefined problem ($A_{0}$ is of size $P \times P$ ), and then
in the proof of the result these variables are used to refer to the original corner panel as well as the
adjacent panels ($A_{0}$ is of size $P + 2M \times P + 2M$ ). Also, I am not sure why $f_{0}$ is not underlined, since it is a vector. Could you please fix this notation?

\qb
\todo{JH}

\qa
6) p. 19. In the same vein as comment 3, I find the absence of any information on conditioning to be a bit startling, since one of the main appeals of working with boundary integral equations is the ability
to form well-conditioned discretizations. Again, I am aware that this falls squarely into the scope of existing work (again, probably [14]), but find this also sufficiently important to at least summarize in the current work.

\qb
\todo{MR}

\qa
7) p. 19. Even for a problem with 22k dofs, 105 iterations of a Krylov method seems like a lot, especially if the problem is well-conditioned. I can?t help but wonder if this is an artifact of the fact that your FMM tolerance is the same as your iterative method tolerance. If you set the latter to 1e-14 or 1e-13, does the number of iterations decrease drastically?

\qb
\todo{MR}

\qa
8) 
p. 21-22. I find the content of Appendix B difficult to understand for a number of reasons. The motivation for such a result is clear, but I?m not sure I totally understand the conclusion. In particular, you want to show that using the adjoint discretization one can interpolate the density on a panel far from the corner. That makes sense. Your approach to showing this is to use the relation (B.1) to find another equivalent integral equation, which you then show can be solved using existing information accurately.
Is the claim that to actually interpolate the density on such a panel, one would need to solve another Dirichlet problem, and it does NOT suffice to just interpolate the value of ? obtained on the GL nodes when solving the original problem? Please clarify this point.

\qb
\todo{MR}

\qa 
There are these other issues I?m having with it:
(a) On your assumptions about the discretization, 1 and 3 have an easy-to-understand interpretation. It?s unclear to me what 2 is really assuming about the discretization, given that it seems to mostly to be introducing notation. Of course, I can imagine conditions where ?0 is less than the width of some panels, but is there some deeper restriction?
(b) Your assumption that ?0 > 1 and your later statement that the rate at which a polynomial interpolant will converge is C??M is a bit awkward, since these choices are specific for a function
on an interval of length 2.
0
(c) The second paragraph on p. 22 is very unclear to me. I don?t even understand the first sentence as to why k(s,t) would be identically 0 on the same segment as ?([s1,s2]), or what is really even meant by ?segment? here. Furthermore, it is mentioned that k(s, t) when considered as a function of t ? C has a singularity at ?(s). Given the current setup wouldn?t the singularity be at s? I would recommend rewriting this entire paragraph to be more transparent.

\qb
\todo{MR}

\qa
Small fixes and typos:

\qb
\todo{JH}

\qa
Reviewer \#4:
This article is not suitable for JCP. Most of it is Theorem, Lemma, Proposition, Remark. Journal of Computational Physics focuses on computational aspects of physical problems and contributions in mathematical and numerical modeling, rather than numerical analysis. This paper should be submitted to SIAM NUM ANALYS., or IMA J. NUM. ANAL., or Numerische Mathematik.

\qb

\todo{MR}

\qa

The scope of the article completely misses an entire arena of literature in the field, the unified transform (Fokas) method that has attacked the problem at hand in a much cleaner and nicer way in only 12 lines of code. It does not require a discretization with 22,240 points. See the work by Dr. Anthony Charles Lewis Ashton, Matthew J. Colbrook, and Natasha Flyer.

\qb

\todo{MR}

\qa

The method does the simplest of problems, Laplace on a convex domain, that was attacked much earlier and neater in 2001/2003 by Fokas. This paper does not show non-convex polygonal domains or Helmholtz or modified Helmholtz.

\qb

\todo{MR}

We thank the reviewer for their careful reads of our manuscript, and comments 
which have helped significantly improve the quality of the manuscript.
We hope that our revised manuscript based on their suggestions is now
suitable for publication in PAA.

\closing{Sincerely,}

\ps

\end{letter}
\end{document}

### 2020-04-09 paper_lap/JCP_response1/01intro.tex
adding response

--- 2020-01-15 paper_lap/01intro.tex
@@
 Once these boundary integral equations are discretized the resulting linear systems are better-conditioned than those obtained by directly discretizing the PDE.
-When the boundary of the domain is smooth there are numerous methods for solving BIEs quickly and accurately (see \cite{hao}, for example).
+When the boundary of the domain is smooth there are numerous methods for solving BIEs quickly and accurately (see~\cite{hao}, for example).
 
@@
  The paper is organized as follows.
-In~\cref{sec:mprelim} we review relevant mathematical results associated with Laplace's equation.~\cref{sec:bvp} describes the reduction of boundary value problems to boundary integral equations via potential theory, and reviews the analytic behavior of solutions near a corner.
+In~\cref{sec:mprelim} we review relevant mathematical results associated with Laplace's equation.~\Cref{sec:bvp} describes the reduction of boundary value problems to boundary integral equations via potential theory, and reviews the analytic behavior of solutions near a corner.
 In~\cref{sec:nprelim,sec:napp} we present our numerical algorithm and the associated analysis.

### 2020-04-09 paper_lap/JCP_response1/04nprelim.tex
adding response

--- 2020-01-08 paper_lap/04nprelim.tex
@@
 In this section we summarize the numerical tools which are necessary for the main result.
-In particular we summarize the method for discretizing the boundary integral equation for the Dirichlet problem described in \cite{}, which uses the expansion in Theorem \ref{thm_cord}.
+In particular we summarize the method for discretizing the boundary integral equation for the Dirichlet problem described in \cite{hoskins2019numerical}, which uses the expansion in Theorem \ref{thm_cord}.
 \subsection{Discretization of the Dirichlet problem}\label{sec:disc_dir}
 In this section we sketch an algorithm for solving the interior Dirichlet boundary integral equation using a Nystr\"{o}m method; the exterior Dirichlet boundary integral equation can be discretized in a similar way.
-See \cite{} for a thorough description of the method.
+See \cite{hoskins2019numerical} for a thorough description of the method.
 
@@
 \begin{align}\label{eqn:numpreint}
-f(s) = -\sigma(s) + \int_0^L k(t,s) \,\sigma(t)\, {\rm d} t
+f(s) = -\frac{\sigma(s)}{2} + \int_0^L k(t,s) \,\sigma(t)\, {\rm d} t
 \end{align}
-with precision $\epsilon.$ In other words, given $f(s_i),-\sigma(s_i) + \int_0^L k(t,s_i) \,\sigma(t)\, {\rm d} t,$ for $i=1,\dots,N,$ the values $f(s)$ and $-\sigma(s) + \int_0^L k(t,s) \,\sigma(t)\, {\rm d} t$ can be obtained for all $0 \le s \le L$ to within $\epsilon.$
+with precision $\epsilon.$ In other words, given $f(s_i),-\sigma(s_i) + \int_0^L k(t,s_i) \,\sigma(t)\, {\rm d} t,$ for $i=1,\dots,N,$ the values $f(s)$ and $-\sigma(s)/2 + \int_0^L k(t,s) \,\sigma(t)\, {\rm d} t$ can be obtained for all $0 \le s \le L$ to within $\epsilon.$
 
@@
 \begin{align}
-f(s_i) \sqrt{w_i} = -\sigma(s_i)\sqrt{w_i} +  \sqrt{w_i}\int_0^L k(t,s_i)\, \sigma(t)\,{\rm d}t,\quad i=1,\dots,N. \label{eqn_1std}
+f(s_i) \sqrt{w_i} = -\frac{\sigma(s_i)\sqrt{w_i}}{2} +  \sqrt{w_i}\int_0^L k(t,s_i)\, \sigma(t)\,{\rm d}t,\quad i=1,\dots,N. \label{eqn_1std}
 \end{align}
@@
 \begin{align}
-  -\sigma_i +  \sum_{j=1}^N W_{ij} \sigma_j \sqrt{w_i w_j}=f(s_i) \sqrt{w_i},\quad i,j=1,\dots,N. 
+  -\frac{\sigma_i}{2} +  \sum_{j=1}^N W_{ij} \sigma_j \sqrt{w_i w_j}=f(s_i) \sqrt{w_i},\quad i,j=1,\dots,N. 
 \end{align}
@@
 
-First, all functions of the form $x^\mu,$ $\mu \in \{0\} \cup [1/2,40],$ $x \in [0,1]$ are discretized using nested Gauss-Legendre panels in $x$ and a single Gauss-Legendre panel in $\mu$.
+First, all functions of the form $x^\mu,$ $\mu \in \{0\} \cup [1/2,50],$ $x \in [0,1]$ are discretized using nested Gauss-Legendre panels in $x$ and a single Gauss-Legendre panel in $\mu$.
 This creates a $N \times M$ matrix where $N$ denotes the number of spatial discretization points $r_i$ and $M$ denotes the number of $\mu_j$ chosen.
@@
 Finally, in many applications one already has a discretization of the Dirichlet problem.
-For example, when considering Laplace transmission problems or triple junction problems one has to solve two decoupled boundary integral equations: one of them a Dirichlet-type boundary integral equation with the diagonal term scaled and the other a Neumann-type boundary integral equation with the identity term scaled (see \cite{} and \cite{} for example).
+For example, when considering Laplace transmission problems or triple junction problems one has to solve two decoupled boundary integral equations: one of them a Dirichlet-type boundary integral equation with the diagonal term scaled and the other a Neumann-type boundary integral equation with the identity term scaled (see \cite{hoskins2018numerical} and \cite{hoskins2019solution} for example).
 In such cases it is convenient to reuse the Dirichlet discretization for the Neumann problem.

### 2020-04-09 paper_lap/JCP_response1/manuscript.tex
adding response

--- 2020-01-21 paper_lap/JCP_submission/manuscript.tex
@@
-\documentclass[12pt]{elsarticle}
+\documentclass[12pt,times]{elsarticle}
 \usepackage{amsmath,amsthm,amssymb,amscd,fancybox,epsfig,float,subfigure}
@@
 \begin{highlights}
-\item Efficient discretization to boundary integral equations corresponding to Laplace's equation with Neumann boundary conditions based on an adjoint Dirichlet discretization resulting
+\item Efficient discretization to boundary integral equations corresponding to Laplace's equation with Neumann boundary conditions on polygonal domains based on an adjoint Dirichlet discretization resulting
 in weak solutions to the integral equation. 

### 2020-04-27 paper_lap/JCP_response1/response.tex
updating appendix b and cleaning up review comments in response

@@
 I find the content of Appendix B difficult to understand for a number of reasons.
-The motivation for such a result is clear, but I?m not sure I totally understand the conclusion.
+The motivation for such a result is clear, but I'm not sure I totally understand the conclusion.
 In particular, you want to show that using the adjoint discretization one can interpolate the density on a panel far from the corner.
@@
 Your approach to showing this is to use the relation (B.1) to find another equivalent integral equation, which you then show can be solved using existing information accurately.
-Is the claim that to actually interpolate the density on such a panel, one would need to solve another Dirichlet problem, and it does NOT suffice to just interpolate the value of ?
-obtained on the GL nodes when solving the original problem?
+Is the claim that to actually interpolate the density on such a panel, one would need to solve another Dirichlet problem, and it does NOT suffice to just interpolate the value of $\sigma$ obtained on the GL nodes when solving the original problem?
 Please clarify this point.
 
-\qb
-\todo{MR}
-
-\qa 
 There are these other issues I?m having with it:
 (a) On your assumptions about the discretization, 1 and 3 have an easy-to-understand interpretation.
-It?s unclear to me what 2 is really assuming about the discretization, given that it seems to mostly to be introducing notation.
-Of course, I can imagine conditions where ?0 is less than the width of some panels, but is there some deeper restriction?
-(b) Your assumption that ?0 > 1 and your later statement that the rate at which a polynomial interpolant will converge is C??M is a bit awkward, since these choices are specific for a function
+It's unclear to me what 2 is really assuming about the discretization, given that it seems to mostly to be introducing notation.
+Of course, I can imagine conditions where $\rho_{0}$ is less than the width of some panels, but is there some deeper restriction?
+(b) Your assumption that $\rho_{0}>1$ and your later statement that the rate at which a polynomial interpolant will converge is $C \rho_{0}^{M}$ is a bit awkward, since these choices are specific for a function
 on an interval of length 2.
-0
 (c) The second paragraph on p.
 22 is very unclear to me.
-I don?t even understand the first sentence as to why k(s,t) would be identically 0 on the same segment as ?([s1,s2]), or what is really even meant by ?segment?
+I don?t even understand the first sentence as to why k(s,t) would be identically 0 on the same segment as $\gamma([s1,s2])$, or what is really even meant by ?segment?
 here.
-Furthermore, it is mentioned that k(s, t) when considered as a function of t ?
-C has a singularity at ?(s).
-Given the current setup wouldn?t the singularity be at s?
+Furthermore, it is mentioned that k(s, t) when considered as a function of $t \in \mathbb{C}$ has a singularity at $\gamma(s)$.
+Given the current setup wouldn't the singularity be at s?
 I would recommend rewriting this entire paragraph to be more transparent.
@@
 \qb
-\todo{MR}
-
+Thank you for pushing on this.
+We have rewritten the section completely to address all of the concerns above and feel that the readability now is significantly improved.
+We have eliminated the assumptions on the geometry completely as it can be confusing and rather reduced it to an error estimate of a solution to a Dirichlet problem using the same grid.
 \qa

### 2020-04-27 paper_lap/JCP_response1/05apparatus.tex
updating appendix b and cleaning up review comments in response

--- 2020-01-08 paper_lap/05apparatus.tex
@@
 
-For a panel $\gamma([s_1,s_2])$ with discretization nodes $x_i,\dots,x_{i+M}$ corresponding to a Gauss-Legendre panel the density is smooth and thus it is expected to be well-represented in the basis of Legendre polynomials (shifted and scaled to the interval $[s_1,s_2]$).
+For a panel $\gamma([s_1,s_2])$ with discretization nodes $x_i,\dots,x_{i+M-1}$ corresponding to a Gauss-Legendre panel the density is smooth and thus it is expected to be well-represented in the basis of Legendre polynomials (shifted and scaled to the interval $[s_1,s_2]$).
 Hence standard interpolation techniques can be used to obtain an accurate approximation to the density $\sigma$ on the interval $s_1 \le s\le s_2$ .

### 2020-04-27 paper_lap/JCP_response1/manuscript.tex
updating appendix b and cleaning up review comments in response

@@
 \newcommand{\dudn}[1]{\frac{\partial u_{#1}}{\partial n}}
+
+\newcommand{\uA}{\underline{A}}
+\newcommand{\usigma}{\underline{\sigma}}
+\newcommand{\uX}{\underline{X}}
+\newcommand{\note}[1]{{\color{red} #1}}
 
@@
 \label{sec:appb}
-In this section, we demonstrate that for a panel which is sufficiently far from the corner and  discretized using $M$ Gauss-Legendre nodes, the density computed using the adjoint of a Dirichlet discretization can be interpolated
+{\color{blue}
+In this section, we demonstrate that for a panel which is sufficiently far from the corner, the density computed using the adjoint of a Dirichlet discretization can be interpolated 
 accurately at any point on the panel. As before let $\Omega$ denote a polygonal domain with boundary $\Gamma$. Let
 $L$ denote the length of the boundary, and let $\gamma: [0,L]\to \mathbb{R}^2$ denote an arc-length parameterization of the boundary.
-Assume that the discretization satisfies the following assumptions:
-\begin{enumerate}
-\item All panels which are not at a corner, are separated from the closest corner by at least their panel length.
-\item Let $E_{\rho}(\Gamma_{i})$ denote the Bernstein $\rho-$ellipse (see \cite{tref_approx}) corresponding to the panel $\Gamma_{i}$, and let $\rho_{i}$ 
-be such that $E_{\rho_{i}}(\Gamma_{i})$ does not intersect $\Gamma \setminus S_{\Gamma_{i}}$, where 
-$S_{\Gamma_{i}}$ is the edge containing $\Gamma_{i}$ (see~\cref{fig:illus-cons}). Let $\rho_{0} = \min_{i} \rho_{i} >1$.
-\item All panels which are not adjacent to a panel at the corner, are separated from the corner by $2r_{c}$ where $r_{c}$ 
-denotes the length of the panel at the corner.
-\end{enumerate}
-Under these assumptions, it can be shown that the accuracy of computing the
-Legendre coefficients of the density (at panels which are not adjacent to a corner panel) for the Neumann problem using the adjoint discretization is related to the accuracy 
-in the computation of the solution to an associated Dirichlet problem.
-\begin{figure}
-\begin{center}
-\includegraphics[width=0.3\linewidth]{paper-figs/geom-restriction-illus}
-\caption{Illustrative figure for demonstrating constraints required on the geometry discretization.
-The panel $\Gamma_{i}$ satisfies restriction 1 if $L_{i}/L_{0}>1$.
-Panel $\Gamma_{j}$ illustrates the largest Bernstein ellipse which intersects the other edges, and Panel $\Gamma_{k}$ illustrates restriction 3 if $r_{k}>2r_{c}$.
-}
-\label{fig:illus-cons}
-\end{center}
-\end{figure}
+Suppose that the boundary is discretized using the procedure discussed in~\cref{sec:resolve}.
+Recall that the discretizaton nodes are denoted by $x_{1},x_{2}\ldots x_{N}$ and the corresponding weights are given by $w_{1}, \ldots w_{N}$.
+Let $X = \mathbb{L}^2({\Gamma})$ and $\underline{X} = \mathbb{R}^{N}$.  Let $\left< \cdot, \cdot \right>_{Y}$
+denote the standard inner products on the Hilbert spaces $Y=X,\underline{X}$.
+Let $S:X \to \uX$ denote the operator which samples a function on the boundary at the discretization nodes scaled by the square root of the weights, i.e. 
+\begin{equation}
+S[f] = (f(x_{1})\sqrt{w_{1}},f(x_{2})\sqrt{w_{2}},\ldots f(x_{N}) \sqrt{w_N} )^{T} = \underline{f} \, .
+\end{equation}
+Let $P:\underline{X} \to X$ denote the operator mapping the discretized samples to it's piecewise interpolant on the boundary.
+Let $\Gamma_{\ell} = \gamma([s_{1},s_{2}])$ denote a panel that does not contain a corner vertex and is discretized with $M$ nodes  $x_{i},x_{i+1},\ldots x_{i+M-1}$.}
 
-Let $A$ denote the operator corresponding to interior Dirichlet problem using a double layer potential. Let $g$ denote the
-right hand side for the Neumann problem, let $\sigma$ denote the corresponding solution. Let $f$ be a Legendre polynomial of
-degree $n$ scaled to the panel $\gamma([s_{1},s_{2}])$ and $0$ everywhere else. Then
+\note{Is there a clean way to give an explicit definition of P or it's obvious?}
+
+{\color{blue}
+Let $A$ denote operator corresponding to the interior Dirichlet problem where the solution is represented as a double layer potential.
+Let $\underline{A}$ denote the $N\times N$ matrix corresponding to the discretization of $A$.
+Let $g$ denote the
+right hand side for the Neumann problem, let $\sigma$ denote the corresponding solution.
+Let $\underline{\sigma}$ denote the solution of the linear system $\uA^{T} \usigma = S[g]$.
+Let $h_{i}$, $i=1,2,\ldots M$, denote the scaled Legendre polynomials to the panel $\Gamma_{\ell}$.
+The main result of this appendix is to show that under suitable assumptions, that the computed density can be accurately interpolated on $\Gamma_{\ell}$, i.e.  
 \begin{equation}
-\left<\sigma, f \right> = \left< (A^{T})^{-1} g, f\right> = \left< g, A^{-1} f \right> = \langle g, \sigma_{f}\rangle \, ,
+e = \max_{i=1,2\ldots M} |\left< \sigma, h_{i} \right>_{X} -  \left< \usigma, S[h_{i}] \right>_{\uX}| < \varepsilon  
 \end{equation}
-where $\sigma_{f}$ is the solution of the interior Dirichlet problem with boundary data $f$ using a double layer potential.
 
-Using~\cref{lem_adjm}, the above statement implies that the error in computing the $M$ Legendre coefficients of
-the density for the Neumann problem is the same as the error in computing the solution of a Dirichlet problem with 
-data given by a Legendre polynomial on the same panel.
+In practice, given boundary data $g$ and a tolerance $\varepsilon$, it is extremely difficult to construct a discretization of the boundary for which the solution to the corresponding integral equation achieves the desired tolerance numerically for a generic $\Gamma$ (even when both the boundary and solution are smooth).
+We instead derive an estimate for $e$ in terms of the error incurred in solving the interior Dirichlet problem for $M$ piecewise smooth boundary functions.
+
+But first, we present a lemma about the accuracy of Gaussian quadrature
+\begin{lem}
+\label{lem:b1}
+Suppose that $p$ is a polynomial of degree less than $M$, then for any function $g$ in $\mathbb{L}^{2}[-1,1]$, then the integral
+$\int_{-1}^{1} p \cdot g$ can be computed accurately using Gaussian quadrature of any order greater than or equal to $M$.
+As a consequence, For any $g$ in $\mathbb{L}^{2}(\Gamma)$, then 
+\begin{equation}
+\left<h_{i},g \right>_{X} = \left< S[h_{i}], S[g] \right>_{\uX}
+\end{equation}
+\end{lem}
 
 Let $V$ denote the collection of corner points in parameter space $[0,L]$, i.e. $a \in V$ if $\gamma(a)$ is a corner vertex.
-Recall that $\sigma_{f}$ denotes the solution of the Dirichlet problem with boundary data $f$, i.e., 
-$\sigma_{f}$ satisfies
+
+\begin{lem}
+\label{lem:b2}
+Let $f_{i}$ be given by
 \begin{equation}
--\frac{\sigma_{f}(s)}{2}   + \int_{0}^{L} k(s,t) \sigma_{f}(t) dt  = f(s) \,  \quad s\in[0,L]\setminus{V}.
+f_{i}(s) = -2 \int_{s_{1}}^{s_{2}} k(s,t) h_{i}(t) dt \, , s\in [0,L] \setminus V \, . \label{eq:deff}
 \end{equation}
- Then $\sigma_{f} = -2f + \tilde{\sigma}$ where $\tilde{\sigma}$ satisfies the integral equation
+Consider the interior Dirichlet problem with boundary data $f_{i}$, where we represent the solution via a double layer potential with density $\sigma_{D,i}$, i.e.
+$\sigma_{D,i}$ satisfies the integral equation
 \begin{equation}
--\frac{\tilde{\sigma}}{2}+ \int_{0}^{L} k(s,t) \tilde{\sigma}(t) dt = -2\int_{s_{1}}^{s_{2}} k(s,t) f(t) dt \, , \quad s\in[0,L] \setminus V \, ,
+A[\sigma_{D,i}] = -\sigma_{D,i}/2 + \int_{0}^{L} k(s,t) \sigma_{D,i}(t) dt  = f_{i}(s) \, , s\in [0,L] \setminus V \, . 
 \end{equation}
-i.e, $\tilde{\sigma}$ is the solution of the Dirichlet with data $\tilde{f}$ given by
+Then,
 \begin{equation}
-\tilde{f}(s) = -2\int_{s_{1}}^{s_{2}} k(s,t) f(t) dt \, , s \in [0,L] \setminus V \, .
+\left< \sigma, h_{i} \right>_{X} -  \left< \usigma, S[h_{i}] \right>_{\uX} = 
+\left< g, \sigma_{D,i} \right> - \left< S[g], \usigma_{D,i} \right>_{\uX}
 \end{equation}
-There are two concerns which must be addressed. First, the accuracy of computing $\tilde{f}(s)$ 
-for any point $s \in [0,L]$ using an $M$ point Gauss-Legendre quadrature on $[s_{1},s_{2}]$, and secondly, 
-the resolution of the function $\tilde{f}(s)$ on the given discretization of the boundary.
+\end{lem}
 
-For any $s$ which is contained on the same segment as $\gamma([s_{1},s_{2}])$, the kernel $k(s,t)$ is identically $0$.
-Thus the boundary data $\tilde{f}(s)=0$  on the same edge as the panel $\gamma([s_{1},s_{2}])$. 
-We further observe that $f(t)$ is an entire function when extended to the complex plane, since it is a Legendre polynomial.
-Moreover, the nearest singularity of the function $k(s,t)$ in the complex plane as a function of $t$ is at $\gamma(s)$.
-From assumption 2, it follows that
-the error in computing $\tilde{f}(s)$ using an $M$ point Gauss-Legendre rule is bounded by $C \rho_{0}^{-M}$, where
-the constant $C$ is related to the smoothness of $k(s,t)$ as a function of $t \in \mathbb{C}.$
-Thus the function $\tilde{f}(s)$ can be computed to any desired precision by increasing the order of quadrature nodes
-used to compute the integrals.
+\begin{proof}
+We first note that if $\sigma_{D,h_{i}}$ is the solution to the integral equation
+\begin{equation}
+A[\sigma_{D,h_{i}}] = -\frac{\sigma_{D,h_{i}}}{2} + \int_{0}^{L} k(s,t) \sigma_{D,h_{i}} dt = h_{i}(s) \, , s \in [0,L] \setminus V \, ,
+\end{equation}
+then, $\sigma_{D,h_{i}} = -2h_{i} + \sigma_{D,i}$. 
+Similarly, the computed solution $\usigma_{D,h_{i}}$ satisfies $\usigma_{D,h_{i}} = -2S[h_{i}] + \usigma_{D,i}$, where
+$\underline{A} [\usigma_{D,h_{i}}] = S[h_{i}]$, and $\underline{A}[\usigma_{D,i}] = S[f_{i}]$.
+The result for $\usigma$ holds since $PS[h_{i}] = h_{i}$, since $h_{i}$ is a polynomial of degree less than $M$ on a Gauss-Legendre panel discretized using $M$ nodes, and since the Nystr\"{o}m discretization of $A$ is interpolatory in nature.
 
-With regards to the resolution of the of the function $\tilde{f}(s)$ on the given discretization of the boundary, 
-we note that the closest singularity of the function $\tilde{f}(s)$ when restricted to a panel away from the corner
-and not on the same edge as $\gamma([s_{1},s_{2}])$ is the closest point on the panel $\gamma([s_{1},s_{2}])$. 
-However, by assumption 2, the error in resolving the function $\tilde{f}(s)$ using an $M$ point Gauss-Legendre
-or Chebyshev panel is bounded by $C \rho_{0}^{-M}$. Note that the behavior of $\tilde{f}(s)$ in the complex plane is related
-to the behavior of $k(s,t)$ in the complex $s$ plane and hence the constant $C$ is $O(1)$.
-For the panels, at the corner, based on the proof in Appendix A, the error in resolving the function $\tilde{f}(s)$ when
-truncated to a Taylor series of order $N$ is less than $C 2^{-N}$, since all points on $\gamma([s_{1},s_{2}])$ are 
-well-separated from corners by twice the panel length $r_{c}$.
-Thus, by making the panels small enough, $\rho$ can be increased arbitrarily to obtain desired tolerances on the boundary data $\tilde{f}(s)$ on the corresponding discretization of the boundary.
+The error in the inner product of the density with $h_{i}$, then is given by
+\begin{equation}
+\begin{aligned}
+\left< \sigma, h_{i} \right>_{X} -  \left< \usigma, S[h_{i}] \right>_{\uX} &=
+\left< (A^{-1})^{T}g, h_{i} \right>_{X} -  \left< (\underline{A}^{-1})^{T}S[g], S[h_{i}] \right>_{\uX}   \\
+&=\left< g, A^{-1}[h_{i}] \right>_{X} -  \left< S[g], \underline{A}^{-1}[S[h_{i}]] \right>_{\uX}   \\
+&=\left< g, \sigma_{D,h_{i}} \right>_{X} -  \left< S[g], \usigma_{D,h_{i}} \right>_{\uX}   \\
+&=\left< g, -2h_{i} + \sigma_{D,i} \right>_{X} -  \left< S[g], -2S[h_{i}] + \usigma_{D,i} \right>_{\uX}   \, .
+\end{aligned}
+\end{equation}
+The result then follows since $\left<g,h_{i} \right>_{X} = \left<S[g],S[h_{i}] \right>_{\uX}$ (\cref{lem:b1}).
+\end{proof}
 
- Thus, the boundary data $\tilde{f}(s)$ is piecewise analytic , which can be approximated to any desired tolerance by appropriately reducing the panel sizes.
-This is the precise setup for which the discretization of the Dirichlet problem is designed to obtain accurate solutions to the density $\tilde{\sigma}$.
+\Cref{lem:b2} shows that the error in evaluating the inner product of the computed density $\usigma$ with a polynomial on
+$\Gamma_{\ell}$ is the same as the error in evaluating the inner product of a computed density for a Dirichlet problem $\usigma_{D,i}$ with boundary data $g$. 
+The Dirichlet boundary data $f_{i}$ (\cref{eq:deff}) corresponding to the density $\sigma_{D,i}$ is an analytic function on each of the edges of the polygon. 
+The discretization of $A$ of~\cite{hoskins2019numerical} is precisely designed to compute $\sigma_{D,i}$ accurately to any desired tolerance, under sufficient refinement of the discretization.
+Since $g$ is also a smooth function, given a tolerance $\varepsilon$, there exists a sufficiently fine discretization of the boundary such that
+\begin{equation}
+\left| \left< g, \sigma_{D,i} \right>_{X} - \left< S[g], \usigma_{D,i} \right>_{\uX} \right| < \varepsilon \, . \label{eq:dest}
+\end{equation}
+In practice, a discretization with macroscopic panels at the corner, panels not at a corner vertex separated from the corner by their panel length, and which resolves $g$ to precision $\varepsilon$ is often sufficient to guarantee~\cref{eq:dest}.
+\begin{rem}
+The size of the panel at the corner needs to be chosen based on the angle formed at the corner---smaller panels for angles closer to $0$ or $2\pi$, in order to resolve the corresponding close to touching interactions.
+\end{rem}
+}
+
+\note{Do we include a description of the discretization procedure we use in practice?}
 

### 2020-04-30 paper_lap/JCP_response1/response.tex
updating response

@@
 \documentclass[11pt]{letter}
-\usepackage{amssymb}
-\usepackage{amsmath}
-\usepackage{color}
-\usepackage{parskip}
+\usepackage{amsmath,amsthm,amssymb,amscd}
+\usepackage{graphicx}
+\usepackage{epstopdf}
+\usepackage{multirow}
+\usepackage{hhline}
+\usepackage{cleveref}
+\usepackage{xcolor}
+\usepackage{tikz}
 \usepackage{comment}
@@
 \usepackage[utf8]{inputenc}
-
 \usepackage[margin=1in]{geometry}
@@
 \qb
-\todo{MR}
+We have included a remark to point out that the conditioning for the solution of Neumann problem is inherited from its corresponding Dirichlet discretization. (see remark)
+
+As noted, with our approach, the conditioning of the discrete system for the Neumann problem inherits the properties of the corresponding Dirichlet discretization.
+The conditioning of using this approach as expected is independent of the number of points used in the discretization.
+However, the physical conditioning of the problem itself is fairly complicated owing to the presence of continuous spectra on various intervals whose sizes depend on the angles formed at the corners.
+This is reflected in any Dirichlet or Neumann discretization for regions with corners and falls outside the scope of this work.
+For the triangle example, we have included a plot of the spectrum of the operator here for reference.
+We also plot the spectrum of the discretized operator based on a dyadic mesh at the corner.
+\begin{center}
+\includegraphics[width=0.4\linewidth]{sp-eigs-plot.pdf}
+\includegraphics[width=0.4\linewidth]{ref-eigs-plot.pdf}
+\end{center}
+
+Similar plots for the singular values of the operators for Dirichlet problem for Laplace and Stokes equations have already been reported in [1] and we feel that it would take away from the main point of the paper.
+
+1. K.~Serkh, V.~Rokhlin, On the solution of elliptic partial differential
+  equations on regions with corners, Journal of Computational Physics 305
+  (2016) 150--171.
 
@@
 Even for a problem with 22k dofs, 105 iterations of a Krylov method seems like a lot, especially if the problem is well-conditioned.
-I can?t help but wonder if this is an artifact of the fact that your FMM tolerance is the same as your iterative method tolerance.
+I can't help but wonder if this is an artifact of the fact that your FMM tolerance is the same as your iterative method tolerance.
 If you set the latter to 1e-14 or 1e-13, does the number of iterations decrease drastically?
@@
 \qb
-\todo{MR}
+We use a version of GMRES which does not suffer from stagnation at low thresholds and an FMM whose tolerance was set to $5 \times 10^{-16}$.
+The number of iterations do not reduce drastically if we increase the iteration count.
+We attach here a plot of the relative residual as a function of iteration number.
+\begin{center}
+\includegraphics[width=0.7\linewidth]{lap-iter-count-wheel.pdf}
+\end{center}
+
+Our boundary data has randomly generated charge strengths and sources.
+For a new run, the original discretization requires $106$ iterations for the Neumann problem.
+The iteration count for the corresponding adjoint Dirichlet problem is $83$, and iteration count on doubling the number of points in our existing discretization is $106$.
 
@@
 \qb
-Thank you for pushing on this.
-We have rewritten the section completely to address all of the concerns above and feel that the readability now is significantly improved.
+Thank you for bringing this to our notice.
+The section as written was confusing and we have rewritten the section completely to address all of the concerns above and feel that the readability now is significantly improved.
 We have eliminated the assumptions on the geometry completely as it can be confusing and rather reduced it to an error estimate of a solution to a Dirichlet problem using the same grid.
+The purpose of our approach is to show that a good Dirichlet discretization of the corner problem can be reutilized to obtain a discretization of the Neumann problem.
 \qa
@@
 \qb
-
-\todo{MR}
+The solution of Laplace's equation in complicated domains is a classical problem in computational physics and has a large array of applications such as electrostatics, fluid flow, diffusion, and magnetohydrodynamics to name a few.
+The use of theorems, lemmas, propositions has been mainly to summarize existing work based which serves as a foundation for our method.
+Here are a few other examples of papers in JCP which we believe are written in a similar style.
 
@@
 
-\todo{MR}
-
+The unified transform method while handles the solution of Laplace's equation on simple polygons, it does not scale for larger problems like the ones presented in the paper.
+The "broken wheel" region for which $22,240$ nodes have been used has $107$
+corners and edges, thereby just requiring approximately $200$ nodes per edge for discretization.
+Moreover, our method has been coupled to FMMs thereby able to solve this problems in $O(N)$ CPU time, where $N$ is the number of degrees of freedom required to discretize the problem.
+We believe that Fokas' method wouldn't be competitive as compared to our method (105 iterations in 15 secs to 13 digits of accuracy and plotting the solution at 250000 points in 6.5 secs on a single CPU core).
+Moreover, our method also extends to discretizations of the Helmholtz problem (for any complex wave number in the first quadrant) and we are currently in the process of describing the discretization procedure for both Dirichlet and Neumann boundary value problems.
 \qa
@@
 
-\todo{MR}
+As stated above, the approach does not scale well for large complicated problems.
+Moreover, our example for the solution in the exterior of the "broken wheel" geometry is emphatically non-convex and we believe is suitably complicated as well.
 
@@
 We hope that our revised manuscript based on their suggestions is now
-suitable for publication in PAA.
+suitable for publication in JCP-X.
 
@@
 \end{letter}
+
 \end{document}

### 2020-04-30 paper_lap/JCP_response1/05apparatus.tex
updating response

@@
 
-\begin{remark1}
+\begin{remark}
 \label{rem:far-field-accuracy}
@@
 the function $K(\by,\gamma(t)) \in S_\epsilon.$ Thus accurate values of the solution in the far-field can be obtained almost immediately.
-\end{remark1}
-\begin{remark1}
+\end{remark}
+\begin{remark}
 \label{rem:strong-sol-smooth}
@@
 The collection of singular powers arising in Neumann problems contain negative powers which are not contained in this set and hence are not interpolated accurately.
-\end{remark1}
+\end{remark}
+\begin{remark}
+In this approach, note that the discretization of the Neumann problem, inherits its spectral properties from the discretization of the corresponding adjoint Dirichlet problem (eigenvalues and singular values are the same, but eigenvectors and singular vectors may differ).
+Thus, when using an iterative method for solving the discrete linear system for the Dirichlet and Neumann problem, the number of iterations required for the relative residual to converge below $\varepsilon$ would be fairly similar.
+\end{remark}
 

### 2020-04-30 paper_lap/JCP_response1/manuscript.tex
updating response

@@
 Let $P:\underline{X} \to X$ denote the operator mapping the discretized samples to it's piecewise interpolant on the boundary.
-Let $\Gamma_{\ell} = \gamma([s_{1},s_{2}])$ denote a panel that does not contain a corner vertex and is discretized with $M$ nodes  $x_{i},x_{i+1},\ldots x_{i+M-1}$.}
+Let $\Gamma_{\ell} = \gamma([s_{1},s_{2}])$ denote a panel that does not contain a corner vertex and is discretized with $M$ nodes  $x_{i},x_{i+1},\ldots x_{i+M-1}$.
 
-\note{Is there a clean way to give an explicit definition of P or it's obvious?}
-
-{\color{blue}
 Let $A$ denote operator corresponding to the interior Dirichlet problem where the solution is represented as a double layer potential.
@@
 
-\note{Do we include a description of the discretization procedure we use in practice?}
-
  \bibliographystyle{elsarticle-num}

### 2020-05-14 paper_lap/JCP_response1/04nprelim.tex
updating response and manuscript

@@
 The Nystr\"{o}m method proceeds as follows.
-We begin by constructing a discretization of the boundary $\Gamma$ with nodes $s_1,\dots,s_N,$ and weights $w_1,\dots,w_N,$ which enable interpolation of the left- and right-hand sides of the boundary integral equation
+We begin by constructing a discretization of the boundary $\Gamma$ with nodes {\color{blue}$x_1,\dots,x_N,$} and weights $w_1,\dots,w_N,$ which enable interpolation of the left- and right-hand sides of the boundary integral equation
 \begin{align}\label{eqn:numpreint}
@@
 \end{align}
-with precision $\epsilon.$ In other words, given $f(s_i),-\sigma(s_i) + \int_0^L k(t,s_i) \,\sigma(t)\, {\rm d} t,$ for $i=1,\dots,N,$ the values $f(s)$ and $-\sigma(s)/2 + \int_0^L k(t,s) \,\sigma(t)\, {\rm d} t$ can be obtained for all $0 \le s \le L$ to within $\epsilon.$
+with precision $\epsilon.$ In other words, given {\color{blue}$f(x_i),-\sigma(x_i) + \int_0^L k(t,x_i) \,\sigma(t)\, {\rm d} t,$} for $i=1,\dots,N,$ the values $f(s)$ and $-\sigma(s)/2 + \int_0^L k(t,s) \,\sigma(t)\, {\rm d} t$ can be obtained for all $0 \le s \le L$ to within $\epsilon.$
 
 Once these nodes and weights have been generated we proceed by enforcing equality of (\ref{eqn:numpreint}) at the discretization nodes, which yields the system of equations
+{\color{blue}
 \begin{align}
-f(s_i) \sqrt{w_i} = -\frac{\sigma(s_i)\sqrt{w_i}}{2} +  \sqrt{w_i}\int_0^L k(t,s_i)\, \sigma(t)\,{\rm d}t,\quad i=1,\dots,N. \label{eqn_1std}
+f(x_i) \sqrt{w_i} = -\frac{\sigma(x_i)\sqrt{w_i}}{2} +  \sqrt{w_i}\int_0^L k(t,x_i)\, \sigma(t)\,{\rm d}t,\quad i=1,\dots,N. \label{eqn_1std}
 \end{align}
+}
 We note that scaling by the square root of the weights in the above equation is equivalent to solving the problem in the $L^2$ sense, and results in discretized operators with condition numbers which are close to those of the original physical systems \cite{bremer3}.
-The new unknowns are $\sigma_i = \sigma(s_i) \sqrt{w_i},$ $i=1,\dots,N.$ Next, for each interpolation node $s_i$ we find a collection of weights $W_{ij}$ such that
+The new unknowns are $\sigma_i = \sigma({\color{blue}x_i}) \sqrt{w_i},$ $i=1,\dots,N.$ Next, for each interpolation node {\color{blue}$x_i$} we find a collection of weights $W_{ij}$ such that
 \begin{align}
-\left|\int_0^L k(t,s_i)\, \sigma(t)\,{\rm d}t- \sum_{j=1}^N W_{ij} \sigma_j\, \sqrt{w_j} \right| < \epsilon,
+\left|\int_0^L k(t,{\color{blue}x_i})\, \sigma(t)\,{\rm d}t- \sum_{j=1}^N W_{ij} \sigma_j\, \sqrt{w_j} \right| < \epsilon,
 \end{align}
@@
 \begin{align}
-  -\frac{\sigma_i}{2} +  \sum_{j=1}^N W_{ij} \sigma_j \sqrt{w_i w_j}=f(s_i) \sqrt{w_i},\quad i,j=1,\dots,N. 
+  -\frac{\sigma_i}{2} +  \sum_{j=1}^N W_{ij} \sigma_j \sqrt{w_i w_j}=f({\color{blue}x_i}) \sqrt{w_i},\quad i,j=1,\dots,N. 
 \end{align}
@@
 Once the discretization has been constructed it is necessary to construct appropriate quadrature for the integrals appearing in equation (\ref{eqn_1std}).
-When $s_i$ and $t$ do not belong to the same corner panel (in particular when either is not itself contained in a corner panel) then the weights and nodes associated with the discretization can be used as the quadrature rule.
+When \upd{$x_i$} and $t$ do not belong to the same corner panel (in particular when either is not itself contained in a corner panel) then the weights and nodes associated with the discretization can be used as the quadrature rule.
 When $s_i$ corresponds to a corner panel special care must be taken.
@@
 \begin{align}
-\int_{0}^\delta k(t,s_j) \tilde{\phi}_j(t)\,{\rm d}t
+\int_{0}^\delta k(t,\upd{x_j}) \tilde{\phi}_j(t)\,{\rm d}t
 \end{align} 
 where $\tilde{\phi}_j$ is a suitably scaled and translated copy of the singular function obtained in the discretization step, and for ease of exposition we assume that the corner panel corresponds to $(-\delta,\delta)$ in the parametrization with $t=0$ corresponding to the corner itself.
-Moreover, in light of symmetry between the two legs of the wedge it suffices to design quadratures assuming  $s_j$ lies in the half of a corner panel parametrized by $(-\delta,0).$
+Moreover, in light of symmetry between the two legs of the wedge it suffices to design quadratures assuming  \upd{$x_j$} lies in the half of a corner panel parametrized by $(-\delta,0).$
 \begin{remark1}
@@
 \begin{remark1}
-By interpolating from the discretization nodes to these quadrature nodes we obtain a set of weights $\tilde{W}_{i,j}$ such that if $s_1,\dots,s_{2K}$ correspond to the discretization of a corner parametrized by $(-\delta,\delta)$ with $0$ corresponding to the corner then
+By interpolating from the discretization nodes to these quadrature nodes we obtain a set of weights $\tilde{W}_{i,j}$ such that if \upd{$x_1,\dots,x_{2K}$} correspond to the discretization of a corner parametrized by $(-\delta,\delta)$ with $0$ corresponding to the corner then
 \begin{align}
-\left| \int_{-\delta}^\delta k(t,s_i) \, \tilde{\phi}_m(t)\,{\rm d}t - \sum_{j=1}^{2K} \tilde{W}_{ij} \tilde{\phi}_{m}(t_j) \right| < \epsilon
+\left| \int_{-\delta}^\delta k(t,\upd{x_i}) \, \tilde{\phi}_m(t)\,{\rm d}t - \sum_{j=1}^{2K} \tilde{W}_{\upd{i,j}} \tilde{\phi}_{m}(\upd{x_j}) \right| < \epsilon
 \end{align}
@@
 \begin{definition}\label{def:seps}
-Let $S_\epsilon \subset L^2([0,L])$ denote the set of functions which can be interpolated from their values at the $N$ discretization nodes to any point in $[0,L]$ with a relative $L^2$ accuracy of $\epsilon.$ That is to say that for $f \in S_\epsilon$ if $\tilde{f}:[0,L] \to \mathbb{R}$ denotes the function obtained by interpolating using the values $f(s_1),\dots,f(s_N)$ then $\|f -\tilde{f}\|_{L^2} < \epsilon.$
+Let $S_\epsilon \subset L^2([0,L])$ denote the set of functions which can be interpolated from their values at the $N$ discretization nodes to any point in $[0,L]$ with a relative $L^2$ accuracy of $\epsilon.$ That is to say that for $f \in S_\epsilon$ if $\tilde{f}:[0,L] \to \mathbb{R}$ denotes the function obtained by interpolating using the values \upd{$f(x_1),\dots,f(x_N)$} then $\|f -\tilde{f}\|_{L^2} < \epsilon.$
 \end{definition}
@@
 The results of this algorithm are summarized in the following theorem (see \cite{}).
+\upd{
 \begin{theorem}
-Let $A$ be the $N\times N$ matrix obtained by discretizing the interior Dirichlet problem in the preceding manner.
-In particular if $f \in S_\epsilon $ is piecewise analytic and ${\bf f} = (\sqrt{w_1}f(s_1),\dots,\sqrt{w_N}f(s_N))^T$ then
+Let $A$ the integral operator corresponding to the interior Dirichlet problem, i.e. 
+\begin{equation}
+A[\sigma](s) = -\frac{\sigma(s)}{2} + \int_{0}^{L} k(t,s) \sigma(t) dt \, . 
+\end{equation}
+Let $\uA \in \mathbb{R}^{N\times N}$ denote the corresponding discretized matrix. In particular if $f \in S_\epsilon $ is piecewise analytic and 
+\begin{equation}
+S[f] = (f(x_{1})\sqrt{w_{1}},f(x_{2})\sqrt{w_{2}},\ldots f(x_{N}) \sqrt{w_N} )^{T} = \underline{f} \, ,
+\end{equation}
+then
 \begin{align}
-\underline{\bf \sigma} = A^{-1} {\bf f}
+\underline{\sigma} = \uA^{-1} {\uf}
 \end{align}
@@
 \end{theorem}
+}
 

### 2020-05-14 paper_lap/JCP_response1/05apparatus.tex
updating response and manuscript

@@
 \subsection{Adjoint discretization}
-
+\upd{Let $X = \mathbb{L}^2([0,L])$ and $\underline{X} = \mathbb{R}^{N}$.  Let $\left< \cdot, \cdot \right>_{Y}$
+denote the standard inner products on the Hilbert spaces $Y=X,\underline{X}$.}
 The following lemma relates the discretization of the inverse of an operator to the adjoint of the discretization of its inverse.
 Its proof follows directly from the definition of the adjoint and is omitted.
+\upd{
 \begin{lemma}\label{lem_adjm}
-Suppose $A: L^2([0,L]) \to L^2([0,L])$ is a bounded invertible operator and that $A_\epsilon$ is an operator such that
+Suppose $A: X \to X$ is a bounded invertible operator and that $\uA: \uX \to \uX$ is the corresponding discretized operator such that
 \begin{align}
-\left| \langle f,A^{-1} g \rangle - \langle f,A^{-1}_\epsilon g \rangle \right| \le \epsilon \|f\| \|g\|,
+\left| \langle f,A^{-1} g \rangle_{X} - \langle S[f],\uA^{-1} S[g] \rangle_{\uX} \right| \le \epsilon \|f\|_{X} \|g\|_{X},
 \end{align}
-for all $f$ and $g$ in some subspace $S_{\epsilon} \subset L^2([0,L]).$ Here $\langle \cdot, \cdot \rangle$ denotes the inner product on $L^2([0,L])$ and $\| \cdot\|$ denotes the norm for $L^2([0,L]).$ Then, for all functions $f$ and $g$ in $S_{\epsilon}$
+for all $f$ and $g$ in some subspace $S_{\epsilon} \subset L^2([0,L]).$  Then, for all functions $f$ and $g$ in $S_{\epsilon}$
 \begin{align}
-\left| \langle f,(A^{-1})^* g \rangle - \langle f,\left(A^{-1}_\epsilon\right)^* g \rangle \right| \le \epsilon \|f\| \|g\|
+\left| \langle f,(A^{-1})^* g \rangle_{X} - \langle S[f],\left(A^{-1}_\epsilon\right)^* S[g] \rangle_{\uX} \right| \le \epsilon \|f\|_{X} \|g\|_{X}
 \end{align}
@@
 \end{lemma}
+}
 
 The following corollary follows immediately from the previous result.
+\upd{
 \begin{corollary}
-Let $A$ be the $N\times N$ matrix obtained by discretizing the interior Dirichlet problem and $S_\epsilon$ be the collection of functions given by Definition \ref{def:seps}.
+Let $\uA$ be the $N\times N$ matrix obtained by discretizing the interior Dirichlet problem and $S_\epsilon$ be the collection of functions given by Definition \ref{def:seps}.
 Then for all functions $f,g \in S_\epsilon$
 \begin{align}
-\left| \langle {\bf g}, (A^T)^{-1}{\bf f} \rangle - \int_0^L g(t)\,\sigma(t)\,{\rm d}t \right| < \epsilon \|f\|\, \|g\|,
+\left| \langle S[g], (\uA^T)^{-1}S[f] \rangle - \int_0^L g(t)\,\sigma(t)\,{\rm d}t \right| < \epsilon \|f\|\, \|g\|,
 \end{align}
-where ${\bf f},{\bf g}$ are the discretizations of $f$ and $g$ scaled by the square roots of the discretization weights, and $\sigma$ is the solution to the exterior Neumann problem with boundary data $f$.
+where $\sigma$ is the solution to the exterior Neumann problem with boundary data $f$.
 \end{corollary}
+}
 
@@
 \end{remark}
+{\color{blue}
 \begin{remark}
@@
 \end{remark}
+}
 
@@
 
-Additionally, we denote the discretization of the interior Dirichlet operator (using the custom quadratures described in Section \ref{sec:disc_dir}) by $A.$ Let $\underline{f} = (f_1,\dots,f_N)^T$ where $f_i = f(x_i) \sqrt{w_i}$ and $f: \partial \Omega \to \mathbb{R}$ is the right-hand side of the exterior Neumann problem.
+Additionally, we denote the discretization of the interior Dirichlet operator (using the custom quadratures described in Section \ref{sec:disc_dir}) by $\upd{\uA}.$ As before, let $\underline{f} = (f_1,\dots,f_N)^T$ where $f_i = f(x_i) \sqrt{w_i}$ and $f: \partial \Omega \to \mathbb{R}$ is the right-hand side of the exterior Neumann problem.
 Finally, let $\underline{\sigma}$ be the approximation to the density (scaled by the square roots of the weights) obtained by solving the linear system
 \begin{align}\label{eqn:adj_linalg}
-A^T \underline{\sigma} = \underline{f}.
+\upd{\uA}^T \underline{\sigma} = \underline{f}.
 \end{align}
@@
 
-For a panel $\gamma([s_1,s_2])$ with discretization nodes $x_i,\dots,x_{i+M-1}$ corresponding to a Gauss-Legendre panel the density is smooth and thus it is expected to be well-represented in the basis of Legendre polynomials (shifted and scaled to the interval $[s_1,s_2]$).
+For a panel $\gamma([s_1,s_2])$ with discretization nodes {\color{blue}$x_i,\dots,x_{i+M-1}$} corresponding to a Gauss-Legendre panel the density is smooth and thus it is expected to be well-represented in the basis of Legendre polynomials (shifted and scaled to the interval $[s_1,s_2]$).
 Hence standard interpolation techniques can be used to obtain an accurate approximation to the density $\sigma$ on the interval $s_1 \le s\le s_2$ .
@@
 \begin{proposition}
-Suppose that $f$ be a piecewise-analytic function in $S_\epsilon$ and  $\underline{\sigma} = (A^T)^{-1} {\bf f}$ is the approximation to the Neumann density obtained using the adjoint of the discretization for the interior Dirichlet boundary integral equation.
+Suppose that $f$ be a piecewise-analytic function in $S_\epsilon$ and  $\underline{\sigma} = (\upd{\uA}^T)^{-1} \upd{\uf}$ is the approximation to the Neumann density obtained using the adjoint of the discretization for the interior Dirichlet boundary integral equation.
 Further suppose that the discretization nodes are ordered so that $s_1,\dots,s_P$ correspond to the corner panel associated with the interval $(-\delta,\delta),$ $s_{P+1},\dots,s_{P+M}$ correspond to the Gauss-Legendre panel immediately to the left associated with the interval $(-2\delta,-\delta),$ and $s_{P+M+1},\dots,s_{P+2M}$ to the Gauss-Legendre panel immediately to the right associated with the interval $(\delta,2\delta).$
@@
 Let $\underline{f}_0$ denote the right-hand side of (\ref{eqn:resolve_neum0}) evaluated at these discretization nodes and scaled by the square roots of the corresponding weights.
-Let $A_0$ be the discretization of the interior Dirichlet problem operator (ie.
+Let $\upd{\uA_0}$ be the discretization of the interior Dirichlet problem operator (ie.
 the operator acting on $\sigma$ on the left-hand side of (\ref{eqn:resolve_diri0})).
-We note that due to the scale invariance of Laplace's equation for polygonal domains the portion of $A_0$ corresponding to the self-interaction of $L_0$ is a submatrix of the original matrix $A.$ All other blocks can be generated using the discretization nodes as quadrature nodes.
+We note that due to the scale invariance of Laplace's equation for polygonal domains the portion of $\upd{\uA_0}$ corresponding to the self-interaction of $L_0$ is a submatrix of the original matrix $\upd{\uA}.$ All other blocks can be generated using the discretization nodes as quadrature nodes.
 
@@
 \begin{align}
-A_0^T \underline{\sigma}_0 = \underline{f}_0
+\upd{\uA_0^T} \underline{\sigma}_0 = \underline{f}_0
 \end{align}
@@
 and $\tilde{\sigma} = (\sigma_1,\dots,\sigma_P)^T$ be the approximation to the solution in the vicinity of the corner obtained by solving the original system (\ref{eqn:adj_linalg}).
-Then $|(f(t)-h(t)) - w(t) U^{-1} A_0^T \tilde{\sigma}| = O(\epsilon)$ for all $t \in(-\delta,\delta).$ In particular, if $\tilde{f}_0$ is the vector of length $N_0$ with entries defined by
+Then $|(f(t)-h(t)) - w(t) U^{-1} \upd{\uA_0^T} \tilde{\sigma}| = O(\epsilon)$ for all $t \in(-\delta,\delta).$ In particular, if $\tilde{f}_0$ is the vector of length $N_0$ with entries defined by
 \begin{align}
-(\tilde{f}_0)_i = w(s^0_i) U^{-1} A_0^T \tilde{\sigma}, \quad i=1,\dots,N_0,
+(\tilde{f}_0)_i = w(s^0_i) U^{-1} \upd{\uA_0^T} \tilde{\sigma}, \quad i=1,\dots,N_0,
 \end{align}
@@
 \begin{align}\label{eqn:linalg_thm}
-\underline{f} = A^T \begin{pmatrix}\tilde{\sigma}\\ \sigma_{P+{2M+1}}\\ \vdots\\ \sigma_N\end{pmatrix}.
+\underline{f} = \upd{\uA^T} \begin{pmatrix}\tilde{\sigma}\\ \sigma_{P+{2M+1}}\\ \vdots\\ \sigma_N\end{pmatrix}.
 \end{align}
-Let $A_0$ be the $(P+2M)\times (P+2M)$ submatrix of $A$ corresponding to the first $P+2M$ rows and columns of $A,$ and $A_{\rm red}$ be the $P+2M \times (N-P-2M)$  submatrix of $A$ corresponding to selecting the first $P+2M$ rows of $A$ and all but the first $P+2M$ columns of $A.$ Using this notation, the first $P+2M$ rows of (\ref{eqn:linalg_thm}) can be re-written as
+Let $\upd{\uA}_0$ be the $(P+2M)\times (P+2M)$ submatrix of $\upd{\uA}$ corresponding to the first $P+2M$ rows and columns of $\upd{\uA},$ and $\upd{\uA}_{\rm red}$ be the $P+2M \times (N-P-2M)$  submatrix of $\upd{\uA}$ corresponding to selecting the first $P+2M$ rows of $\upd{\uA}$ and all but the first $P+2M$ columns of $\upd{\uA}.$ Using this notation, the first $P+2M$ rows of (\ref{eqn:linalg_thm}) can be re-written as
 \begin{align}
-\begin{pmatrix}f_1\\\vdots \\ f_{P+2M}\end{pmatrix}  = A_{\rm red}^T \begin{pmatrix} \sigma_{P+2M+1}\\ \vdots\\ \sigma_N\end{pmatrix} + A_0^T \tilde{\sigma}.
+\begin{pmatrix}f_1\\\vdots \\ f_{P+2M}\end{pmatrix}  = \upd{\uA}_{\rm red}^T \begin{pmatrix} \sigma_{P+2M+1}\\ \vdots\\ \sigma_N\end{pmatrix} + \upd{\uA}_0^T \tilde{\sigma}.
 \end{align}
@@
 \begin{align}
-(f(s_1)-h(s_1),\dots,f(s_{P+2M})-h(s_{P+2M}))^T = A_0^T \tilde{\sigma}.
+(f(s_1)-h(s_1),\dots,f(s_{P+2M})-h(s_{P+2M}))^T = \upd{\uA}_0^T \tilde{\sigma}.
 \end{align}

### 2020-05-14 paper_lap/JCP_response1/manuscript.tex
updating response and manuscript

@@
 \newcommand{\usigma}{\underline{\sigma}}
+\newcommand{\uf}{\underline{f}}
 \newcommand{\uX}{\underline{X}}
 \newcommand{\note}[1]{{\color{red} #1}}
+\newcommand{\upd}[1]{{\color{blue} #1}}
 
@@
 Suppose that the boundary is discretized using the procedure discussed in~\cref{sec:resolve}.
-Recall that the discretizaton nodes are denoted by $x_{1},x_{2}\ldots x_{N}$ and the corresponding weights are given by $w_{1}, \ldots w_{N}$.
-Let $X = \mathbb{L}^2({\Gamma})$ and $\underline{X} = \mathbb{R}^{N}$.  Let $\left< \cdot, \cdot \right>_{Y}$
-denote the standard inner products on the Hilbert spaces $Y=X,\underline{X}$.
-Let $S:X \to \uX$ denote the operator which samples a function on the boundary at the discretization nodes scaled by the square root of the weights, i.e. 
+Recall that the discretizaton nodes are denoted by $x_{1},x_{2}\ldots x_{N}$, the corresponding weights are given by $w_{1}, \ldots w_{N}$, $X = \mathbb{L}^2({\Gamma})$, $\underline{X} = \mathbb{R}^{N}$, $\left< \cdot, \cdot \right>_{Y}$
+denote the standard inner products on the Hilbert spaces $Y=X,\underline{X}$, and
+$S:X \to \uX$ denote the operator which samples a function on the boundary at the discretization nodes scaled by the square root of the weights, i.e. 
 \begin{equation}

### 2020-06-10 paper_lap/JCP_response2/response.tex
update

--- 2020-04-30 paper_lap/JCP_response1/response.tex
@@
 \qb
-We have included a remark to point out that the conditioning for the solution of Neumann problem is inherited from its corresponding Dirichlet discretization. (see remark)
+We have included a remark to point out that the conditioning for the solution of Neumann problem is inherited from its corresponding Dirichlet discretization. (see remark 5.3)
 
@@
 \qb
-The solution of Laplace's equation in complicated domains is a classical problem in computational physics and has a large array of applications such as electrostatics, fluid flow, diffusion, and magnetohydrodynamics to name a few.
-The use of theorems, lemmas, propositions has been mainly to summarize existing work based which serves as a foundation for our method.
+The solution of Laplace's equation in complicated domains is a classical problem in computational physics and has many applications such as electrostatics, fluid flow, diffusion, and magnetohydrodynamics to name a few.
+Theorems, lemmas, propositions have been mainly used to summarize existing work which serves as a foundation for our method.
 Here are a few other examples of papers in JCP which we believe are written in a similar style.
@@
 
-The unified transform method while handles the solution of Laplace's equation on simple polygons, it does not scale for larger problems like the ones presented in the paper.
-The "broken wheel" region for which $22,240$ nodes have been used has $107$
+The unified transform method while handles the solution of Laplace's equation on simple polygons, does not scale in performance for larger problems like the ones presented in the paper.
+The "broken wheel" region for which $22,240$ discretization nodes are used, has $107$
 corners and edges, thereby just requiring approximately $200$ nodes per edge for discretization.
-Moreover, our method has been coupled to FMMs thereby able to solve this problems in $O(N)$ CPU time, where $N$ is the number of degrees of freedom required to discretize the problem.
-We believe that Fokas' method wouldn't be competitive as compared to our method (105 iterations in 15 secs to 13 digits of accuracy and plotting the solution at 250000 points in 6.5 secs on a single CPU core).
-Moreover, our method also extends to discretizations of the Helmholtz problem (for any complex wave number in the first quadrant) and we are currently in the process of describing the discretization procedure for both Dirichlet and Neumann boundary value problems.
+Moreover, our method is accelerated with simple modifications to the standard FMMs and thereby able to solve such problems in $O(N)$ CPU time, where $N$ is the number of degrees of freedom required to discretize the problem.
+We believe that Fokas' method wouldn't be competitive in performance when compared to our method on complicated geometries (105 iterations in 15 secs to obtain 13 digits of accuracy in the computed solution and plotting the solution at 250000 points in 6.5 secs on a single CPU core).
+Moreover, our method also extends to discretizations of the Helmholtz problem (for any complex wave number in the first quadrant) and we are currently preparing a manuscript which describes the discretization procedure for both Dirichlet and Neumann boundary value problems.
 \qa
@@
 
-We thank the reviewer for their careful reads of our manuscript, and comments 
+We thank the reviewers for their careful reads of our manuscript, and comments 
 which have helped significantly improve the quality of the manuscript.

### 2020-06-10 paper_lap/JCP_response2/01intro.tex
update

--- 2020-04-09 paper_lap/JCP_response1/01intro.tex
@@
 \section{Introduction}
-Laplace's equation arises in a vast array of contexts (electrostatics, harmonic functions, low-frequency acoustics, percolation theory, homogenization theory, and the study field enhancements in vacuum insulators for example) and serves as a useful model problem for the study of general elliptic partial differential equations (PDEs).
+Laplace's equation arises in a vast array of contexts (electrostatics, harmonic functions, low-frequency acoustics, percolation theory, homogenization theory, and the study of field enhancements in vacuum insulators for example) and serves as a useful model problem for the study of general elliptic partial differential equations (PDEs).
 As such, effective numerical methods for quickly and robustly solving Laplace's equation with high accuracy are desirable.
@@
 Moreover, the corner refinement and compression can be done in tandem resulting in fast and accurate solvers for elliptic PDEs (see \cite{helsing}, \cite{helsing2},  \cite{ojala}, \cite{helsjcp} and \cite{helsinv}  for  one approach called recursive compressed preconditioning, and  \cite{gillman}, \cite{bremer},\cite{bremer2}, and \cite{bremer3}  for other compression-based methods for solving Laplace's equation).
-Unfortunately, this approach becomes considerably more expensive in three dimensions limiting its application in that context.
+Unfortunately, this approach becomes considerably more expensive in three dimensions {\color{red}limiting its application in that context}.
 
@@
 We then show how this solution can be used to obtain accurate solutions to the Neumann problem arbitrarily close to a corner by solving a set of local subproblems in the vicinity of that corner.
+{\color{olive}This approach generalizes naturally to three-dimensional problems, though efficient discretization of the corresponding Dirichlet problems is the subject of ongoing research.
+A similar analysis as in \cite{} can be used to characterize the singularities along edges and near vertices, though there are a few challenges which prevent the immediate application of this analysis to the design of suitable discretizations.}
 

### 2020-06-10 paper_lap/JCP_response2/03bvp.tex
update

--- 2020-01-08 paper_lap/03bvp.tex
@@
 \end{equation}
-where $\nu(\bx)$ is the inward-pointing normal to $\Gamma$ at $\bx.$ It will often be convenient to 
+where $\bnu(\bx)$ is the inward-pointing normal to $\Gamma$ at $\bx.$ It will often be convenient to 
 work instead with a parametrization of $K.$ In particular, if $\gamma :[0,L] \to \Gamma$ is a counterclockwise 
@@
 \end{align}
+{\color{olive}By a standard abuse of notation we use $\cS$ and $\cD$ to denote both the operators acting on $L^2(\Gamma)$ as well as the corresponding operators acting on $L^2([0,L]),$ the latter being obtained from the former by composition with the parameterization.}
 \end{definition}
 
-The following theorems describe the behavior of the single and double layer potentials in the vicinity of the boundary curve $\Gamma.$
+The following theorems {\color{olive}(see \cite{kress1989linear})} describe the behavior of the single and double layer potentials in the vicinity of the boundary curve $\Gamma.$
 
@@
 for some $\alpha >0.$ Then for any continuous function $\sigma:\Gamma \to \mathbb{R},$
+{\color{olive}
 \begin{align}
 &\lim_{\bx \to \bx_0} \cS[\sigma](\bx) = \cS[\sigma](\bx_0)\\
-&\lim_{\bx \to \bx_0} \cD[\sigma](\bx) = \cD[\sigma](\bx_0)- \frac{\sigma(\bx_0)}{2})\\
-&\lim_{\bx \to \bx_0} \left.\frac{{\rm d}}{{\rm d}\tau}\right|_{\tau= 0}\cS[\sigma](\bx+\tau \bnu(\bx_0)) = \left.\frac{{\rm d}}{{\rm d}\tau}\right|_{\tau= 0}\cS[\sigma](\bx_0+\tau \bnu(\bx_0))+ \frac{\sigma(\bx_0)}{2}.
+&\lim_{\bx \to \bx_0} \cD[\sigma](\bx) = \cD[\sigma](\bx_0)- \frac{\sigma(\bx_0)}{2}\\
+&\lim_{\bx \to \bx_0} \left.\frac{{\rm d}}{{\rm d}\tau}\right|_{\tau= 0}\cS[\sigma](\bx+\tau \bnu(\bx_0)) = \left.\frac{{\rm d}}{{\rm d}\tau}\right|_{\tau= 0^+}\cS[\sigma](\bx_0+\tau \bnu(\bx_0))+ \frac{\sigma(\bx_0)}{2},
 \end{align}
-Similarly, if $\bx$ approaches a point $\bx_0 = \gamma(t_0)$ from the outside then for any continuous function $\sigma:\Gamma \to \mathbb{R},$
+where $\bnu$ is the inward-pointing normal.} Similarly, if $\bx$ approaches a point $\bx_0 = \gamma(t_0)$ from the outside then for any continuous function $\sigma:\Gamma \to \mathbb{R},$
+{\color{olive}
 \begin{align}
@@
 &\lim_{\bx \to \bx_0} \cD[\sigma](\bx) = \cD[\sigma](\bx_0)+ \frac{\sigma(\bx_0)}{2}\\
-&\lim_{\bx \to \bx_0} \left.\frac{{\rm d}}{{\rm d}\tau}\right|_{\tau= 0}\cS[\sigma](\bx+\tau \bnu(\bx_0)) = \left.\frac{{\rm d}}{{\rm d}\tau}\right|_{\tau= 0}\cS[\sigma](\bx_0+\tau \bnu(\bx_0))- \frac{\sigma(\bx_0)}{2}.
-\end{align}
+&\lim_{\bx \to \bx_0} \left.\frac{{\rm d}}{{\rm d}\tau}\right|_{\tau= 0}\cS[\sigma](\bx+\tau \bnu(\bx_0)) = \left.\frac{{\rm d}}{{\rm d}\tau}\right|_{\tau= 0^+}\cS[\sigma](\bx_0+\tau \bnu(\bx_0))- \frac{\sigma(\bx_0)}{2}.
+\end{align}}
 \end{theorem}
@@
 \begin{align}
-\bnu(\by)\cdot \nabla \cS[\rho] (\bx_0) = \left.\frac{{\rm d}}{{\rm d}\tau}\right|_{\tau = 0} \cS[\rho](\bx_0 + \tau \bnu(\bx_0)),
+\bnu(\bx_0)\cdot \nabla \cS[\rho] (\bx_0) = \left.\frac{{\rm d}}{{\rm d}\tau}\right|_{\tau = 0} \cS[\rho](\bx_0 + \tau \bnu(\bx_0)).
 \end{align}
-where $\gamma(t_0) = \bx_0.$
+{\color{red}where $\gamma(t_0) = \bx_0.$}
 \end{definition}
@@
 \begin{theorem} [Interior Dirichlet problem for Laplace's equation]
-For every $f:[0,L] \rightarrow \mathbb{R}$ in $L^{2}[0,L],$ there exists a unique $\sigma \in L^{2}[0,L]$ which satisfies
+For every $f:[0,L] \rightarrow \mathbb{R}$ in $L^{2}([0,L]),$ there exists a unique $\sigma \in L^{2}([0,L])$ which satisfies
 \begin{align}
@@
 \end{align}
-Moreover, the solution to the interior Dirichlet problem for Laplace's equation with boundary data $f$ is given by $u(\by) = \cD[\sigma](\by)$ for all $\by \in \Omega.$
+for all $s \in [0,L).$ Moreover, the solution to the interior Dirichlet problem for Laplace's equation with boundary data $f$ is given by $u(\by) = \cD[\sigma](\by)$ for all $\by \in \Omega.$
 \end{theorem}
@@
 \begin{theorem} [Exterior Dirichlet problem for Laplace's equation]
-For every $f:[0,L] \rightarrow \mathbb{R}$ in $L^{2}[0,L]$ there exists a unique $\sigma \in L^{2}[0,L]$ which
+For every $f:[0,L] \rightarrow \mathbb{R}$ in $L^{2}([0,L])$ there exists a unique $\sigma \in L^{2}([0,L])$ which
 satisfies
@@
 \begin{theorem}[Interior Neumann problem for Laplace's equation]
-For every  $f:[0,L] \rightarrow \mathbb{C}$ in $L^{2}[0,L]$ such that $\int_{0}^{L} f(t) = 0,$ there exists a unique $\sigma \in L^{2}[0,L]$ which satisfies
+For every  $f:[0,L] \rightarrow \mathbb{R}$ in $L^{2}([0,L])$ such that $\int_{0}^{L} f(t)\,{\rm d}t = 0,$ there exists a unique $\sigma \in L^{2}([0,L])$ which satisfies
 \begin{align}
@@
 \end{align}
-Moreover, the solution to the interior Neumann problem for Laplace's equation with boundary data $f$ is given by $u(\by) = \cS[\sigma](\by)$ for all $\by \in \Omega.$
+for all $s \in [0,L).$ Moreover, the solution to the interior Neumann problem for Laplace's equation with boundary data $f$ is given by $u(\by) = \cS[\sigma](\by)$ for all $\by \in \Omega.$
 \end{theorem}
@@
 \begin{theorem}[Exterior Neumann problem for Laplace's equation]
-For every $f:[0,L] \rightarrow \mathbb{C}$ in $L^{2}[0,L]$ there exists a unique $\sigma \in L^{2}[0,L]$ which satisfies
+For every $f:[0,L] \rightarrow \mathbb{R}$ in $L^{2}([0,L])$ there exists a unique $\sigma \in L^{2}([0,L])$ which satisfies
 \begin{align}
@@
 
-In the remainder of this section, we assume $\Gamma$ is an open wedge with sides of length one and interior angle $\pi \alpha$ with $0 <\alpha<2.$ Let $\gamma:[-1,1] \rightarrow \Gamma$ be an arc length parametrization of $\Gamma$ and $\nu:[-1,1] \rightarrow \mathbb{R}^2$ be the inward-pointing normal to $\Gamma.$
+In the remainder of this section, we assume $\Gamma$ is an open wedge with sides of length one and interior angle $\pi \alpha$ with $0 <\alpha<2.$ Let $\gamma:[-1,1] \rightarrow \Gamma$ be an arclength parametrization of $\Gamma$ and $\bnu:[-1,1] \rightarrow \mathbb{R}^2$ be the inward-pointing normal to $\Gamma.$
 The following theorem  gives an explicit representation of the solutions of the boundary integral equation (\ref{bie_intd}) in this geometry.
@@
 \begin{align}
-\sigma(t) =& b_0+\sum_{i=1}^{\overline{L}} b_i |t|^{\frac{2i-1}{\alpha}}+\sum_{i=1}^{\underline{M}} b_{\overline{L}+i} |t|^\frac{2i}{2-\alpha}\left(\log|t|\right)^{\sigma_{N,\alpha}(i)}\nonumber\\
-&+\sum_{i=1}^{\overline{M}}c_i \sgn(t) |t|^\frac{2i-1}{2-\alpha}+\sum_{i=1}^{\underline{L}}c_{\overline{M}+i} \sgn(t) |t|^\frac{2i}{\alpha}\left(\log|t|\right)^{\nu_{N,\alpha}(i)}\label{eqn_rhfm}
+\sigma(t) =& b_0+\sum_{i=1}^{\overline{L}} b_i |t|^{\frac{2i-1}{\alpha}}+\sum_{i=1}^{\underline{M}} b_{\overline{L}+i} |t|^\frac{2i}{2-\alpha}\left(\log|t|\right)^{\phi_{N,\alpha}(i)}\nonumber\\
+&+\sum_{i=1}^{\overline{M}}c_i \sgn(t) |t|^\frac{2i-1}{2-\alpha}+\sum_{i=1}^{\underline{L}}c_{\overline{M}+i} \sgn(t) |t|^\frac{2i}{\alpha}\left(\log|t|\right)^{\psi_{N,\alpha}(i)}\label{eqn_rhfm}
 \end{align}
-where $b_0,b_1,\dots,b_N$ and $c_1,c_2,\dots,c_N$ are arbitrary real numbers and the functions $\sigma_{\alpha,N}(i)$ and $\nu_{\alpha,N}(i)$ are defined as follows
+where $b_0,b_1,\dots,b_N$ and $c_1,c_2,\dots,c_N$ are arbitrary real numbers and the functions $\phi_{N,\alpha}(i)$ and $\psi_{N,\alpha}(i)$ are defined as follows
 \begin{align}
-\sigma_{N,\alpha}(i) = \begin{cases}
+\phi_{N,\alpha}(i) = \begin{cases}
 1 \quad\quad & \,\text{if}\,\, \frac{2i}{2-\alpha} = \frac{2j-1}{\alpha}\,\,\text{for some}\,\, j \in \mathbb{Z},\, 1\le j \le \left\lceil \frac{\alpha N}{2} \right\rceil\\
@@
 \begin{align}
-\nu_{N,\alpha}(i) = \begin{cases}
+\psi_{N,\alpha}(i) = \begin{cases}
 1 \quad\quad & \,\text{if}\,\, \frac{2i}{\alpha} = \frac{2j-1}{2-\alpha}\,\,\text{for some}\,\, j \in \mathbb{Z},\, 1\le j \le \left\lceil \frac{(2-\alpha) N}{2} \right\rceil\\
@@
 Suppose further that $N$ is an arbitrary positive integer.
-Then, for all angles $\pi \alpha$ there exist unique real numbers $b_0,\,b_1,\,\dots,\,b_N$ and $c_0,\,c_1,\,\dots,\,c_N$ such that $\rho,$ defined by (\ref{eqn_rhfm}), solves equation  (\ref{eqn_grho}) to within an error ${\rm O}(t^{N+1}).$
+Then, for all angles $\pi \alpha$ there exist unique real numbers $b_0,\,b_1,\,\dots,\,b_N$ and $c_0,\,c_1,\,\dots,\,c_N$ such that $\sigma,$ defined by (\ref{eqn_rhfm}), solves equation  (\ref{eqn_grho}) to within an error ${\rm O}(t^{N+1}).$
 \end{theorem}
@@
 \end{remark1}
+
+{\color{olive}
+\begin{remark1}
+We note that the smoothness of the kernel $k$ for well-separated portions of the domain guarantees that the problem of determining the singularities arising in the vicinity of a corner for a polygonal domain can be reduced to the analysis of the wedge case, see the discussion in \cite{} for example.
+\end{remark1}
+}
 

### 2020-06-10 paper_lap/JCP_response2/04nprelim.tex
update

--- 2020-05-14 paper_lap/JCP_response1/04nprelim.tex
@@
 \end{align}
-with precision $\epsilon.$ In other words, given {\color{blue}$f(x_i),-\sigma(x_i) + \int_0^L k(t,x_i) \,\sigma(t)\, {\rm d} t,$} for $i=1,\dots,N,$ the values $f(s)$ and $-\sigma(s)/2 + \int_0^L k(t,s) \,\sigma(t)\, {\rm d} t$ can be obtained for all $0 \le s \le L$ to within $\epsilon.$
+with precision $\epsilon.$ In other words, given {\color{blue}$f(x_i),$ and $-\sigma(x_i)/2 + \int_0^L k(t,x_i) \,\sigma(t)\, {\rm d} t,$} for $i=1,\dots,N,$ the values $f(s)$ and $-\sigma(s)/2 + \int_0^L k(t,s) \,\sigma(t)\, {\rm d} t$ can be obtained for all $0 \le s \le L$ to within $\epsilon.$
 
@@
 
-The boundary $\Gamma$ is separated into a collection of intervals which are at least a fixed distance $\delta$  (measured in terms of arclength) away from a corner and the collection of intervals of length $2 \delta$ centered about each corner.
-The former are discretized using a standard smooth quadrature rule such as nested Gauss-Legendre quadrature while the latter are discretized using a custom set of interpolation nodes constructed in the following way.
+The boundary {\color{olive}$\Gamma$ is divided into a collection of disjoint pieces each of which are at least a fixed distance $\delta$  (measured in terms of arclength) away from a corner, and a collection of pieces of length $2 \delta$ centered about each corner.
+}The former are discretized using a standard smooth quadrature rule such as {\color{red}nested} Gauss-Legendre quadrature while the latter are discretized using a custom set of interpolation nodes constructed in the following way.
 
-First, all functions of the form $x^\mu,$ $\mu \in \{0\} \cup [1/2,50],$ $x \in [0,1]$ are discretized using nested Gauss-Legendre panels in $x$ and a single Gauss-Legendre panel in $\mu$.
-This creates a $N \times M$ matrix where $N$ denotes the number of spatial discretization points $r_i$ and $M$ denotes the number of $\mu_j$ chosen.
-$M$ and $N$ are increased until it is guaranteed that using Lagrange interpolation from the nested discretization the function $x^\mu$ can be interpolated to within an $L^2$ error less than $\epsilon$ on the interval $[0,1]$ for any $\mu$ in the specified range.
-A singular value decomposition is then performed on the $N\times M$ matrix.
-Let $K$ denote the number of singular values greater than $\epsilon.$ The right singular vectors correspond to discretizations of an orthonormal set of functions $\phi_1,\dots,\phi_K$ such that $x^\mu$ is in the span of $\phi_1,\dots,\phi_K$ to within an accuracy of $\epsilon.$
+First, all functions of the form $x^\mu,$ $\mu \in \{0\} \cup [1/2,50],$ $x \in [0,1]$ are discretized {\color{olive} in $x$ using an adaptive interpolation scheme based on Gauss-Legendre panels}, and {\color{olive}in $\mu$ using} a single Gauss-Legendre panel for the range $[1/2,50].$ This creates a $N_x \times (N_\mu+1)$ matrix where $N_x$ denotes the number of spatial discretization points $r_i$ and $N_\mu$ denotes the number of $\mu_j$ chosen.
+The extra row in the matrix corresponds to the special case when $\mu = 0.$ $N_x$ and $N_\mu$ are increased until it is guaranteed that using Lagrange interpolation from the nested discretization the function $x^\mu$ can be interpolated to within an $L^2$ error less than $\epsilon$ on the interval $[0,1]$ for any $\mu$ in the specified range.
+A singular value decomposition is then performed on the $N_x \times (N_\mu+1)$ matrix.
+Let $K$ denote the number of singular values greater than $\epsilon.$ The left singular vectors correspond to discretizations of an orthonormal set of functions $\phi_1,\dots,\phi_K$ such that $x^\mu$ is in the span of $\phi_1,\dots,\phi_K$ to within an accuracy of $\epsilon.$
 
@@
 In practice suitable interpolation points can be obtained by using the roots of $\phi_{K+1}$ and calculating the corresponding weights by solving a linear system.
-The corresponding discretization nodes and weights for the corner-containing intervals of $\Gamma$ are obtained by suitable translations and scalings of $\{x_j\}$ and $\{w_j\}.$
+The corresponding discretization nodes and weights for the corner-containing intervals of $\Gamma$ are obtained by suitable translations and scalings of $\{x_j\}$ and $\{w_j\}.$ {\color{olive}We note that in practice, to achieve an accuracy of $10^{-15}$ for all powers $\mu \in \{0\} \cup [1/2,50],$ $x \in [0,1],$ only about $35$ nodes are required (i.e.
+$K = 35$).}
 
@@
 \begin{align}
-\int_{0}^\delta k(t,\upd{x_j}) \tilde{\phi}_j(t)\,{\rm d}t
+\int_{0}^\delta k(t,\upd{x_i}) \tilde{\phi}_j(t)\,{\rm d}t
 \end{align} 
@@
 \begin{align}
-\int_{0}^1 k(t,-x_j) {\phi}_j(t)\,{\rm d}t,
+\int_{0}^1 k(t,-x_i) {\phi}_j(t)\,{\rm d}t,
 \end{align} 
-where $x_j$ was one of the original discretization nodes generated on the interval $[0,1].$
+where $x_i$ was one of the original discretization nodes generated on the interval $[0,1].$
 \end{remark1}
@@
 
-After all the quadratures have been constructed the result is an $N \times N$ linear system the solution of which gives an approximation to $\sigma$ sampled at the discretization nodes.
+After all the quadratures have been constructed the result is an $N \times N$ linear system the {\color{olive}scaled} solution of which gives an approximation to $\sigma$ sampled at the discretization nodes.
 
@@
 
-The results of this algorithm are summarized in the following theorem (see \cite{}).
+The results of this algorithm are summarized in the following theorem (see \cite{hoskins2019numerical}).
 \upd{
@@
 \end{equation}
-then
+then, {\color{olive}after a suitable rescaling,}
 \begin{align}
@@
 In such cases it is convenient to reuse the Dirichlet discretization for the Neumann problem.
+
+{\color{olive}For ease of exposition, here we describe the exterior Neumann problem though an identical procedure can be used for the interior Neumann problem.
+In the latter case it is well-known that the naive boundary integral equation formulation has a one-dimensional nullspace (corresponding to the fact that solutions to the corresponding PDE are unique only up to a constant).
+Using standard techniques (see \cite{} for example) this issue can be corrected and the method of this paper can be applied in a straightforward manner.}

### 2020-06-10 paper_lap/JCP_response2/05apparatus.tex
update

--- 2020-05-14 paper_lap/JCP_response1/05apparatus.tex
@@
 \subsection{Adjoint discretization}
-\upd{Let $X = \mathbb{L}^2([0,L])$ and $\underline{X} = \mathbb{R}^{N}$.  Let $\left< \cdot, \cdot \right>_{Y}$
-denote the standard inner products on the Hilbert spaces $Y=X,\underline{X}$.}
+{\color{olive}Let $X = \mathbb{L}^2([0,L])$ and $\underline{X} = \mathbb{R}^{N}$.  Let $\left< \cdot, \cdot \right>_{X},\left< \cdot, \cdot \right>_{\underline{X}}$
+denote the standard inner products on the Hilbert spaces $X,$ and $\underline{X}$ respectively.
 The following lemma relates the discretization of the inverse of an operator to the adjoint of the discretization of its inverse.
 Its proof follows directly from the definition of the adjoint and is omitted.
-\upd{
+
 \begin{lemma}\label{lem_adjm}
@@
 \end{align}
-for all $f$ and $g$ in some subspace $S_{\epsilon} \subset L^2([0,L]).$  Then, for all functions $f$ and $g$ in $S_{\epsilon}$
+for all $f$ and $g$ in some subspace $Y \subset L^2([0,L]).$  Then, for all functions $f$ and $g$ in $Y$
 \begin{align}
-\left| \langle f,(A^{-1})^* g \rangle_{X} - \langle S[f],\left(A^{-1}_\epsilon\right)^* S[g] \rangle_{\uX} \right| \le \epsilon \|f\|_{X} \|g\|_{X}
+\left| \langle f,(A^{-1})^* g \rangle_{X} - \langle S[f],\left(A^{-1}_\epsilon\right)^T S[g] \rangle_{\uX} \right| \le \epsilon \|f\|_{X} \|g\|_{X}
 \end{align}
@@
 Hence a discretization of the Neumann problem can be obtained simply by taking the adjoint of the Dirichlet problem.
-The resulting density $\sigma$ obtained is accurate in a weak sense, ie.
+The resulting density $\sigma$ obtained is accurate in a weak sense, i.e.
 its inner products against functions in $S_\epsilon$ are accurate to within an error of $\epsilon.$
@@
 \label{rem:far-field-accuracy}
-We observe that if the solution to the boundary value problem is being calculated at a point $\by \in \mathbb{R}^2\setminus \Omega$ more than one panel length away from the boundary curve $\Gamma$ then the Neumann density $\sigma$ obtained using the above result will give an accuracy of $\epsilon,$ ie.
+We observe that if the solution to the boundary value problem is being calculated at a point $\by \in \mathbb{R}^2\setminus \Omega$ more than one panel length away from the boundary curve $\Gamma$ then the Neumann density $\sigma$ obtained using the above result will give an accuracy of $\epsilon,$ i.e.
 the function $K(\by,\gamma(t)) \in S_\epsilon.$ Thus accurate values of the solution in the far-field can be obtained almost immediately.
@@
 
-Additionally, we denote the discretization of the interior Dirichlet operator (using the custom quadratures described in Section \ref{sec:disc_dir}) by $\upd{\uA}.$ As before, let $\underline{f} = (f_1,\dots,f_N)^T$ where $f_i = f(x_i) \sqrt{w_i}$ and $f: \partial \Omega \to \mathbb{R}$ is the right-hand side of the exterior Neumann problem.
+Additionally, we denote the discretization of the interior Dirichlet operator (using the custom quadratures described in Section \ref{sec:disc_dir}) by $\upd{\uA}.$ As before, let $\underline{f} = (f_1,\dots,f_N)^T$ where $f_i = f(x_i) \sqrt{w_i}$ and $f: \Gamma \to \mathbb{R}$ is the right-hand side of the exterior Neumann problem.
 Finally, let $\underline{\sigma}$ be the approximation to the density (scaled by the square roots of the weights) obtained by solving the linear system
@@
 \end{align}
-For notational convenience we let $\gamma:[-\delta,L-\delta] \to \partial \Omega$ be a counterclockwise arclength parametrization of $\partial \Omega$ such that  $\gamma(0)$ corresponds to a vertex and $\gamma[-\delta,\delta]$ corresponds to a corner panel.
+For notational convenience we let $\gamma:[-2\delta,L-2\delta] \to \Gamma$ be a counterclockwise arclength parametrization of $\Gamma$ such that  $\gamma(0)$ corresponds to a vertex and $\gamma([-\delta,\delta])$ corresponds to a corner panel.
 
 For a panel $\gamma([s_1,s_2])$ with discretization nodes {\color{blue}$x_i,\dots,x_{i+M-1}$} corresponding to a Gauss-Legendre panel the density is smooth and thus it is expected to be well-represented in the basis of Legendre polynomials (shifted and scaled to the interval $[s_1,s_2]$).
-Hence standard interpolation techniques can be used to obtain an accurate approximation to the density $\sigma$ on the interval $s_1 \le s\le s_2$ .
-Typically we use 16th order Gauss-Legendre panels and choose their sizes so that their length is no more than their distance to the nearest corner.
-This latter choice guarantees that for any $\epsilon>0$ there exists an $M$ such that if the Gauss-Legendre panels are discretized using an $M$-point Gauss-Legendre rule then the density on that panel can be interpolated to relative precision $\epsilon$ in an $L^2$-sense.
-(We discuss a sketch of a proof in~\cref{sec:appb})
+Hence standard interpolation techniques can be used to obtain an accurate approximation to the density $\sigma$ on the interval $s_1 \le s\le s_2.$ Typically we use 16th order Gauss-Legendre panels and choose their sizes so that their length is no more than their distance to the nearest corner.
+This latter choice guarantees that for any $\epsilon>0$ there exists an $M$ such that if the Gauss-Legendre panels are discretized using an $M$-point Gauss-Legendre rule then the density on that panel can be interpolated to relative precision $\epsilon$ in an $L^2$-sense
+(we discuss a sketch of a proof in~\cref{sec:appb}).
 
-For corner panels the nodes were constructed to enable stable interpolation of densities $s^\mu,$ $\mu \in 0 \cup [1/2,50],$ on the interval $s \in (-\delta,\delta)$ - assuming for simplicity that the corner is at $0$ and the panel is of length $2 \delta.$ As mentioned above, the density is expected to contain terms of the form $s^\mu$ for some finite collection of $\mu$ in the interval $(-1/2,1/2),$ and hence will not in general be stably interpolable on the interval $(-\delta,\delta).$ However, it is possible to use the density obtained using (\ref{eqn:adj_linalg}) to construct a sequence of nested problems in the neighborhood of the corner, the solutions of which enable accurate interpolation of the density arbitrarily close to the vertex.
+For corner panels the nodes were constructed to enable stable interpolation of densities $s^\mu,$ $\mu \in \{0\} \cup [1/2,50],$ on the interval $s \in (-\delta,\delta)$ - assuming for simplicity that the corner is at $0$ and the panel is of length $2 \delta.$ As mentioned above, the density is expected to contain terms of the form $s^\mu$ for some finite collection of $\mu$ in the interval $(-1/2,1/2),$ and hence will not in general be stably interpolable on the interval $(-\delta,\delta).$ However, it is possible to use the density obtained using (\ref{eqn:adj_linalg}) to construct a sequence of nested problems in the neighborhood of the corner, the solutions of which enable accurate interpolation of the density arbitrarily close to the vertex.
 The number of these problems depends only on the distance of the closest evaluation point to the corner.
@@
 We begin with the following proposition, the proof of which follows immediately from the definition of the kernel $k$ and is omitted.
-\begin{proposition}
-Suppose that $f$ be a piecewise-analytic function in $S_\epsilon$ and  $\underline{\sigma} = (\upd{\uA}^T)^{-1} \upd{\uf}$ is the approximation to the Neumann density obtained using the adjoint of the discretization for the interior Dirichlet boundary integral equation.
+\begin{proposition}\label{prop_hanalytic}
+Suppose that $f$ is a piecewise-analytic function in $S_\epsilon$ and  $\underline{\sigma} = (\upd{\uA}^T)^{-1} \upd{\uf}$ is the approximation to the Neumann density obtained using the adjoint of the discretization for the interior Dirichlet boundary integral equation.
 Further suppose that the discretization nodes are ordered so that $s_1,\dots,s_P$ correspond to the corner panel associated with the interval $(-\delta,\delta),$ $s_{P+1},\dots,s_{P+M}$ correspond to the Gauss-Legendre panel immediately to the left associated with the interval $(-2\delta,-\delta),$ and $s_{P+M+1},\dots,s_{P+2M}$ to the Gauss-Legendre panel immediately to the right associated with the interval $(\delta,2\delta).$
 Then
-\begin{align}
+\begin{align}\label{eqn:def_hfun}
 h(t) = \sum_{i=P+2M+1}^N k(s_i,t) \sqrt{w_i} \,\underline{\sigma}_i
@@
 In light of this we consider the following integral equation
+{\color{olive}
 \begin{align}\label{eqn:resolve_neum0}
--\sigma(s) + \int_{-2\delta}^{2\delta} k(s,t) \sigma(t)\,{\rm d}t = f(s)-h(s), \quad -2\delta \le s \le 2\delta.
+-\frac{\sigma(s)}{2} + \int_{-2\delta}^{2\delta} k(s,t) \sigma(t)\,{\rm d}t = f(s)-h(s), \quad -2\delta \le s \le 2\delta.
 \end{align}
+}
 We note that the solution to (\ref{eqn:resolve_neum0}) is equal to the solution of the original boundary integral equation (\ref{bie_extn}) restricted to the interval $[-2\delta,2\delta].$ Taking the adjoint of (\ref{eqn:resolve_neum0}) we obtain
+{\color{olive}
 \begin{align}\label{eqn:resolve_diri0}
--\sigma(s) + \int_{-2\delta}^{2\delta} k(t,s) \sigma(t)\,{\rm d}t = f(s)-h(s), \quad -2\delta \le s \le 2\delta.
-\end{align}
+-\frac{\sigma(s)}{2} + \int_{-2\delta}^{2\delta} k(t,s) \sigma(t)\,{\rm d}t = f(s)-h(s), \quad -2\delta \le s \le 2\delta,
+\end{align}}
 which is a Dirichlet boundary integral equation for a wedge with a piecewise analytic right-hand side.
 In particular, we can discretize the operator using the method summarized in the previous section.
-Specifically, we subdivide the interval $[-\delta,\delta]$ into three subintervals $I_0 = [-\delta,\delta/2],$ $L_0 = [-\delta/2,\delta/2],$ and $J_0 = [\delta/2,\delta].$ On $I_0$ and $J_0$ we place standard Gauss-Legendre discretization nodes, while on $L_0$ we use the custom discretization scheme for corners, outlined in Section \ref{sec:disc_dir} (see \cite{} for a detailed description of the method).
-On the intervals $[-2\delta,-\delta]$ and $[\delta,2\delta]$ we use the same discretization nodes and weights as in the original system for those intervals (we call these panels $K_0$ and $Q_0$ respectively).
-Let $\underline{f}_0$ denote the right-hand side of (\ref{eqn:resolve_neum0}) evaluated at these discretization nodes and scaled by the square roots of the corresponding weights.
-Let $\upd{\uA_0}$ be the discretization of the interior Dirichlet problem operator (ie.
+Specifically, we subdivide the interval $[-\delta,\delta]$ into three subintervals $I_0 = [-\delta,\delta/2],$ $L_0 = [-\delta/2,\delta/2],$ and $J_0 = [\delta/2,\delta].$ On $I_0$ and $J_0$ we place standard Gauss-Legendre discretization nodes, while on $L_0$ we use the custom discretization scheme for corners, outlined in Section \ref{sec:disc_dir} (see \cite{hoskins2019numerical} for a detailed description of the method).
+On the intervals $[-2\delta,-\delta]$ and $[\delta,2\delta]$ we use the same discretization nodes and weights as in the original system for those intervals.{\color{red} (we call these panels $K_0$ and $Q_0$ respectively).} Let $\underline{f}_0$ denote the right-hand side of (\ref{eqn:resolve_neum0}) evaluated at these discretization nodes and scaled by the square roots of the corresponding weights.
+Let $\upd{\uA_0}$ be the discretization of the interior Dirichlet problem operator (i.e.
 the operator acting on $\sigma$ on the left-hand side of (\ref{eqn:resolve_diri0})).
@@
 The analysis of the previous section then shows that if $\underline{\sigma}_0$ is the solution of the equation
-\begin{align}
+\begin{align}\label{eqn_reduced}
 \upd{\uA_0^T} \underline{\sigma}_0 = \underline{f}_0
@@
 
+{\color{olive}
 \begin{remark}
-Though the above method produces a viable method for reducing the problem, as written the reduction is non-local --- in order to compute the right-hand side for the sub-problem one must evaluate contributions from the rest of the domain.
-\end{remark}
+Though the above method produces a viable method for reducing the problem, as written the reduction appears to be non-local --- in order to compute the right-hand side of the subproblem one must evaluate contributions from the rest of the domain.
+In fact, the values of $\underline{f}_0$ can be obtained using only local information.
+Specifically, we observe that
+\begin{align}
+\left(h(s_i) \sqrt{w_1}, \dots, h(s_{P+2M}) \sqrt{w_{P+2M}}\right)^T =& \left(f(s_i) \sqrt{w_1}, \dots, f(s_{P+2M}) \sqrt{w_{P+2M}}\right)^T-\\
+& \underline{A}_{\rm red}^T \left(\sigma_1 \sqrt{w}_1,\dots, \sigma_{P+2M} \sqrt{w_{P+2M}}\right)^T,
+\end{align}
+where $\underline{A}_{\rm red}$ is the submatrix of $\underline{A}$ corresponding to the first $P+2M$ rows and columns.
+Since $h$ is analytic on $(-2\delta,2 \delta),$ $h(t)$ can be accurately approximated for any $-2\delta<t<2\delta$ by interpolation from its values at the nodes $s_1,\dots,s_{P+2M}.$
+\end{remark}}
 
-The following theorem shows that the right-hand side $\underline{f}_0$ can be computed only using local data (i.e. values of the weak solution in the vicinity of the corner).\\
-\begin{theorem}
-Suppose that $\underline{f}_0$ is the discretization of the right-hand side of (\ref{eqn:resolve_diri0}) corresponding to nodes $s^0_1,\dots,s^0_{N_0}.$ Further suppose that $U$ is the $P\times P$ matrix with entries $U_{ij} = \phi_i(s_j) \sqrt{w_j},$ where $\phi_1,\dots,\phi_P$ are the orthonormal functions on $(-\delta,\delta)$ spanning $,{\rm sgn}(s)|s|^\mu, |s|^\mu,$ $\mu=0,1/2-40$ on that interval.
-Let $w:(-\delta,\delta) \to \mathbb{R}^P$ be the vector-valued function defined by
-\begin{align}
-w(t) = (\phi_1(t),\phi_2(t),\dots,\phi_P(t)),
-\end{align}
-and $\tilde{\sigma} = (\sigma_1,\dots,\sigma_P)^T$ be the approximation to the solution in the vicinity of the corner obtained by solving the original system (\ref{eqn:adj_linalg}).
-Then $|(f(t)-h(t)) - w(t) U^{-1} \upd{\uA_0^T} \tilde{\sigma}| = O(\epsilon)$ for all $t \in(-\delta,\delta).$ In particular, if $\tilde{f}_0$ is the vector of length $N_0$ with entries defined by
-\begin{align}
-(\tilde{f}_0)_i = w(s^0_i) U^{-1} \upd{\uA_0^T} \tilde{\sigma}, \quad i=1,\dots,N_0,
-\end{align}
-then $\| \underline{f}_0 - \tilde{f}_0\| = O(\epsilon).$
-\end{theorem}
-\begin{proof}
-We begin by observing that both $f$ and $h$ are analytic on the interval $(-\delta,\delta).$ In particular, they can be accurately interpolated using $\phi_1,\dots,\phi_P$ on the interval $(-\delta,\delta).$ Hence,
-\begin{align}\label{eqn:approx_thm}
-f(t)-h(t) \approx w(t) U^{-1} (f(s_1)-h(s_1),\dots,f(s_P)-h(s_P))^T.
-\end{align}
-A similar argument shows that $f(t)-h(t)$ is interpolable on $[-2\delta,-\delta]$ and $[\delta,2\delta].$
-On the other hand, by construction,
-\begin{align}\label{eqn:linalg_thm}
-\underline{f} = \upd{\uA^T} \begin{pmatrix}\tilde{\sigma}\\ \sigma_{P+{2M+1}}\\ \vdots\\ \sigma_N\end{pmatrix}.
-\end{align}
-Let $\upd{\uA}_0$ be the $(P+2M)\times (P+2M)$ submatrix of $\upd{\uA}$ corresponding to the first $P+2M$ rows and columns of $\upd{\uA},$ and $\upd{\uA}_{\rm red}$ be the $P+2M \times (N-P-2M)$  submatrix of $\upd{\uA}$ corresponding to selecting the first $P+2M$ rows of $\upd{\uA}$ and all but the first $P+2M$ columns of $\upd{\uA}.$ Using this notation, the first $P+2M$ rows of (\ref{eqn:linalg_thm}) can be re-written as
-\begin{align}
-\begin{pmatrix}f_1\\\vdots \\ f_{P+2M}\end{pmatrix}  = \upd{\uA}_{\rm red}^T \begin{pmatrix} \sigma_{P+2M+1}\\ \vdots\\ \sigma_N\end{pmatrix} + \upd{\uA}_0^T \tilde{\sigma}.
-\end{align}
-The first term on the right-hand side is $(h(s_1),\dots,h(s_{P+2M}))^T.$ Substituting this into the previous equation, we obtain
-\begin{align}
-(f(s_1)-h(s_1),\dots,f(s_{P+2M})-h(s_{P+2M}))^T = \upd{\uA}_0^T \tilde{\sigma}.
-\end{align}
-The result follows by substituting the above equality into (\ref{eqn:approx_thm}).
-\end{proof}
-
-This can be iterated to obtain an interpolable approximation to the density on $L_0 = [-\delta,\delta].$ In particular, we consider the restriction of the exterior Neumann integral equation, as well as its, adjoint to the interval $I_0$ and $J_0.$ For the right-hand side we use the original right-hand side $f$ minus the contribution from the remainder of the domain.
+This can be iterated to obtain an interpolable approximation to the density on $L_0 = [-\delta,\delta].$ In particular, we consider the restriction of the exterior Neumann integral equation, as well as its adjoint, to the interval $I_0$ and $J_0.$ For the right-hand side we use the original right-hand side $f$ minus the contribution from the remainder of the domain.
 In particular, if we define
@@
 then $\sigma$ restricted to the interval $I_0\cup L_0 \cup J_0$ satisfies
+{\color{olive}
 \begin{align}\label{eqn:resolve_neum1}
--\sigma(s) + \int_{-\delta}^{\delta} k(s,t) \sigma(t)\,{\rm d} t = f(s)-h(s)-h_1(s), \quad -\delta \le s \le \delta.
+-\frac{\sigma(s)}{2} + \int_{-\delta}^{\delta} k(s,t) \sigma(t)\,{\rm d} t = f(s)-h(s)-h_1(s), \quad -\delta \le s \le \delta.
 \end{align}
+}
 The corresponding adjoint equation is given by 
+{\color{olive}
 \begin{align}\label{eqn:resolve_diri1}
--\sigma(s) + \int_{-\delta}^{\delta} k(t,s) \sigma(t)\,{\rm d} t = f(s)-h(s)-h_1(s), \quad -\delta \le s \le \delta.
+-\frac{\sigma(s)}{2} + \int_{-\delta}^{\delta} k(t,s) \sigma(t)\,{\rm d} t = f(s)-h(s)-h_1(s), \quad -\delta \le s \le \delta.
 \end{align}
-
+}
 Once again, we divide $L_0$ into three intervals $I_1,$ $L_1,$ and $J_1$ and discretize each interval as before.
@@
 
-This process can be repeated an arbitrary number of times to yield a sequence of solutions $\underline{\sigma}_j,$ $j=0,1,2,\dots$ together with corresponding intervals $I_0,I_1,\dots$ and $J_0,J_1,\dots$ on which it can be interpolated.
+This process can be repeated an arbitrary number of times to yield a sequence of solutions $\underline{\sigma}_j,$ $j=0,1,2,\dots$ together with corresponding intervals $I_0,I_1,\dots$ and $J_0,J_1,\dots$ on which each can be interpolated.
 

### 2020-06-10 paper_lap/JCP_response2/06num.tex
update

--- 2020-01-21 paper_lap/JCP_submission/06num.tex
@@
 
-\begin{rem}
+\begin{remark1}
 Though $2^{-200}$ is significantly smaller than machine precision, the matrix entries corresponding to the
@@
 computing interactions of nearby points.
-\end{rem} 
-\begin{rem}
+\end{remark1} 
+\begin{remark1}
 Simple arguments from complex analysis show that when using graded meshes, in order to obtain full 
@@
 panel size of $2^{-200}$. 
-\end{rem}
+\end{remark1}
 
@@
 \label{eq:farfieldpot}
-u(\by) = \int_{\Gamma} G(\bx,\by) \sigma(\bx) dS_{\bx} \approx \sum_{i=1}^{N}  G(\gamma(s_{i}),\by) \sigma_{i} \sqrt{w_{i}}
+u(\by) = \int_{\Gamma} G(\bx,\by) \sigma(\bx) dS_{\bx} \approx \sum_{i=1}^{N}  G(\gamma(s_{i}),\by) \sigma_{i} \sqrt{w_{i}}.
 \end{equation}
 In~\cref{fig:scatteringtest}, we compute the error in the solution at target
-locations for a scattering problem whose right hand side is given by a collection of three interior charges
+locations for a scattering problem whose {\color{olive}boundary condition} is given by a collection of three interior charges
 \begin{equation}
@@
 \includegraphics[width=\linewidth]{paper-figs/weaktest}
-\caption{Left panel: Solution to Neumann problem with data given by~\cref{eq:scatboundarydata}, center panel: error in computing the potential in the formula using the underlying smooth quadrature~\cref{eq:farfieldpot}, and on the right the density $\sigma$ as a function of arc-length}.
+\caption{Left panel: Solution to Neumann problem with data given by~\cref{eq:scatboundarydata}, center panel: error in computing the potential in the formula using the underlying smooth quadrature~\cref{eq:farfieldpot}, and on the right the density $\sigma$ as a function of arclength}.
 \label{fig:scatteringtest}
@@
 \int_{\Gamma} x_{1} \sigma_{2}(\bx) dS_{\bx} & \int_{\Gamma} x_{2} \sigma_{2}(\bx) dS_{\bx} 
-\end{bmatrix}
+\end{bmatrix}.
 \end{equation}
@@
 1.3 \times. 10^{-14} & 2.7 \times 10^{-15}
-\end{bmatrix}
+\end{bmatrix}.
 \end{equation}
@@
 The strengths $c_{j}$ are chosen such that they average to $0$.
-The domain contains $108$ corners, was discretized using $22240$ nodes and required $105$ iterations to converge to a residue of $10^{-15}$.
+The domain contains $108$ corners, was discretized using $22240$ nodes and required $105$ iterations {\color{olive}of GMRES} to converge to a residue of $10^{-15}$.
 The matrix at each iteration was applied using an FMM whose tolerance was also set to $10^{-15}$.

### 2020-06-10 paper_lap/JCP_response2/Significance.tex
update

--- 2020-01-21 paper_lap/JCP_submission/Significance.tex
@@
-\documentclass[10pt]{article}
+\documentclass[12pt,times]{elsarticle}
 \usepackage{amsmath,amsthm,amssymb,amscd,fancybox,epsfig,float,subfigure}
@@
  \maketitle
-The solution to boundary integral equations corresponding to Laplace's equations
+The solutions to boundary integral equations corresponding to Laplace's equations
 with polygonal domains
@@
 If the boundary data on each edge of the polygon is smooth, then the solution
-to the corresponding boundary equation has an expansion terms of certain analytically
+to the corresponding boundary integral equation has an expansion in terms of certain analytically
 available singular powers. 
-Using the known behavior of he solution to the integral equation, efficient
+Using the known behavior of the solution to the integral equation, efficient
 discretizations have been constructed for the Dirichlet problem.
@@
 inner-products of the solution with smooth functions can be computed accurately. 
-Further, we show that the solution is also accurate point wise away from the corners. 
+Further, we show that the solution is also accurate pointwise away from the corners. 
 We also present an algorithm to obtain accurate solutions in the vicinity of the corner
-by solving a series of local sub-problems in the vicinity of the corner. 
+by solving a series of local subproblems in the vicinity of the corner. 
 This enables accurate evaluation of the corresponding potential at target locations arbitrarily
-close to the corner. We present the effectiveness of our method, both in terms of accuracy
+close to a corner. We present the effectiveness of our method, both in terms of accuracy
 and speed through several numerical examples.

### 2020-06-10 paper_lap/JCP_response2/manuscript.tex
update

--- 2020-05-14 paper_lap/JCP_response1/manuscript.tex
@@
 Using the known behavior of the solution, universal discretizations have been constructed for the solution of the Dirichlet problem.
-However, the leading order behavior of solutions to the Neumann problem is $O(t^{\mu})$ for $\mu \in (-1/2,0)$ depending on the angle at the corner (compared to $O(C+t^{\mu})$ with $\mu>1/2$ for the Dirichlet problem); this presents a significant challenge in the design of universal discretizations.
+However, the leading order behavior of solutions to the Neumann problem is $O(t^{\mu})$ for {\color{olive}$\mu \in (-1/2,1/2)$} depending on the angle at the corner (compared to $O(C+t^{\mu})$ with $\mu>1/2$ for the Dirichlet problem); this presents a significant challenge in the design of universal discretizations.
 Our approach is based on using the discretization for the Dirichlet problem in order to compute a solution in the ``weak sense'' by solving an adjoint linear system; namely, it can be used to compute inner products with smooth functions accurately, but it cannot be interpolated.
@@
 \begin{highlights}
-\item Efficient discretization to boundary integral equations corresponding to Laplace's equation with Neumann boundary conditions on polygonal domains based on an adjoint Dirichlet discretization resulting
+{\color{olive}
+\item Efficient discretization of boundary integral equations corresponding to Laplace's equation with Neumann boundary conditions on polygonal domains based on an adjoint Dirichlet discretization resulting
 in weak solutions to the integral equation. 
-\item A local re-solve algorithm for obtaining pointwise accurate solutions of the integral equation arbitrarily close to the corner.
-\item Rapid evaluation of solution at target locations in the volume arbitrarily close to the corner.
+\item A local re-solve algorithm for obtaining pointwise accurate solutions of the integral equation arbitrarily close to the corner, and rapid evaluation of solution at target locations in the volume arbitrarily close to the corner.
+\item Accurate solution of Laplace's equation arbitrarily close to corners at which solutions may have singularities.}
 \end{highlights}
@@
 \section{Approximation of data on corner panels for re-solve}
-Here we give explicit bounds for the rate of convergence of the contribution of the rest of the boundary to a corner panel.
-In particular, given a polygonal domain with boundary $\Gamma,$ let $\bx$ denote a vertex of $\Gamma$ and $C = \Gamma \cap B_r(\bx),$ where $B_r(\bx)$ is the ball of radius of $r$ centered at $\bx.$ We choose $r$ so that $\Gamma \cap B_{2r}(\bx)$ corresponds to a wedge with internal angle $\pi \alpha$ and side lengths $2r.$
-
-%Let $\Gamma_*$ be any other straight line segment contained entirely within $\Gamma \setminus B_{2r}(\bx).$ Then
+Here we give explicit bounds for the rate of convergence of the contribution of the rest of the boundary to a corner panel.{\color{red} In particular, given a polygonal domain with boundary $\Gamma,$ let $\bx$ denote a vertex of $\Gamma$ and $C = \Gamma \cap B_r(\bx),$ where $B_r(\bx)$ is the ball of radius of $r$ centered at $\bx.$ We choose $r$ so that $\Gamma \cap B_{2r}(\bx)$ corresponds to a wedge with internal angle $\pi \alpha$ and side lengths $2r.$ }
 
@@
 Let $\Gamma$ be the boundary of a polygon and $\bx$ be a vertex.
-Let $r>0$ be a real number such that $\Gamma \cap B_{2r}(\bx)$ corresponds to a wedge with internal angle $\pi \alpha$ and side lengths $2r,$ where $B_R(\bx)$ denotes a ball of radius $R$ centered at $\bx.$ Let $L$ denote the length of $\Gamma$ and $\gamma: [-L/2,L/2]\to \Gamma$ be an arclength counterclockwise parameterization of $\Gamma$ such that $\gamma(0) = \bx.$ Finally, for any $f \in L^2(\Gamma),$ let $H:[0,r] \to \mathbb{R}$ be the function defined by
+Let $r>0$ be a real number such that $\Gamma \cap B_{2r}(\bx)$ corresponds to a wedge with internal angle $\pi \alpha$ and side lengths $2r,$ where $B_R(\bx)$ denotes a ball of radius $R$ centered at $\bx.$ Let $L$ denote the length of\, $\Gamma$ and $\gamma: [-L/2,L/2]\to \Gamma$ be an arclength counterclockwise parameterization of\, $\Gamma$ such that $\gamma(0) = \bx.$ Finally, for any $f \in L^2(\Gamma),$ let $H:[0,r] \to \mathbb{R}$ be the function defined by
 \begin{align}
-H(t) = \int_{\Gamma\backslash B_{2r}(\bx)} K(\gamma(t),\gamma(s)) f(s)\,{\rm d}s.
+H(t) = \int_{\Gamma\backslash B_{2r}(\bx)} K(\gamma(t),\gamma(s)) f(\gamma(s))\,{\rm d}s.
 \end{align}
@@
 \begin{equation}
-S[f] = (f(x_{1})\sqrt{w_{1}},f(x_{2})\sqrt{w_{2}},\ldots f(x_{N}) \sqrt{w_N} )^{T} = \underline{f} \, .
+S[f] = (f(x_{1})\sqrt{w_{1}},f(x_{2})\sqrt{w_{2}},\ldots, f(x_{N}) \sqrt{w_N} )^{T} = \underline{f} \, .
 \end{equation}
@@
 Let $g$ denote the
-right hand side for the Neumann problem, let $\sigma$ denote the corresponding solution.
+right-hand side for the Neumann problem, and let $\sigma$ denote the corresponding solution.
 Let $\underline{\sigma}$ denote the solution of the linear system $\uA^{T} \usigma = S[g]$.
@@
 \begin{equation}
-e = \max_{i=1,2\ldots M} |\left< \sigma, h_{i} \right>_{X} -  \left< \usigma, S[h_{i}] \right>_{\uX}| < \varepsilon  
+e = \max_{i=1,2\ldots, M} |\left< \sigma, h_{i} \right>_{X} -  \left< \usigma, S[h_{i}] \right>_{\uX}| < \varepsilon  
 \end{equation}
@@
 The Dirichlet boundary data $f_{i}$ (\cref{eq:deff}) corresponding to the density $\sigma_{D,i}$ is an analytic function on each of the edges of the polygon. 
-The discretization of $A$ of~\cite{hoskins2019numerical} is precisely designed to compute $\sigma_{D,i}$ accurately to any desired tolerance, under sufficient refinement of the discretization.
+The discretization of $A$ in~\cite{hoskins2019numerical} is precisely designed to compute $\sigma_{D,i}$ accurately to any desired tolerance, under sufficient refinement of the discretization.
 Since $g$ is also a smooth function, given a tolerance $\varepsilon$, there exists a sufficiently fine discretization of the boundary such that

### 2020-06-16 paper_lap/JCP_response1/01intro.tex
updating paper

@@
 Moreover, the corner refinement and compression can be done in tandem resulting in fast and accurate solvers for elliptic PDEs (see \cite{helsing}, \cite{helsing2},  \cite{ojala}, \cite{helsjcp} and \cite{helsinv}  for  one approach called recursive compressed preconditioning, and  \cite{gillman}, \cite{bremer},\cite{bremer2}, and \cite{bremer3}  for other compression-based methods for solving Laplace's equation).
-Unfortunately, this approach becomes considerably more expensive in three dimensions limiting its application in that context.
+Unfortunately, this approach becomes considerably more expensive in three dimensions.
 
@@
 We then show how this solution can be used to obtain accurate solutions to the Neumann problem arbitrarily close to a corner by solving a set of local subproblems in the vicinity of that corner.
+\upd{This approach generalizes naturally to three-dimensional problems, though efficient discretization of the corresponding Dirichlet problems is the subject of ongoing research.
+A similar analysis as in \cite{} can be used to characterize the singularities along edges and near vertices, though there are a few challenges which prevent the immediate application of this analysis to the design of suitable discretizations.}
 

### 2020-06-16 paper_lap/JCP_response1/03bvp.tex
updating paper

--- 2020-06-10 paper_lap/JCP_response2/03bvp.tex
@@
 \end{align}
-{\color{olive}By a standard abuse of notation we use $\cS$ and $\cD$ to denote both the operators acting on $L^2(\Gamma)$ as well as the corresponding operators acting on $L^2([0,L]),$ the latter being obtained from the former by composition with the parameterization.}
+\upd{By a standard abuse of notation we use $\cS$ and $\cD$ to denote both the operators acting on $L^2(\Gamma)$ as well as the corresponding operators acting on $L^2([0,L]),$ the latter being obtained from the former by composition with the parameterization.}
 \end{definition}
@@
 for some $\alpha >0.$ Then for any continuous function $\sigma:\Gamma \to \mathbb{R},$
-{\color{olive}
+\upd{
 \begin{align}
@@
 where $\bnu$ is the inward-pointing normal.} Similarly, if $\bx$ approaches a point $\bx_0 = \gamma(t_0)$ from the outside then for any continuous function $\sigma:\Gamma \to \mathbb{R},$
-{\color{olive}
+\upd{
 \begin{align}
@@
 \end{align}
-{\color{red}where $\gamma(t_0) = \bx_0.$}
 \end{definition}
@@
 
-\begin{remark1}
+\begin{remark}
 A similar result holds for the case where the identity term in (\ref{eqn_grho}) is replaced by its negative; the change in sign corresponds to replacing the boundary integral equation for the interior Dirichlet problem with the boundary integral equation corresponding to exterior Dirichlet problem.
 Similar expansions also hold for both the exterior and interior Neumann problems, in which case the singular powers are obtained by subtracting one from the singular powers arising in the Dirichlet problem.
-\end{remark1}
+\end{remark}
 
-{\color{olive}
-\begin{remark1}
+\upd{
+\begin{remark}
 We note that the smoothness of the kernel $k$ for well-separated portions of the domain guarantees that the problem of determining the singularities arising in the vicinity of a corner for a polygonal domain can be reduced to the analysis of the wedge case, see the discussion in \cite{} for example.
-\end{remark1}
+\end{remark}
 }

### 2020-06-16 paper_lap/JCP_response1/04nprelim.tex
updating paper

@@
 The Nystr\"{o}m method proceeds as follows.
-We begin by constructing a discretization of the boundary $\Gamma$ with nodes {\color{blue}$x_1,\dots,x_N,$} and weights $w_1,\dots,w_N,$ which enable interpolation of the left- and right-hand sides of the boundary integral equation
+We begin by constructing a discretization of the boundary $\Gamma$ with nodes \upd{$x_1,\dots,x_N,$} and weights $w_1,\dots,w_N,$ which enable interpolation of the left- and right-hand sides of the boundary integral equation
 \begin{align}\label{eqn:numpreint}
@@
 \end{align}
-with precision $\epsilon.$ In other words, given {\color{blue}$f(x_i),-\sigma(x_i) + \int_0^L k(t,x_i) \,\sigma(t)\, {\rm d} t,$} for $i=1,\dots,N,$ the values $f(s)$ and $-\sigma(s)/2 + \int_0^L k(t,s) \,\sigma(t)\, {\rm d} t$ can be obtained for all $0 \le s \le L$ to within $\epsilon.$
+with precision $\epsilon.$ In other words, given \upd{$f(x_i),$ and $-\sigma(x_i)/2 + \int_0^L k(t,x_i) \,\sigma(t)\, {\rm d} t,$} for $i=1,\dots,N,$ the values $f(s)$ and $-\sigma(s)/2 + \int_0^L k(t,s) \,\sigma(t)\, {\rm d} t$ can be obtained for all $0 \le s \le L$ to within $\epsilon.$
 
 Once these nodes and weights have been generated we proceed by enforcing equality of (\ref{eqn:numpreint}) at the discretization nodes, which yields the system of equations
-{\color{blue}
+\upd{
 \begin{align}
@@
 We note that scaling by the square root of the weights in the above equation is equivalent to solving the problem in the $L^2$ sense, and results in discretized operators with condition numbers which are close to those of the original physical systems \cite{bremer3}.
-The new unknowns are $\sigma_i = \sigma({\color{blue}x_i}) \sqrt{w_i},$ $i=1,\dots,N.$ Next, for each interpolation node {\color{blue}$x_i$} we find a collection of weights $W_{ij}$ such that
+The new unknowns are $\sigma_i = \sigma(\upd{x_i}) \sqrt{w_i},$ $i=1,\dots,N.$ Next, for each interpolation node \upd{$x_i$} we find a collection of weights $W_{ij}$ such that
 \begin{align}
-\left|\int_0^L k(t,{\color{blue}x_i})\, \sigma(t)\,{\rm d}t- \sum_{j=1}^N W_{ij} \sigma_j\, \sqrt{w_j} \right| < \epsilon,
+\left|\int_0^L k(t,\upd{x_i})\, \sigma(t)\,{\rm d}t- \sum_{j=1}^N W_{ij} \sigma_j\, \sqrt{w_j} \right| < \epsilon,
 \end{align}
@@
 \begin{align}
-  -\frac{\sigma_i}{2} +  \sum_{j=1}^N W_{ij} \sigma_j \sqrt{w_i w_j}=f({\color{blue}x_i}) \sqrt{w_i},\quad i,j=1,\dots,N. 
+  -\frac{\sigma_i}{2} +  \sum_{j=1}^N W_{ij} \sigma_j \sqrt{w_i w_j}=f(\upd{x_i}) \sqrt{w_i},\quad i,j=1,\dots,N. 
 \end{align}
@@
 
-The boundary $\Gamma$ is separated into a collection of intervals which are at least a fixed distance $\delta$  (measured in terms of arclength) away from a corner and the collection of intervals of length $2 \delta$ centered about each corner.
-The former are discretized using a standard smooth quadrature rule such as nested Gauss-Legendre quadrature while the latter are discretized using a custom set of interpolation nodes constructed in the following way.
+The boundary \upd{$\Gamma$ is divided into a collection of disjoint pieces each of which are at least a fixed distance $\delta$  (measured in terms of arclength) away from a corner, and a collection of pieces of length $2 \delta$ centered about each corner.
+}The former are discretized using a standard smooth quadrature rule such as Gauss-Legendre quadrature while the latter are discretized using a custom set of interpolation nodes constructed in the following way.
 
-First, all functions of the form $x^\mu,$ $\mu \in \{0\} \cup [1/2,50],$ $x \in [0,1]$ are discretized using nested Gauss-Legendre panels in $x$ and a single Gauss-Legendre panel in $\mu$.
-This creates a $N \times M$ matrix where $N$ denotes the number of spatial discretization points $r_i$ and $M$ denotes the number of $\mu_j$ chosen.
-$M$ and $N$ are increased until it is guaranteed that using Lagrange interpolation from the nested discretization the function $x^\mu$ can be interpolated to within an $L^2$ error less than $\epsilon$ on the interval $[0,1]$ for any $\mu$ in the specified range.
-A singular value decomposition is then performed on the $N\times M$ matrix.
-Let $K$ denote the number of singular values greater than $\epsilon.$ The right singular vectors correspond to discretizations of an orthonormal set of functions $\phi_1,\dots,\phi_K$ such that $x^\mu$ is in the span of $\phi_1,\dots,\phi_K$ to within an accuracy of $\epsilon.$
+First, all functions of the form $x^\mu,$ $\mu \in \{0\} \cup [1/2,50],$ $x \in [0,1]$ are discretized \upd{ in $x$ using an adaptive interpolation scheme based on Gauss-Legendre panels}, and \upd{in $\mu$ using} a single Gauss-Legendre panel for the range $[1/2,50].$ This creates a $N_x \times (N_\mu+1)$ matrix where $N_x$ denotes the number of spatial discretization points $r_i$ and $N_\mu$ denotes the number of $\mu_j$ chosen.
+The extra row in the matrix corresponds to the special case when $\mu = 0.$ $N_x$ and $N_\mu$ are increased until it is guaranteed that using Lagrange interpolation from the nested discretization the function $x^\mu$ can be interpolated to within an $L^2$ error less than $\epsilon$ on the interval $[0,1]$ for any $\mu$ in the specified range.
+A singular value decomposition is then performed on the $N_x \times (N_\mu+1)$ matrix.
+Let $K$ denote the number of singular values greater than $\epsilon.$ The left singular vectors correspond to discretizations of an orthonormal set of functions $\phi_1,\dots,\phi_K$ such that $x^\mu$ is in the span of $\phi_1,\dots,\phi_K$ to within an accuracy of $\epsilon.$
 
@@
 In practice suitable interpolation points can be obtained by using the roots of $\phi_{K+1}$ and calculating the corresponding weights by solving a linear system.
-The corresponding discretization nodes and weights for the corner-containing intervals of $\Gamma$ are obtained by suitable translations and scalings of $\{x_j\}$ and $\{w_j\}.$
+The corresponding discretization nodes and weights for the corner-containing intervals of $\Gamma$ are obtained by suitable translations and scalings of $\{x_j\}$ and $\{w_j\}.$ \upd{We note that in practice, to achieve an accuracy of $10^{-15}$ for all powers $\mu \in \{0\} \cup [1/2,50],$ $x \in [0,1],$ only about $36$ nodes are required (i.e.
+$K = 36$).}
 
@@
 Moreover, in light of symmetry between the two legs of the wedge it suffices to design quadratures assuming  \upd{$x_j$} lies in the half of a corner panel parametrized by $(-\delta,0).$
-\begin{remark1}
+\begin{remark}
 Due to scale invariance, it suffices to compute quadratures for 
 \begin{align}
-\int_{0}^1 k(t,-x_j) {\phi}_j(t)\,{\rm d}t,
+\int_{0}^1 k(t,-x_i) {\phi}_j(t)\,{\rm d}t,
 \end{align} 
-where $x_j$ was one of the original discretization nodes generated on the interval $[0,1].$
-\end{remark1}
-\begin{remark1}
+where $x_i$ was one of the original discretization nodes generated on the interval $[0,1].$
+\end{remark}
+\begin{remark}
 By interpolating from the discretization nodes to these quadrature nodes we obtain a set of weights $\tilde{W}_{i,j}$ such that if \upd{$x_1,\dots,x_{2K}$} correspond to the discretization of a corner parametrized by $(-\delta,\delta)$ with $0$ corresponding to the corner then
@@
 for all $i=1,\dots,2K$ and $m=1,\dots,K.$
-\end{remark1}
+\end{remark}
 
-After all the quadratures have been constructed the result is an $N \times N$ linear system the solution of which gives an approximation to $\sigma$ sampled at the discretization nodes.
+After all the quadratures have been constructed the result is an $N \times N$ linear system the \upd{scaled} solution of which gives an approximation to $\sigma$ sampled at the discretization nodes.
 
@@
 
-The results of this algorithm are summarized in the following theorem (see \cite{}).
+The results of this algorithm are summarized in the following theorem (see \cite{hoskins2019numerical}).
 \upd{
 \begin{theorem}
-Let $A$ the integral operator corresponding to the interior Dirichlet problem, i.e. 
+Let $A$ denote the integral operator corresponding to the interior Dirichlet problem, i.e. 
 \begin{equation}
@@
 \end{equation}
-then
+then, after a suitable rescaling,
 \begin{align}
@@
 In such cases it is convenient to reuse the Dirichlet discretization for the Neumann problem.
+
+\upd{For ease of exposition, here we describe the exterior Neumann problem though an identical procedure can be used for the interior Neumann problem.
+In the latter case it is well-known that the naive boundary integral equation formulation has a one-dimensional nullspace (corresponding to the fact that solutions to the corresponding PDE are unique only up to a constant).
+Using standard techniques (see \cite{} for example) this issue can be corrected and the method of this paper can be applied in a straightforward manner.}

### 2020-06-16 paper_lap/JCP_response1/05apparatus.tex
updating paper

@@
 \subsection{Adjoint discretization}
-\upd{Let $X = \mathbb{L}^2([0,L])$ and $\underline{X} = \mathbb{R}^{N}$.  Let $\left< \cdot, \cdot \right>_{Y}$
-denote the standard inner products on the Hilbert spaces $Y=X,\underline{X}$.}
+\upd{Let $X = \mathbb{L}^2([0,L])$ and $\underline{X} = \mathbb{R}^{N}$.  Let $\left< \cdot, \cdot \right>_{X},\left< \cdot, \cdot \right>_{\underline{X}}$
+denote the standard inner products on the Hilbert spaces $X,$ and $\underline{X}$ respectively.
 The following lemma relates the discretization of the inverse of an operator to the adjoint of the discretization of its inverse.
 Its proof follows directly from the definition of the adjoint and is omitted.
-\upd{
+
 \begin{lemma}\label{lem_adjm}
@@
 Those panels which contain a vertex are discretized using a custom discretization scheme (see Section \ref{sec:disc_dir}) while the remaining panels are discretized using a standard smooth quadrature rule (such as Gauss-Legendre or Chebyshev nodes).
-In the following we assume that an $M$-point Gauss-Legendre quadrature rule is used and the corner panels are discretized using $P$ nodes (together with a collection of orthonormal functions on that interval $\phi_1,\dots,\phi_P$).
+In the following we assume that an $M$-point Gauss-Legendre quadrature rule is used and the corner panels are discretized using \upd{$K$} nodes (together with a collection of orthonormal functions on that interval $\phi_1,\dots,\upd{\phi_K}$).
 
-Additionally, we denote the discretization of the interior Dirichlet operator (using the custom quadratures described in Section \ref{sec:disc_dir}) by $\upd{\uA}.$ As before, let $\underline{f} = (f_1,\dots,f_N)^T$ where $f_i = f(x_i) \sqrt{w_i}$ and $f: \partial \Omega \to \mathbb{R}$ is the right-hand side of the exterior Neumann problem.
+Additionally, we denote the discretization of the interior Dirichlet operator (using the custom quadratures described in Section \ref{sec:disc_dir}) by $\upd{\uA}.$ As before, let $\underline{f} = (f_1,\dots,f_N)^T$ where $f_i = f(x_i) \sqrt{w_i}$ and $f: \Gamma \to \mathbb{R}$ is the right-hand side of the exterior Neumann problem.
 Finally, let $\underline{\sigma}$ be the approximation to the density (scaled by the square roots of the weights) obtained by solving the linear system
@@
 \end{align}
-For notational convenience we let $\gamma:[-\delta,L-\delta] \to \partial \Omega$ be a counterclockwise arclength parametrization of $\partial \Omega$ such that  $\gamma(0)$ corresponds to a vertex and $\gamma[-\delta,\delta]$ corresponds to a corner panel.
+For notational convenience we let $\gamma:[-2\delta,L-2\delta] \to \Gamma$ be a counterclockwise arclength parametrization of $\Gamma$ such that  $\gamma(0)$ corresponds to a vertex and $\gamma([-\delta,\delta])$ corresponds to a corner panel.
 
-For a panel $\gamma([s_1,s_2])$ with discretization nodes {\color{blue}$x_i,\dots,x_{i+M-1}$} corresponding to a Gauss-Legendre panel the density is smooth and thus it is expected to be well-represented in the basis of Legendre polynomials (shifted and scaled to the interval $[s_1,s_2]$).
-Hence standard interpolation techniques can be used to obtain an accurate approximation to the density $\sigma$ on the interval $s_1 \le s\le s_2$ .
+For a panel $\gamma([s_1,s_2])$ with discretization nodes \upd{$x_i,\dots,x_{i+M-1}$} corresponding to a Gauss-Legendre panel the density is smooth and thus it is expected to be well-represented in the basis of Legendre polynomials (shifted and scaled to the interval $[s_1,s_2]$).
+Hence standard interpolation techniques can be used to obtain an accurate approximation to the density $\sigma$ on the interval $s_1 \le s\le s_2.$ In~\cref{sec:appb}, we show that the interpolation error in the density
+at panels away from the corner is related to the interpolation error in the solution to a related Dirichlet boundary value problem.
+{\color{red}
 Typically we use 16th order Gauss-Legendre panels and choose their sizes so that their length is no more than their distance to the nearest corner.
 This latter choice guarantees that for any $\epsilon>0$ there exists an $M$ such that if the Gauss-Legendre panels are discretized using an $M$-point Gauss-Legendre rule then the density on that panel can be interpolated to relative precision $\epsilon$ in an $L^2$-sense.
-(We discuss a sketch of a proof in~\cref{sec:appb})
+(we discuss a sketch of a proof in~\cref{sec:appb})}.
 
-For corner panels the nodes were constructed to enable stable interpolation of densities $s^\mu,$ $\mu \in 0 \cup [1/2,50],$ on the interval $s \in (-\delta,\delta)$ - assuming for simplicity that the corner is at $0$ and the panel is of length $2 \delta.$ As mentioned above, the density is expected to contain terms of the form $s^\mu$ for some finite collection of $\mu$ in the interval $(-1/2,1/2),$ and hence will not in general be stably interpolable on the interval $(-\delta,\delta).$ However, it is possible to use the density obtained using (\ref{eqn:adj_linalg}) to construct a sequence of nested problems in the neighborhood of the corner, the solutions of which enable accurate interpolation of the density arbitrarily close to the vertex.
+For corner panels the nodes were constructed to enable stable interpolation of densities $s^\mu,$ $\mu \in \{0\} \cup [1/2,50],$ on the interval $s \in (-\delta,\delta)$ - assuming for simplicity that the corner is at $0$ and the panel is of length $2 \delta.$ As mentioned above, the density is expected to contain terms of the form $s^\mu$ for some finite collection of $\mu$ in the interval $(-1/2,1/2),$ and hence will not in general be stably interpolable on the interval $(-\delta,\delta).$ However, it is possible to use the density obtained using (\ref{eqn:adj_linalg}) to construct a sequence of nested problems in the neighborhood of the corner, the solutions of which enable accurate interpolation of the density arbitrarily close to the vertex.
 The number of these problems depends only on the distance of the closest evaluation point to the corner.
@@
 In light of this we consider the following integral equation
+\upd{
 \begin{align}\label{eqn:resolve_neum0}
--\sigma(s) + \int_{-2\delta}^{2\delta} k(s,t) \sigma(t)\,{\rm d}t = f(s)-h(s), \quad -2\delta \le s \le 2\delta.
+-\frac{\sigma(s)}{2} + \int_{-2\delta}^{2\delta} k(s,t) \sigma(t)\,{\rm d}t = f(s)-h(s), \quad -2\delta \le s \le 2\delta.
 \end{align}
+}
 We note that the solution to (\ref{eqn:resolve_neum0}) is equal to the solution of the original boundary integral equation (\ref{bie_extn}) restricted to the interval $[-2\delta,2\delta].$ Taking the adjoint of (\ref{eqn:resolve_neum0}) we obtain
+\upd{
 \begin{align}\label{eqn:resolve_diri0}
--\sigma(s) + \int_{-2\delta}^{2\delta} k(t,s) \sigma(t)\,{\rm d}t = f(s)-h(s), \quad -2\delta \le s \le 2\delta.
-\end{align}
+-\frac{\sigma(s)}{2} + \int_{-2\delta}^{2\delta} k(t,s) \sigma(t)\,{\rm d}t = f(s)-h(s), \quad -2\delta \le s \le 2\delta,
+\end{align}}
 which is a Dirichlet boundary integral equation for a wedge with a piecewise analytic right-hand side.
 In particular, we can discretize the operator using the method summarized in the previous section.
-Specifically, we subdivide the interval $[-\delta,\delta]$ into three subintervals $I_0 = [-\delta,\delta/2],$ $L_0 = [-\delta/2,\delta/2],$ and $J_0 = [\delta/2,\delta].$ On $I_0$ and $J_0$ we place standard Gauss-Legendre discretization nodes, while on $L_0$ we use the custom discretization scheme for corners, outlined in Section \ref{sec:disc_dir} (see \cite{} for a detailed description of the method).
-On the intervals $[-2\delta,-\delta]$ and $[\delta,2\delta]$ we use the same discretization nodes and weights as in the original system for those intervals (we call these panels $K_0$ and $Q_0$ respectively).
+Specifically, we subdivide the interval $[-\delta,\delta]$ into three subintervals $I_0 = [-\delta,\delta/2],$ $L_0 = [-\delta/2,\delta/2],$ and $J_0 = [\delta/2,\delta].$ On $I_0$ and $J_0$ we place standard Gauss-Legendre discretization nodes, while on $L_0$ we use the custom discretization scheme for corners, outlined in Section \ref{sec:disc_dir} (see \cite{hoskins2019numerical} for a detailed description of the method).
+On the intervals $[-2\delta,-\delta]$ and $[\delta,2\delta]$ we use the same discretization nodes and weights as in the original system for those intervals.
 Let $\underline{f}_0$ denote the right-hand side of (\ref{eqn:resolve_neum0}) evaluated at these discretization nodes and scaled by the square roots of the corresponding weights.
-Let $\upd{\uA_0}$ be the discretization of the interior Dirichlet problem operator (ie.
+Let $\upd{\uA_0}$ be the discretization of the interior Dirichlet problem operator (i.e.
 the operator acting on $\sigma$ on the left-hand side of (\ref{eqn:resolve_diri0})).
@@
 
+\upd{
 \begin{remark}
-Though the above method produces a viable method for reducing the problem, as written the reduction is non-local --- in order to compute the right-hand side for the sub-problem one must evaluate contributions from the rest of the domain.
-\end{remark}
+Though the above method produces a viable method for reducing the problem, as written the reduction appears to be non-local --- in order to compute the right-hand side of the subproblem one must evaluate contributions from the rest of the domain.
+In fact, the values of $\underline{f}_0$ can be obtained using only local information.
+Specifically, we observe that
+\begin{align}
+\left(h(s_i) \sqrt{w_1}, \dots, h(s_{P+2M}) \sqrt{w_{P+2M}}\right)^T =& \left(f(s_i) \sqrt{w_1}, \dots, f(s_{P+2M}) \sqrt{w_{P+2M}}\right)^T-\\
+& \underline{A}_{\rm red}^T \left(\sigma_1 \sqrt{w}_1,\dots, \sigma_{P+2M} \sqrt{w_{P+2M}}\right)^T,
+\end{align}
+where $\underline{A}_{\rm red}$ is the submatrix of $\underline{A}$ corresponding to the first $P+2M$ rows and columns.
+Since $h$ is analytic on $(-2\delta,2 \delta),$ $h(t)$ can be accurately approximated for any $-2\delta<t<2\delta$ by interpolation from its values at the nodes $s_1,\dots,s_{P+2M}.$
+\end{remark}}
 
-The following theorem shows that the right-hand side $\underline{f}_0$ can be computed only using local data (i.e. values of the weak solution in the vicinity of the corner).\\
-\begin{theorem}
-Suppose that $\underline{f}_0$ is the discretization of the right-hand side of (\ref{eqn:resolve_diri0}) corresponding to nodes $s^0_1,\dots,s^0_{N_0}.$ Further suppose that $U$ is the $P\times P$ matrix with entries $U_{ij} = \phi_i(s_j) \sqrt{w_j},$ where $\phi_1,\dots,\phi_P$ are the orthonormal functions on $(-\delta,\delta)$ spanning $,{\rm sgn}(s)|s|^\mu, |s|^\mu,$ $\mu=0,1/2-40$ on that interval.
-Let $w:(-\delta,\delta) \to \mathbb{R}^P$ be the vector-valued function defined by
-\begin{align}
-w(t) = (\phi_1(t),\phi_2(t),\dots,\phi_P(t)),
-\end{align}
-and $\tilde{\sigma} = (\sigma_1,\dots,\sigma_P)^T$ be the approximation to the solution in the vicinity of the corner obtained by solving the original system (\ref{eqn:adj_linalg}).
-Then $|(f(t)-h(t)) - w(t) U^{-1} \upd{\uA_0^T} \tilde{\sigma}| = O(\epsilon)$ for all $t \in(-\delta,\delta).$ In particular, if $\tilde{f}_0$ is the vector of length $N_0$ with entries defined by
-\begin{align}
-(\tilde{f}_0)_i = w(s^0_i) U^{-1} \upd{\uA_0^T} \tilde{\sigma}, \quad i=1,\dots,N_0,
-\end{align}
-then $\| \underline{f}_0 - \tilde{f}_0\| = O(\epsilon).$
-\end{theorem}
-\begin{proof}
-We begin by observing that both $f$ and $h$ are analytic on the interval $(-\delta,\delta).$ In particular, they can be accurately interpolated using $\phi_1,\dots,\phi_P$ on the interval $(-\delta,\delta).$ Hence,
-\begin{align}\label{eqn:approx_thm}
-f(t)-h(t) \approx w(t) U^{-1} (f(s_1)-h(s_1),\dots,f(s_P)-h(s_P))^T.
-\end{align}
-A similar argument shows that $f(t)-h(t)$ is interpolable on $[-2\delta,-\delta]$ and $[\delta,2\delta].$
-On the other hand, by construction,
-\begin{align}\label{eqn:linalg_thm}
-\underline{f} = \upd{\uA^T} \begin{pmatrix}\tilde{\sigma}\\ \sigma_{P+{2M+1}}\\ \vdots\\ \sigma_N\end{pmatrix}.
-\end{align}
-Let $\upd{\uA}_0$ be the $(P+2M)\times (P+2M)$ submatrix of $\upd{\uA}$ corresponding to the first $P+2M$ rows and columns of $\upd{\uA},$ and $\upd{\uA}_{\rm red}$ be the $P+2M \times (N-P-2M)$  submatrix of $\upd{\uA}$ corresponding to selecting the first $P+2M$ rows of $\upd{\uA}$ and all but the first $P+2M$ columns of $\upd{\uA}.$ Using this notation, the first $P+2M$ rows of (\ref{eqn:linalg_thm}) can be re-written as
-\begin{align}
-\begin{pmatrix}f_1\\\vdots \\ f_{P+2M}\end{pmatrix}  = \upd{\uA}_{\rm red}^T \begin{pmatrix} \sigma_{P+2M+1}\\ \vdots\\ \sigma_N\end{pmatrix} + \upd{\uA}_0^T \tilde{\sigma}.
-\end{align}
-The first term on the right-hand side is $(h(s_1),\dots,h(s_{P+2M}))^T.$ Substituting this into the previous equation, we obtain
-\begin{align}
-(f(s_1)-h(s_1),\dots,f(s_{P+2M})-h(s_{P+2M}))^T = \upd{\uA}_0^T \tilde{\sigma}.
-\end{align}
-The result follows by substituting the above equality into (\ref{eqn:approx_thm}).
-\end{proof}
-
-This can be iterated to obtain an interpolable approximation to the density on $L_0 = [-\delta,\delta].$ In particular, we consider the restriction of the exterior Neumann integral equation, as well as its, adjoint to the interval $I_0$ and $J_0.$ For the right-hand side we use the original right-hand side $f$ minus the contribution from the remainder of the domain.
+This can be iterated to obtain an interpolable approximation to the density on $[-\delta,\delta].$ In particular, we consider the restriction of the exterior Neumann integral equation, as well as its adjoint, to the interval $I_0$ and $J_0.$ For the right-hand side we use the original right-hand side $f$ minus the contribution from the remainder of the domain.
 In particular, if we define
@@
 then $\sigma$ restricted to the interval $I_0\cup L_0 \cup J_0$ satisfies
+\upd{
 \begin{align}\label{eqn:resolve_neum1}
--\sigma(s) + \int_{-\delta}^{\delta} k(s,t) \sigma(t)\,{\rm d} t = f(s)-h(s)-h_1(s), \quad -\delta \le s \le \delta.
+-\frac{\sigma(s)}{2} + \int_{-\delta}^{\delta} k(s,t) \sigma(t)\,{\rm d} t = f(s)-h(s)-h_1(s), \quad -\delta \le s \le \delta.
 \end{align}
+}
 The corresponding adjoint equation is given by 
+\upd{
 \begin{align}\label{eqn:resolve_diri1}
--\sigma(s) + \int_{-\delta}^{\delta} k(t,s) \sigma(t)\,{\rm d} t = f(s)-h(s)-h_1(s), \quad -\delta \le s \le \delta.
+-\frac{\sigma(s)}{2} + \int_{-\delta}^{\delta} k(t,s) \sigma(t)\,{\rm d} t = f(s)-h(s)-h_1(s), \quad -\delta \le s \le \delta.
 \end{align}
-
+}
 Once again, we divide $L_0$ into three intervals $I_1,$ $L_1,$ and $J_1$ and discretize each interval as before.

### 2020-06-16 paper_lap/JCP_response1/06num.tex
updating paper

--- 2020-06-10 paper_lap/JCP_response2/06num.tex
@@
 
-\begin{remark1}
+\begin{remark}
 Though $2^{-200}$ is significantly smaller than machine precision, the matrix entries corresponding to the
@@
 computing interactions of nearby points.
-\end{remark1} 
-\begin{remark1}
+\end{remark} 
+\begin{remark}
 Simple arguments from complex analysis show that when using graded meshes, in order to obtain full 
@@
 panel size of $2^{-200}$. 
-\end{remark1}
+\end{remark}
 
@@
 In~\cref{fig:scatteringtest}, we compute the error in the solution at target
-locations for a scattering problem whose {\color{olive}boundary condition} is given by a collection of three interior charges
+locations for a scattering problem whose \upd{boundary condition} is given by a collection of three interior charges
 \begin{equation}
@@
 The strengths $c_{j}$ are chosen such that they average to $0$.
-The domain contains $108$ corners, was discretized using $22240$ nodes and required $105$ iterations {\color{olive}of GMRES} to converge to a residue of $10^{-15}$.
+The domain contains $108$ corners, was discretized using $22240$ nodes and required $105$ iterations \upd{of GMRES} to converge to a residue of $10^{-15}$.
 The matrix at each iteration was applied using an FMM whose tolerance was also set to $10^{-15}$.

### 2020-06-16 paper_lap/JCP_response1/manuscript.tex
updating paper

@@
 \newtheorem{corollary}{Corollary}[section]
-\newtheorem{remark1}{Remark}[section]
 \newcommand{\beqn}{\begin{equation}}
@@
 \begin{highlights}
-\item Efficient discretization to boundary integral equations corresponding to Laplace's equation with Neumann boundary conditions on polygonal domains based on an adjoint Dirichlet discretization resulting
+\upd{
+\item Efficient discretization of boundary integral equations corresponding to Laplace's equation with Neumann boundary conditions on polygonal domains based on an adjoint Dirichlet discretization resulting
 in weak solutions to the integral equation. 
-\item A local re-solve algorithm for obtaining pointwise accurate solutions of the integral equation arbitrarily close to the corner.
-\item Rapid evaluation of solution at target locations in the volume arbitrarily close to the corner.
+\item A local re-solve algorithm for obtaining pointwise accurate solutions of the integral equation arbitrarily close to the corner, and rapid evaluation of solution at target locations in the volume arbitrarily close to the corner.
+\item Accurate solution of Laplace's equation arbitrarily close to corners at which solutions may have singularities.}
 \end{highlights}
@@
 \section{Approximation of data on corner panels for re-solve}
-Here we give explicit bounds for the rate of convergence of the contribution of the rest of the boundary to a corner panel.
-In particular, given a polygonal domain with boundary $\Gamma,$ let $\bx$ denote a vertex of $\Gamma$ and $C = \Gamma \cap B_r(\bx),$ where $B_r(\bx)$ is the ball of radius of $r$ centered at $\bx.$ We choose $r$ so that $\Gamma \cap B_{2r}(\bx)$ corresponds to a wedge with internal angle $\pi \alpha$ and side lengths $2r.$
-
-%Let $\Gamma_*$ be any other straight line segment contained entirely within $\Gamma \setminus B_{2r}(\bx).$ Then
+Here we give explicit bounds for the rate of convergence of the contribution of the rest of the boundary to a corner panel.{\color{red}  In particular, given a polygonal domain with boundary $\Gamma,$ let $\bx$ denote a vertex of $\Gamma$ and $C = \Gamma \cap B_r(\bx),$ where $B_r(\bx)$ is the ball of radius of $r$ centered at $\bx.$ We choose $r$ so that $\Gamma \cap B_{2r}(\bx)$ corresponds to a wedge with internal angle $\pi \alpha$ and side lengths $2r.$ }
 
@@
 \label{sec:appb}
-{\color{blue}
+\upd{
 In this section, we demonstrate that for a panel which is sufficiently far from the corner, the density computed using the adjoint of a Dirichlet discretization can be interpolated 

### 2020-06-18 paper_lap/JCP_response1/01intro.tex
minor edits

@@
 \upd{This approach generalizes naturally to three-dimensional problems, though efficient discretization of the corresponding Dirichlet problems is the subject of ongoing research.
-A similar analysis as in \cite{} can be used to characterize the singularities along edges and near vertices, though there are a few challenges which prevent the immediate application of this analysis to the design of suitable discretizations.}
+A similar analysis as in \cite{serkhacha} can be used to characterize the singularities along edges and near vertices, though there are a few challenges which prevent the immediate application of this analysis to the design of suitable discretizations.}
 

### 2020-06-18 paper_lap/JCP_response1/03bvp.tex
minor edits

@@
 
-The following theorems {\color{olive}(see \cite{kress1989linear})} describe the behavior of the single and double layer potentials in the vicinity of the boundary curve $\Gamma.$
+The following theorems {\color{blue}(see for example \cite{kress1989linear})} describe the behavior of the single and double layer potentials in the vicinity of the boundary curve $\Gamma.$
 
@@
 \begin{remark}
-We note that the smoothness of the kernel $k$ for well-separated portions of the domain guarantees that the problem of determining the singularities arising in the vicinity of a corner for a polygonal domain can be reduced to the analysis of the wedge case, see the discussion in \cite{} for example.
+We note that the smoothness of the kernel $k$ for well-separated portions of the domain guarantees that the problem of determining the singularities arising in the vicinity of a corner for a polygonal domain can be reduced to the analysis of the wedge case, see the discussion in \cite{hoskins2019numerical,serkhrachh} for example.
 \end{remark}

### 2020-06-18 paper_lap/JCP_response1/response.tex
minor changes

@@
 
-\todo{JH}
+The discussion about the disadvantage of compression-based approaches in 3D has been removed and a discussion in the second last paragraph about generalizations to 3D has been added.
 
@@
 
-\todo{JH}
+The notation in Theorem 6 has been cleaned up and a remark has been added afterward discussing the connection between the problem on the polygon and the problem on the wedge.
 
@@
 \qb
-\todo{JH}
+
+The value of K used in our experiments has been stated explicitly.
 
@@
 \qb
-\todo{JH}
+
+We thank the referee for pointing this out. A comment has been added discussing the interior Neumann problem.
 
@@
 \qb
-\todo{JH}
+
+The theorem has been eliminated in favor of a remark, and the corresponding notation has been cleaned up.
 
@@
 \qb
-\todo{JH}
+We thank the referee for pointing out these typos and small fixes!
 

### 2020-07-15 paper_lap/JCP_response1/response.tex
updating response and manuscript

@@
 reviewers after reading our manuscript \emph{On the discretization of Laplace's equation with Neumann boundary conditions on polygonal domains}.
-In short, we have made revisions to the paper, namely:
 
-Below are the reviews reports indented and in italics, interlaced with
+Below are the reviewers' reports indented and in italics, interlaced with
 our responses.
@@
 Reviewer \#1:
-This manuscript extends a recent line of work on handling the singularities in the density of the standard boundary integral equation formulation of Laplace?s equation that arise at the corners of polygonal domains, through the use of specialized, high-order quadratures, which are computed using analytic expansions of the density.
+This manuscript extends a recent line of work on handling the singularities in the density of the standard boundary integral equation formulation of Laplace's equation that arise at the corners of polygonal domains, through the use of specialized, high-order quadratures, which are computed using analytic expansions of the density.
 Previous work in this direction has difficulties directly applying this strategy to Neumann problems, since the singularities are significantly worse here than in the Dirichlet case.
@@
 The theory as developed considers only the exterior Neumann problem.
-I?m guessing a similar duality relationship holds with the interior Neumann problem and the exterior Dirichlet problem, and the procedure carries over straightforwardly (indeed, you consider an interior Neumann problem in the numerical results).
+I'm guessing a similar duality relationship holds with the interior Neumann problem and the exterior Dirichlet problem, and the procedure carries over straightforwardly (indeed, you consider an interior Neumann problem in the numerical results).
 For the sake of completeness, could you add a brief remark on whether or not the procedure is exactly the same for the interior Neumann problem, and state if there are any special considerations that are different from the exterior Neumann case?
@@
 
-There are these other issues I?m having with it:
+There are these other issues I'm having with it:
 (a) On your assumptions about the discretization, 1 and 3 have an easy-to-understand interpretation.
@@
 22 is very unclear to me.
-I don?t even understand the first sentence as to why k(s,t) would be identically 0 on the same segment as $\gamma([s1,s2])$, or what is really even meant by ?segment?
-here.
+I don't even understand the first sentence as to why k(s,t) would be identically 0 on the same segment as $\gamma([s1,s2])$, or what is really even meant by segment here.
 Furthermore, it is mentioned that k(s, t) when considered as a function of $t \in \mathbb{C}$ has a singularity at $\gamma(s)$.
@@
 The solution of Laplace's equation in complicated domains is a classical problem in computational physics and has many applications such as electrostatics, fluid flow, diffusion, and magnetohydrodynamics to name a few.
-Theorems, lemmas, propositions have been mainly used to summarize existing work which serves as a foundation for our method.
+We have significantly reduced the use of theorems and definitions to summarize classical results and standard definitions.
 Here are a few other examples of papers in JCP which we believe are written in a similar style.
+
+\begin{enumerate}
+\item G. Widmer, R. Hiptmair, C. Schwab, Sparse adaptive finite elements for radiative transfer, Journal of Computational Physics 227 (2008) 6071-6105. 
+\item K. Serkh, V. Rokhlin, On the solution of elliptic partial differential equations on regions with corners, Journal of Computational Physics 305 (2016) 150-171.
+\item C.
+Jerez-Hanckes, C.
+Peres-Arancibia, C.
+Turc, Multitrace/single trace fomulations and domain decomposition methods for the solution of Helmholtz transmission problems for bounded composite scatterers, Journal of Computational Physics 350 (2017) 343-360.
+\end{enumerate}
 

### 2020-07-15 paper_lap/JCP_response1/01intro.tex
updating response and manuscript

@@
 an amount which is comparable to the number required for smooth portions of the boundary).
-This approach has been used to generate efficient discretizations for Dirichlet problems for Laplace's equation on polygonal domains\cite{hoskins2019numerical}.
+This approach has been used to generate efficient discretizations for Dirichlet problems for Laplace's equation on polygonal domains~\cite{hoskins2019numerical}.
 

### 2020-07-15 paper_lap/JCP_response1/02mprelim.tex
adding response
updating response and manuscript

--- 2020-01-06 paper_lap/02mprelim.tex
@@
-\section{Mathematical preliminaries}
+\section{Mathematical preliminaries \label{sec:mprelim}}
 \subsection{Boundary value problems}
@@
 $f: \Gamma \to \mathbb{R},$ we consider 
-the following four boundary value problems.
+the following four boundary value problems for Laplace's equation.
 
 \begin{enumerate}
-\item The interior Dirichlet problem for Laplace's equation:
+\item The interior Dirichlet problem:
 \begin{align}\label{eqn:BVPIDL}
@@
 
-\item The exterior Dirichlet problem for Laplace's equation:
+\item The exterior Dirichlet problem:
 \begin{align}\label{eqn:BVPEDL}
@@
 
-\item The interior Neumann problem for Laplace's equation:
+\item The interior Neumann problem:
 \begin{align}\label{eqn:BVPINL}
@@
 
-\item The exterior Neumann problem for Laplace's equation:
+\item The exterior Neumann problem:
 \begin{align}\label{eqn:BVPEDL}
@@
 \begin{remark}
-The existence and uniqueness of the solutions to the above equations is a well-known result (see \cite{} for example). 
+The existence and uniqueness of the solutions to the above equations is a well-known result (see \cite{kress1989linear} for example). 
 \end{remark}

### 2020-07-15 paper_lap/JCP_response1/03bvp.tex
updating response and manuscript

@@
 Before describing this procedure we first define the single and double layer potential operators and summarize their relevant properties.
+\upd{
  \subsection{Layer potentials}
-\begin{definition}\label{def_layerpots}
 Given a function $\sigma:\Gamma \to \mathbb{R}$, the single-layer potential is defined by
@@
 \eeqn
-\end{definition}
 In the following we will often refer to the function $\sigma$ as the {\it density} which generates the corresponding potential.
-\begin{definition}
+
 For $\bx \in \Gamma$ we define the kernel $K(\bx,\by)$ by
@@
 \begin{align}
+\label{eq:def_kerst}
 k(s,t) = K(\gamma(s),\gamma(t)).
 \end{align}
-\upd{By a standard abuse of notation we use $\cS$ and $\cD$ to denote both the operators acting on $L^2(\Gamma)$ as well as the corresponding operators acting on $L^2([0,L]),$ the latter being obtained from the former by composition with the parameterization.}
-\end{definition}
+By a standard abuse of notation we use $\cS$ and $\cD$ to denote both the operators acting on $L^2(\Gamma)$ as well as the corresponding operators acting on $L^2([0,L]),$ the latter being obtained from the former by composition with the parameterization.}
 
@@
 Next we define the following operator which arises in the study of Neumann boundary value problems.
-\begin{definition}\label{def_singder}
 Let $\cS$ be the single-layer potential operator and $\bnu\cdot \nabla \cS$  denote its normal derivative restricted to $\Gamma.$ In particular, for $\bx_0 \in \Gamma,$
@@
 \end{align}
-\end{definition}
 
-The following proposition relates the normal derivative of the single-layer operator to the double-layer operator.
-Its proof follows directly from Definitions \ref{def_layerpots} and \ref{def_singder}.
-\begin{proposition}
-Let $\cS,\cD:L^2(\Gamma) \to L^2(\Gamma)$ be defined as above.
-Let $\bnu \cdot \nabla \cS$ denote the normal derivative of $\cS$ in the sense of the previous definition.
-Then $\bnu \cdot \nabla \cS= \cD^{T}$ where $T$ denotes the adjoint operator with respect to the inner product
+\upd{
+It is well known that $\bnu \cdot \nabla \cS = \cD^{T}$ where $^T$ denotes the adjoint with respect to
+the inner product, 
 \beqn
@@
 \eeqn
-where $\gamma:[0,L] \to \Gamma$ is a counterclockwise arclength parametrization of $\Gamma.$ 
+and $\gamma:[0,L] \to \Gamma$ is a counterclockwise arclength parametrization of $\Gamma.$  
 In particular, for all $\rho,\sigma \in L^2(\Gamma),$
@@
 \begin{align}
-\bnu(\gamma(t))\cdot \nabla\cS[\rho](\gamma(t)) = \int_0^L k(t,s)\,\rho(\gamma(s))\, {\rm d}s.
+\bnu(\gamma(t))\cdot \nabla\cS[\rho](\gamma(t)) = \int_0^L k(t,s)\,\rho(\gamma(s))\, {\rm d}s \,
 \end{align}
-\end{proposition}
+where $k(s,t)$ is defined in~\cref{eq:def_kerst}.
 
@@
 In this section we describe the conversion of the Laplace boundary value problems (interior Dirichlet, exterior  Dirichlet, interior Neumann, and exterior Neumann) to second-kind integral equations.
+\upd{These results are classical and we present them below for completeness (see~\cite{kress1989linear}, for example).}
 
-\begin{theorem} [Interior Dirichlet problem for Laplace's equation]
+\begin{enumerate}
+\item Interior Dirichlet problem: \\ 
 For every $f:[0,L] \rightarrow \mathbb{R}$ in $L^{2}([0,L]),$ there exists a unique $\sigma \in L^{2}([0,L])$ which satisfies
@@
 \end{align}
-for all $s \in [0,L).$ Moreover, the solution to the interior Dirichlet problem for Laplace's equation with boundary data $f$ is given by $u(\by) = \cD[\sigma](\by)$ for all $\by \in \Omega.$
-\end{theorem}
+for all $s \in [0,L).$ Moreover, the solution to the interior Dirichlet problem with boundary data $f$ is given by $u(\by) = \cD[\sigma](\by)$ for all $\by \in \Omega.$
 
-\begin{theorem} [Exterior Dirichlet problem for Laplace's equation]
+\item Exterior Dirichlet problem:\\ 
 For every $f:[0,L] \rightarrow \mathbb{R}$ in $L^{2}([0,L])$ there exists a unique $\sigma \in L^{2}([0,L])$ which
@@
 for all $s \in [0,L].$ 
-Moreover, the solution to the exterior Dirichlet problem for Laplace's equation with boundary data $f$ is given by $u(\by) = \cD[\sigma](\by) + \int_{0}^{L} \sigma(t) dt$
+Moreover, the solution to the exterior Dirichlet problem with boundary data $f$ is given by $u(\by) = \cD[\sigma](\by) + \int_{0}^{L} \sigma(t) dt$
 for all $\by \in \mathbb{R}^2 \setminus \Omega.$
-\end{theorem}
 
-\begin{theorem}[Interior Neumann problem for Laplace's equation]
+\item Interior Neumann problem:\\ 
 For every  $f:[0,L] \rightarrow \mathbb{R}$ in $L^{2}([0,L])$ such that $\int_{0}^{L} f(t)\,{\rm d}t = 0,$ there exists a unique $\sigma \in L^{2}([0,L])$ which satisfies
@@
 \end{align}
-for all $s \in [0,L).$ Moreover, the solution to the interior Neumann problem for Laplace's equation with boundary data $f$ is given by $u(\by) = \cS[\sigma](\by)$ for all $\by \in \Omega.$
-\end{theorem}
+for all $s \in [0,L).$ Moreover, a solution to the interior Neumann problem with boundary data $f$ is given by $u(\by) = \cS[\sigma](\by)$ for all $\by \in \Omega.$
 
-\begin{theorem}[Exterior Neumann problem for Laplace's equation]
+\item Exterior Neumann problem:\\
 For every $f:[0,L] \rightarrow \mathbb{R}$ in $L^{2}([0,L])$ there exists a unique $\sigma \in L^{2}([0,L])$ which satisfies
@@
 \end{align}
-for all $s \in [0,L).$ Moreover, the solution to the interior Neumann problem for Laplace's equation with boundary data $f$ is given by $u(\by) = \cS[\sigma](\by)$ for all $\by \in \Omega.$
-\end{theorem}
+for all $s \in [0,L).$ Moreover, the solution to the exterior Neumann problem with boundary data $f$ is given by $u(\by) = \cS[\sigma](\by)$ for all $\by \in \mathbb{R}^{2} \setminus \Omega.$
+\end{enumerate}
+}
 

### 2020-07-15 paper_lap/JCP_response1/04nprelim.tex
updating response and manuscript

@@
 When \upd{$x_i$} and $t$ do not belong to the same corner panel (in particular when either is not itself contained in a corner panel) then the weights and nodes associated with the discretization can be used as the quadrature rule.
-When $s_i$ corresponds to a corner panel special care must be taken.
+When \upd{$x_i$} corresponds to a corner panel special care must be taken.
 Instead, using an algorithm for generating generalized Gaussian quadratures \cite{bremer2010}, quadrature nodes are chosen which integrate
@@
 In principle a similar method could be employed to discretize the Neumann boundary integral equations.
-Unfortunately, the singular nature of the powers (the smallest in the expansion given in Theorem \ref{thm_cord} lies in the range $(-1/2,0)$) makes it difficult to produce universal discretizations and quadratures which work for large ranges of angles.
+Unfortunately, the singular nature of the powers (the smallest in the expansion given in Theorem \ref{thm_cord} lies in the range \upd{$(-1/2,1/2)$} makes it difficult to produce universal discretizations and quadratures which work for large ranges of angles.
 When the above method is run on these problems, discretization nodes tend to accumulate close to the corner (within $10^{-14}$).
@@
 In the latter case it is well-known that the naive boundary integral equation formulation has a one-dimensional nullspace (corresponding to the fact that solutions to the corresponding PDE are unique only up to a constant).
-Using standard techniques (see \cite{} for example) this issue can be corrected and the method of this paper can be applied in a straightforward manner.}
+Using standard techniques (see \cite{sifuentes2014randomized} for example) this issue can be corrected and the method of this paper can be applied in a straightforward manner.}

### 2020-07-15 paper_lap/JCP_response1/05apparatus.tex
updating response and manuscript

@@
 \subsection{Adjoint discretization}
-\upd{Let $X = \mathbb{L}^2([0,L])$ and $\underline{X} = \mathbb{R}^{N}$.  Let $\left< \cdot, \cdot \right>_{X},\left< \cdot, \cdot \right>_{\underline{X}}$
+\upd{Let $X = L^2([0,L])$ and $\underline{X} = \mathbb{R}^{N}$.  Let $\left< \cdot, \cdot \right>_{X},\left< \cdot, \cdot \right>_{\underline{X}}$
 denote the standard inner products on the Hilbert spaces $X,$ and $\underline{X}$ respectively.
@@
 \begin{align}
-\left| \langle f,(A^{-1})^* g \rangle_{X} - \langle S[f],\left(A^{-1}_\epsilon\right)^T S[g] \rangle_{\uX} \right| \le \epsilon \|f\|_{X} \|g\|_{X}
+\left| \langle f,(A^{-1})^T g \rangle_{X} - \langle S[f],\left(A^{-1}_\epsilon\right)^T S[g] \rangle_{\uX} \right| \le \epsilon \|f\|_{X} \|g\|_{X}
 \end{align}
-where $\,{{}^*}\,$ denotes the adjoint.
+where $\,{{}^T}\,$ denotes the adjoint.
 \end{lemma}
@@
 For a panel $\gamma([s_1,s_2])$ with discretization nodes \upd{$x_i,\dots,x_{i+M-1}$} corresponding to a Gauss-Legendre panel the density is smooth and thus it is expected to be well-represented in the basis of Legendre polynomials (shifted and scaled to the interval $[s_1,s_2]$).
-Hence standard interpolation techniques can be used to obtain an accurate approximation to the density $\sigma$ on the interval $s_1 \le s\le s_2.$ In~\cref{sec:appb}, we show that the interpolation error in the density
-at panels away from the corner is related to the interpolation error in the solution to a related Dirichlet boundary value problem.
-{\color{red}
-Typically we use 16th order Gauss-Legendre panels and choose their sizes so that their length is no more than their distance to the nearest corner.
-This latter choice guarantees that for any $\epsilon>0$ there exists an $M$ such that if the Gauss-Legendre panels are discretized using an $M$-point Gauss-Legendre rule then the density on that panel can be interpolated to relative precision $\epsilon$ in an $L^2$-sense.
-(we discuss a sketch of a proof in~\cref{sec:appb})}.
+Hence standard interpolation techniques can be used to obtain an accurate approximation to the density $\sigma$ on the interval $s_1 \le s\le s_2.$ \upd{In~\cref{sec:appb}, we show that the interpolation error in the density
+at panels away from the corner is related to the interpolation error in the solution to a related Dirichlet boundary value problem.}
 
@@
 Suppose that $f$ is a piecewise-analytic function in $S_\epsilon$ and  $\underline{\sigma} = (\upd{\uA}^T)^{-1} \upd{\uf}$ is the approximation to the Neumann density obtained using the adjoint of the discretization for the interior Dirichlet boundary integral equation.
-Further suppose that the discretization nodes are ordered so that $s_1,\dots,s_P$ correspond to the corner panel associated with the interval $(-\delta,\delta),$ $s_{P+1},\dots,s_{P+M}$ correspond to the Gauss-Legendre panel immediately to the left associated with the interval $(-2\delta,-\delta),$ and $s_{P+M+1},\dots,s_{P+2M}$ to the Gauss-Legendre panel immediately to the right associated with the interval $(\delta,2\delta).$
+Further suppose that the discretization nodes are ordered so that $x_1,\dots,x_{2K}$ correspond to the corner panel associated with the interval $(-\delta,\delta),$ $x_{2K+1},\dots,x_{2K+M}$ correspond to the Gauss-Legendre panel immediately to the left associated with the interval $(-2\delta,-\delta),$ and $x_{2K+M+1},\dots,x_{2K+2M}$ to the Gauss-Legendre panel immediately to the right associated with the interval $(\delta,2\delta).$
 Then
 \begin{align}\label{eqn:def_hfun}
-h(t) = \sum_{i=P+2M+1}^N k(s_i,t) \sqrt{w_i} \,\underline{\sigma}_i
+h(t) = \sum_{i=2K+2M+1}^N k(x_i,t) \sqrt{w_i} \,\underline{\sigma}_i
 \end{align}
@@
 \begin{align}
-\left(h(s_i) \sqrt{w_1}, \dots, h(s_{P+2M}) \sqrt{w_{P+2M}}\right)^T =& \left(f(s_i) \sqrt{w_1}, \dots, f(s_{P+2M}) \sqrt{w_{P+2M}}\right)^T-\\
-& \underline{A}_{\rm red}^T \left(\sigma_1 \sqrt{w}_1,\dots, \sigma_{P+2M} \sqrt{w_{P+2M}}\right)^T,
+\left(h(x_i) \sqrt{w_1}, \dots, h(x_{2K+2M}) \sqrt{w_{2K+2M}}\right)^T =& \left(f(k_i) \sqrt{w_1}, \dots, f(k_{2K+2M}) \sqrt{w_{2K+2M}}\right)^T-\\
+& \underline{A}_{\rm red}^T \left(\sigma_1 \sqrt{w}_1,\dots, \sigma_{2K+2M} \sqrt{w_{2K+2M}}\right)^T,
 \end{align}
-where $\underline{A}_{\rm red}$ is the submatrix of $\underline{A}$ corresponding to the first $P+2M$ rows and columns.
-Since $h$ is analytic on $(-2\delta,2 \delta),$ $h(t)$ can be accurately approximated for any $-2\delta<t<2\delta$ by interpolation from its values at the nodes $s_1,\dots,s_{P+2M}.$
+where $\underline{A}_{\rm red}$ is the submatrix of $\underline{A}$ corresponding to the first $2K+2M$ rows and columns.
+Since $h$ is analytic on $(-2\delta,2 \delta),$ $h(t)$ can be accurately approximated for any $-2\delta<t<2\delta$ by interpolation from its values at the nodes $x_1,\dots,x_{2K+2M}.$
 \end{remark}}

### 2020-07-15 paper_lap/JCP_response1/manuscript.tex
updating response and manuscript

@@
 \usetikzlibrary{arrows,automata}
-\newtheorem{definition}{Definition}[section]
-\newtheorem{remark}{Remark}[section]
-\newtheorem{conjecture}{Conjecture}[section]
-\newtheorem{proposition}{Proposition}[section]
-\newtheorem{corollary}{Corollary}[section]
+\newtheorem{definition}{Definition}
+\newtheorem{remark}[definition]{Remark}
+\newtheorem{conjecture}[definition]{Conjecture}
+\newtheorem{proposition}[definition]{Proposition}
+\newtheorem{corollary}[definition]{Corollary}
 \newcommand{\beqn}{\begin{equation}}
@@
 
-\newtheorem{theorem}{Theorem}
-\newtheorem{thm}{Theorem}
-\newtheorem{lemma}{Lemma}
-\newtheorem{lem}{Lemma}
-\newtheorem{rem}{Remark}
-\newtheorem{comment}{Remark}
+\newtheorem{theorem}[definition]{Theorem}
+\newtheorem{lemma}[definition]{Lemma}
 
@@
 Using the known behavior of the solution, universal discretizations have been constructed for the solution of the Dirichlet problem.
-However, the leading order behavior of solutions to the Neumann problem is $O(t^{\mu})$ for {\color{olive}$\mu \in (-1/2,1/2)$} depending on the angle at the corner (compared to $O(C+t^{\mu})$ with $\mu>1/2$ for the Dirichlet problem); this presents a significant challenge in the design of universal discretizations.
+However, the leading order behavior of solutions to the Neumann problem is $O(t^{\mu})$ for \upd{$\mu \in (-1/2,1/2)$} depending on the angle at the corner (compared to $O(C+t^{\mu})$ with $\mu>1/2$ for the Dirichlet problem); this presents a significant challenge in the design of universal discretizations.
 Our approach is based on using the discretization for the Dirichlet problem in order to compute a solution in the ``weak sense'' by solving an adjoint linear system; namely, it can be used to compute inner products with smooth functions accurately, but it cannot be interpolated.
@@
 \section{Approximation of data on corner panels for re-solve}
-Here we give explicit bounds for the rate of convergence of the contribution of the rest of the boundary to a corner panel.{\color{red}  In particular, given a polygonal domain with boundary $\Gamma,$ let $\bx$ denote a vertex of $\Gamma$ and $C = \Gamma \cap B_r(\bx),$ where $B_r(\bx)$ is the ball of radius of $r$ centered at $\bx.$ We choose $r$ so that $\Gamma \cap B_{2r}(\bx)$ corresponds to a wedge with internal angle $\pi \alpha$ and side lengths $2r.$ }
-
+Here we give explicit bounds for the rate of convergence of the contribution of the rest of the boundary to a corner panel.
 \begin{theorem}
@@
 But first, we present a lemma about the accuracy of Gaussian quadrature
-\begin{lem}
+\begin{lemma}
 \label{lem:b1}
@@
 \end{equation}
-\end{lem}
+\end{lemma}
 
@@
 
-\begin{lem}
+\begin{lemma}
 \label{lem:b2}
@@
 In practice, a discretization with macroscopic panels at the corner, panels not at a corner vertex separated from the corner by their panel length, and which resolves $g$ to precision $\varepsilon$ is often sufficient to guarantee~\cref{eq:dest}.
-\begin{rem}
+\begin{remark}
 The size of the panel at the corner needs to be chosen based on the angle formed at the corner---smaller panels for angles closer to $0$ or $2\pi$, in order to resolve the corresponding close to touching interactions.
-\end{rem}
+\end{remark}
 }

### 2020-07-15 paper_lap/JCP_response1/03bvp.tex
updating manuscript

@@
 
-\begin{remark}
 A similar result holds for the case where the identity term in (\ref{eqn_grho}) is replaced by its negative; the change in sign corresponds to replacing the boundary integral equation for the interior Dirichlet problem with the boundary integral equation corresponding to exterior Dirichlet problem.
 Similar expansions also hold for both the exterior and interior Neumann problems, in which case the singular powers are obtained by subtracting one from the singular powers arising in the Dirichlet problem.
-\end{remark}
 

### 2020-07-15 paper_lap/JCP_response1/05apparatus.tex
updating manuscript

@@
 For a panel $\gamma([s_1,s_2])$ with discretization nodes \upd{$x_i,\dots,x_{i+M-1}$} corresponding to a Gauss-Legendre panel the density is smooth and thus it is expected to be well-represented in the basis of Legendre polynomials (shifted and scaled to the interval $[s_1,s_2]$).
-Hence standard interpolation techniques can be used to obtain an accurate approximation to the density $\sigma$ on the interval $s_1 \le s\le s_2.$ \upd{In~\cref{sec:appb}, we show that the interpolation error in the density
+Hence standard interpolation techniques can be used to obtain an accurate approximation to the density $\sigma$ on the interval $s_1 \le s\le s_2.$ \upd{In~\ref{sec:appb}, we show that the interpolation error in the density
 at panels away from the corner is related to the interpolation error in the solution to a related Dirichlet boundary value problem.}

### 2020-07-15 paper_lap/JCP_response1/manuscript.tex
updating manuscript

@@
 Suppose that the boundary is discretized using the procedure discussed in~\cref{sec:resolve}.
-Recall that the discretizaton nodes are denoted by $x_{1},x_{2}\ldots x_{N}$, the corresponding weights are given by $w_{1}, \ldots w_{N}$, $X = \mathbb{L}^2({\Gamma})$, $\underline{X} = \mathbb{R}^{N}$, $\left< \cdot, \cdot \right>_{Y}$
+Recall that the discretizaton nodes are denoted by $x_{1},x_{2}\ldots x_{N}$, the corresponding weights are given by $w_{1}, \ldots w_{N}$, $X = L^2({\Gamma})$, $\underline{X} = \mathbb{R}^{N}$, $\left< \cdot, \cdot \right>_{Y}$
 denote the standard inner products on the Hilbert spaces $Y=X,\underline{X}$, and
@@
 \label{lem:b1}
-Suppose that $p$ is a polynomial of degree less than $M$, then for any function $g$ in $\mathbb{L}^{2}[-1,1]$, then the integral
+Suppose that $p$ is a polynomial of degree less than $M$, then for any function $g$ in $L^{2}[-1,1]$, then the integral
 $\int_{-1}^{1} p \cdot g$ can be computed accurately using Gaussian quadrature of any order greater than or equal to $M$.
-As a consequence, For any $g$ in $\mathbb{L}^{2}(\Gamma)$, then 
+As a consequence, For any $g$ in $\L^{2}(\Gamma)$, then 
 \begin{equation}

### 2020-07-20 paper_lap/JCP_response1/01intro.tex
updated files

@@
 \upd{This approach generalizes naturally to three-dimensional problems, though efficient discretization of the corresponding Dirichlet problems is the subject of ongoing research.
-A similar analysis as in \cite{serkhacha} can be used to characterize the singularities along edges and near vertices, though there are a few challenges which prevent the immediate application of this analysis to the design of suitable discretizations.}
+A similar analysis as in \cite{serkhacha} can, in principle, be used to characterize the singularities along edges and near vertices, though there are a few challenges which prevent the immediate application of this analysis to the design of suitable discretizations.}
 

### 2020-07-20 paper_lap/JCP_response1/04nprelim.tex
updated files

@@
 In principle a similar method could be employed to discretize the Neumann boundary integral equations.
-Unfortunately, the singular nature of the powers (the smallest in the expansion given in Theorem \ref{thm_cord} lies in the range \upd{$(-1/2,1/2)$} makes it difficult to produce universal discretizations and quadratures which work for large ranges of angles.
+Unfortunately, the singular nature of the powers (the smallest in the expansion given in Theorem \ref{thm_cord} lies in the range \upd{$(-1/2,1/2)$}) makes it difficult to produce universal discretizations and quadratures which work for large ranges of angles.
 When the above method is run on these problems, discretization nodes tend to accumulate close to the corner (within $10^{-14}$).

### 2020-07-20 paper_lap/JCP_response1/05apparatus.tex
updated files

@@
 \begin{remark}
-In this approach, note that the discretization of the Neumann problem, inherits its spectral properties from the discretization of the corresponding adjoint Dirichlet problem (eigenvalues and singular values are the same, but eigenvectors and singular vectors may differ).
+In this approach, note that the discretization of the Neumann problem inherits its spectral properties from the discretization of the corresponding adjoint Dirichlet problem (eigenvalues and singular values are the same, but eigenvectors and singular vectors may differ).
 Thus, when using an iterative method for solving the discrete linear system for the Dirichlet and Neumann problem, the number of iterations required for the relative residual to converge below $\varepsilon$ would be fairly similar.
@@
 Specifically, we subdivide the interval $[-\delta,\delta]$ into three subintervals $I_0 = [-\delta,\delta/2],$ $L_0 = [-\delta/2,\delta/2],$ and $J_0 = [\delta/2,\delta].$ On $I_0$ and $J_0$ we place standard Gauss-Legendre discretization nodes, while on $L_0$ we use the custom discretization scheme for corners, outlined in Section \ref{sec:disc_dir} (see \cite{hoskins2019numerical} for a detailed description of the method).
-On the intervals $[-2\delta,-\delta]$ and $[\delta,2\delta]$ we use the same discretization nodes and weights as in the original system for those intervals.
+On the intervals $\upd{K_0}=[-2\delta,-\delta]$ and $\upd{Q_0}=[\delta,2\delta]$ we use the same discretization nodes and weights as in the original system for those intervals.
 Let $\underline{f}_0$ denote the right-hand side of (\ref{eqn:resolve_neum0}) evaluated at these discretization nodes and scaled by the square roots of the corresponding weights.

### 2020-07-20 paper_lap/JCP_response1/manuscript.tex
updated files

@@
 denote the standard inner products on the Hilbert spaces $Y=X,\underline{X}$, and
-$S:X \to \uX$ denote the operator which samples a function on the boundary at the discretization nodes scaled by the square root of the weights, i.e. 
+$S:X \to \uX$ denotes the operator which samples a function on the boundary at the discretization nodes scaled by the square root of the weights, i.e. 
 \begin{equation}
@@
 \end{equation}
-Let $P:\underline{X} \to X$ denote the operator mapping the discretized samples to it's piecewise interpolant on the boundary.
+Let $P:\underline{X} \to X$ denote the operator mapping the discretized samples to its piecewise interpolant on the boundary.
 Let $\Gamma_{\ell} = \gamma([s_{1},s_{2}])$ denote a panel that does not contain a corner vertex and is discretized with $M$ nodes  $x_{i},x_{i+1},\ldots x_{i+M-1}$.
@@
 Let $h_{i}$, $i=1,2,\ldots M$, denote the scaled Legendre polynomials to the panel $\Gamma_{\ell}$.
-The main result of this appendix is to show that under suitable assumptions, that the computed density can be accurately interpolated on $\Gamma_{\ell}$, i.e.  
+The main result of this appendix is to show that under suitable assumptions the computed density can be accurately interpolated on $\Gamma_{\ell}$, i.e.  
 \begin{equation}
@@
 
-But first, we present a lemma about the accuracy of Gaussian quadrature
+Before doing so, we first state a lemma about the accuracy of Gaussian quadrature.
 \begin{lemma}
